---
title: "CERP Annual Report Information"
author: "ELWilliams"
date: "`r Sys.Date()`"
output: 
  html_document: default
  word_document: default
params:
  Start_date: "2023-10-01"
  End_date: "2024-09-30"
  Excel_name: "CERP_2025"

knit: (function(inputFile, encoding) {
  rmarkdown::render(
    input = inputFile, 
    encoding = encoding,
    output_file = paste0(substr(inputFile, 1, nchar(inputFile)-4), " - ", with(rmarkdown::yaml_front_matter(inputFile), paste(params$Excel_name)), '.html')
    ) 
      })
---
<style>
.main-container {
    max-width: 9000px;
    margin-left: 20px;
    margin-right: auto;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
#
Estuary_code <- c("CR", "SL", "LX")
Start_date <- as.Date(params$Start_date)
End_date <- as.Date(params$End_date)
Flow_sites <- c("SL", "LX", "CR")
sheet_lookup <- c(SL = "SLESum", LX = "LOXSum", CR = "S79")
Summary_Excel_file_name <- params$Excel_name
#
#Packages
if (!require("pacman")) {install.packages("pacman")}
#p_unlock()
pacman::p_load(odbc, DBI, dbplyr,
  tidyverse, dplyr,  stringr, #DF manipulation
  DT, openxlsx, readxl,        #Excel
  lubridate, zoo,         #Dates
  knitr, kableExtra, scales, gt, gtExtras,
  install = TRUE)
```

```{css}
p {
font-size: 12pt;
}

caption {
  color: black;
  font-weight: bold;
  font-size: 14;
  text-indent: 5%;
} 

h1 {
font-size: 21pt;
font-weight: bold;
}

h2 {
font-size: 17pt;
font-weight: bold;
}

h3 {
font-size: 13pt;
font-style: italic;
text-decoration: underline;
}

h4 {
  color: black;
  font-weight: bold;
  font-size: 17;
  text-indent: 5%;
}
```

```{r Data gather from summary file, include = FALSE}
WQ_Sal_s <-  readWorkbook("../Quarterly/Summary data/CERP_PBC_WQ_Summary_Data.xlsx", sheet = 'Salinity Station', detectDates = TRUE, check.names = TRUE) %>% dplyr::select(starts_with(Estuary_code))
WQ_Secchi_s <-  readWorkbook("../Quarterly/Summary data/CERP_PBC_WQ_Summary_Data.xlsx", sheet = 'Secchi Station', detectDates = TRUE, check.names = TRUE) %>% dplyr::select(starts_with(Estuary_code))
WQ_Temp_s <-  readWorkbook("../Quarterly/Summary data/CERP_PBC_WQ_Summary_Data.xlsx", sheet = 'Temp Station', detectDates = TRUE, check.names = TRUE) %>% dplyr::select(starts_with(Estuary_code))
WQ_pH_s <-  readWorkbook("../Quarterly/Summary data/CERP_PBC_WQ_Summary_Data.xlsx", sheet = 'pH Station', detectDates = TRUE, check.names = TRUE) %>% dplyr::select(starts_with(Estuary_code))
WQ_DO_s <-  readWorkbook("../Quarterly/Summary data/CERP_PBC_WQ_Summary_Data.xlsx", sheet = 'DO Station', detectDates = TRUE, check.names = TRUE) %>% dplyr::select(starts_with(Estuary_code))

Dermo_df <- readWorkbook("../Quarterly/Summary data/CERP_PBC_Summary_Data.xlsx", sheet = 'Dermo Station', detectDates = TRUE, check.names = TRUE) %>% dplyr::select(starts_with(Estuary_code))
Rcrt_df <- readWorkbook("../Quarterly/Summary data/CERP_PBC_Summary_Data.xlsx", sheet = 'Rcrt Station', detectDates = TRUE, check.names = TRUE) %>% dplyr::select(starts_with(Estuary_code))
Repro_df <- readWorkbook("../Quarterly/Summary data/CERP_PBC_Summary_Data.xlsx", sheet = 'Repro', detectDates = TRUE, check.names = TRUE) %>% dplyr::select(starts_with(Estuary_code))
Counts_df <- readWorkbook("../Quarterly/Summary data/CERP_PBC_Summary_Data.xlsx", sheet = 'DeadRatio Station', detectDates = TRUE, check.names = TRUE) %>% dplyr::select(Survey, AnalysisDate, starts_with(Estuary_code))
SH_df <- readWorkbook("../Quarterly/Summary data/CERP_PBC_Summary_Data.xlsx", sheet = 'SH Station', detectDates = TRUE, check.names = TRUE)  %>% dplyr::select(Survey, AnalysisDate, starts_with(Estuary_code))
Cage_df <- readWorkbook("../Quarterly/Summary data/CERP_PBC_Summary_Data.xlsx", sheet = 'SH Mort Cage', detectDates = TRUE, check.names = TRUE)  %>% dplyr::select(AnalysisDate, starts_with(Estuary_code))
#
#Data selection and cleaning follows below by type of data being assessed.
```

```{r Salinity data, include = FALSE}
#
## Summary R Markdown file:
##Data cleaning
WQ_Sal <- WQ_Sal_s %>% 
  subset(SL.C_RetDate_Sal > Start_date & SL.C_RetDate_Sal < End_date) %>% 
  rename(RetDate = SL.C_RetDate_Sal) %>% 
  dplyr::select(RetDate, everything(), -contains("_RetDate_Sal")) %>% 
  mutate(RetDate = as.yearmon(RetDate))
#
#Data by station
WQ_Sal_tab <- WQ_Sal %>% 
  gather(Site_Station, Salinity, -RetDate) %>% 
  mutate(Site_Station = gsub(("_Sal|\\."), "", Site_Station)) %>% 
  mutate(Site = substr(Site_Station, 1, 3), 
         Station = substr(Site_Station, 4, 5)) %>%
  dplyr::select(-Site_Station)
#
#Data table outout - for RMarkdown file
WQ_Sal_out <- WQ_Sal_tab %>% 
  mutate(Site = case_when(Site == "CRE" | Site == "CRW" ~ "CR", TRUE ~ Site))  %>% 
  spread(Station, Salinity) %>% 
  gt(groupname_col = "Site") %>% 
  data_color(columns = contains(c("1","2","3","4")), 
             fn = scales::col_numeric(palette = "plasma", 
                                      domain = WQ_Sal %>% 
                                        dplyr::select(contains("Sal")) %>% 
                                        unlist() %>% 
                                        range(na.rm = T))) %>% 
  cols_align(align = c("center"), columns = everything())
#
#
## Excel summary data
WQ_Sal_Excel <- WQ_Sal_s %>% 
  subset(SL.C_RetDate_Sal > Start_date & SL.C_RetDate_Sal < End_date) %>% 
  dplyr::select(starts_with("LX"), starts_with("SL"), everything())
#
WQ_Sal_Excel_summ <- WQ_Sal_tab %>%
  filter(Salinity > 0) %>% 
  group_by(Site) %>%
  summarise(Min = round(min(Salinity, na.rm = T),2),
            Max = round(max(Salinity, na.rm = T),2),
            Mean = round(mean(Salinity, na.rm = T),2)) %>%
  gather(-Site, key = "Summ", value= "Value") %>%
  spread(key = "Site", value= "Value") %>%
  mutate(Summ = factor(Summ, levels = c("Min", "Max", "Mean"))) %>%
  arrange(Summ)
#
WQ_Sal_Excel_Sitesumm <- WQ_Sal_tab %>%
  filter(Salinity > 0) %>% 
  mutate(Site = substr(Site, 1, 2)) %>%
  group_by(Site) %>%
  summarise(Min = round(min(Salinity, na.rm = T),2),
            Max = round(max(Salinity, na.rm = T),2),
            Mean = round(mean(Salinity, na.rm = T),2)) %>%
  gather(-Site, key = "Summ", value= "Value") %>%
  spread(key = "Site", value= "Value") %>%
  mutate(Summ = factor(Summ, levels = c("Min", "Max", "Mean"))) %>%
  arrange(Summ)
#
#
```

```{r Secchi data, include = FALSE}
#
## Summary R Markdown file:
##Data cleaning
#Secchi
WQ_Sec <- WQ_Secchi_s %>% 
  subset(SL.C_RetDate_SP > Start_date & SL.C_RetDate_SP < End_date) %>% 
  rename(RetDate = SL.C_RetDate_SP) %>% 
  mutate(RetDate = as.yearmon(RetDate)) %>% 
  dplyr::select(RetDate, everything(), -contains("_RetDate_SP"))
#
#Data by station
WQ_Sec_tab <- WQ_Sec %>% 
  gather(Site_Station, Secchi, -RetDate) %>% 
  mutate(Site_Station = gsub(("_SP|\\."), "", Site_Station)) %>% 
  mutate(Site = substr(Site_Station, 1, 3), 
         Station = substr(Site_Station, 4, 4)) %>%
  dplyr::select(-Site_Station)
#
#Data table output - for RMarkdown file
WQ_Sec_out <- WQ_Sec_tab %>% 
  mutate(Site = case_when(Site == "CRE" | Site == "CRW" ~ "CR", TRUE ~ Site))  %>% 
  spread(Station, Secchi) %>% 
  gt(groupname_col = "Site") %>% 
  data_color(columns = contains(c("1","2","3","4")), 
             fn = scales::col_numeric(palette = "plasma", 
                                      domain = WQ_Sec %>% 
                                        dplyr::select(contains("SP")) %>% 
                                        unlist() %>% 
                                        range(na.rm = T))) %>% 
  cols_align(align = c("center"), columns = everything())
#
#
## Excel summary data
WQ_Sec_Excel <- WQ_Secchi_s %>% 
  subset(SL.C_RetDate_SP > Start_date & SL.C_RetDate_SP < End_date) %>% 
  dplyr::select(starts_with("LX"), starts_with("SL"), everything())
#
WQ_Sec_Excel_summ <- WQ_Sec_tab %>%
  filter(Secchi > 0) %>% 
  group_by(Site) %>%
  summarise(Min = round(min(Secchi, na.rm = T),2),
            Max = round(max(Secchi, na.rm = T),2),
            Mean = round(mean(Secchi, na.rm = T),2)) %>%
  gather(-Site, key = "Summ", value= "Value") %>%
  spread(key = "Site", value= "Value") %>%
  mutate(Summ = factor(Summ, levels = c("Min", "Max", "Mean"))) %>%
  arrange(Summ)
#
WQ_Sec_Excel_Sitesumm <- WQ_Sec_tab %>%
  filter(Secchi > 0) %>% 
  mutate(Site = substr(Site, 1, 2)) %>%
  group_by(Site) %>%
  summarise(Min = round(min(Secchi, na.rm = T),2),
            Max = round(max(Secchi, na.rm = T),2),
            Mean = round(mean(Secchi, na.rm = T),2)) %>%
  gather(-Site, key = "Summ", value= "Value") %>%
  spread(key = "Site", value= "Value") %>%
  mutate(Summ = factor(Summ, levels = c("Min", "Max", "Mean"))) %>%
  arrange(Summ)
#
#
```

```{r Temperature data, include = FALSE}
#
## Summary R Markdown file:
##Data cleaning
#Temp
WQ_Tem <- WQ_Temp_s %>% 
  subset(SL.C_RetDate_Temp > Start_date & SL.C_RetDate_Temp < End_date) %>% 
  rename(RetDate = SL.C_RetDate_Temp) %>% 
  mutate(RetDate = as.yearmon(RetDate)) %>% 
  dplyr::select(RetDate, everything(), -contains("_RetDate_Temp"))
#
#Data by station
WQ_Tem_tab <- WQ_Tem %>% 
  gather(Site_Station, Temp, -RetDate) %>% 
  mutate(Site_Station = gsub(("_Temp|\\."), "", Site_Station)) %>% 
  mutate(Site = substr(Site_Station, 1, 3), 
         Station = substr(Site_Station, 4, 4)) %>%
  dplyr::select(-Site_Station)
#
#Data table output - for RMarkdown file
WQ_Tem_out <- WQ_Tem_tab %>% 
  mutate(Site = case_when(Site == "CRE" | Site == "CRW" ~ "CR", TRUE ~ Site))  %>% 
  spread(Station, Temp) %>% 
  gt(groupname_col = "Site") %>% 
  data_color(columns = contains(c("1","2","3","4")), 
             fn = scales::col_numeric(palette = "plasma", 
                                      domain = WQ_Tem %>% 
                                        dplyr::select(contains("Temp")) %>% 
                                        unlist() %>% 
                                        range(na.rm = T))) %>% 
  cols_align(align = c("center"), columns = everything())
#
#
## Excel summary data
WQ_Tem_Excel <- WQ_Temp_s %>% 
  subset(SL.C_RetDate_Temp > Start_date & SL.C_RetDate_Temp < End_date) %>% 
  dplyr::select(starts_with("LX"), starts_with("SL"), everything())
#
WQ_Tem_Excel_summ <- WQ_Tem_tab %>%
  filter(Temp > 0) %>% 
  group_by(Site) %>%
  summarise(Min = round(min(Temp, na.rm = T),2),
            Max = round(max(Temp, na.rm = T),2),
            Mean = round(mean(Temp, na.rm = T),2)) %>%
  gather(-Site, key = "Summ", value= "Value") %>%
  spread(key = "Site", value= "Value") %>%
  mutate(Summ = factor(Summ, levels = c("Min", "Max", "Mean"))) %>%
  arrange(Summ)
#
WQ_Tem_Excel_Sitesumm <- WQ_Tem_tab %>%
  filter(Temp > 0) %>% 
  mutate(Site = substr(Site, 1, 2)) %>%
  group_by(Site) %>%
  summarise(Min = round(min(Temp, na.rm = T),2),
            Max = round(max(Temp, na.rm = T),2),
            Mean = round(mean(Temp, na.rm = T),2)) %>%
  gather(-Site, key = "Summ", value= "Value") %>%
  spread(key = "Site", value= "Value") %>%
  mutate(Summ = factor(Summ, levels = c("Min", "Max", "Mean"))) %>%
  arrange(Summ)
#
#
```

```{r pH data, include = FALSE}
#
## Summary R Markdown file:
##Data cleaning
#pH
WQ_pH <- WQ_pH_s %>% 
  subset(SL.C_RetDate_pH > Start_date & SL.C_RetDate_pH < End_date) %>% 
  rename(RetDate = SL.C_RetDate_pH) %>% 
  mutate(RetDate = as.yearmon(RetDate)) %>% 
  dplyr::select(RetDate, everything(), -contains("_RetDate_pH"))
#
#Data by station
WQ_pH_tab <- WQ_pH %>% 
  gather(Site_Station, pH, -RetDate) %>% 
  mutate(Site_Station = gsub(("_pH|\\."), "", Site_Station)) %>% 
  mutate(Site = substr(Site_Station, 1, 3), 
         Station = substr(Site_Station, 4, 4)) %>%
  dplyr::select(-Site_Station)
#
#Data table output - for RMarkdown file
WQ_pH_out <- WQ_pH_tab %>% 
  mutate(Site = case_when(Site == "CRE" | Site == "CRW" ~ "CR", TRUE ~ Site))  %>% 
  spread(Station, pH) %>% 
  gt(groupname_col = "Site") %>% 
  data_color(columns = contains(c("1","2","3","4")), 
             fn = scales::col_numeric(palette = "plasma", 
                                      domain = WQ_pH %>% 
                                        dplyr::select(contains("pH")) %>% 
                                        unlist() %>% 
                                        range(na.rm = T))) %>% 
  cols_align(align = c("center"), columns = everything())
#
#
## Excel summary data
WQ_pH_Excel <- WQ_pH_s %>% 
  subset(SL.C_RetDate_pH > Start_date & SL.C_RetDate_pH < End_date) %>% 
  dplyr::select(starts_with("LX"), starts_with("SL"), everything())
#
WQ_pH_Excel_summ <- WQ_pH_tab %>%
  filter(pH > 0) %>% 
  group_by(Site) %>%
  summarise(Min = round(min(pH, na.rm = T),2),
            Max = round(max(pH, na.rm = T),2),
            Mean = round(mean(pH, na.rm = T),2)) %>%
  gather(-Site, key = "Summ", value= "Value") %>%
  spread(key = "Site", value= "Value") %>%
  mutate(Summ = factor(Summ, levels = c("Min", "Max", "Mean"))) %>%
  arrange(Summ)
#
WQ_pH_Excel_Sitesumm <- WQ_pH_tab %>%
  filter(pH > 0) %>% 
  mutate(Site = substr(Site, 1, 2)) %>%
  group_by(Site) %>%
  summarise(Min = round(min(pH, na.rm = T),2),
            Max = round(max(pH, na.rm = T),2),
            Mean = round(mean(pH, na.rm = T),2)) %>%
  gather(-Site, key = "Summ", value= "Value") %>%
  spread(key = "Site", value= "Value") %>%
  mutate(Summ = factor(Summ, levels = c("Min", "Max", "Mean"))) %>%
  arrange(Summ)
#
#
```

```{r DO data, include = FALSE}
#
## Summary R Markdown file:
##Data cleaning
#pH
WQ_DO <- WQ_DO_s %>% 
  subset(SL.C_RetDate_DO > Start_date & SL.C_RetDate_DO < End_date) %>% 
  rename(RetDate = SL.C_RetDate_DO) %>% 
  mutate(RetDate = as.yearmon(RetDate)) %>% 
  dplyr::select(RetDate, everything(), -contains("_RetDate_DO"))
#
#Data by station
WQ_DO_tab <- WQ_DO %>% 
  gather(Site_Station, DO, -RetDate) %>% 
  mutate(Site_Station = gsub(("_DOl|\\."), "", Site_Station)) %>% 
  mutate(Site = substr(Site_Station, 1, 3), 
         Station = substr(Site_Station, 4, 4)) %>%
  dplyr::select(-Site_Station)
#
#Data table output - for RMarkdown file
WQ_DO_out <- WQ_DO_tab %>% 
  mutate(Site = case_when(Site == "CRE" | Site == "CRW" ~ "CR", TRUE ~ Site))  %>% 
  spread(Station, DO) %>% 
  gt(groupname_col = "Site") %>% 
  data_color(columns = contains(c("1","2","3","4")), 
             fn = scales::col_numeric(palette = "plasma", 
                                      domain = WQ_DO %>% 
                                        dplyr::select(contains("DO")) %>% 
                                        unlist() %>% 
                                        range(na.rm = T))) %>% 
  cols_align(align = c("center"), columns = everything())
#
#
## Excel summary data
WQ_DO_Excel <- WQ_DO_s %>% 
  subset(SL.C_RetDate_DO > Start_date & SL.C_RetDate_DO < End_date) %>% 
  dplyr::select(starts_with("LX"), starts_with("SL"), everything())
#
WQ_DO_Excel_summ <- WQ_DO_tab %>%
  filter(DO > 0) %>% 
  group_by(Site) %>%
  summarise(Min = round(min(DO, na.rm = T),2),
            Max = round(max(DO, na.rm = T),2),
            Mean = round(mean(DO, na.rm = T),2)) %>%
  gather(-Site, key = "Summ", value= "Value") %>%
  spread(key = "Site", value= "Value") %>%
  mutate(Summ = factor(Summ, levels = c("Min", "Max", "Mean"))) %>%
  arrange(Summ)
#
WQ_DO_Excel_Sitesumm <- WQ_DO_tab %>%
  filter(DO > 0) %>% 
  mutate(Site = substr(Site, 1, 2)) %>%
  group_by(Site) %>%
  summarise(Min = round(min(DO, na.rm = T),2),
            Max = round(max(DO, na.rm = T),2),
            Mean = round(mean(DO, na.rm = T),2)) %>%
  gather(-Site, key = "Summ", value= "Value") %>%
  spread(key = "Site", value= "Value") %>%
  mutate(Summ = factor(Summ, levels = c("Min", "Max", "Mean"))) %>%
  arrange(Summ)
#
#
```

```{r Survey data, include = FALSE}
#
## Summary R Markdown file:
##Data cleaning
##Survey counts
Counts <- Counts_df %>% 
  mutate(AnalysisDate = as.yearmon(AnalysisDate)) %>% 
  subset(AnalysisDate > as.yearmon(Start_date %m-% months(2)) & AnalysisDate < as.yearmon(End_date %m+% months(1))) %>% 
  replace(is.na(.), -999) %>%
  mutate(across(-Survey,
      ~ if_else(
        str_detect(Survey, "Spring|Fall"),
        .x,
        replace_na(.x, -999)))
  ) %>%
  mutate(
    across(
      c(CR.E1_LiveMean, CR.E1_LiveSD, CR.W4_LiveMean, CR.W4_LiveSD, 
        CR.E1_DeadRatioMean, CR.E1_DeadRatioSD, CR.W4_DeadRatioMean, CR.W4_DeadRatioSD),
      ~ if_else(
        str_detect(Survey, "Summer|Winter"),
        NA,
        .x
      )
    )
  ) %>%
  dplyr::select(Survey, AnalysisDate, starts_with("LX"), starts_with("SL"), everything())
#
LiveOy <- Counts %>% dplyr::select(Survey, AnalysisDate, contains("LiveMean"))
DeadOy <- Counts %>% dplyr::select(Survey, AnalysisDate, contains("DeadRatioMean"))
#
##Survey SHs
SH <- SH_df %>% 
  #Remove CR 1,4 Summer Winter
  mutate(AnalysisDate = as.yearmon(AnalysisDate)) %>% 
  subset(AnalysisDate > as.yearmon(Start_date %m-% months(2)) & AnalysisDate < as.yearmon(End_date %m+% months(1))) %>% 
  #replace(is.na(.), -999) %>%
   mutate(across(-Survey,
      ~ if_else(
        str_detect(Survey, "Spring|Fall"),
        .x,
        replace_na(.x, -999)))
  ) %>%
  mutate(
    across(
      c(CR.E1_SHMean, CR.E1_SHSD, CR.W4_SHMean, CR.W4_SHSD),
      ~ if_else(
        str_detect(Survey, "Summer|Winter"),
        NA,
        .x
      )
    )
  ) %>%
  dplyr::select(Survey, AnalysisDate, starts_with("LX"), starts_with("SL"), everything()) %>%
  dplyr::select(Survey, AnalysisDate, contains("Mean"))
#
#
#
#Data by station
Live_tab <- LiveOy %>% 
  gather(Site_Station, Count, -AnalysisDate, -Survey) %>% 
  mutate(Site_Station = gsub(("_LiveMean|\\."), "", Site_Station)) %>% 
  mutate(Site = substr(Site_Station, 1, 3), 
         Station = substr(Site_Station, 4, 5)) %>%
  dplyr::select(-Site_Station)
#
Dead_tab <- DeadOy %>% 
  gather(Site_Station, Count, -AnalysisDate, -Survey) %>% 
  mutate(Site_Station = gsub(("_DeadRatioMean|\\."), "", Site_Station)) %>% 
  mutate(Site = substr(Site_Station, 1, 3), 
         Station = substr(Site_Station, 4, 5)) %>%
  dplyr::select(-Site_Station)
#
SH_tab <- SH %>% 
  gather(Site_Station, SHs, -AnalysisDate, -Survey) %>% 
  mutate(Site_Station = gsub(("_SHMean|\\."), "", Site_Station)) %>% 
  mutate(Site = substr(Site_Station, 1, 3), 
         Station = substr(Site_Station, 4, 5)) %>%
  dplyr::select(-Site_Station)
#
#
#
#Data table output - for RMarkdown file
Live_out <- Live_tab %>% 
  mutate(Site = case_when(Site == "CRE" | Site == "CRW" ~ "CR", TRUE ~ Site))  %>% 
  spread(Station, Count) %>% 
  arrange(AnalysisDate) %>%
  gt(groupname_col = "Site") %>% 
  data_color(columns = contains(c("1","2","3","4")), 
             fn = scales::col_numeric(palette = "plasma", 
                                      domain = Live_tab %>% 
                                        filter(Survey != min(Survey)) %>%
                                        dplyr::select(contains("Count")) %>% 
                                        filter(Count > 0) %>%
                                        unlist() %>% 
                                        range(na.rm = T))) %>% 
  cols_align(align = c("center"), columns = everything())
#
Dead_out <- Dead_tab %>% 
  mutate(Site = case_when(Site == "CRE" | Site == "CRW" ~ "CR", TRUE ~ Site))  %>% 
  spread(Station, Count) %>% 
  arrange(AnalysisDate) %>%
  gt(groupname_col = "Site") %>% 
  data_color(columns = contains(c("1","2","3","4")), 
             fn = scales::col_numeric(palette = "plasma", 
                                      domain = Dead_tab %>% 
                                        filter(Survey != min(Survey)) %>%
                                        dplyr::select(contains("Count")) %>% 
                                        filter(Count > 0) %>%
                                        unlist() %>% 
                                        range(na.rm = T))) %>% 
  cols_align(align = c("center"), columns = everything())
#
SH_out <- SH_tab %>% 
  mutate(Site = case_when(Site == "CRE" | Site == "CRW" ~ "CR", TRUE ~ Site))  %>% 
  spread(Station, SHs) %>% 
  arrange(Site, AnalysisDate) %>%
  gt(groupname_col = "Site") %>% 
  data_color(columns = contains(c("1","2","3","4")), 
             fn = scales::col_numeric(palette = "plasma", 
                                      domain = SH_tab %>% 
                                        filter(Survey != min(Survey)) %>%
                                        dplyr::select(contains("SHs")) %>% 
                                        filter(SHs > 0) %>%
                                        unlist() %>% 
                                        range(na.rm = T))) %>% 
  cols_align(align = c("center"), columns = everything()) 
#
#
## Excel summary data
Live_Excel <- LiveOy %>% 
  subset(AnalysisDate >= as.yearmon(Start_date) & AnalysisDate <= as.yearmon(End_date)) %>% 
  dplyr::select(Survey, AnalysisDate, starts_with("LX"), starts_with("SL"), everything())
#
Live_Excel_Sitesumm <- Live_tab %>%
  filter(Count > -1, Survey != min(Survey)) %>% 
  group_by(Site) %>%
  summarise(Min = round(min(Count, na.rm = T),2),
            Max = round(max(Count, na.rm = T),2),
            Mean = round(mean(Count, na.rm = T),2)) %>%
  gather(-Site, key = "Summ", value= "Value") %>%
  spread(key = "Site", value= "Value") %>%
  mutate(Summ = factor(Summ, levels = c("Min", "Max", "Mean"))) %>%
  arrange(Summ) %>%
  dplyr::select(Summ, starts_with("LX"), starts_with("SL"), everything())
#
Live_Excel_SeasonSitesumm <- Live_tab %>%
  filter(Count > -1, Survey != min(Survey)) %>%
  mutate(Season = gsub(" .*", "", Survey)) %>%
  group_by(Season, Site) %>%
  summarise(Mean = round(mean(Count, na.rm = T),2)) %>%
  spread(key = "Site", value = "Mean") %>%
  filter(Season %in% c("Spring", "Fall")) %>%
  dplyr::select(Season, starts_with("LX"), starts_with("SL"), everything())
#
#
Dead_Excel <- DeadOy %>% 
  subset(AnalysisDate >= as.yearmon(Start_date) & AnalysisDate <= as.yearmon(End_date)) %>% 
  dplyr::select(Survey, AnalysisDate, starts_with("LX"), starts_with("SL"), everything())
#
Dead_Excel_Sitesumm <- Dead_tab %>%
  filter(Count > -1, Survey != min(Survey)) %>% 
  group_by(Site) %>%
  summarise(Min = round(min(Count, na.rm = T),2),
            Max = round(max(Count, na.rm = T),2),
            Mean = round(mean(Count, na.rm = T),2)) %>%
  gather(-Site, key = "Summ", value= "Value") %>%
  spread(key = "Site", value= "Value") %>%
  mutate(Summ = factor(Summ, levels = c("Min", "Max", "Mean"))) %>%
  arrange(Summ) %>%
  dplyr::select(Summ, starts_with("LX"), starts_with("SL"), everything())
#
Dead_Excel_SeasonSitesumm <- Dead_tab %>%
  filter(Count > -1, Survey != min(Survey)) %>%
  mutate(Season = gsub(" .*", "", Survey)) %>%
  group_by(Season, Site) %>%
  summarise(Mean = round(mean(Count, na.rm = T),2)) %>%
  spread(key = "Site", value = "Mean") %>%
  filter(Season %in% c("Spring", "Fall")) %>%
  dplyr::select(Season, starts_with("LX"), starts_with("SL"), everything())
#
#
SH_Excel <- SH %>% 
  subset(AnalysisDate >= as.yearmon(Start_date) & AnalysisDate <= as.yearmon(End_date)) %>% 
  dplyr::select(Survey, AnalysisDate, starts_with("LX"), starts_with("SL"), everything())
#
SH_Excel_Sitesumm <- SH_tab %>%
  filter(SHs > -1, Survey != min(Survey)) %>% 
  group_by(Site) %>%
  summarise(Min = round(min(SHs, na.rm = T),2),
            Max = round(max(SHs, na.rm = T),2),
            Mean = round(mean(SHs, na.rm = T),2)) %>%
  gather(-Site, key = "Summ", value= "Value") %>%
  spread(key = "Site", value= "Value") %>%
  mutate(Summ = factor(Summ, levels = c("Min", "Max", "Mean"))) %>%
  arrange(Summ) %>%
  dplyr::select(Summ, starts_with("LX"), starts_with("SL"), everything())
#
SH_Excel_SeasonSitesumm <- SH_tab %>%
  filter(SHs > -1, Survey != min(Survey)) %>%
  mutate(Season = gsub(" .*", "", Survey)) %>%
  group_by(Season, Site) %>%
  summarise(Mean = round(mean(SHs, na.rm = T),2)) %>%
  spread(key = "Site", value = "Mean") %>%
  filter(Season %in% c("Spring", "Fall")) %>%
  dplyr::select(Season, starts_with("LX"), starts_with("SL"), everything())
#
#
```

```{r Dermo data, include = FALSE}
#
## Summary R Markdown file:
##Data cleaning
Dermo_t <- Dermo_df %>% 
  subset(SL.C_RetDate > Start_date & SL.C_RetDate < End_date) %>% 
  rename(RetDate = SL.C_RetDate) %>% 
  dplyr::select(RetDate, everything(), -contains("_RetDate")) %>% 
  mutate(RetDate = as.yearmon(RetDate))
#
DermoI <- Dermo_t %>% 
  dplyr::select(-contains(c("SD", "Pct")))
DermoP <- Dermo_t %>% 
  dplyr::select(-contains(c("SD", "Mean")))
#Data by station
DermoI_tab <- DermoI %>% 
  gather(Site_Station, Intensity, -RetDate) %>% 
  mutate(Site_Station = gsub(("_Sal|\\."), "", Site_Station)) %>% 
  mutate(Site = substr(Site_Station, 1, 3), 
         Station = substr(Site_Station, 4, 4)) %>%
  dplyr::select(-Site_Station)
DermoP_tab <- DermoP %>% 
  gather(Site_Station, Prevalence, -RetDate) %>% 
  mutate(Site_Station = gsub(("_Sal|\\."), "", Site_Station)) %>% 
  mutate(Site = substr(Site_Station, 1, 3), 
         Station = substr(Site_Station, 4, 4)) %>%
  dplyr::select(-Site_Station)
#
#Data table output - for RMarkdown file
DermoI_out <- DermoI_tab %>% 
  mutate(Site = case_when(Site == "CRE" | Site == "CRW" ~ "CR", TRUE ~ Site))  %>% 
  spread(Station, Intensity) %>% 
  gt(groupname_col = "Site") %>% 
  data_color(columns = contains(c("1","2","3","4")), 
             fn = scales::col_numeric(palette = "plasma", 
                                      domain = DermoI %>% 
                                        dplyr::select(contains("Mean")) %>% 
                                        unlist() %>% 
                                        range(na.rm = T))) %>% 
  cols_align(align = c("center"), columns = everything())
#
DermoP_out <- DermoP_tab %>% 
  mutate(Site = case_when(Site == "CRE" | Site == "CRW" ~ "CR", TRUE ~ Site))  %>% 
  spread(Station, Prevalence) %>% 
  gt(groupname_col = "Site") %>% 
  data_color(columns = contains(c("1","2","3","4")), 
             fn = scales::col_numeric(palette = "plasma", 
                                      domain = DermoP %>% 
                                        dplyr::select(contains("Pct")) %>% 
                                        unlist() %>% 
                                        range(na.rm = T))) %>% 
  cols_align(align = c("center"), columns = everything())
#
#
## Excel summary data
DermoI_Excel <- DermoI %>% 
  dplyr::select(RetDate, starts_with("LX"), starts_with("SL"), everything())
DermoP_Excel <- DermoP %>% 
  dplyr::select(RetDate, starts_with("LX"), starts_with("SL"), everything())
#
DermoI_Excel_summ <- DermoI_tab %>%
  group_by(Site) %>%
  summarise(Min = round(min(Intensity, na.rm = T),2),
            Max = round(max(Intensity, na.rm = T),2),
            Mean = round(mean(Intensity, na.rm = T),2)) %>%
  gather(-Site, key = "Summ", value= "Value") %>%
  spread(key = "Site", value= "Value") %>%
  mutate(Summ = factor(Summ, levels = c("Min", "Max", "Mean"))) %>%
  arrange(Summ)

DermoP_Excel_summ <- DermoP_tab %>%
  group_by(Site) %>%
  summarise(Min = round(min(Prevalence, na.rm = T),2),
            Max = round(max(Prevalence, na.rm = T),2),
            Mean = round(mean(Prevalence, na.rm = T),2)) %>%
  gather(-Site, key = "Summ", value= "Value") %>%
  spread(key = "Site", value= "Value") %>%
  mutate(Summ = factor(Summ, levels = c("Min", "Max", "Mean"))) %>%
  arrange(Summ)
#
DermoI_Excel_Sitesumm <- DermoI_tab %>%
  mutate(Site = substr(Site, 1, 2)) %>%
  group_by(Site) %>%
  summarise(Min = round(min(Intensity, na.rm = T),2),
            Max = round(max(Intensity, na.rm = T),2),
            Mean = round(mean(Intensity, na.rm = T),2)) %>%
  gather(-Site, key = "Summ", value= "Value") %>%
  spread(key = "Site", value= "Value") %>%
  mutate(Summ = factor(Summ, levels = c("Min", "Max", "Mean"))) %>%
  arrange(Summ)
DermoP_Excel_Sitesumm <- DermoP_tab %>%
  mutate(Site = substr(Site, 1, 2)) %>%
  group_by(Site) %>%
  summarise(Min = round(min(Prevalence, na.rm = T),2),
            Max = round(max(Prevalence, na.rm = T),2),
            Mean = round(mean(Prevalence, na.rm = T),2)) %>%
  gather(-Site, key = "Summ", value= "Value") %>%
  spread(key = "Site", value= "Value") %>%
  mutate(Summ = factor(Summ, levels = c("Min", "Max", "Mean"))) %>%
  arrange(Summ)
#
#
```

```{r Repro data, include = FALSE}
#
## Summary R Markdown file:
##Data cleaning
Repro_t <- Repro_df %>% 
  subset(SL.C_RetDate > Start_date & SL.C_RetDate < End_date) %>% 
  rename(RetDate = SL.C_RetDate) %>% 
  dplyr::select(RetDate, everything(), -contains("_RetDate")) %>% 
  mutate(RetDate = as.yearmon(RetDate))
#
#Data by station
Repro_tab <- Repro_t %>% 
  gather(Site_Station, Pct, -RetDate) %>%
  mutate(Site_Station = gsub(("_Sal|\\."), "", Site_Station)) %>% 
  mutate(Site = substr(Site_Station, 1, 3), 
         Stage = substr(Site_Station, 5, 8)) %>% 
  dplyr::select(-Site_Station)
#
#Data table output - for RMarkdown file
Repro_out <- Repro_tab %>% 
  spread(Stage, Pct) %>% 
  gt(rowname_col = "RetDate", groupname_col = "Site") %>% 
  cols_move(Dev, Ind) %>% 
  data_color(direction = "row", method = "numeric", palette = c("plasma"), alpha = 0.8) %>% 
  cols_align(align = c("center"), columns = everything())
#
#
## Excel summary data
Repro_Excel <- Repro_t %>% 
  dplyr::select(
    map(
      unique(str_extract(names(.), "^[^_]+")),
      function(grp) {
        grp_cols <- names(.)[str_detect(names(.), paste0("^", grp))]
        
        c(
          grp_cols[str_detect(grp_cols, regex("Ind", ignore_case = TRUE))],
          grp_cols[str_detect(grp_cols, regex("Dev", ignore_case = TRUE))],
          grp_cols[!str_detect(grp_cols, regex("Ind|Dev", ignore_case = TRUE))]
        )
      }
    ) %>% flatten_chr()
  ) %>%
  dplyr::select(RetDate, starts_with("LX"), starts_with("SL"), everything())
#
#
#
#
```

```{r Recruitment data, include = FALSE}
#
## Summary R Markdown file:
##Data cleaning
Rcrt_t <- Rcrt_df %>% 
  subset(SL.C_RetDate > Start_date & SL.C_RetDate < End_date) %>% 
  rename(RetDate = SL.C_RetDate) %>% 
  dplyr::select(RetDate, everything(), -contains("_RetDate")) %>% 
  mutate(RetDate = as.yearmon(RetDate))
#
#Data by station
Rcrt_tab <- Rcrt_t %>% 
  dplyr::select(-contains("SD")) %>%
  gather(Site_Station, Mean, -RetDate) %>% 
  mutate(Site_Station = gsub(("_Mean|\\."), "", Site_Station)) %>% 
  mutate(Site = substr(Site_Station, 1, 3), 
         Station = substr(Site_Station, 4, 5)) %>%
  dplyr::select(-Site_Station)
#
#Data table output - for RMarkdown file
Rcrt_out <- Rcrt_tab %>% 
  mutate(Site = case_when(Site == "CRE" | Site == "CRW" ~ "CR", TRUE ~ Site))  %>% 
  spread(Station, Mean) %>% 
  gt(groupname_col = "Site") %>% 
  data_color(columns = contains(c("1","2","3","4")), 
             fn = scales::col_numeric(palette = "plasma", 
                                      domain = Rcrt_tab %>% 
                                        dplyr::select(contains("Mean")) %>% 
                                        filter(Mean > 0) %>%
                                        unlist() %>% 
                                        range(na.rm = T)),
             na_color = "gray80") %>% 
  cols_align(align = c("center"), columns = everything())
#
#
## Excel summary data
Rcrt_Excel <- Rcrt_df %>% 
    subset(SL.C_RetDate > Start_date & SL.C_RetDate < End_date) %>%
  dplyr::select(starts_with("LX"), starts_with("SL"), everything())
#
Rcrt_Excel_summ <- Rcrt_tab %>%
  group_by(Site) %>%
  summarise(Min = round(min(Mean, na.rm = T),2),
            Max = round(max(Mean, na.rm = T),2),
            Mean = round(mean(Mean, na.rm = T),2)) %>%
  gather(-Site, key = "Summ", value= "Value") %>%
  spread(key = "Site", value= "Value") %>%
  mutate(Summ = factor(Summ, levels = c("Min", "Max", "Mean"))) %>%
  arrange(Summ)
#
Rcrt_Excel_Sitesumm <- Rcrt_tab %>%
  mutate(Site = substr(Site, 1, 2)) %>%
  group_by(Site) %>%
  summarise(Min = round(min(Mean, na.rm = T),2),
            Max = round(max(Mean, na.rm = T),2),
            Mean = round(mean(Mean, na.rm = T),2)) %>%
  gather(-Site, key = "Summ", value= "Value") %>%
  spread(key = "Site", value= "Value") %>%
  mutate(Summ = factor(Summ, levels = c("Min", "Max", "Mean"))) %>%
  arrange(Summ)
#
#
```

```{r Cage data, include = FALSE}
#
## Summary R Markdown file:
##Data cleaning
## Cage counts
Cage_t <- Cage_df %>%
  mutate(AnalysisDate = as.yearmon(AnalysisDate)) %>% 
  subset(AnalysisDate > as.yearmon(Start_date %m-% months(2)) & AnalysisDate < as.yearmon(End_date %m+% months(1))) %>%
  dplyr::select(AnalysisDate, starts_with("LX"), starts_with("SL"), everything())
#
CageSH <- Cage_t %>% dplyr::select(AnalysisDate, contains("SHMean"))
CageCounts <- Cage_t %>% dplyr::select(AnalysisDate, contains("PctMean"))
#
#
#Data by station
CageSH_tab <- CageSH %>% 
  gather(Site_Station, SH, -AnalysisDate) %>% 
  mutate(Site_Station = gsub(("_SHMean|\\."), "", Site_Station)) %>% 
  mutate(Site = substr(Site_Station, 1, 3), 
         Type = substr(Site_Station, 6, 8)) %>%
  dplyr::select(-Site_Station) %>%
  group_by(AnalysisDate, Site, Type) %>%
  summarise(MeanSH = mean(SH, na.rm = T))
#
CageCounts_tab <- CageCounts %>% 
  gather(Site_Station, DeadPct, -AnalysisDate) %>% 
  mutate(Site_Station = gsub(("_PctMean|\\."), "", Site_Station)) %>% 
  mutate(Site = substr(Site_Station, 1, 3)) %>%
  dplyr::select(-Site_Station) %>%
  group_by(AnalysisDate, Site) %>%
  summarise(MeanPct = mean(DeadPct, na.rm = T))
#
#
#
#Data table output - for RMarkdown file
CageSHs_out <- CageSH_tab %>% 
  spread(Type, MeanSH) %>% 
  mutate(Dep = round(Dep, 2),
         Ret = round(Ret, 2),
         Growth = round(Ret - Dep, 2)) %>%
  gt(groupname_col = "Site") %>% 
  cols_align(align = c("center"), columns = everything())
#
CageCounts_out <- CageCounts_tab %>% 
  mutate(MeanPct = round(MeanPct, 2)) %>%
  spread(Site, MeanPct) %>% 
  gt(groupname_col = "Site") %>% 
  cols_align(align = c("center"), columns = everything())
#
#
#
## Excel summary data
Cage_Excel <- left_join(CageSH_tab %>% spread(Type, MeanSH) %>% 
                          mutate(Dep = round(Dep, 2),
                                 Ret = round(Ret, 2),
                                 Growth = round(Ret - Dep, 2)), 
                        CageCounts_tab)
#
Cage_Excel_SiteSumm <- Cage_Excel %>%
  group_by(Site) %>%
  summarise(
    across(c(Dep, Ret, Growth, MeanPct),
           list(
             Min  = ~ round(min(.x, na.rm = TRUE), 2),
             Max  = ~ round(max(.x, na.rm = TRUE), 2),
             Mean = ~ round(mean(.x, na.rm = TRUE), 2)),
           .names = "{.col}_{.fn}"),
    .groups = "drop") %>%
  pivot_longer(
    cols = -Site,
    names_to = c("Type", "Summ"),
    names_sep = "_",
    values_to = "Value"
  ) %>%
  mutate(Summ = factor(Summ, levels = c("Min", "Max", "Mean"))) %>%
  pivot_wider(
    names_from = Type,
    values_from = Value
  ) %>%
  arrange(Site, Summ)
#
#
#
Cage_AveGrowth <- Cage_Excel %>%
  group_by(Site) %>%
  summarise(MeanGrowth = mean(Growth, na.rm = T)) %>%
  pivot_wider(
    names_from = Site,
    values_from = MeanGrowth
  )
#
#
#
```

```{r Flow data, include = FALSE}
#
# Compile file names and load into one df
files <- file.path("../DBHYDRO/Shared_data", paste0(Flow_sites, "_Flow.xlsx"))
flow_list <- map2(
  files,
  sheet_lookup[Flow_sites],
  ~ read_excel(.x, sheet = .y)
)
flow_list_long <- imap(flow_list, ~
  .x %>%
    select(-any_of(c("DBKEY", "Site", "Data_Station"))) %>%   # safely remove if present
    pivot_longer(
      cols = -c(Analysis_Date, Date, Estuary),
      names_to = "Station",
      values_to = "Flow"
    )
)
flow_df <- bind_rows(flow_list_long) %>%
  mutate(Year = format(Analysis_Date, format = "%Y"))
#
# Flow summaries
SL_flow <- flow_df %>% 
  filter(Estuary == "SL" & str_ends(Station, "Sum")) %>%
  group_by(Estuary, Year) %>%
  summarise(Min = min(Flow, na.rm = T),
            Max = max(Flow, na.rm = T),
            Mean = mean(Flow, na.rm = T))
#
LX_flow <- flow_df %>% 
  filter(Estuary == "LX" & str_ends(Station, "Sum")) %>%
  group_by(Estuary, Year) %>%
  summarise(Min = min(Flow, na.rm = T),
            Max = max(Flow, na.rm = T),
            Mean = mean(Flow, na.rm = T))
#
LXN_flow <- flow_df %>% 
  filter(Estuary == "LX" & Station == "LOX_Flow") %>%
  group_by(Estuary, Year) %>%
  mutate(Estuary = "LXN") %>%
  summarise(Min = min(Flow, na.rm = T),
            Max = max(Flow, na.rm = T),
            Mean = mean(Flow, na.rm = T))
LXS_flow <- flow_df %>% 
  filter(Estuary == "LX" & Station == "S46_Flow") %>%
  group_by(Estuary, Year) %>%
  mutate(Estuary = "LXS") %>%
  summarise(Min = min(Flow, na.rm = T),
            Max = max(Flow, na.rm = T),
            Mean = mean(Flow, na.rm = T))
#
CR_flow <- flow_df %>% 
  filter(Estuary == "CR") %>%
  group_by(Estuary, Year) %>%
  summarise(Min = min(Flow, na.rm = T),
            Max = max(Flow, na.rm = T),
            Mean = mean(Flow, na.rm = T))
#
#
#
```

```{r Excel file output, include = FALSE}
file_path <- paste0("../CERP/", Summary_Excel_file_name, ".xlsx")

# If file exists, load it; otherwise create a new workbook
if (file.exists(file_path)) {
  wb <- loadWorkbook(file_path)
} else {
  wb <- createWorkbook()
}
#
#
## Flow 
sheet_name <- "Flow_data"
# If the sheet already exists, remove it (optional but avoid duplicate sheets)
if (sheet_name %in% names(wb)) {
  removeWorksheet(wb, sheet_name)
}
# Add the sheet
addWorksheet(wb, sheet_name)
# Write data starting at cell A1
writeData(wb, sheet = sheet_name, x = SL_flow, startCol = 1, startRow = 2)
writeData(wb, sheet = sheet_name, x = LX_flow, startCol = 7, startRow = 2)
writeData(wb, sheet = sheet_name, x = CR_flow, startCol = 14, startRow = 2)
writeData(wb, sheet = sheet_name, x = LXN_flow, startCol = 5, startRow = 33)
writeData(wb, sheet = sheet_name, x = LXS_flow, startCol = 12, startRow = 33)
#
#
## Salinity 
sheet_name <- "Salinity_data"
# If the sheet already exists, remove it (optional but avoid duplicate sheets)
if (sheet_name %in% names(wb)) {
  removeWorksheet(wb, sheet_name)
}
# Add the sheet
addWorksheet(wb, sheet_name)
# Write data starting at cell A1
writeData(wb, sheet = sheet_name, x = WQ_Sal_Excel, startCol = 1, startRow = 1)
writeData(wb, sheet = sheet_name, x = WQ_Sal_Excel_summ, startCol = 1, startRow = 18)
writeData(wb, sheet = sheet_name, x = WQ_Sal_Excel_Sitesumm, startCol = 1, startRow = 23)
#
#
## Secchi 
sheet_name <- "Secchi_data"
# If the sheet already exists, remove it (optional but avoid duplicate sheets)
if (sheet_name %in% names(wb)) {
  removeWorksheet(wb, sheet_name)
}
# Add the sheet
addWorksheet(wb, sheet_name)
# Write data starting at cell A1
writeData(wb, sheet = sheet_name, x = WQ_Sec_Excel, startCol = 1, startRow = 1)
writeData(wb, sheet = sheet_name, x = WQ_Sec_Excel_summ, startCol = 1, startRow = 18)
writeData(wb, sheet = sheet_name, x = WQ_Sec_Excel_Sitesumm, startCol = 1, startRow = 23)
#
#
#
## Temp 
sheet_name <- "Temp_data"
# If the sheet already exists, remove it (optional but avoid duplicate sheets)
if (sheet_name %in% names(wb)) {
  removeWorksheet(wb, sheet_name)
}
# Add the sheet
addWorksheet(wb, sheet_name)
# Write data starting at cell A1
writeData(wb, sheet = sheet_name, x = WQ_Tem_Excel, startCol = 1, startRow = 1)
writeData(wb, sheet = sheet_name, x = WQ_Tem_Excel_summ, startCol = 1, startRow = 18)
writeData(wb, sheet = sheet_name, x = WQ_Tem_Excel_Sitesumm, startCol = 1, startRow = 23)
#
#
## pH 
sheet_name <- "pH_data"
# If the sheet already exists, remove it (optional but avoid duplicate sheets)
if (sheet_name %in% names(wb)) {
  removeWorksheet(wb, sheet_name)
}
# Add the sheet
addWorksheet(wb, sheet_name)
# Write data starting at cell A1
writeData(wb, sheet = sheet_name, x = WQ_pH_Excel, startCol = 1, startRow = 1)
writeData(wb, sheet = sheet_name, x = WQ_pH_Excel_summ, startCol = 1, startRow = 18)
writeData(wb, sheet = sheet_name, x = WQ_pH_Excel_Sitesumm, startCol = 1, startRow = 23)
#
#
#
## DO 
sheet_name <- "DO_data"
# If the sheet already exists, remove it (optional but avoid duplicate sheets)
if (sheet_name %in% names(wb)) {
  removeWorksheet(wb, sheet_name)
}
# Add the sheet
addWorksheet(wb, sheet_name)
# Write data starting at cell A1
writeData(wb, sheet = sheet_name, x = WQ_DO_Excel, startCol = 1, startRow = 1)
writeData(wb, sheet = sheet_name, x = WQ_DO_Excel_summ, startCol = 1, startRow = 18)
writeData(wb, sheet = sheet_name, x = WQ_DO_Excel_Sitesumm, startCol = 1, startRow = 23)
#
#
#
## Survey
sheet_name <- "Density_data"
# If the sheet already exists, remove it (optional but avoid duplicate sheets)
if (sheet_name %in% names(wb)) {
  removeWorksheet(wb, sheet_name)
}
# Add the sheet
addWorksheet(wb, sheet_name)
# Write data starting at cell A1
writeData(wb, sheet = sheet_name, x = Live_Excel, startCol = 1, startRow = 1)
writeData(wb, sheet = sheet_name, x = Live_Excel_Sitesumm, startCol = 1, startRow = 10)
writeData(wb, sheet = sheet_name, x = Live_Excel_SeasonSitesumm, startCol = 2, startRow = 15)
writeData(wb, sheet = sheet_name, x = Dead_Excel, startCol = 1, startRow = 21)
writeData(wb, sheet = sheet_name, x = Dead_Excel_Sitesumm, startCol = 1, startRow = 30)
writeData(wb, sheet = sheet_name, x = Dead_Excel_SeasonSitesumm, startCol = 2, startRow = 35)
#
sheet_name <- "SH_data"
# If the sheet already exists, remove it (optional but avoid duplicate sheets)
if (sheet_name %in% names(wb)) {
  removeWorksheet(wb, sheet_name)
}
# Add the sheet
addWorksheet(wb, sheet_name)
# Write data starting at cell A1
writeData(wb, sheet = sheet_name, x = SH_Excel, startCol = 1, startRow = 1)
writeData(wb, sheet = sheet_name, x = SH_Excel_Sitesumm, startCol = 1, startRow = 10)
writeData(wb, sheet = sheet_name, x = SH_Excel_SeasonSitesumm, startCol = 2, startRow = 15)
#
#
#
## Dermo 
sheet_name <- "Dermo_data"
# If the sheet already exists, remove it (optional but avoid duplicate sheets)
if (sheet_name %in% names(wb)) {
  removeWorksheet(wb, sheet_name)
}
# Add the sheet
addWorksheet(wb, sheet_name)
# Write data starting at cell B1
writeData(wb, sheet = sheet_name, x = DermoI_Excel, startCol = 2, startRow = 1)
writeData(wb, sheet = sheet_name, x = DermoI_Excel_summ, startCol = 2, startRow = 18)
writeData(wb, sheet = sheet_name, x = DermoI_Excel_Sitesumm, startCol = 2, startRow = 22)
writeData(wb, sheet = sheet_name, x = DermoP_Excel, startCol = 2, startRow = 27)
writeData(wb, sheet = sheet_name, x = DermoP_Excel_summ, startCol = 2, startRow = 44)
writeData(wb, sheet = sheet_name, x = DermoP_Excel_Sitesumm, startCol = 2, startRow = 48)
#
#
#
## Repro 
sheet_name <- "Repro_data"
# If the sheet already exists, remove it (optional but avoid duplicate sheets)
if (sheet_name %in% names(wb)) {
  removeWorksheet(wb, sheet_name)
}
# Add the sheet
addWorksheet(wb, sheet_name)
# Write data starting at cell A1
writeData(wb, sheet = sheet_name, x = Repro_Excel, startCol = 1, startRow = 1)
#
#
#
## Recruitment 
sheet_name <- "Rcrt_data"
# If the sheet already exists, remove it (optional but avoid duplicate sheets)
if (sheet_name %in% names(wb)) {
  removeWorksheet(wb, sheet_name)
}
# Add the sheet
addWorksheet(wb, sheet_name)
# Write data starting at cell A1
writeData(wb, sheet = sheet_name, x = Rcrt_Excel, startCol = 1, startRow = 1)
writeData(wb, sheet = sheet_name, x = Rcrt_Excel_summ, startCol = 1, startRow = 18)
writeData(wb, sheet = sheet_name, x = Rcrt_Excel_Sitesumm, startCol = 1, startRow = 23)
#
#
#
## Cage 
sheet_name <- "Cage_data"
# If the sheet already exists, remove it (optional but avoid duplicate sheets)
if (sheet_name %in% names(wb)) {
  removeWorksheet(wb, sheet_name)
}
# Add the sheet
addWorksheet(wb, sheet_name)
# Write data starting at cell A1
writeData(wb, sheet = sheet_name, x = Cage_Excel %>% filter(Site == "CRE"), startCol = 1, startRow = 1)
writeData(wb, sheet = sheet_name, x = Cage_Excel %>% filter(Site == "CRW"), startCol = 6, startRow = 1)
writeData(wb, sheet = sheet_name, x = Cage_Excel %>% filter(Site == "LXN"), startCol = 12, startRow = 1)
writeData(wb, sheet = sheet_name, x = Cage_Excel %>% filter(Site == "SLC"), startCol = 18, startRow = 1)
writeData(wb, sheet = sheet_name, x = Cage_Excel_SiteSumm %>% filter(Site == "CRE"), 
          startCol = 1, startRow = 18)
writeData(wb, sheet = sheet_name, x = Cage_Excel_SiteSumm %>% filter(Site == "CRW"), 
          startCol = 6, startRow = 18)
writeData(wb, sheet = sheet_name, x = Cage_Excel_SiteSumm %>% filter(Site == "LXN"), 
          startCol = 12, startRow = 18)
writeData(wb, sheet = sheet_name, x = Cage_Excel_SiteSumm %>% filter(Site == "SLC"), 
          startCol = 18, startRow = 18)
writeData(wb, sheet = sheet_name, x = Cage_AveGrowth, startCol = 1, startRow = 23)
#
#
#
#
#
# Save workbook (overwrite = TRUE ensures updates)
saveWorkbook(wb, file_path, overwrite = TRUE)
```

## Report summary
This data summary was compiled on `r format(Sys.Date(), "%d %B %Y")` and summarizes data for **CERP** annual report from `r format(Start_date, "%B %Y")` through `r format(End_date, "%B %Y")`.\

<h1>`r paste("Water quality summary")`</h1>
<h2>`r paste("Salinity")`</h2>
<h3>`r paste("Summary by estuary")`</h3>
`r WQ_Sal_tab %>% mutate(Site = substr(Site, 1, 2)) %>% group_by(Site) %>% summarise(Min = min(Salinity, na.rm = T), Max = max(Salinity, na.rm = T), Mean = round(mean(Salinity, na.rm = T),3)) %>% gt()`
<h3>`r paste("Summary by site")`</h3>
`r WQ_Sal_tab %>% group_by(Site) %>% summarise(Min = min(Salinity, na.rm = T), Max = max(Salinity, na.rm = T), Mean = round(mean(Salinity, na.rm = T),3)) %>% gt()`
`r WQ_Sal_out %>% tab_caption(caption = "Monthly salinity measurements")`
\
<h2>`r paste("Secchi")`</h2>
<h3>`r paste("Summary by estuary")`</h3>
`r WQ_Sec_tab %>% mutate(Site = substr(Site, 1, 2)) %>% group_by(Site) %>% summarise(Min = min(Secchi, na.rm = T), Max = max(Secchi, na.rm = T), Mean = round(mean(Secchi, na.rm = T),3)) %>% gt()`
<h3>`r paste("Summary by site")`</h3>
`r WQ_Sec_tab %>% group_by(Site) %>% summarise(Min = min(Secchi, na.rm = T), Max = max(Secchi, na.rm = T), Mean = round(mean(Secchi, na.rm = T),3)) %>% gt()`
`r WQ_Sec_out %>% tab_caption(caption = "Monthly Secchi measurements")`
\
<h2>`r paste("Temp")`</h2>
<h3>`r paste("Summary by estuary")`</h3>
`r WQ_Tem_tab %>% mutate(Site = substr(Site, 1, 2)) %>% group_by(Site) %>% summarise(Min = min(Temp, na.rm = T), Max = max(Temp, na.rm = T), Mean = round(mean(Temp, na.rm = T),3)) %>% gt()`
<h3>`r paste("Summary by site")`</h3>
`r WQ_Tem_tab %>% group_by(Site) %>% summarise(Min = min(Temp, na.rm = T), Max = max(Temp, na.rm = T), Mean = round(mean(Temp, na.rm = T),3)) %>% gt()`
`r WQ_Tem_out %>% tab_caption(caption = "Monthly Temp measurements")`
\
<h2>`r paste("pH")`</h2>
<h3>`r paste("Summary by estuary")`</h3>
`r WQ_pH_tab %>% mutate(Site = substr(Site, 1, 2)) %>% group_by(Site) %>% summarise(Min = min(pH, na.rm = T), Max = max(pH, na.rm = T), Mean = round(mean(pH, na.rm = T),3)) %>% gt()`
<h3>`r paste("Summary by site")`</h3>
`r WQ_pH_tab %>% group_by(Site) %>% summarise(Min = min(pH, na.rm = T), Max = max(pH, na.rm = T), Mean = round(mean(pH, na.rm = T),3)) %>% gt()`
`r WQ_Tem_out %>% tab_caption(caption = "Monthly pH measurements")`
\
<h2>`r paste("DO")`</h2>
<h3>`r paste("Summary by estuary")`</h3>
`r WQ_DO_tab %>% mutate(Site = substr(Site, 1, 2)) %>% group_by(Site) %>% summarise(Min = min(DO, na.rm = T), Max = max(DO, na.rm = T), Mean = round(mean(DO, na.rm = T),3)) %>% gt()`
<h3>`r paste("Summary by site")`</h3>
`r WQ_DO_tab %>% group_by(Site) %>% summarise(Min = min(DO, na.rm = T), Max = max(DO, na.rm = T), Mean = round(mean(DO, na.rm = T),3)) %>% gt()`
`r WQ_Tem_out %>% tab_caption(caption = "Monthly DO measurements")`
\
\
\
<h1>`r paste("Survey summary")`</h1>
<h2>`r paste("Live Means")`</h2>
<h3>`r paste("Summary by Site")`</h3>
`r Live_Excel_Sitesumm %>% gt()`
<h3>`r paste("Summary by Season")`</h3>
`r Live_Excel_SeasonSitesumm %>% gt()`
`r Live_out %>% tab_caption(caption = "Monthly mean live counts")`
\
<h2>`r paste("Dead Means")`</h2>
<h3>`r paste("Summary by Site")`</h3>
`r Dead_Excel_Sitesumm %>% gt()`
<h3>`r paste("Summary by Season")`</h3>
`r Dead_Excel_SeasonSitesumm %>% gt()`
`r Dead_out %>% tab_caption(caption = "Monthly mean dead counts")`
\
<h2>`r paste("Mean Shell Heights")`</h2>
<h3>`r paste("Summary by Site")`</h3>
`r SH_Excel_Sitesumm %>% gt()`
<h3>`r paste("Summary by Season")`</h3>
`r SH_Excel_SeasonSitesumm %>% gt()`
`r SH_out %>% tab_caption(caption = "Monthly mean shell heights")`
\
\
\
<h1>`r paste("Dermo summary")`</h1>
<h2>`r paste("Dermo Intensity Means")`</h2>
<h3>`r paste("Summary by estuary")`</h3>
`r DermoI_Excel_Sitesumm %>% gt()`
<h3>`r paste("Summary by site")`</h3>
`r DermoI_Excel_summ %>% gt()`
`r DermoI_out %>% tab_caption(caption = "Monthly mean dermo intensity")`
\
<h2>`r paste("Dermo Prevalence Means")`</h2>
<h3>`r paste("Summary by estuary")`</h3>
`r DermoP_Excel_Sitesumm %>% gt()`
<h3>`r paste("Summary by site")`</h3>
`r DermoP_Excel_summ %>% gt()`
`r DermoP_out %>% tab_caption(caption = "Monthly mean dermo prevalence")`
\
\
\
<h1>`r paste("Repro summary")`</h1>
<h2>`r paste("Repro Stage Means")`</h2>
<h3>`r paste("Summary by estuary")`</h3>
`r Repro_Excel %>% gt()`
`r Repro_out %>% tab_caption(caption = "Monthly mean repro stage")`
\
\
\
<h1>`r paste("Recruitment summary")`</h1>
<h2>`r paste("Recruitment Means")`</h2>
<h3>`r paste("Summary by Site")`</h3>
`r Rcrt_Excel_Sitesumm %>% gt()`
<h3>`r paste("Summary by Estuary")`</h3>
`r Rcrt_Excel_summ %>% gt()`
`r Rcrt_out %>% tab_caption(caption = "Monthly mean recruitment")`
\
\
\
<h1>`r paste("Cage summary")`</h1>
`r CageSHs_out %>% tab_caption(caption = "Monthly mean shell heights")`
`r CageCounts_out %>% tab_caption(caption = "Monthly mean percent mortatlity")`