---
title: "CERP Monthly Report - `r params$Year`-`r params$Month`"
output: word_document
params: 
  Month: "02"  #Enter 2-digit month
  Year: "2024" #Enter 4-digit year

knit: (function(inputFile, encoding) {
  rmarkdown::render(
    input = inputFile, encoding = encoding,
    output_file = paste0(substr(inputFile, 1, nchar(inputFile)-4), " - ", with(rmarkdown::yaml_front_matter(inputFile), paste(params$Year, params$Month)), " - ", format(Sys.Date(), "%b %d %y"), '.docx')) 
      })
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

Author <- c("E Levine") #Change to your name
Month <- params$Month 
Year <- params$Year   
#######File locations required to be updated for use.

Survey <- ifelse(as.numeric(Month) > 11 | as.numeric(Month) < 3, paste0("Winter", Year),
                 ifelse(as.numeric(Month) > 2 & as.numeric(Month) < 6, paste0("Spring", Year),
                        ifelse(as.numeric(Month) > 5 & as.numeric(Month) < 9, paste0("Summer", Year), paste0("Fall", Year))))
```

```{r Packages, base DFs, and time frame}
#Load required packages
if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, dplyr,  #DF manipulation
               readxl,          #Excel
               lubridate,         #Dates
               knitr, here,
               flextable,
               install = TRUE)

#Load required data - salinity, recruitment, dermo, survey counts - all but WQ limited to 2023 data
WaterQual <- read_excel("...", sheet = "RawData", skip = 3, col_names = TRUE, na = c("", "Z"), trim_ws = TRUE, .name_repair = "universal") %>% 
  filter(!grepl('Proof', Date)) %>% drop_na(Date)

Rcrt_df <- read_excel("...", sheet = "Spat", skip = 22719, col_names = c("Ret.Date",	"Jul.Ret", "Jul.Dep",	"Num.Days",	"Site",	"Station",	"Rep", "Shell",	"..Bottom",	"..Top", "Comments"), na = c("", "Z", "z"), trim_ws = TRUE, .name_repair = "universal")  %>%
  mutate(Ret.Date = as.Date(as.numeric(Ret.Date), origin = "1899-12-30"),
         Num.Days = as.numeric(Num.Days)) %>% drop_na(Ret.Date)

Rcrt_df2 <- read_excel("...", sheet = "Spat", skip = 2, col_names = c("Ret.Date",	"Jul.Ret", "Jul.Dep",	"Num.Days",	"Site",	"Station",	"Rep", "Shell",	"..Bottom",	"..Top", "Comments"), na = c("", "Z", "z"), trim_ws = TRUE, .name_repair = "universal") %>% 
  mutate(Ret.Date = as.Date(as.numeric(Ret.Date), origin = "1899-12-30"),
         Num.Days = as.numeric(Num.Days)) %>% drop_na(Ret.Date)

Dermo_df <- read_excel("...", sheet = "Dermo2012", skip = 1724, col_names = c("Date",	"Site",	"Sample.Number",	"Station", 	"SH..mm.",	"Total.Weight..g.",	"Shell.Wet.Wt..g.",	"Dermo.Mantle",	"Dermo.Gill", "Comments"), na = c("", "Z", "z"), trim_ws = TRUE, .name_repair = "universal") %>% mutate(Date = as.Date(as.numeric(Date), origin = "1899-12-30")) %>% drop_na(Date)

Dermo_df2 <- read_excel("...", sheet = "Dermo", skip = 1364, col_names = c("Date",	"Site",	"Sample.Number",	"Station", 	"SH..mm.",	"Total.Weight..g.",	"Shell.Wet.Wt..g.",	"Dermo.Mantle",	"Dermo.Gill"), na = c("", "Z", "z"), trim_ws = TRUE, .name_repair = "universal") %>% mutate(Date = as.Date(as.numeric(Date), origin = "1899-12-30")) %>% drop_na(Date)

Survey_df <- if(Month == "03" | Month == "06" | Month == "09" | Month == "12") {read_excel(paste0("...",Survey, ".xlsx"), sheet = "Counts", skip = 3, col_names = TRUE, na = c("", "Z", "z"), trim_ws = TRUE, .name_repair = "universal") %>% drop_na()} else {"Survey was not conducted"}

MonYr <- paste(month.abb[as.numeric(Month)], Year, sep = " ")
Start_date <- as.Date(paste(Year, Month, "01", sep = "-")) - months(1)
End_date <- format(ceiling_date(Start_date %m+% months(2)) - days(1), "%Y-%m-%d")
```

```{r Data filtering}
Sal <- WaterQual %>% filter(Date >= Start_date & Date <= End_date) %>% 
  mutate(Month = format(Date, "%B")) #Add month for summary output

Rcrt <- rbind(Rcrt_df %>% filter(Ret.Date >= Start_date & Ret.Date <= End_date),
              Rcrt_df2 %>% filter(Ret.Date >= Start_date & Ret.Date <= End_date) %>% mutate(Comments = NA)) %>% 
  mutate(Station = as.factor(Station),
         Month = format(Ret.Date, "%B"), #Add month for summary output
         Shell = as.numeric(sub(" .*", "", Shell)), #Remove " - Top" from shell numbers
         Bottom = as.numeric(ifelse((Site == "SL-C" & Shell > 1 & Shell < 6) | (Site == "SL-C" & Shell > 7 & Shell < 12), ..Bottom, 
                         ifelse((Site == "CR-E" & Shell > 1 & Shell < 12) | (Site == "CR-W" & Shell > 1 & Shell < 12),..Bottom, NA)))) %>% #Drop 1, 6, 7, 12 from bottom shells SL-C and 1, 12 from bottom shells CR-E/CR-W
  mutate(Bottom_Month = (Bottom/(Num.Days/28)))

Dermo <- rbind(Dermo_df %>% filter(Date >= Start_date & Date <= End_date),
               Dermo_df2 %>% filter(Date >= Start_date & Date <= End_date) %>% mutate(Comments = NA)) %>% 
  mutate(Month = format(Date, "%B"), #Add month for summary output
         DermoSum = ifelse(rowSums(select(., contains("Dermo"))) >0, 1, 0)) #Dermo presence(1)/absence(0)

Srvy <- if(Month == "03" | Month == "06" | Month == "09" | Month == "12") {Survey_df %>% 
    mutate(Month = format(Date, "%B"),
           Live = ..1.4.m2..Live*4,
           Dead = ..1.4.m2..Dead*4)} else {"Survey was not conducted"} #Add month for summary output

```


```{r Data summary}
Sal_summary <- rbind(Sal %>% filter(Site == "SL-C") %>% group_by(Month, Site) %>%
                       summarise(meanSal = round(mean(Salinity..ppt., na.rm = T),2)),
                     Sal %>% filter(Site == "CR-E" | Site == "CR-W") %>% filter(Station == 2 | Station == 3) %>% group_by(Month, Site, Station) %>%
                       summarise(meanSal = round(mean(Salinity..ppt., na.rm = T),2)))  %>% #Monthly mean
  dplyr::select(Month, Site, Station, meanSal) %>% arrange(Site, Station, Month)

Rcrt_summary <- rbind(Rcrt %>% filter(Site == "SL-C") %>% group_by(Month, Site) %>% 
                        summarise(meanRcrt = round(mean(Bottom/(Num.Days/28), na.rm = T),2)), 
                      Rcrt %>% filter(Site == "CR-E" | Site == "CR-W") %>% filter(Station == 2 | Station == 3)%>%
                        group_by(Month, Site, Station) %>%
                        summarise(meanRcrt = round(mean(Bottom/(Num.Days/28), na.rm = T),3))) %>% #Monthly mean
  dplyr::select(Month, Site, Station, meanRcrt) %>% arrange(Site, Station, Month)

Dermo_summary <- rbind(Dermo %>% filter(Site == "SL-C") %>% group_by(Month, Site) %>%
                         summarise(Percent = round(sum(DermoSum, na.rm = T)/n()*100, 2)),
                       Dermo %>% filter(Site == "CR-E" | Site == "CR-W") %>% filter(Station == 2 | Station == 3) %>% group_by(Month, Site, Station) %>% 
                         summarise(Percent = round(sum(DermoSum, na.rm = T)/n()*100, 2))) %>%
  dplyr::select(Month, Site, Station, Percent) %>% arrange(Site, Station, Month)

Srvy_summary <- if(Month == "03" | Month == "06" | Month == "09" | Month == "12") {rbind(
  Srvy %>% filter(Site == "SL-C") %>% group_by(Month, Site) %>%
    summarise(meanLive = round(mean(Live, na.rm = T),0),
              meanDead = round(mean(Dead, na.rm = T),0)),
  Srvy %>% filter(Site == "CR-E" | Site == "CR-W") %>% filter(Station == 2 | Station == 3) %>% group_by(Month, Site, Station) %>%
    summarise(meanLive = round(mean(Live, na.rm = T),0),
              meanDead = round(mean(Dead, na.rm = T),0))) %>%
    dplyr::select(Month, Site, Station, everything()) %>% arrange(Site, Station, Month)} else {"Survey was not conducted."}

SLC_Srvy_note <- if(Month == "03" | Month == "06" | Month == "09" | Month == "12") {paste0("During the biannual ", if(Month == "03") {paste("spring")} else if(Month == "06") {paste("summer")} else if (Month == "09") {paste("fall")} else {paste("winter")}, " survey there were approximately ", (Srvy_summary %>% filter(Site == "SL-C"))$meanLive, " live and ", (Srvy_summary %>% filter(Site == "SL-C"))$meanDead, " dead oysters per 1 m2 quadrat.")} else {paste("Survey was not conducted this month")}

CRE_Srvy_note <- if(Month == "03" | Month == "06" | Month == "09" | Month == "12") {paste0("During the biannual ", if(Month == "03") {paste("spring")} else if(Month == "06") {paste("summer")} else if (Month == "09") {paste("fall")} else {paste("winter")}, " survey at Iona Cove there were approximately ", (Srvy_summary %>% filter(Site == "CR-E"))$meanLive, " live and approximately ", (Srvy_summary %>% filter(Site == "CR-E"))$meanDead, " dead oysters per 1 m2 quadrat.")} else {paste("Survey was not conducted this month")}

CRW_Srvy_note <- if(Month == "03" | Month == "06" | Month == "09" | Month == "12") {paste0("During the biannual ", if(Month == "03") {paste("spring")} else if(Month == "06") {paste("summer")} else if (Month == "09") {paste("fall")} else {paste("winter")}, " survey at Bird Island there were approximately ", (Srvy_summary %>% filter(Site == "CR-W"))$meanLive, " live and approximately ", (Srvy_summary %>% filter(Site == "CR-W"))$meanDead, " dead oysters per 1 m2 quadrat.")} else {paste("Survey was not conducted this month")}
```

```{r Data summary output}

SLC_survey_output <- if(Month == "03" | Month == "06" | Month == "09" | Month == "12"){
  Srvy %>% filter(Site == "SL-C") %>% group_by(Date, Site) %>%
    summarise(meanLive = round(mean(Live, na.rm = T),2),
              sdLive = round(sd(Live, na.rm = T), 2),
              meanDead = round(mean(Dead, na.rm = T), 2),
              sdDead = round(sd(Dead, na.rm = T),2))
} else {(data.frame(Site = "SL-C", meanLive = NA, sdLive = NA, meanDead = NA, sdDead = NA))}

SLC1_survey_output <- if(Month == "03" | Month == "06" | Month == "09" | Month == "12"){
  Srvy %>% filter(Site == "SL-C" & Station == 1) %>% group_by(Date, Site) %>%
    summarise(meanLive = round(mean(Live, na.rm = T),2),
              sdLive = round(sd(Live, na.rm = T), 2),
              meanDead = round(mean(Dead, na.rm = T), 2),
              sdDead = round(sd(Dead, na.rm = T),2))
} else {data.frame(Site = "SLC", meanLive = NA, sdLive = NA, meanDead = NA, sdDead = NA)}

CRE_survey_output <- if(Month == "03" | Month == "06" | Month == "09" | Month == "12"){
  Srvy %>% filter(Site == "CR-E" & Station == 2) %>% group_by(Date, Site) %>%
    summarise(meanLive = round(mean(Live, na.rm = T),2),
              sdLive = round(sd(Live, na.rm = T), 2),
              meanDead = round(mean(Dead, na.rm = T), 2),
              sdDead = round(sd(Dead, na.rm = T),2))
} else {data.frame(Site = "CR-E", meanLive = NA, sdLive = NA, meanDead = NA, sdDead = NA)}

CRW_survey_output <- if(Month == "03" | Month == "06" | Month == "09" | Month == "12"){
  Srvy %>% filter(Site == "CR-W" & Station == 3) %>% group_by(Date, Site) %>% 
    summarise(meanLive = round(mean(Live, na.rm = T),2),
              sdLive = round(sd(Live, na.rm = T), 2),
              meanDead = round(mean(Dead, na.rm = T), 2),
              sdDead = round(sd(Dead, na.rm = T),2))
} else {data.frame(Site = "CR-W", meanLive = NA, sdLive = NA, meanDead = NA, sdDead = NA)}

SLC_Excel_summ <- left_join(
  left_join(
    left_join(Sal %>% filter(Site == "SL-C") %>% group_by(Date, Site) %>%
              summarise(meanSal = round(mean(Salinity..ppt., na.rm = T),2),
                        sdSal = round(sd(Salinity..ppt., na.rm = T), 2)), 
            Rcrt %>% filter(Site == "SL-C") %>% group_by(Ret.Date, Site) %>% 
              summarise(meanRcrt = round(mean(Bottom/(Num.Days/28), na.rm = T),2),
                        sdRcrt = round(sd(Bottom/(Num.Days/28), na.rm = T),2)) %>% rename(Date = Ret.Date)),
  Dermo %>% filter(Site == "SL-C") %>% group_by(Date, Site) %>%
    summarise(PctDermo = round(sum(DermoSum, na.rm = T)/n()*100, 2))),
  SLC_survey_output) %>%
  mutate(Date = format(as.Date(Date, "%Y-%m-%d"), "%b-%y")) %>% as.data.frame()

SLC1_Excel_summ <- left_join(
  left_join(
    left_join(Sal %>% filter(Site == "SL-C" & Station == 1) %>% group_by(Date, Site) %>%
              summarise(meanSal = round(mean(Salinity..ppt., na.rm = T),2),
                        sdSal = round(sd(Salinity..ppt., na.rm = T), 2)), 
            Rcrt %>% filter(Site == "SL-C" & Station == 1) %>% group_by(Ret.Date, Site) %>% 
              summarise(meanRcrt = round(mean(Bottom/(Num.Days/28), na.rm = T),2),
                        sdRcrt = round(sd(Bottom/(Num.Days/28), na.rm = T),2)) %>% rename(Date = Ret.Date)),
  Dermo %>% filter(Site == "SL-C" & Station == 1) %>% group_by(Date, Site) %>%
    summarise(PctDermo = round(sum(DermoSum, na.rm = T)/n()*100, 2))),
  SLC_survey_output) %>%
  mutate(Date = format(as.Date(Date, "%Y-%m-%d"), "%b-%y")) %>% as.data.frame()

CRE_Excel_summ <- left_join(
  left_join(
    left_join(Sal %>% filter(Site == "CR-E") %>% filter(Station == 2) %>% group_by(Date, Site, Station) %>% 
                summarise(meanSal = round(mean(Salinity..ppt., na.rm = T),2)),
              Rcrt %>% filter(Site == "CR-E") %>% filter(Station == 2)%>%  mutate(Station = as.numeric(Station)) %>%
                group_by(Ret.Date, Site, Station) %>%
                summarise(meanRcrt = round(mean(Bottom/(Num.Days/28), na.rm = T),2),
                        sdRcrt = round(sd(Bottom/(Num.Days/28), na.rm = T),2)) %>% rename(Date = Ret.Date)),
    Dermo %>% filter(Site == "CR-E") %>% filter(Station == 2) %>% group_by(Date, Site, Station) %>% 
      summarise(PctDermo = round(sum(DermoSum, na.rm = T)/n()*100, 2))),
  CRE_survey_output) %>% dplyr::select(-Station) %>% 
  mutate(Date = format(as.Date(Date, "%Y-%m-%d"), "%b-%y")) %>% as.data.frame()

CRW_Excel_summ <- left_join(
  left_join(
    left_join(Sal %>% filter(Site == "CR-W") %>% filter(Station == 3) %>% group_by(Date, Site, Station) %>%  
                summarise(meanSal = round(mean(Salinity..ppt., na.rm = T),2)),
              Rcrt %>% filter(Site == "CR-W") %>% filter(Station == 3) %>% mutate(Station = as.numeric(Station)) %>%
                group_by(Ret.Date, Site, Station) %>%
                summarise(meanRcrt = round(mean(Bottom/(Num.Days/28), na.rm = T),2),
                        sdRcrt = round(sd(Bottom/(Num.Days/28), na.rm = T),2)) %>% rename(Date = Ret.Date)),
    Dermo %>% filter(Site == "CR-W") %>% filter(Station == 3) %>% group_by(Date, Site, Station) %>% 
      summarise(PctDermo = round(sum(DermoSum, na.rm = T)/n()*100, 2))),
  CRW_survey_output) %>% dplyr::select(-Station) %>% 
  mutate(Date = format(as.Date(Date, "%Y-%m-%d"), "%b-%y")) %>% as.data.frame()
```
## Report summary
Compiled by: `r Author` on `r format(Sys.Date(), "%d %B %Y")`.\
This report details data for **CERP** sites in **`r MonYr`**.
Analysis covers data occurring between *`r Start_date`* and *`r End_date`* at St. Lucie-Central and at Caloosahatchee River.\

## St. Lucie Central summary

Here is the monthly report with the data collected from the St. Lucie Estuary on `r max((Sal %>% filter(Site == "SL-C"))$Date) %>% format("%B %d, %Y")`:

*	Mean salinity 
`r if((Sal_summary %>% filter(Site == "SL-C" & Month == min((Sal %>% filter(Site == "SL-C"))$Date) %>% format("%B")))$meanSal > (Sal_summary %>% filter(Site == "SL-C" & Month == max((Sal %>% filter(Site == "SL-C"))$Date) %>% format("%B")))$meanSal) {paste("decreased")} else if ((Sal_summary %>% filter(Site == "SL-C" & Month == min((Sal %>% filter(Site == "SL-C"))$Date) %>% format("%B")))$meanSal < (Sal_summary %>% filter(Site == "SL-C" & Month == max((Sal %>% filter(Site == "SL-C"))$Date) %>% format("%B")))$meanSal) {paste("increased")} else {paste("stayed the same")}` 
from 
`r (Sal_summary %>% filter(Site == "SL-C" & Month == min((Sal %>% filter(Site == "SL-C"))$Date) %>% format("%B")))$meanSal` 
in 
`r min((Sal %>% filter(Site == "SL-C"))$Date) %>% format("%B")` 
to 
`r (Sal_summary %>% filter(Site == "SL-C" & Month == max((Sal %>% filter(Site == "SL-C"))$Date) %>% format("%B")))$meanSal` 
in 
`r max((Sal %>% filter(Site == "SL-C"))$Date) %>% format("%B")`.
*	The mean recruitment rate 
`r if((Rcrt_summary %>% filter(Site == "SL-C" & Month == min((Rcrt %>% filter(Site == "SL-C"))$Ret.Date) %>% format("%B")))$meanRcrt > (Rcrt_summary %>% filter(Site == "SL-C" & Month == max((Rcrt %>% filter(Site == "SL-C"))$Ret.Date) %>% format("%B")))$meanRcrt) {paste("decreased")} else if ((Rcrt_summary %>% filter(Site == "SL-C" & Month == min((Rcrt %>% filter(Site == "SL-C"))$Ret.Date) %>% format("%B")))$meanRcrt < (Rcrt_summary %>% filter(Site == "SL-C" & Month == max((Rcrt %>% filter(Site == "SL-C"))$Ret.Date) %>% format("%B")))$meanRcrt) {paste("increased")} else {paste("stayed the same")}` 
from 
`r (Rcrt_summary %>% filter(Site == "SL-C" & Month == min((Rcrt %>% filter(Site == "SL-C"))$Ret.Date) %>% format("%B")))$meanRcrt` 
spat/shell in 
`r min((Rcrt %>% filter(Site == "SL-C"))$Ret.Date) %>% format("%B")` 
to 
`r (Rcrt_summary %>% filter(Site == "SL-C" & Month == max((Rcrt %>% filter(Site == "SL-C"))$Ret.Date) %>% format("%B")))$meanRcrt` 
spat/shell in 
`r max((Rcrt %>% filter(Site == "SL-C"))$Ret.Date) %>% format("%B")`.
*	Dermo prevalence 
`r if((Dermo_summary %>% filter(Site == "SL-C" & Month == min((Dermo %>% filter(Site == "SL-C"))$Date) %>% format("%B")))$Percent > (Dermo_summary %>% filter(Site == "SL-C" & Month == max((Dermo %>% filter(Site == "SL-C"))$Date) %>% format("%B")))$Percent) {paste("decreased")} else if ((Dermo_summary %>% filter(Site == "SL-C" & Month == min((Dermo %>% filter(Site == "SL-C"))$Date) %>% format("%B")))$Percent < (Dermo_summary %>% filter(Site == "SL-C" & Month == max((Dermo %>% filter(Site == "SL-C"))$Date) %>% format("%B")))$Percent) {paste("increased")} else {paste("stayed the same")}` 
from
`r (Dermo_summary %>% filter(Site == "SL-C" & Month == min((Dermo %>% filter(Site == "SL-C"))$Date) %>% format("%B")))$Percent`% 
in 
`r min((Dermo %>% filter(Site == "SL-C"))$Date) %>% format("%B")` 
to 
`r (Dermo_summary %>% filter(Site == "SL-C" & Month == max((Dermo %>% filter(Site == "SL-C"))$Date) %>% format("%B")))$Percent`% 
in
`r max((Dermo %>% filter(Site == "SL-C"))$Date) %>% format("%B")`.
* `r if(Month == "03" | Month == "06"  | Month == "09" | Month == "12") {paste(SLC_Srvy_note)} else {paste("Survey was not conducted this month")}`
\

## Caloosahatchee River summary 

Here is the monthly report with data collected from Caloosahatchee on `r max((Sal %>% filter(Site == "CR-E"))$Date) %>% format("%B %d, %Y")`:

*	Mean salinity 
`r if((Sal_summary %>% filter(Site == "CR-E" & Month == min((Sal %>% filter(Site == "CR-E"))$Date) %>% format("%B")))$meanSal > (Sal_summary %>% filter(Site == "CR-E" & Month == max((Sal %>% filter(Site == "CR-E"))$Date) %>% format("%B")))$meanSal) {paste("decreased")} else if ((Sal_summary %>% filter(Site == "CR-E" & Month == min((Sal %>% filter(Site == "CR-E"))$Date) %>% format("%B")))$meanSal < (Sal_summary %>% filter(Site == "CR-E" & Month == max((Sal %>% filter(Site == "CR-E"))$Date) %>% format("%B")))$meanSal) {paste("increased")} else {paste("stayed the same")}` 
from 
`r (Sal_summary %>% filter(Site == "CR-E" & Month == min((Sal %>% filter(Site == "CR-E"))$Date) %>% format("%B")))$meanSal` 
in 
`r min((Sal %>% filter(Site == "CR-E"))$Date) %>% format("%B")` 
to 
`r (Sal_summary %>% filter(Site == "CR-E" & Month == max((Sal %>% filter(Site == "CR-E"))$Date) %>% format("%B")))$meanSal` 
in 
`r max((Sal %>% filter(Site == "CR-E"))$Date) %>% format("%B")`
at the Iona Cove station, and 
`r if((Sal_summary %>% filter(Site == "CR-W" & Month == min((Sal %>% filter(Site == "CR-W"))$Date) %>% format("%B")))$meanSal > (Sal_summary %>% filter(Site == "CR-W" & Month == max((Sal %>% filter(Site == "CR-W"))$Date) %>% format("%B")))$meanSal) {paste("decreased")} else if ((Sal_summary %>% filter(Site == "CR-W" & Month == min((Sal %>% filter(Site == "CR-W"))$Date) %>% format("%B")))$meanSal < (Sal_summary %>% filter(Site == "CR-W" & Month == max((Sal %>% filter(Site == "CR-W"))$Date) %>% format("%B")))$meanSal) {paste("increased")} else {paste("stayed the same")}` 
from 
`r (Sal_summary %>% filter(Site == "CR-W" & Month == min((Sal %>% filter(Site == "CR-W"))$Date) %>% format("%B")))$meanSal` 
in 
`r min((Sal %>% filter(Site == "CR-W"))$Date) %>% format("%B")` 
to 
`r (Sal_summary %>% filter(Site == "CR-W" & Month == max((Sal %>% filter(Site == "CR-W"))$Date) %>% format("%B")))$meanSal` 
in 
`r max((Sal %>% filter(Site == "CR-W"))$Date) %>% format("%B")`
at the Bird Island station.
*	The mean recruitment rate 
`r if((Rcrt_summary %>% filter(Site == "CR-E" & Month == min((Rcrt %>% filter(Site == "CR-E"))$Ret.Date) %>% format("%B")))$meanRcrt > (Rcrt_summary %>% filter(Site == "CR-E" & Month == max((Rcrt %>% filter(Site == "CR-E"))$Ret.Date) %>% format("%B")))$meanRcrt) {paste("decreased")} else if ((Rcrt_summary %>% filter(Site == "CR-E" & Month == min((Rcrt %>% filter(Site == "CR-E"))$Ret.Date) %>% format("%B")))$meanRcrt < (Rcrt_summary %>% filter(Site == "CR-E" & Month == max((Rcrt %>% filter(Site == "CR-E"))$Ret.Date) %>% format("%B")))$meanRcrt) {paste("increased")} else {paste("stayed the same")}` 
from 
`r (Rcrt_summary %>% filter(Site == "CR-E" & Month == min((Rcrt %>% filter(Site == "CR-E"))$Ret.Date) %>% format("%B")))$meanRcrt` 
spat/shell in 
`r min((Rcrt %>% filter(Site == "CR-E"))$Ret.Date) %>% format("%B")` 
to 
`r (Rcrt_summary %>% filter(Site == "CR-E" & Month == max((Rcrt %>% filter(Site == "CR-E"))$Ret.Date) %>% format("%B")))$meanRcrt` 
spat/shell in 
`r max((Rcrt %>% filter(Site == "CR-E"))$Ret.Date) %>% format("%B")`
at the Iona Cove station, and
`r if((Rcrt_summary %>% filter(Site == "CR-W" & Month == min((Rcrt %>% filter(Site == "CR-W"))$Ret.Date) %>% format("%B")))$meanRcrt > (Rcrt_summary %>% filter(Site == "CR-W" & Month == max((Rcrt %>% filter(Site == "CR-W"))$Ret.Date) %>% format("%B")))$meanRcrt) {paste("decreased")} else if ((Rcrt_summary %>% filter(Site == "CR-W" & Month == min((Rcrt %>% filter(Site == "CR-W"))$Ret.Date) %>% format("%B")))$meanRcrt < (Rcrt_summary %>% filter(Site == "CR-W" & Month == max((Rcrt %>% filter(Site == "CR-W"))$Ret.Date) %>% format("%B")))$meanRcrt) {paste("increased")} else {paste("stayed the same")}` 
from 
`r (Rcrt_summary %>% filter(Site == "CR-W" & Month == min((Rcrt %>% filter(Site == "CR-W"))$Ret.Date) %>% format("%B")))$meanRcrt` 
spat/shell in 
`r min((Rcrt %>% filter(Site == "CR-W"))$Ret.Date) %>% format("%B")` 
to 
`r (Rcrt_summary %>% filter(Site == "CR-W" & Month == max((Rcrt %>% filter(Site == "CR-W"))$Ret.Date) %>% format("%B")))$meanRcrt` 
spat/shell in 
`r max((Rcrt %>% filter(Site == "CR-W"))$Ret.Date) %>% format("%B")`
*	Dermo prevalence 
`r if((Dermo_summary %>% filter(Site == "CR-E" & Month == min((Dermo %>% filter(Site == "CR-E"))$Date) %>% format("%B")))$Percent > (Dermo_summary %>% filter(Site == "CR-E" & Month == max((Dermo %>% filter(Site == "CR-E"))$Date) %>% format("%B")))$Percent) {paste("decreased")} else if ((Dermo_summary %>% filter(Site == "CR-E" & Month == min((Dermo %>% filter(Site == "CR-E"))$Date) %>% format("%B")))$Percent < (Dermo_summary %>% filter(Site == "CR-E" & Month == max((Dermo %>% filter(Site == "CR-E"))$Date) %>% format("%B")))$Percent) {paste("increased")} else {paste("stayed the same")}` 
from
`r (Dermo_summary %>% filter(Site == "CR-E" & Month == min((Dermo %>% filter(Site == "CR-E"))$Date) %>% format("%B")))$Percent`% 
in 
`r min((Dermo %>% filter(Site == "CR-E"))$Date) %>% format("%B")` 
to 
`r (Dermo_summary %>% filter(Site == "CR-E" & Month == max((Dermo %>% filter(Site == "CR-E"))$Date) %>% format("%B")))$Percent`% 
in
`r max((Dermo %>% filter(Site == "CR-E"))$Date) %>% format("%B")`
at the Iona Cove station, and 
`r if((Dermo_summary %>% filter(Site == "CR-W" & Month == min((Dermo %>% filter(Site == "CR-W"))$Date) %>% format("%B")))$Percent > (Dermo_summary %>% filter(Site == "CR-W" & Month == max((Dermo %>% filter(Site == "CR-W"))$Date) %>% format("%B")))$Percent) {paste("decreased")} else if ((Dermo_summary %>% filter(Site == "CR-W" & Month == min((Dermo %>% filter(Site == "CR-W"))$Date) %>% format("%B")))$Percent < (Dermo_summary %>% filter(Site == "CR-W" & Month == max((Dermo %>% filter(Site == "CR-W"))$Date) %>% format("%B")))$Percent) {paste("increased")} else {paste("stayed the same")}` 
from
`r (Dermo_summary %>% filter(Site == "CR-W" & Month == min((Dermo %>% filter(Site == "CR-W"))$Date) %>% format("%B")))$Percent`% 
in 
`r min((Dermo %>% filter(Site == "CR-W"))$Date) %>% format("%B")` 
to 
`r (Dermo_summary %>% filter(Site == "CR-W" & Month == max((Dermo %>% filter(Site == "CR-W"))$Date) %>% format("%B")))$Percent`% 
in
`r max((Dermo %>% filter(Site == "CR-W"))$Date) %>% format("%B")` 
at the Bird Island station.
*	`r if(Month == "03" | Month == "06" | Month == "09" | Month == "12") {paste(CRE_Srvy_note, CRW_Srvy_note, sep = " ")} else {paste("Survey was not conducted this month")}`

\newpage

## Data summary output (for Excel files)
The following data updates the "CERPMonthlyReportData" Excel file:

Here is the data summary output for "Monthly CERP data" Excel sheet:
```{r echo=FALSE, results='asis'}
flextable(SLC_Excel_summ) %>% align(align = "center") %>% set_table_properties(width = 0.2) %>% fontsize(size = 10, part = "all")
```
\
\
Here is the data summary output for "Monthly CR data" Excel sheet:
```{r echo=FALSE, results='asis'}
flextable(CRE_Excel_summ) %>% align(align = "center") %>% set_table_properties(width = 0.2) %>% fontsize(size = 10, part = "all")
flextable(CRW_Excel_summ) %>% align(align = "center") %>% set_table_properties(width = 0.2) %>% fontsize(size = 10, part = "all")
```
\
\
\
\
The following data updates the "CERPMonthlyReportData_Rio_Station (05-Present)" Excel file:

Here is the data summary output for "SLC_1" Excel sheet:
```{r echo=FALSE, results='asis'}
flextable(SLC1_Excel_summ) %>% align(align = "center") %>% set_table_properties(width = 0.2) %>% fontsize(size = 10, part = "all")
```
