---
title: "CERP Monthly Report - `r params$Year`-`r params$Month`"
output: 
  officedown::rdocx_document:
      reference_docx: Monthly-Reports-template.docx
params: 
  Month: "05"  #Enter 2-digit month
  Year: "2025" #Enter 4-digit year
  
knit: (function(inputFile, encoding) {
  rmarkdown::render(
    input = inputFile, encoding = encoding,
    output_file = paste0(substr(inputFile, 1, nchar(inputFile)-14), " - ", with(rmarkdown::yaml_front_matter(inputFile), paste(params$Year, params$Month)),'.docx')) 
      })
---

```{r VariableSet, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

Author <- c("EL Williams") #Change to your name


Database <- "Oysters_test"  #Set the local database to use
Server = "localhost\\ERICALOCALSQL" #Set the local Server to use
#File locations for link in output required: approx. lines 532, 648

####Don't modify code in rest of section
Estuaries <- c("SL", "CR", "LX")
LocationIDs <- c("0255", "0256", "0257", "0231", "0232")
Month <- params$Month 
Year <- params$Year   
Survey <- ifelse(as.numeric(Month) > 11 | as.numeric(Month) < 3, paste0("Winter", Year),
                 ifelse(as.numeric(Month) > 2 & as.numeric(Month) < 6, paste0("Spring", Year),
                        ifelse(as.numeric(Month) > 5 & as.numeric(Month) < 9, paste0("Summer", Year), paste0("Fall", Year))))
```

```{r PackageLoad & VarSet, echo = FALSE, warning = FALSE, message = FALSE}
# Load necessary R packages
if (!require("pacman")) {install.packages("pacman")}
pacman::p_load(odbc, DBI, dbplyr,
  tidyverse, dplyr,  #DF manipulation
  #readxl,          #Excel
  lubridate,         #Dates
  knitr, here,
  flextable,
  install = TRUE)

MonYr <- paste(month.abb[as.numeric(Month)], Year, sep = " ")
ReportStart <- as.Date(paste(Year, Month, "01", sep = "-")) - months(1)
ReportEnd <- as.Date(format(ceiling_date(ReportStart %m+% months(2)) - days(1), "%Y-%m-%d"))
```

```{r DatabaseDownload}
# Connect to Local database server and pull all necessary data, then close connection 
con <- dbConnect(odbc(),
                    Driver = "SQL Server", 
                    Server = Server,
                    Database = Database,
                    Authentication = "ActiveDirectoryIntegrated")

dboFixedLocations <- tbl(con,in_schema("dbo", "FixedLocations")) %>%
  collect() %>% 
  filter(Estuary %in% Estuaries)
hsdbSampleEventWQ <- tbl(con,in_schema("hsdb", "SampleEventWQ")) %>%
  collect() %>%
  filter(substring(SampleEventID, 1, 2) %in% Estuaries)
dboSampleEventWQ <- tbl(con,in_schema("dbo", "SampleEventWQ")) %>%
  collect() %>%
  filter(substring(SampleEventID, 1, 2) %in% Estuaries)
hsdbRecruitment <- tbl(con,in_schema("hsdb", "Recruitment")) %>%
  collect() %>%
  filter(substring(SampleEventID, 1, 2) %in% Estuaries)
dboRecruitment <- tbl(con,in_schema("dbo", "Recruitment")) %>%
  collect() %>%
  filter(substring(SampleEventID, 1, 2) %in% Estuaries)
hsdbDermo <- tbl(con,in_schema("hsdb", "Dermo")) %>%
  collect() %>%
  filter(substring(SampleEventID, 1, 2) %in% Estuaries)
dboDermo <- tbl(con,in_schema("dbo", "Dermo")) %>%
  collect() %>%
  filter(substring(SampleEventID, 1, 2) %in% Estuaries) %>%
  mutate(DermoMantle = as.numeric(DermoMantle),
         DermoGill = as.numeric(DermoGill))
if(Month == "03" | Month == "06" | Month == "09" | Month == "12"){
  hsdbSurvey <- tbl(con,in_schema("hsdb", "SurveyQuadrat")) %>%
    collect() %>%
    filter(substring(SampleEventID, 1, 2) %in% Estuaries)
  dboSurvey <- tbl(con,in_schema("dbo", "SurveyQuadrat")) %>%
    collect() %>%
    filter(substring(SampleEventID, 1, 2) %in% Estuaries)} else {Survey <- "Survey was not conducted"}
DBI::dbDisconnect(con)
```

```{r DataFilters and Summaries}
# Filter data frames so that only data collected for inclusion in the CERP Monthly Report are present.
FixedLocations1 <- dboFixedLocations %>% 
  mutate(StationNumber = as.numeric(StationNumber)) %>% 
  filter(FixedLocationID %in% LocationIDs) %>% #Only need SLC stations (0255-0257), CR2 (0231), and CR3 (0232)
  select(FixedLocationID,
         Estuary,
         SectionName, 
         StationNumber) %>% 
  distinct()  

### WATER QUALITY ###
WQ1 <- union(hsdbSampleEventWQ, dboSampleEventWQ) %>%
  mutate(RetDate = as.Date(substring(SampleEventID, 8, 15), format = "%Y%m%d"), 
         FixedLocationID = substring(SampleEventID, 19, 22), 
         AnalysisDate = as.Date(floor_date(RetDate, unit = "month")),
         Plot_Date = as.Date(AnalysisDate + 14),
         SecchiPercent = (Secchi / Depth) * 100) %>%
  select(SampleEventWQID,
         FixedLocationID,
         SampleEventID,
         RetDate,
         AnalysisDate,
         Plot_Date,
         Temperature,
         Salinity,
         DissolvedOxygen,
         pH,
         SecchiPercent) %>% 
  drop_na(Temperature) %>%
  filter(RetDate >= ReportStart & RetDate < ReportEnd) %>%
  left_join(FixedLocations1, by = c("FixedLocationID")) 

SLC_WQStats <- WQ1 %>% 
  filter(str_detect(SampleEventWQID, 'COLL') & Estuary == "SL") %>%
  group_by(AnalysisDate, 
           Plot_Date, 
           RetDate,
           Estuary,  
           SectionName) %>% 
  summarise(SalMean = mean(Salinity, na.rm = TRUE),
            SalSD = sd(Salinity, na.rm = T))

SLC1_WQStats <- WQ1 %>%
  filter(str_detect(SampleEventWQID, 'COLL') & Estuary == "SL" & StationNumber == 1) %>%
  group_by(AnalysisDate, 
           Plot_Date,  
           RetDate,
           Estuary,  
           SectionName) %>% 
  summarise(SalMean = mean(Salinity, na.rm = TRUE),
            SalSD = sd(Salinity, na.rm = T))

CR_WQStats <- WQ1 %>% 
  filter(str_detect(SampleEventWQID, 'COLL') & Estuary == "CR") %>%
  group_by(AnalysisDate, 
           Plot_Date,  
           RetDate,
           Estuary, 
           StationNumber, 
           SectionName) %>% 
  summarise(SalMean = mean(Salinity, na.rm = TRUE),
            SalSD = sd(Salinity, na.rm = T))


### RECRUITMENT ###
Recruit <- union(hsdbRecruitment, dboRecruitment) %>% 
  mutate(DeployedDate = as.Date(DeployedDate), 
         RetDate = as.Date(substring(SampleEventID, 8, 15), format = "%Y%m%d"), 
         FixedLocationID = substring(ShellID, 19, 22), 
         NumDays = as.numeric(RetDate-DeployedDate),
         BottomMonth= NumBottom/(NumDays/28),
         AnalysisDate = as.Date(floor_date(RetDate, unit = "month")),
         Plot_Date = as.Date(AnalysisDate + 14)) %>%
  select(ShellID,
         FixedLocationID,
         SampleEventID,
         DeployedDate,
         RetDate,
         AnalysisDate,
         Plot_Date,
         NumDays,
         ShellPosition,
         NumBottom,
         BottomMonth) %>% 
  filter(RetDate >= ReportStart & RetDate < ReportEnd) %>%
  left_join(FixedLocations1, by = c("FixedLocationID"))
#SL and CR RCRT calculate differently so compiling separately
SL_Recruit <- Recruit %>% 
  filter(ShellPosition %in% c(2,3,4,5,8,9,10,11), substr(ShellID, 1, 2) == "SL")

CR_Recruit <- Recruit %>% 
  filter(ShellPosition %in% c(2,3,4,5,6,7,8,9,10,11), substr(ShellID, 1, 2) == "CR") 
  
SLC_RecruitStats <- SL_Recruit %>% 
  filter(Estuary == "SL" & SectionName == "C") %>%
  group_by(AnalysisDate, Plot_Date, RetDate, Estuary, SectionName) %>% 
  summarise(RcrtMean = mean(BottomMonth, na.rm = TRUE), 
            RcrtSD= sd(BottomMonth, na.rm = TRUE))

SLC1_RecruitStats <- SL_Recruit %>% 
  filter(Estuary == "SL" & SectionName == "C" & StationNumber == 1) %>%
  group_by(AnalysisDate, Plot_Date, RetDate, Estuary, SectionName, StationNumber) %>% 
  summarise(RcrtMean = mean(BottomMonth, na.rm = TRUE), 
            RcrtSD= sd(BottomMonth, na.rm = TRUE))

CR_RecruitStats <- CR_Recruit %>% 
  filter(Estuary == "CR" & FixedLocationID %in% LocationIDs) %>%
  group_by(AnalysisDate, Plot_Date, RetDate, Estuary, SectionName, StationNumber) %>% 
  summarise(RcrtMean = mean(BottomMonth, na.rm = TRUE), 
            RcrtSD= sd(BottomMonth, na.rm = TRUE))



### DERMO ###
Dermo1 <- union((hsdbDermo %>% dplyr::select(-OldSampleNumber)), dboDermo) %>% 
  mutate(FixedLocationID = substring(SampleEventID, 19, 22), 
         RetDate = as.Date(substring(SampleEventID, 8, 15), format = "%Y%m%d"),
         AnalysisDate = as.Date(floor_date(RetDate, unit = "month")),
         Plot_Date = as.Date(AnalysisDate + 14),
         DermoSum = as.numeric(ifelse(rowSums(select(., contains("Dermo"))) >0, 1, 0))) %>%
  select(OysterID,
         FixedLocationID,
         SampleEventID,
         RetDate,
         AnalysisDate,
         Plot_Date,
         DermoMantle,
         DermoGill,
         DermoSum) %>% 
  filter(RetDate >= ReportStart & RetDate < ReportEnd) %>%
  left_join(FixedLocations1, by = c("FixedLocationID"))

SLC_DermoStats <- Dermo1 %>%
  filter(Estuary == "SL") %>%
  group_by(AnalysisDate, 
           Plot_Date,  
           RetDate,
           Estuary,  
           SectionName) %>% 
  summarise(DermoPct = (sum(DermoSum, na.rm = TRUE)/n())*100)

SLC1_DermoStats <- Dermo1 %>%
  filter(Estuary == "SL" & StationNumber == 1) %>%
  group_by(AnalysisDate, 
           Plot_Date,  
           RetDate,
           Estuary,  
           SectionName) %>% 
  summarise(DermoPct = (sum(DermoSum, na.rm = TRUE)/n())*100)

CR_DermoStats <- Dermo1 %>%
  filter(Estuary == "CR") %>%
  group_by(AnalysisDate, 
           Plot_Date,  
           RetDate,
           Estuary,  
           SectionName,
           StationNumber) %>% 
  summarise(DermoPct = (sum(DermoSum, na.rm = TRUE)/n())*100)


### SURVEY ###
if(Month == "03" | Month == "06" | Month == "09" | Month == "12"){
  Survey1 <- union(hsdbSurvey, dboSurvey) %>% 
    mutate(FixedLocationID = substring(SampleEventID, 19, 22), 
           RetDate = as.Date(substring(SampleEventID, 8, 15), format = "%Y%m%d"),
           AnalysisDate = as.Date(floor_date(RetDate, unit = "month")),
           Plot_Date = as.Date(AnalysisDate + 14),
           Live = NumLive * 4,
           Dead = NumDead * 4) %>%
    select(QuadratID,
           FixedLocationID,
           SampleEventID,
           RetDate,
           AnalysisDate,
           Plot_Date,
           QuadratNumber,
           Live,
           Dead) %>% 
    filter(RetDate >= ReportStart & RetDate < ReportEnd & FixedLocationID %in% LocationIDs) %>%
    left_join(FixedLocations1, by = c("FixedLocationID"))
}else{Survey1 <- "Survey was not conducted."}

if(Month == "03" | Month == "06" | Month == "09" | Month == "12"){
  SLC_SurveyStats <- Survey1 %>%
    filter(Estuary == "SL") %>%
    group_by(AnalysisDate, 
             Plot_Date,  
             RetDate,
             Estuary,  
             SectionName) %>%
    summarise(LiveMean = mean(Live, na.rm = T),
              LiveSD = sd(Live, na.rm = T),
              DeadMean = mean(Dead, na.rm = T),
              DeadSD = sd(Dead, na.rm = T))
}else{SLC_SurveyStats <- Survey1}

if(Month == "03" | Month == "06" | Month == "09" | Month == "12"){
  SLC1_SurveyStats <- Survey1 %>%
    filter(Estuary == "SL" & StationNumber == 1) %>%
    group_by(AnalysisDate, 
             Plot_Date,  
             RetDate,
             Estuary,  
             SectionName, 
             StationNumber) %>%
    summarise(LiveMean = mean(Live, na.rm = T),
              LiveSD = sd(Live, na.rm = T),
              DeadMean = mean(Dead, na.rm = T),
              DeadSD = sd(Dead, na.rm = T))
}else{SLC1_SurveyStats <- Survey1}

if(Month == "03" | Month == "06" | Month == "09" | Month == "12"){
  CR_SurveyStats <- Survey1 %>%
    filter(Estuary == "CR") %>%
    group_by(AnalysisDate, 
             Plot_Date,  
             RetDate,
             Estuary,  
             SectionName,
             StationNumber) %>%
    summarise(LiveMean = mean(Live, na.rm = T),
              LiveSD = sd(Live, na.rm = T),
              DeadMean = mean(Dead, na.rm = T),
              DeadSD = sd(Dead, na.rm = T))
}else{CR_SurveyStats <- Survey1}

```

```{r Missing data summary}
#
WQ_check <- WQ1 %>% filter(AnalysisDate > ReportStart) %>% mutate(StationNumber = case_when(is.na(Estuary) & (FixedLocationID %in% c('0242', '0246', '0261', '0269', '0230')) ~ 1, is.na(Estuary) & (FixedLocationID %in% c('0243', '0247', '0262', '0270')) ~ 2, is.na(Estuary) & (FixedLocationID %in% c('0244', '0249', '0264', '0271')) ~ 3, is.na(Estuary) & (FixedLocationID == '0233') ~ 4, TRUE ~ StationNumber), SectionName = case_when(is.na(Estuary) & (FixedLocationID %in% c('0242', '0243', '0244', '0261', '0262', '0264')) ~ 'N', is.na(Estuary) & (FixedLocationID %in% c('0246', '0247', '0249', '0269', '0270', '0271')) ~ 'S', TRUE ~ SectionName), Estuary = case_when(is.na(Estuary) & (FixedLocationID %in% c('0242', '0243', '0244', '0246', '0247', '0249')) ~ "LX", is.na(Estuary) & (FixedLocationID %in% c('0261', '0262', '0264', '0269', '0270', '0271')) ~ "SL", is.na(Estuary) & (FixedLocationID %in% c('0233', '0230')) ~ "CR", TRUE ~ Estuary)) %>% mutate(ID = paste0(Estuary, SectionName, "-", StationNumber)) %>% dplyr::select(ID, Temperature:SecchiPercent) %>% filter(is.na(Temperature) | is.na(Salinity) | is.na(DissolvedOxygen) | is.na(pH) | is.na(SecchiPercent))
#
Rcrt_check <- Recruit %>% filter(AnalysisDate > ReportStart) %>% mutate(StationNumber = case_when(is.na(Estuary) & (FixedLocationID %in% c('0242', '0246', '0261', '0269', '0230')) ~ 1, is.na(Estuary) & (FixedLocationID %in% c('0243', '0247', '0262', '0270')) ~ 2, is.na(Estuary) & (FixedLocationID %in% c('0244', '0249', '0264', '0271')) ~ 3, is.na(Estuary) & (FixedLocationID == '0233') ~ 4, TRUE ~ StationNumber), SectionName = case_when(is.na(Estuary) & (FixedLocationID %in% c('0242', '0243', '0244', '0261', '0262', '0264')) ~ 'N', is.na(Estuary) & (FixedLocationID %in% c('0246', '0247', '0249', '0269', '0270', '0271')) ~ 'S', TRUE ~ SectionName), Estuary = case_when(is.na(Estuary) & (FixedLocationID %in% c('0242', '0243', '0244', '0246', '0247', '0249')) ~ "LX", is.na(Estuary) & (FixedLocationID %in% c('0261', '0262', '0264', '0269', '0270', '0271')) ~ "SL", is.na(Estuary) & (FixedLocationID %in% c('0233', '0230')) ~ "CR", TRUE ~ Estuary)) %>% mutate(ID = paste0(Estuary, SectionName, "-", StationNumber), Stringer = case_when(as.numeric(str_sub(ShellID, -2)) < 7 ~ "1A", as.numeric(str_sub(ShellID, -2)) > 6 & as.numeric(str_sub(ShellID, -2)) < 13 ~ "1B", as.numeric(str_sub(ShellID, -2)) > 12 & as.numeric(str_sub(ShellID, -2)) < 19 ~ "2A", as.numeric(str_sub(ShellID, -2)) > 18 & as.numeric(str_sub(ShellID, -2)) < 25 ~ "2B", as.numeric(str_sub(ShellID, -2)) > 24 & as.numeric(str_sub(ShellID, -2)) < 31 ~ "3A", as.numeric(str_sub(ShellID, -2)) > 30 ~ "3B", TRUE ~ "TEMP")) %>% group_by(ID, Stringer) %>% summarise(MeanBott = mean(NumBottom)) %>% filter(is.na(MeanBott))
#
Dermo_check <- Dermo1 %>% filter(AnalysisDate > ReportStart) %>% mutate(StationNumber = case_when(is.na(Estuary) & (FixedLocationID %in% c('0242', '0246', '0261', '0269', '0230')) ~ 1, is.na(Estuary) & (FixedLocationID %in% c('0243', '0247', '0262', '0270')) ~ 2, is.na(Estuary) & (FixedLocationID %in% c('0244', '0249', '0264', '0271')) ~ 3, is.na(Estuary) & (FixedLocationID == '0233') ~ 4, TRUE ~ StationNumber), SectionName = case_when(is.na(Estuary) & (FixedLocationID %in% c('0242', '0243', '0244', '0261', '0262', '0264')) ~ 'N', is.na(Estuary) & (FixedLocationID %in% c('0246', '0247', '0249', '0269', '0270', '0271')) ~ 'S', TRUE ~ SectionName), Estuary = case_when(is.na(Estuary) & (FixedLocationID %in% c('0242', '0243', '0244', '0246', '0247', '0249')) ~ "LX", is.na(Estuary) & (FixedLocationID %in% c('0261', '0262', '0264', '0269', '0270', '0271')) ~ "SL", is.na(Estuary) & (FixedLocationID %in% c('0233', '0230')) ~ "CR", TRUE ~ Estuary)) %>% mutate(ID = paste0(Estuary, SectionName, "-", StationNumber)) %>% dplyr::select(ID, DermoMantle, DermoGill) %>% filter(is.na(DermoMantle) | is.na(DermoGill))
#
```

```{r Data summary tables}
#Output tables for SLC, SLC1, CR - combining WQ, Rcrt, Dermo, and Survey
SLC_Summary <- left_join(
  left_join(
    left_join(SLC_WQStats %>% ungroup() %>% dplyr::select(AnalysisDate, SalMean, SalSD),
              SLC_RecruitStats %>% ungroup() %>% dplyr::select(AnalysisDate, RcrtMean, RcrtSD)),
    SLC_DermoStats %>% ungroup() %>% dplyr::select(AnalysisDate, DermoPct)),
    #Add in survey data or placeholder if no survey conducted
  if(Month == "03" | Month == "06" | Month == "09" | Month == "12"){
    SLC_SurveyStats %>% ungroup() %>% dplyr::select(AnalysisDate, LiveMean:DeadSD) %>%
  mutate(Season = case_when(month(AnalysisDate) > 4 & month(AnalysisDate) < 10 ~ "WetSeason", TRUE ~ "DrySeason"), .before = LiveMean)
    }else{
      data.frame(AnalysisDate = SLC_WQStats$AnalysisDate, LiveMean = NA)
    }) %>%
  mutate(across(where(is.numeric), round, 2))


SLC1_Summary <- left_join(
  left_join(
    left_join(SLC1_WQStats %>% ungroup() %>% dplyr::select(AnalysisDate, SalMean, SalSD),
              SLC1_RecruitStats %>% ungroup() %>% 
                dplyr::select(AnalysisDate, RcrtMean, RcrtSD)),
    SLC1_DermoStats %>% ungroup() %>% dplyr::select(AnalysisDate, DermoPct)),
  #Add in survey data or placeholder if no survey conducted
  if(Month == "03" | Month == "06" | Month == "09" | Month == "12"){
    SLC1_SurveyStats %>% ungroup() %>% dplyr::select(AnalysisDate, LiveMean:DeadSD) %>%
      mutate(Season = case_when(month(AnalysisDate) > 4 & month(AnalysisDate) < 10 ~ "WetSeason", TRUE ~ "DrySeason"), .before = LiveMean)
    }else{
      data.frame(AnalysisDate = SLC1_WQStats$AnalysisDate, LiveMean = NA)
      }) %>%
  mutate(across(where(is.numeric), round, 2),
         Density = LiveMean,
         .after = DermoPct) 

CR_Summary <- data.frame()
for (i in list(unique(CR_WQStats$StationNumber))){
CR_i <- left_join(
    left_join(
      left_join(CR_WQStats %>% ungroup() %>% subset(StationNumber == i) %>%
                  dplyr::select(StationNumber, AnalysisDate, SalMean), 
                CR_RecruitStats %>% ungroup() %>% subset(StationNumber == i) %>%
                  dplyr::select(StationNumber, AnalysisDate, RcrtMean, RcrtSD)),
      CR_DermoStats %>% ungroup() %>% subset(StationNumber == i) %>%
        dplyr::select(StationNumber, AnalysisDate, DermoPct)),  #Add in survey data or placeholder if no survey conducted
  if(Month == "03" | Month == "06" | Month == "09" | Month == "12"){
    CR_SurveyStats %>% ungroup() %>% subset(StationNumber == i) %>%
      dplyr::select(StationNumber, AnalysisDate, LiveMean:DeadSD) %>%
      mutate(Season = case_when(month(AnalysisDate) > 4 & month(AnalysisDate) < 10 ~ "WetSeason", TRUE ~ "DrySeason"), .before = LiveMean)
  }else{
      data.frame(AnalysisDate = CR_WQStats$AnalysisDate, StationNumber = i, LiveMean = NA)
  }) %>%
  mutate(across(where(is.numeric), round, 2),
         Density = LiveMean,
         .after = DermoPct)

CR_Summary <- rbind(CR_Summary, CR_i)
CR_Summary <- if(Month == "03" | Month == "06" | Month == "09" | Month == "12"){CR_Summary %>% pivot_wider(names_from = StationNumber, values_from = c(3:12), names_glue = "{StationNumber}_{.value}")} else {CR_Summary %>% pivot_wider(names_from = StationNumber, values_from = c(3:8), names_glue = "{StationNumber}_{.value}")}

}

#Order columns for output - duplicate date for each station then arrange by stations
CR_Summary <- CR_Summary %>% mutate(AnalysisDate_B = AnalysisDate) %>%
  dplyr::select(AnalysisDate, starts_with("2_"), 
                AnalysisDate_B, everything())
```

```{r Survey Text}
#Text for survey section of monthly report
SLC_Srvy_note <- if(Month == "03" | Month == "06" | Month == "09" | Month == "12") {paste0("During the biannual ", if(Month == "03") {paste("spring")} else if(Month == "06") {paste("summer")} else if (Month == "09") {paste("fall")} else {paste("winter")}, " survey there were approximately ", round(SLC_SurveyStats$LiveMean,0), " live and ", round(SLC_SurveyStats$DeadMean,0), " dead oysters per 1 m2 quadrat.")} else {paste("Survey was not conducted this month")}

CRE_Srvy_note <- if(Month == "03" | Month == "06" | Month == "09" | Month == "12") {paste0("During the biannual ", if(Month == "03") {paste("spring")} else if(Month == "06") {paste("summer")} else if (Month == "09") {paste("fall")} else {paste("winter")}, " survey at Iona Cove there were approximately ", round((CR_SurveyStats %>% filter(SectionName == "E"))$LiveMean,0), " live and ", round((CR_SurveyStats %>% filter(SectionName == "E"))$DeadMean,0), " dead oysters per 1 m2 quadrat.")} else {paste("Survey was not conducted this month")}

CRW_Srvy_note <- if(Month == "03" | Month == "06" | Month == "09" | Month == "12") {paste0("During the biannual ", if(Month == "03") {paste("spring")} else if(Month == "06") {paste("summer")} else if (Month == "09") {paste("fall")} else {paste("winter")}, " survey at Bird Island there were approximately ", round((CR_SurveyStats %>% filter(SectionName == "W"))$LiveMean,0), " live and ", round((CR_SurveyStats %>% filter(SectionName == "W"))$DeadMean,0), " dead oysters per 1 m2 quadrat.")} else {paste("Survey was not conducted this month")}

```

```{r ReportText}
#Report Text in area below
```

## Report summary
This monthly report was compiled by `r Author` on `r format(Sys.Date(), "%d %B %Y")` and summarizes data for **CERP** sites in **`r MonYr`**. Analysis covers data occurring between *`r format(ReportStart, "%d %B %Y")`* and *`r format(ReportEnd, "%d %B %Y")`* at St. Lucie-Central and at Caloosahatchee River sites.\

## St. Lucie Central summary

Here is the monthly report with the data collected from the St. Lucie Estuary on `r max(SLC_WQStats$RetDate) %>% format("%B %d, %Y")`:

*	Mean salinity 
`r if(round((SLC_WQStats %>% filter(RetDate == min(SLC_WQStats$RetDate)))$SalMean,2) > round((SLC_WQStats %>% filter(RetDate == max(SLC_WQStats$RetDate)))$SalMean,2)) {paste("decreased")} else if (round((SLC_WQStats %>% filter(RetDate == min(SLC_WQStats$RetDate)))$SalMean,2) < round((SLC_WQStats %>% filter(RetDate == max(SLC_WQStats$RetDate)))$SalMean,2)) {paste("increased")} else {paste("stayed the same")}` 
from 
`r round((SLC_WQStats %>% filter(RetDate == min(SLC_WQStats$RetDate)))$SalMean,2)` 
in 
`r min(SLC_WQStats$RetDate) %>% format("%B")` 
to 
`r round((SLC_WQStats %>% filter(RetDate == max(SLC_WQStats$RetDate)))$SalMean,2)` 
in 
`r max(SLC_WQStats$RetDate) %>% format("%B")`.
*	The mean recruitment rate 
`r if(round((SLC_RecruitStats %>% filter(RetDate == min(SLC_RecruitStats$RetDate)))$RcrtMean,1) > round((SLC_RecruitStats %>% filter(RetDate == max(SLC_RecruitStats$RetDate)))$RcrtMean,1)) {paste("decreased")} else if (round((SLC_RecruitStats %>% filter(RetDate == min(SLC_RecruitStats$RetDate)))$RcrtMean,1) < round((SLC_RecruitStats %>% filter(RetDate == max(SLC_RecruitStats$RetDate)))$RcrtMean,1)) {paste("increased")} else {paste("stayed the same")}` 
from 
`r round((SLC_RecruitStats %>% filter(RetDate == min(SLC_RecruitStats$RetDate)))$RcrtMean,1)` 
spat/shell in 
`r min(SLC_RecruitStats$RetDate) %>% format("%B")` 
to 
`r round((SLC_RecruitStats %>% filter(RetDate == max(SLC_RecruitStats$RetDate)))$RcrtMean,1)` 
spat/shell in 
`r max(SLC_RecruitStats$RetDate) %>% format("%B")`.
*	Dermo prevalence 
`r if(round((SLC_DermoStats %>% filter(RetDate == min(SLC_DermoStats$RetDate)))$DermoPct,1) > round((SLC_DermoStats %>% filter(RetDate == max(SLC_DermoStats$RetDate)))$DermoPct,1)) {paste("decreased")} else if (round((SLC_DermoStats %>% filter(RetDate == min(SLC_DermoStats$RetDate)))$DermoPct,1) < round((SLC_DermoStats %>% filter(RetDate == max(SLC_DermoStats$RetDate)))$DermoPct,1)) {paste("increased")} else {paste("stayed the same")}` 
from
`r round((SLC_DermoStats %>% filter(RetDate == min(SLC_DermoStats$RetDate)))$DermoPct,1)`% 
in 
`r min(SLC_DermoStats$RetDate) %>% format("%B")` 
to 
`r round((SLC_DermoStats %>% filter(RetDate == max(SLC_DermoStats$RetDate)))$DermoPct,1)`% 
of the oysters sampled in
`r max(SLC_DermoStats$RetDate) %>% format("%B")`.
* `r if(Month == "03" | Month == "06"  | Month == "09" | Month == "12") {paste(SLC_Srvy_note)} else {paste("Survey was not conducted this month")}`
\

## Caloosahatchee River summary 

Here is the monthly report with data collected from Caloosahatchee on `r max(CR_WQStats$RetDate) %>% format("%B %d, %Y")`:

*	Mean salinity 
`r if(round((CR_WQStats %>% filter(SectionName == "E" & RetDate == min((CR_WQStats %>% filter(SectionName == "E"))$RetDate)))$SalMean,2) > round((CR_WQStats %>% filter(SectionName == "E" & RetDate == max((CR_WQStats %>% filter(SectionName == "E"))$RetDate)))$SalMean,2)) {paste("decreased")} else if (round((CR_WQStats %>% filter(SectionName == "E" & RetDate == min((CR_WQStats %>% filter(SectionName == "E"))$RetDate)))$SalMean,2) < round((CR_WQStats %>% filter(SectionName == "E" & RetDate == max((CR_WQStats %>% filter(SectionName == "E"))$RetDate)))$SalMean,2)) {paste("increased")} else {paste("stayed the same")}` 
from 
`r round((CR_WQStats %>% filter(SectionName == "E" & RetDate == min((CR_WQStats %>% filter(SectionName == "E"))$RetDate)))$SalMean,2)` 
in 
`r min((CR_WQStats %>% filter(SectionName == "E"))$RetDate) %>% format("%B")` 
to 
`r round((CR_WQStats %>% filter(SectionName == "E" & RetDate == max((CR_WQStats %>% filter(SectionName == "E"))$RetDate)))$SalMean,2)` 
in 
`r max((CR_WQStats %>% filter(SectionName == "E"))$RetDate) %>% format("%B")`
at the Iona Cove station and 
`r if(round((CR_WQStats %>% filter(SectionName == "W" & RetDate == min((CR_WQStats %>% filter(SectionName == "W"))$RetDate)))$SalMean,2) > round((CR_WQStats %>% filter(SectionName == "W" & RetDate == max((CR_WQStats %>% filter(SectionName == "W"))$RetDate)))$SalMean,2)) {paste("decreased")} else if (round((CR_WQStats %>% filter(SectionName == "W" & RetDate == min((CR_WQStats %>% filter(SectionName == "W"))$RetDate)))$SalMean,2) < round((CR_WQStats %>% filter(SectionName == "W" & RetDate == max((CR_WQStats %>% filter(SectionName == "W"))$RetDate)))$SalMean,2)) {paste("increased")} else {paste("stayed the same")}` 
from 
`r round((CR_WQStats %>% filter(SectionName == "W" & RetDate == min((CR_WQStats %>% filter(SectionName == "W"))$RetDate)))$SalMean,2)` 
in 
`r min((CR_WQStats %>% filter(SectionName == "W"))$RetDate) %>% format("%B")` 
to 
`r round((CR_WQStats %>% filter(SectionName == "W" & RetDate == max((CR_WQStats %>% filter(SectionName == "W"))$RetDate)))$SalMean,2)` 
in 
`r max((CR_WQStats %>% filter(SectionName == "W"))$RetDate) %>% format("%B")`
at the Bird Island station.
*	The mean recruitment rate 
`r if(round((CR_RecruitStats %>% filter(SectionName == "E" & RetDate == min((CR_RecruitStats %>% filter(SectionName == "E"))$RetDate)))$RcrtMean,1) > round((CR_RecruitStats %>% filter(SectionName == "E" & RetDate == max((CR_RecruitStats %>% filter(SectionName == "E"))$RetDate)))$RcrtMean,1)) {paste("decreased")} else if (round((CR_RecruitStats %>% filter(SectionName == "E" & RetDate == min((CR_RecruitStats %>% filter(SectionName == "E"))$RetDate)))$RcrtMean,1) < round((CR_RecruitStats %>% filter(SectionName == "E" & RetDate == max((CR_RecruitStats %>% filter(SectionName == "E"))$RetDate)))$RcrtMean,1)) {paste("increased")} else {paste("stayed the same")}` 
from 
`r round((CR_RecruitStats %>% filter(SectionName == "E" & RetDate == min((CR_RecruitStats %>% filter(SectionName == "E"))$RetDate)))$RcrtMean,1)` 
spat/shell in 
`r min((CR_RecruitStats %>% filter(SectionName == "E"))$RetDate) %>% format("%B")` 
to 
`r round((CR_RecruitStats %>% filter(SectionName == "E" & RetDate == max((CR_RecruitStats %>% filter(SectionName == "E"))$RetDate)))$RcrtMean,1)` 
spat/shell in 
`r max((CR_RecruitStats %>% filter(SectionName == "E"))$RetDate) %>% format("%B")`
at the Iona Cove station and
`r if(round((CR_RecruitStats %>% filter(SectionName == "W" & RetDate == min((CR_RecruitStats %>% filter(SectionName == "W"))$RetDate)))$RcrtMean,1) > round((CR_RecruitStats %>% filter(SectionName == "W" & RetDate == max((CR_RecruitStats %>% filter(SectionName == "W"))$RetDate)))$RcrtMean,1)) {paste("decreased")} else if (round((CR_RecruitStats %>% filter(SectionName == "W" & RetDate == min((CR_RecruitStats %>% filter(SectionName == "W"))$RetDate)))$RcrtMean,1) < round((CR_RecruitStats %>% filter(SectionName == "W" & RetDate == max((CR_RecruitStats %>% filter(SectionName == "W"))$RetDate)))$RcrtMean,1)) {paste("increased")} else {paste("stayed the same")}` 
from 
`r round((CR_RecruitStats %>% filter(SectionName == "W" & RetDate == min((CR_RecruitStats %>% filter(SectionName == "W"))$RetDate)))$RcrtMean,1)` 
spat/shell in 
`r min((CR_RecruitStats %>% filter(SectionName == "W"))$RetDate) %>% format("%B")` 
to 
`r round((CR_RecruitStats %>% filter(SectionName == "W" & RetDate == max((CR_RecruitStats %>% filter(SectionName == "W"))$RetDate)))$RcrtMean,1)` 
spat/shell in 
`r max((CR_RecruitStats %>% filter(SectionName == "W"))$RetDate) %>% format("%B")`
at the Bird Island station.
*	Dermo prevalence 
`r if(round((CR_DermoStats %>% filter(SectionName == "E" & RetDate == min((CR_DermoStats %>% filter(SectionName == "E"))$RetDate)))$DermoPct,1) > round((CR_DermoStats %>% filter(SectionName == "E" & RetDate == max((CR_DermoStats %>% filter(SectionName == "E"))$RetDate)))$DermoPct,1)) {paste("decreased")} else if (round((CR_DermoStats %>% filter(SectionName == "E" & RetDate == min((CR_DermoStats %>% filter(SectionName == "E"))$RetDate)))$DermoPct,1) < round((CR_DermoStats %>% filter(SectionName == "E" & RetDate == max((CR_DermoStats %>% filter(SectionName == "E"))$RetDate)))$DermoPct,1)) {paste("increased")} else {paste("stayed the same")}` 
from
`r round((CR_DermoStats %>% filter(SectionName == "E" & RetDate == min((CR_DermoStats %>% filter(SectionName == "E"))$RetDate)))$DermoPct,1)`% 
in 
`r min((CR_DermoStats %>% filter(SectionName == "E"))$RetDate) %>% format("%B")` 
to 
`r round((CR_DermoStats %>% filter(SectionName == "E" & RetDate == max((CR_DermoStats %>% filter(SectionName == "E"))$RetDate)))$DermoPct,1)`% 
in
`r max((CR_DermoStats %>% filter(SectionName == "E"))$RetDate) %>% format("%B")`
at the Iona Cove station and 
`r if(round((CR_DermoStats %>% filter(SectionName == "W" & RetDate == min((CR_DermoStats %>% filter(SectionName == "W"))$RetDate)))$DermoPct,1) > round((CR_DermoStats %>% filter(SectionName == "W" & RetDate == max((CR_DermoStats %>% filter(SectionName == "W"))$RetDate)))$DermoPct,1)) {paste("decreased")} else if (round((CR_DermoStats %>% filter(SectionName == "W" & RetDate == min((CR_DermoStats %>% filter(SectionName == "W"))$RetDate)))$DermoPct,1) < round((CR_DermoStats %>% filter(SectionName == "W" & RetDate == max((CR_DermoStats %>% filter(SectionName == "W"))$RetDate)))$DermoPct,1)) {paste("increased")} else {paste("stayed the same")}` 
from
`r round((CR_DermoStats %>% filter(SectionName == "W" & RetDate == min((CR_DermoStats %>% filter(SectionName == "W"))$RetDate)))$DermoPct,1)`% 
in 
`r min((CR_DermoStats %>% filter(SectionName == "W"))$RetDate) %>% format("%B")` 
to 
`r round((CR_DermoStats %>% filter(SectionName == "W" & RetDate == max((CR_DermoStats %>% filter(SectionName == "W"))$RetDate)))$DermoPct,1)`% 
in
`r max((CR_DermoStats %>% filter(SectionName == "W"))$RetDate) %>% format("%B")` 
at the Bird Island station.
*	`r if(Month == "03" | Month == "06" | Month == "09" | Month == "12") {paste(CRE_Srvy_note, CRW_Srvy_note, sep = " ")} else {paste("Survey was not conducted this month")}`
\
\

## CERP missing data

**Any samples listed below were missing in `r paste(MonYr)`:**
\
\
*Water quality*
\
`r if(nrow(WQ_check) > 0) {flextable(WQ_checks) %>% align(align = "center", part = "all")  %>% autofit() %>% font(fontname = "Arial", part = "all")} else {paste("No missing water quality data.")}`
\
\
*Recruitment*
\
`r if(nrow(Rcrt_check) > 0) {flextable(Rcrt_check %>% dplyr::select(-MeanBott)) %>% align(align = "center", part = "all")  %>% autofit() %>% font(fontname = "Arial", part = "all")} else {paste("No missing recruitment data.")}`
\
\
*Dermo*
\
`r if(nrow(Dermo_check) > 0) {flextable(Dermo_check) %>% align(align = "center", part = "all")  %>% autofit() %>% font(fontname = "Arial", part = "all")} else {paste("No missing dermo data.")}`
\
\

\newpage
<!---BLOCK_LANDSCAPE_START--->
## Data summary output (for Excel files)
*The following data updates the "CERPMonthlyReportData" [Excel file](...).*
\
Here is the data summary output for SLC on the "Monthly CERP data" Excel sheet:
```{r echo=FALSE, results='asis'}
flextable(SLC_Summary) %>% align(align = "center") %>% set_table_properties(width = 0.2) %>% font(fontname = "Arial", part = "all") %>% fontsize(size = 10, part = "all") %>% fontsize(size = 9, part = "header") 
```
\
Here is the data summary output for CRE and CRW on the "Monthly CR data" Excel sheet:
```{r echo=FALSE, results='asis'}
flextable(CR_Summary %>% dplyr::select(AnalysisDate, starts_with("2"))) %>% align(align = "center") %>% set_table_properties(width = 0.15) %>%  font(fontname = "Arial", part = "all") %>% fontsize(size = 10, part = "all") %>% fontsize( size = 9, part = "header") 

flextable(CR_Summary %>% dplyr::select(AnalysisDate_B, starts_with("3"))) %>% align(align = "center") %>% set_table_properties(width = 0.15) %>%  font(fontname = "Arial", part = "all") %>% fontsize(size = 10, part = "all") %>% fontsize(size = 9, part = "header")
```
\
\
\
*The following data updates the "CERPMonthlyReportData_Rio_Station (05-Present)" [Excel file](...).*
\
Here is the data summary output for St. Lucie-Central station 1 on the "SLC_1" Excel sheet:
```{r echo=FALSE, results='asis'}
flextable(SLC1_Summary) %>% align(align = "center") %>% set_table_properties(width = 0.15) %>% font(fontname = "Arial", part = "all") %>% fontsize(size = 10, part = "all") %>% fontsize(size = 9, part = "header") 
```
<!---BLOCK_LANDSCAPE_STOP--->