---
title: "PBC Monthly Report - `r params$Year`-`r params$Month`"
output: word_document
params: 
  Month: "11"  #Enter 2-digit month
  Year: "2023" #Enter 4-digit year

knit: (function(inputFile, encoding) {
  rmarkdown::render(
    input = inputFile, encoding = encoding,
    output_file = paste0(substr(inputFile, 1, nchar(inputFile)-4), " - ",
    with(rmarkdown::yaml_front_matter(inputFile), paste(params$Year, params$Month)), " - ",
     format(Sys.Date(), "%b %d %y"), '.docx'))
      })
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

Author <- c("E Levine") #Change to your name
Month <- params$Month 
Year <- params$Year 
#######File locations required to be updated for use.

Survey <- ifelse(as.numeric(Month) > 11 | as.numeric(Month) < 3, paste0("Winter", Year),
                 ifelse(as.numeric(Month) > 2 & as.numeric(Month) < 6, paste0("Spring", Year),
                        ifelse(as.numeric(Month) > 5 & as.numeric(Month) < 9, paste0("Summer", Year), paste0("Fall", Year))))
```

```{r Packages, base DFs, and time frame}
#Load required packages
if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, dplyr,  #DF manipulation
               readxl,          #Excel
               lubridate,         #Dates
               knitr, here,
               flextable, officer,
               install = TRUE)

#Load required data - salinity, recruitment, dermo, survey counts
WaterQual <- read_excel("...", sheet = "RawData", skip = 2, col_names = TRUE, na = c("", "Z"), trim_ws = TRUE, .name_repair = "universal") %>% 
  filter(!grepl('Proof', Date)) %>%
  mutate(Date = as.Date(as.numeric(Date), origin = "1899-12-30")) %>% drop_na(Date)

Rcrt_df <- read_excel("...", sheet = "Spat", skip = 2, col_names = TRUE, na = c("", "Z"), trim_ws = TRUE, .name_repair = "universal")  %>% drop_na(Ret.Date)

Dermo_df <- read_excel("...", sheet = "Dermo", skip = 3, col_names = TRUE, na = c("", "Z"), trim_ws = TRUE, .name_repair = "universal") %>% drop_na(Date)

Sedi_df <- read_excel("...", sheet = "Final Data", skip = 3, col_names = TRUE, na = c("", "Z", "z"), trim_ws = TRUE, .name_repair = "universal") %>% drop_na(Dep.Date)

Survey_df <- if(Month == "03" | Month == "09"){read_excel(paste0("...",Survey, ".xlsx"), sheet = "Counts", skip = 3, col_names = TRUE, na = c("", "Z"), trim_ws = TRUE, .name_repair = "universal") %>% drop_na()} else {"Survey was not conducted"}

MonYr <- paste(month.abb[as.numeric(Month)], Year, sep = " ")
Start_date <- as.Date(paste(Year, Month, "01", sep = "-")) - months(1)
End_date <- format(ceiling_date(Start_date %m+% months(2)) - days(1), "%Y-%m-%d")
```

```{r Data filtering}
Sal <- WaterQual %>% filter(Date >= Start_date & Date <= End_date) %>% 
  mutate(Month = format(Date, "%B")) #Add month for summary output

Rcrt <- Rcrt_df %>% filter(Ret.Date >= Start_date & Ret.Date <= End_date) %>% 
  mutate(Station = as.factor(Station),
         Month = format(Ret.Date, "%B"), #Add month for summary output
         Shell = as.numeric(sub(" .*", "", Shell)), #Remove " - Top" from shell numbers
         Bottom = ifelse((Shell > 1 & Shell < 6) | (Shell > 7 & Shell < 12), ..Bottom, NA)) #Drop 1, 6, 7, 12 from bottom shells

Dermo <- Dermo_df %>% filter(Date >= Start_date & Date <= End_date) %>% 
  mutate(Month = format(Date, "%B"), #Add month for summary output
         DermoSum = ifelse(rowSums(select(., contains("Dermo"))) >0, 1, 0)) #Dermo presence(1)/absence(0)

Sedi <- Sedi_df %>% filter(Ret.Date >= Start_date & Ret.Date <= End_date) %>%
  mutate(Month = format(Ret.Date, "%B"), #Add month for summary output
         Station = factor(Station, levels = c("LWR4", "LWL1", "LWL2", "LWR2", "LWR3", "LWL3")),
         Position = as.factor(ifelse(Station == "LWR4" | Station == "LWL1" | Station == "LWL2", "N", "S")))

Srvy <- if(Month == "03" | Month == "09") {Survey_df %>% 
    mutate(Month = format(Date, "%B"),
           Live = ..1.4.m2..Live*4,
           Dead = ..1.4.m2..Dead*4)} else {"Survey was not conducted"} #Add month for summary output

```

```{r Data summary}
Sal_summary <- Sal %>% group_by(Month, Site) %>% 
  summarise(meanSal = round(mean(Salinity..ppt., na.rm = T),2)) #Monthly mean

Rcrt_summary <- Rcrt %>% group_by(Month, Site) %>% 
  summarise(meanRcrt = round(mean(Bottom/(Num.Days/28), na.rm = T),2)) #Monthly mean

Dermo_summary <- Dermo %>% group_by(Month, Site) %>%
  summarise(Percent = round(sum(DermoSum, na.rm = T)/n()*100, 2))

Sedi_summary <- Sedi %>% group_by(Month, Station) %>%
  summarise(Month_Rate = round(mean(Total.Sediment.Dry.Weight/(Days.Deployed/28), na.rm = T),2),
            Mean_Pct_Organic = round(mean(..Total.Organic, na.rm = T),2))

Sedi_NS_summary <- Sedi %>% group_by(Month, Position) %>%
  summarise(Month_Rate = round(mean(Total.Sediment.Dry.Weight/(Days.Deployed/28), na.rm = T),2),
            Mean_Pct_Organic = round(mean(..Total.Organic, na.rm = T),2))

Srvy_summary <- if(Month == "03" | Month == "09") {Srvy %>% group_by(Month, Site) %>%
    summarise(meanLive = round(mean(Live, na.rm = T),0),
              meanDead = round(mean(Dead, na.rm = T),0))} else {"Survey was not conducted."}

LW_Srvy_note <- if(Month == "03" | Month == "09") {paste0("During the biannual ", if(Month == "03") {paste("spring")} else {paste("fall")}, " survey there were ", (Srvy_summary %>% filter(Site == "LW"))$meanLive, " live and ", (Srvy_summary %>% filter(Site == "LW"))$meanDead, " dead oysters per 1 m2 quadrat.")} else {paste("Survey was not conducted this month")}

LWR_Srvy_note <- if(Month == "03" | Month == "09") {paste0("During the biannual ", if(Month == "03") {paste("spring")} else {paste("fall")}, " survey there were ", (Srvy_summary %>% filter(Site == "LW-R"))$meanLive, " live and ", (Srvy_summary %>% filter(Site == "LW-R"))$meanDead, " dead oysters per 1 m2 quadrat.")} else {paste("Survey was not conducted this month")}
```

## Report summary
Compiled by: `r Author` on `r format(Sys.Date(), "%d %B %Y")`.\
This report details data for **Palm Beach County** in **`r MonYr`**.
Analysis covers data occurring between *`r Start_date`* and *`r End_date`* at natural reef and restored reef stations.\

##Lake Worth Lagoon summary

Here is the monthly report with the data collected from the Lake Worth Lagoon stations on `r max(Sal$Date) %>% format("%B %d, %Y")`:

*	Mean salinity 
`r if((Sal_summary %>% filter(Site == "LW" & Month == min(Sal$Date) %>% format("%B")))$meanSal > (Sal_summary %>% filter(Site == "LW" & Month == max(Sal$Date) %>% format("%B")))$meanSal) {paste("decreased")} else if ((Sal_summary %>% filter(Site == "LW" & Month == min(Sal$Date) %>% format("%B")))$meanSal < (Sal_summary %>% filter(Site == "LW" & Month == max(Sal$Date) %>% format("%B")))$meanSal) {paste("increased")} else {paste("stayed the same")}` 
from 
`r (Sal_summary %>% filter(Site == "LW" & Month == min(Sal$Date) %>% format("%B")))$meanSal` 
in 
`r min(Sal$Date) %>% format("%B")` 
to 
`r (Sal_summary %>% filter(Site == "LW" & Month == max(Sal$Date) %>% format("%B")))$meanSal` 
in 
`r max(Sal$Date) %>% format("%B")`.
*	The mean recruitment rate 
`r if((Rcrt_summary %>% filter(Site == "LW" & Month == min(Rcrt$Ret.Date) %>% format("%B")))$meanRcrt > (Rcrt_summary %>% filter(Site == "LW" & Month == max(Rcrt$Ret.Date) %>% format("%B")))$meanRcrt) {paste("decreased")} else if ((Rcrt_summary %>% filter(Site == "LW" & Month == min(Rcrt$Ret.Date) %>% format("%B")))$meanRcrt < (Rcrt_summary %>% filter(Site == "LW" & Month == max(Rcrt$Ret.Date) %>% format("%B")))$meanRcrt) {paste("increased")} else {paste("stayed the same")}` 
from 
`r (Rcrt_summary %>% filter(Site == "LW" & Month == min(Rcrt$Ret.Date) %>% format("%B")))$meanRcrt` 
spat/shell in 
`r min(Rcrt$Ret.Date) %>% format("%B")` 
to 
`r (Rcrt_summary %>% filter(Site == "LW" & Month == max(Rcrt$Ret.Date) %>% format("%B")))$meanRcrt` 
spat/shell in 
`r max(Rcrt$Ret.Date) %>% format("%B")`.
*	Dermo prevalence 
`r if((Dermo_summary %>% filter(Site == "LW" & Month == min(Dermo$Date) %>% format("%B")))$Percent > (Dermo_summary %>% filter(Site == "LW" & Month == max(Dermo$Date) %>% format("%B")))$Percent) {paste("decreased")} else if ((Dermo_summary %>% filter(Site == "LW" & Month == min(Dermo$Date) %>% format("%B")))$Percent < (Dermo_summary %>% filter(Site == "LW" & Month == max(Dermo$Date) %>% format("%B")))$Percent) {paste("increased")} else {paste("stayed the same")}` 
from
`r (Dermo_summary %>% filter(Site == "LW" & Month == min(Dermo$Date) %>% format("%B")))$Percent`% 
in 
`r min(Dermo$Date) %>% format("%B")` 
to 
`r (Dermo_summary %>% filter(Site == "LW" & Month == max(Dermo$Date) %>% format("%B")))$Percent`% 
in
`r max(Dermo$Date) %>% format("%B")`.
* `r if(Month == "03" | Month == "09") {paste(LW_Srvy_note)} else {paste("Survey was not conducted this month.")}`

\
\
##Lake Worth Restoration summary 

Here is the monthly report with data collected from the Lake Worth Restoration stations on `r max(Sal$Date) %>% format("%B %d, %Y")`:

*	Mean salinity 
`r if((Sal_summary %>% filter(Site == "LW-R" & Month == min(Sal$Date) %>% format("%B")))$meanSal > (Sal_summary %>% filter(Site == "LW-R" & Month == max(Sal$Date) %>% format("%B")))$meanSal) {paste("decreased")} else if ((Sal_summary %>% filter(Site == "LW-R" & Month == min(Sal$Date) %>% format("%B")))$meanSal < (Sal_summary %>% filter(Site == "LW-R" & Month == max(Sal$Date) %>% format("%B")))$meanSal) {paste("increased")} else {paste("stayed the same")}` 
from 
`r (Sal_summary %>% filter(Site == "LW-R" & Month == min(Sal$Date) %>% format("%B")))$meanSal` 
in 
`r min(Sal$Date) %>% format("%B")` 
to 
`r (Sal_summary %>% filter(Site == "LW-R" & Month == max(Sal$Date) %>% format("%B")))$meanSal` 
in 
`r max(Sal$Date) %>% format("%B")`.
*	The mean recruitment rate 
`r if((Rcrt_summary %>% filter(Site == "LW-R" & Month == min(Rcrt$Ret.Date) %>% format("%B")))$meanRcrt > (Rcrt_summary %>% filter(Site == "LW-R" & Month == max(Rcrt$Ret.Date) %>% format("%B")))$meanRcrt) {paste("decreased")} else if ((Rcrt_summary %>% filter(Site == "LW-R" & Month == min(Rcrt$Ret.Date) %>% format("%B")))$meanRcrt < (Rcrt_summary %>% filter(Site == "LW-R" & Month == max(Rcrt$Ret.Date) %>% format("%B")))$meanRcrt) {paste("increased")} else {paste("stayed the same")}` 
from 
`r (Rcrt_summary %>% filter(Site == "LW-R" & Month == min(Rcrt$Ret.Date) %>% format("%B")))$meanRcrt` 
spat/shell in 
`r min(Rcrt$Ret.Date) %>% format("%B")` 
to 
`r (Rcrt_summary %>% filter(Site == "LW-R" & Month == max(Rcrt$Ret.Date) %>% format("%B")))$meanRcrt` 
spat/shell in 
`r max(Rcrt$Ret.Date) %>% format("%B")`.
*	Dermo prevalence 
`r if((Dermo_summary %>% filter(Site == "LW-R" & Month == min(Dermo$Date) %>% format("%B")))$Percent > (Dermo_summary %>% filter(Site == "LW-R" & Month == max(Dermo$Date) %>% format("%B")))$Percent) {paste("decreased")} else if ((Dermo_summary %>% filter(Site == "LW-R" & Month == min(Dermo$Date) %>% format("%B")))$Percent < (Dermo_summary %>% filter(Site == "LW-R" & Month == max(Dermo$Date) %>% format("%B")))$Percent) {paste("increased")} else {paste("stayed the same")}` 
from
`r (Dermo_summary %>% filter(Site == "LW-R" & Month == min(Dermo$Date) %>% format("%B")))$Percent`% 
in 
`r min(Dermo$Date) %>% format("%B")` 
to 
`r (Dermo_summary %>% filter(Site == "LW-R" & Month == max(Dermo$Date) %>% format("%B")))$Percent`% 
in
`r max(Dermo$Date) %>% format("%B")`.
*	`r if(Month == "03" | Month == "09") {paste(LWR_Srvy_note)} else {paste("Survey was not conducted this month.")}`

##Lake Worth sediment trap summary 

Here is the monthly report with data collected from the Lake Worth Lagoon and Lake Worth Restoration stations on `r max(Sal$Date) %>% format("%B %d, %Y")`:

* The mean monthly sedimentation rate at the stations north of the C-51 output 
`r if((Sedi_NS_summary %>% filter(Position == "N" & Month == min(Sedi$Ret.Date) %>% format("%B")))$Month_Rate > (Sedi_NS_summary %>% filter(Position == "N" & Month == max(Sedi$Ret.Date) %>% format("%B")))$Month_Rate) {paste("decreased")} else if ((Sedi_NS_summary %>% filter(Position == "N" & Month == min(Sedi$Ret.Date) %>% format("%B")))$Month_Rate < (Sedi_NS_summary %>% filter(Position == "N" & Month == max(Sedi$Ret.Date) %>% format("%B")))$Month_Rate) {paste("increased")} else {paste("stayed the same")}` 
from 
`r (Sedi_NS_summary %>% filter(Position == "N" & Month == min(Sedi$Ret.Date) %>% format("%B")))$Month_Rate`
g/month in 
`r min(Sedi$Ret.Date) %>% format("%B")` 
to 
`r (Sedi_NS_summary %>% filter(Position == "N" & Month == max(Sedi$Ret.Date) %>% format("%B")))$Month_Rate`
g/month in
`r max(Sedi$Ret.Date) %>% format("%B")`,
and the mean percent organic content
`r if((Sedi_NS_summary %>% filter(Position == "N" & Month == min(Sedi$Ret.Date) %>% format("%B")))$Mean_Pct_Organic > (Sedi_NS_summary %>% filter(Position == "N" & Month == max(Sedi$Ret.Date) %>% format("%B")))$Mean_Pct_Organic) {paste("decreased")} else if ((Sedi_NS_summary %>% filter(Position == "N" & Month == min(Sedi$Ret.Date) %>% format("%B")))$Mean_Pct_Organic < (Sedi_NS_summary %>% filter(Position == "N" & Month == max(Sedi$Ret.Date) %>% format("%B")))$Mean_Pct_Organic) {paste("increased")} else {paste("stayed the same")}` 
from 
`r (Sedi_NS_summary %>% filter(Position == "N" & Month == min(Sedi$Ret.Date) %>% format("%B")))$Mean_Pct_Organic`%
in 
`r min(Sedi$Ret.Date) %>% format("%B")` 
to 
`r (Sedi_NS_summary %>% filter(Position == "N" & Month == max(Sedi$Ret.Date) %>% format("%B")))$Mean_Pct_Organic`%
in
`r max(Sedi$Ret.Date) %>% format("%B")`.
* The mean monthly sedimentation rate at the stations south of the C-51 output 
`r if((Sedi_NS_summary %>% filter(Position == "S" & Month == min(Sedi$Ret.Date) %>% format("%B")))$Month_Rate > (Sedi_NS_summary %>% filter(Position == "S" & Month == max(Sedi$Ret.Date) %>% format("%B")))$Month_Rate) {paste("decreased")} else if ((Sedi_NS_summary %>% filter(Position == "S" & Month == min(Sedi$Ret.Date) %>% format("%B")))$Month_Rate < (Sedi_NS_summary %>% filter(Position == "S" & Month == max(Sedi$Ret.Date) %>% format("%B")))$Month_Rate) {paste("increased")} else {paste("stayed the same")}` 
from 
`r (Sedi_NS_summary %>% filter(Position == "S" & Month == min(Sedi$Ret.Date) %>% format("%B")))$Month_Rate`
g/month in 
`r min(Sedi$Ret.Date) %>% format("%B")` 
to 
`r (Sedi_NS_summary %>% filter(Position == "S" & Month == max(Sedi$Ret.Date) %>% format("%B")))$Month_Rate`
g/month in
`r max(Sedi$Ret.Date) %>% format("%B")`,
and the mean percent organic content
`r if((Sedi_NS_summary %>% filter(Position == "S" & Month == min(Sedi$Ret.Date) %>% format("%B")))$Mean_Pct_Organic > (Sedi_NS_summary %>% filter(Position == "S" & Month == max(Sedi$Ret.Date) %>% format("%B")))$Mean_Pct_Organic) {paste("decreased")} else if ((Sedi_NS_summary %>% filter(Position == "S" & Month == min(Sedi$Ret.Date) %>% format("%B")))$Mean_Pct_Organic < (Sedi_NS_summary %>% filter(Position == "S" & Month == max(Sedi$Ret.Date) %>% format("%B")))$Mean_Pct_Organic) {paste("increased")} else {paste("stayed the same")}` 
from 
`r (Sedi_NS_summary %>% filter(Position == "S" & Month == min(Sedi$Ret.Date) %>% format("%B")))$Mean_Pct_Organic`%
in 
`r min(Sedi$Ret.Date) %>% format("%B")` 
to 
`r (Sedi_NS_summary %>% filter(Position == "S" & Month == max(Sedi$Ret.Date) %>% format("%B")))$Mean_Pct_Organic`%
in
`r max(Sedi$Ret.Date) %>% format("%B")`.
\
\
```{r echo=FALSE, restults = 'asis'}
#Create base table
Sedi_table <- Sedi_summary %>% rename("Monthly rate (g/month)" = Month_Rate, "Mean % Organic" = Mean_Pct_Organic) %>% pivot_wider(id_cols = Station, names_from = Month, values_from = c("Monthly rate (g/month)", "Mean % Organic"), names_glue = "{Month}_{.value}")

flextable(Sedi_table) %>% separate_header() %>% align(align = "center") %>% 
  hline(i = 3, border = officer::fp_border(style = "dashed")) %>% autofit()
```