---
title: "F5595 Final Figures"
author: "ELevine"
date: "`r Sys.Date()`"
output: 
  word_document: 
    reference_docx: Monthly-Reports-template.docx
    fig_caption: yes
geometry: "margin=1in"
params:
  Start_date: "2023-10-01"
  End_date: "2025-09-30"
  Excel_name: "PBC_5595"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
# make sure to check flow scale ranges when plotting Sal/Flow plots
Estuary_code <- c("LW", "LW-L", "LW-R")
Start_date <- as.Date(params$Start_date)
End_date <- as.Date(params$End_date)

#Packages
if (!require("pacman")) {install.packages("pacman")}
#p_unlock()
pacman::p_load(odbc, DBI, dbplyr,
  tidyverse, dplyr,  stringr, #DF manipulation
  DT, openxlsx,         #Excel
  lubridate, zoo,         #Dates
  knitr, kableExtra, scales, gt, gtExtras, ggpubr, ggpattern, magick, 
  flextable, officer,
  gridExtra, grid,
  install = TRUE)
```

```{r FigureFormatting, include = FALSE}
#
PBC_sites <- c("LWL", "LWR")
LWL_stations <- c("LWL1", "LWL2", "LWL3")
LWR_stations <- c("LWR2", "LWR3", "LWR4")
#
# Station information
StationInfo <- data.frame(
  Group = c("Lake Worth", "Lake Worth", "Lake Worth", "Lake Worth-Restoration", "Lake Worth-Restoration", "Lake Worth-Restoration"),
  Type = c("Natural", "Natural", "Natural", "Restored", "Restored", "Restored"),
  Station = c("1", "2", "3", "2", "3", "4"), 
  StationName = c("Audubon Island", "John's Island", "Hypoluxo Bird Island", "Grassy Flats", "Snook Island", "Tarpon Cove")
)
#
#Shared formatting for figure consistency
BaseForm <- theme_classic() +
  theme(panel.border = element_rect(color = "black", fill = NA), #Add border
        axis.title = element_text(family = "serif", color = "black", size = 17), axis.title.x = element_text(margin = margin(t = 12)), #Adjust axis title and text
        axis.text = element_text(family = "serif", color = "black", size = 12), 
        axis.text.x = element_text(angle = 45, hjust = 0.9),
        axis.line = element_line(color = "black"),
        axis.ticks.length.x = unit(0.10, "cm"),
        axis.ticks.length.y = unit(0.15, "cm"))
Xnudge <- theme(axis.text.x = element_text(hjust = 1.1))

Survey_legend <- theme(legend.position = "inside", legend.position.inside = c(.25, .97), legend.justification = c("left", "top"), legend.box.just = "left", #legend.box.spacing = unit(0.05, "lines"), #Adjust legend position
                     legend.background = element_rect(color = "black", fill = "white", linetype = "solid"),
                     legend.title = element_blank(), legend.key.spacing.y = unit(0.20, "lines"),
                     legend.key.width = unit(0.0001, "pt"), legend.key.height = unit(0.000001, "pt"), #Adjust legend title and spacing
                     legend.text = element_text(family = "serif", color = "black", size = 12))

Legend <- theme(legend.position = "inside", legend.position.inside = c(.005, .97), legend.justification = c("left", "top"), legend.box.just = "left", legend.box.spacing = unit(0.15, "lines"), #Adjust legend position
                     legend.background = element_rect(color = "black", fill = "white", linetype = "solid"),
                     legend.title = element_blank(), legend.key.height = unit(0.7, "lines"), legend.key.spacing.y = unit(0.25, "lines"),
                     legend.key.width = unit(1.5, "lines"), #Adjust legend title and spacing
                     legend.text = element_text(family = "serif", color = "black", size = 12))

FacetForm <- theme(strip.placement = "outside", strip.text.x.top = element_text(vjust = 1, hjust = 0, size = 13, family = "serif"), strip.clip = "off", panel.spacing.y = unit(0.5, "lines"), strip.background = element_blank())

PlotTitle <- theme(plot.title = element_text(size = 13, family = "serif", margin = margin(b = 0.07, t = 0.025)))

#Color and shape to station number
Stat_pal <- c(rgb(0, 0, 228, maxColorValue = 255), rgb(245, 0, 0, maxColorValue = 255), rgb(0, 118, 0, maxColorValue = 255), rgb(102, 0, 102, maxColorValue = 255))
Stations <- c("1" = "Station 1", "2" = "Station 2", "3" = "Station 3", "4" = "Station 4") 
Station_fill <- scale_fill_manual("", labels = Stations, values = setNames(Stat_pal, 1:4), na.value = "#999999")
Station_color <- scale_color_manual("", labels = Stations, values = setNames(Stat_pal, 1:4), na.value = "#999999")
Station_shape <- scale_shape_manual("",labels = Stations, values = setNames(c(21, 25, 22, 23), 1:4))

#Color to Stage
Stat_pal3 <- c(rgb(255, 255, 255, maxColorValue = 255), rgb(153, 255, 255, maxColorValue = 255), rgb(0, 0, 255, maxColorValue = 255), rgb(0, 0, 102, maxColorValue = 255))
Stages <- c("Ind" = "Indifferent", "Dev" = "Developing", "Rip" = "Ripe/Spawning", "Spe" = "Spent/Recyling") 
Stage_fill <- scale_fill_manual("", labels = Stages, values = Stat_pal3, na.value = "#999999")
#
#Sediment formatting
Sediment_list <- c("Rate", "OrgContent", "OrgWt")
Stat_pal2 <- c(rgb(0, 0, 228, maxColorValue = 255), rgb(245, 0, 0, maxColorValue = 255))
Positions <- c("N" = "North", "S" = "South")
Position_fill <- scale_fill_manual("", labels = Positions, values = Stat_pal2, na.value = "#999999")
Position_color <- scale_color_manual("", labels = Positions, values = Stat_pal2, na.value = "#999999")
#
#
```

```{r Data gather from summary file, include=FALSE}
###Water Quality
WQ_Sal_s <-  readWorkbook("../Data/CERP_PBC_WQ_Summary_Data.xlsx", sheet = 'Salinity Station', detectDates = TRUE, check.names = TRUE)
LW_Flow_raw <- readWorkbook("Data/LWL_WQ_Data.xlsx", sheet = 'Flow_df', detectDates = TRUE, check.names = TRUE) %>% filter(Date >= Start_date %m-% days(30) & Date <= End_date) %>% dplyr::select(Analysis_Date, Estuary, Date, S155_Flow, S41_Flow, S44_Flow, LWSum)
WQ_Tem_s <-  readWorkbook("../Data/CERP_PBC_WQ_Summary_Data.xlsx", sheet = 'Temp Station', detectDates = TRUE, check.names = TRUE)
WQ_pH_s <-  readWorkbook("../Data/CERP_PBC_WQ_Summary_Data.xlsx", sheet = 'pH Station', detectDates = TRUE, check.names = TRUE)
WQ_DO_s <-  readWorkbook("../Data/CERP_PBC_WQ_Summary_Data.xlsx", sheet = 'DO Station', detectDates = TRUE, check.names = TRUE)
WQ_Secchi_s <-  readWorkbook("../Data/CERP_PBC_WQ_Summary_Data.xlsx", sheet = 'Secchi Station', detectDates = TRUE, check.names = TRUE)
#
Counts_df <- readWorkbook("../Data/CERP_PBC_Summary_Data.xlsx", sheet = 'DeadRatio Station', detectDates = TRUE, check.names = TRUE)
SH_df <- readWorkbook("../Data/CERP_PBC_Summary_Data.xlsx", sheet = 'SH Station', detectDates = TRUE, check.names = TRUE)
Rcrt_df <- readWorkbook("../Data/CERP_PBC_Summary_Data.xlsx", sheet = 'Rcrt Station', detectDates = TRUE, check.names = TRUE)
Repro_df <- readWorkbook("../Data/CERP_PBC_Summary_Data.xlsx", sheet = 'Repro', detectDates = TRUE, check.names = TRUE)
Dermo_df <- readWorkbook("../Data/CERP_PBC_Summary_Data.xlsx", sheet = 'Dermo Station', detectDates = TRUE, check.names = TRUE)
Sedi_sta <- readWorkbook("../Data/CERP_PBC_Summary_Data.xlsx", sheet = 'Sedi Stations', detectDates = TRUE, check.names = TRUE)
Sedi_pos <- readWorkbook("../Data/CERP_PBC_Summary_Data.xlsx", sheet = 'Sedi Position', detectDates = TRUE, check.names = TRUE)
#
```

```{r Water Quality Data selection and cleaning}
#
##Salinity
names(WQ_Sal_s) <- gsub("\\.", "", names(WQ_Sal_s))
PBC_Sal <- WQ_Sal_s %>% dplyr::select(contains("LW")) %>% 
  filter(LWL_RetDate_Sal > Start_date & LWL_RetDate_Sal < End_date) %>% 
  rename("RetDate" = LWL_RetDate_Sal) %>% 
  dplyr::select(-LWR_RetDate_Sal) %>% 
  gather(SiteStation, Salinity, -RetDate) %>% 
  mutate(Site = factor(substr(SiteStation, 1, 3), levels = c("LWL", "LWR")), 
         Station = factor(substr(SiteStation, 4, 4)), Helper = case_when(is.na(Salinity) ~ "*", TRUE ~ NA)) %>% 
  #Add legend placeholder for Flow data
  rbind(data.frame(RetDate = NA, SiteStation = 'LWL5_Flow', Salinity = NA, Site = 'LWL', Station = '5', Helper = NA, stringsAsFactors = TRUE)) %>% 
  rbind(data.frame(RetDate = NA, SiteStation = 'LWR5_Flow', Salinity = NA, Site = 'LWL', Station = '5', Helper = NA, stringsAsFactors = TRUE))
#
#
#Flow 
flow_maxScale <- ceiling(max(LW_Flow_raw$LWSum, na.rm = TRUE) / 100) * 100
flow_step <- ceiling(flow_maxScale / 3 / 100) * 100
flow_breaks <- seq(0, flow_step * 3, by = flow_step)
flow_max <- max(flow_breaks)
LW_Flow <- rbind(LW_Flow_raw %>% dplyr::select(Date, LWSum) %>% mutate(Site = "LWL"), 
                    LW_Flow_raw %>% dplyr::select(Date, LWSum) %>% mutate(Site = "LWR")) %>%
  mutate(Rescale = (LWSum)/(flow_max)*(40-0)+0, #Rescale flow to salinity and flow axis limits for plotting
         Rescale16 = (LWSum)/(flow_max)*(16-0)+0,
         Rescale10 = (LWSum)/(flow_max)*(10-7)+7)
#
#
#
##Temperature
names(WQ_Tem_s) <- gsub("\\.", "", names(WQ_Tem_s))
PBC_Temp <- WQ_Tem_s %>% 
  dplyr::select(contains("LW")) %>% 
  filter(LWL_RetDate_Temp > Start_date & LWL_RetDate_Temp < End_date) %>% 
  dplyr::select(-LWR_RetDate_Temp) %>% 
  rename("RetDate" = LWL_RetDate_Temp) %>%
  gather(SiteStation, Temperature, -RetDate) %>% 
  mutate(Site = factor(substr(SiteStation, 1, 3), levels = c("LWL", "LWR")), Station = as.factor(substr(SiteStation, 4, 4)))
#
#
#
##DO
names(WQ_DO_s) <- gsub("\\.", "", names(WQ_DO_s))
PBC_DO <- WQ_DO_s %>% 
  dplyr::select(contains("LW")) %>% 
  filter(LWL_RetDate_DO > Start_date & LWL_RetDate_DO < End_date) %>% 
  dplyr::select(-LWR_RetDate_DO) %>% 
  rename("RetDate" = LWL_RetDate_DO) %>% 
  gather(SiteStation, DO, -RetDate) %>% 
  mutate(Site = factor(substr(SiteStation, 1, 3), levels = c("LWL", "LWR")), Station = as.factor(substr(SiteStation, 4, 4)))
#
#
#
##pH
names(WQ_pH_s) <- gsub("\\.", "", names(WQ_pH_s))
PBC_pH <- WQ_pH_s %>% 
  dplyr::select(contains("LW")) %>% 
  filter(LWL_RetDate_pH > Start_date & LWL_RetDate_pH < End_date) %>% 
  dplyr::select(-LWR_RetDate_pH) %>% 
  rename("RetDate" = LWL_RetDate_pH) %>% 
  gather(SiteStation, pH, -RetDate) %>% 
  mutate(Site = factor(substr(SiteStation, 1, 3), levels = c("LWL", "LWR")), Station = as.factor(substr(SiteStation, 4, 4)))
#
#
#
##Secchi
names(WQ_Secchi_s) <- gsub("\\.", "", names(WQ_Secchi_s))
PBC_SP <- WQ_Secchi_s %>% 
  dplyr::select(contains("LW")) %>% 
  filter(LWL_RetDate_SP > Start_date & LWL_RetDate_SP < End_date) %>% 
  dplyr::select(-LWR_RetDate_SP) %>% 
  rename("RetDate" = LWL_RetDate_SP) %>% 
  gather(SiteStation, SP, -RetDate) %>% 
  mutate(Site = factor(substr(SiteStation, 1, 3), levels = c("LWL", "LWR")), Station = as.factor(substr(SiteStation, 4, 4)))
#
#
#
```

```{r Data selection and cleaning}
#
####SURVEY DATA
names(Counts_df) <- gsub("\\.", "", names(Counts_df))
Surveys <- Counts_df %>% 
  arrange(AnalysisDate) %>% 
  filter(AnalysisDate >= Start_date & AnalysisDate <= End_date) %>% 
  dplyr::select(AnalysisDate, Survey)
Counts <- Counts_df %>% 
  filter(AnalysisDate >= Start_date & AnalysisDate <= End_date) %>% 
  dplyr::select(Survey, AnalysisDate, contains("LW")) %>% 
  gather(SiteStation, DataType, -Survey, -AnalysisDate) %>% 
  mutate(Measure = case_when(grepl("Mean", SiteStation) ~ "Mean", 
                             grepl("SD", SiteStation) ~ "SD", 
                             TRUE ~ NA)) %>%
  mutate(SiteStation = case_when(grepl("Dead", SiteStation) ~ substr(SiteStation, 1, 14), 
                                 grepl("Live", SiteStation) ~ substr(SiteStation, 1, 9), 
                                 TRUE ~ "MISSING INFO")) %>% 
  spread(Measure, DataType) %>% 
  mutate(Site = factor(substr(SiteStation, 1, 3), levels = c("LWL", "LWR")), 
         Station = as.factor(substr(SiteStation, 4, 4)), 
         Helper = case_when(is.na(Mean) ~ "*", 
                            grepl("Winter", Survey) & is.na(Mean) ~ "*", 
                            grepl("Summer", Survey) & is.na(Mean) ~ "*", TRUE ~ NA))
#
#
#
names(SH_df) <- gsub("\\.", "", names(SH_df))
SHs <- SH_df %>% 
  dplyr::select(Survey, AnalysisDate, contains("LW")) %>% 
  filter(AnalysisDate >= Start_date & AnalysisDate <= End_date) %>% 
  gather(SiteStation, Value, -Survey, -AnalysisDate) %>% 
  mutate(Measure = case_when(grepl("Mean", SiteStation) ~ "Mean", 
                             grepl("SD", SiteStation) ~ "SD", 
                             TRUE ~ NA)) %>% 
  mutate(SiteStation = substr(SiteStation, 1, 4)) %>% 
  spread(Measure, Value) %>% 
  mutate(Site = factor(substr(SiteStation, 1, 3), levels = c("LWL", "LWR")), 
         Station = as.factor(substr(SiteStation, 4, 4)), 
         Helper = case_when(is.na(Mean) ~ "*", 
                            grepl("Winter", Survey) & is.na(Mean) ~ "*", 
                            grepl("Summer", Survey) & is.na(Mean) ~ "*", 
                            TRUE ~ NA))
#
#
#
####DERMO DATA
names(Dermo_df) <- gsub("\\.", "", names(Dermo_df))
DermoP <- Dermo_df %>% 
  dplyr::select(contains("LW")) %>% 
  dplyr::select(contains('RetDate')|contains('Pct'))  %>% 
  filter(LWL_RetDate >= Start_date & LWL_RetDate <= End_date) %>% 
  dplyr::select(-LWR_RetDate)  %>% 
  rename("RetDate" = LWL_RetDate) %>% 
  gather(SiteStation, Value, -RetDate) %>% 
  mutate(Site = factor(substr(SiteStation, 1, 3), levels = c("LWL", "LWR")), 
         Station = as.factor(substr(SiteStation, 4, 4)), 
         Helper = case_when(is.na(Value) ~ "*", TRUE ~ NA))
#
#
DermoI <- Dermo_df %>% 
  dplyr::select(contains("LW")) %>% 
  dplyr::select(contains('RetDate')|-contains('Pct')) %>% 
  filter(LWL_RetDate >= Start_date & LWL_RetDate <= End_date) %>% 
  dplyr::select(-LWR_RetDate)  %>% 
  rename("RetDate" = LWL_RetDate)  %>% 
  gather(SiteStation, Value, -RetDate) %>% 
  mutate(Site = factor(substr(SiteStation, 1, 3), levels = c("LWL", "LWR")), 
         Station = as.factor(substr(SiteStation, 4, 4)), 
         Measure = case_when(grepl("Mean", SiteStation) ~ "Mean", 
                             grepl("SD", SiteStation) ~ "SD", 
                             TRUE ~ NA), 
         SiteStation = substr(SiteStation, 1, 4)) %>%  
  spread(Measure, Value) %>% 
  mutate(Helper = case_when(is.na(Mean) ~ "*", TRUE ~ NA))
#
#
#
####REPRO DATA
names(Repro_df) <- gsub("\\.", "", names(Repro_df))
Repro_PBC <- Repro_df %>% 
  dplyr::select(contains("LW")) %>% 
  filter(LWL_RetDate >= Start_date & LWL_RetDate <= End_date) %>% 
  dplyr::select(-LWR_RetDate)  %>% 
  rename("RetDate" = LWL_RetDate) %>% 
  gather(SiteStation, Value, -RetDate) %>% 
  mutate(Stage = factor(substr(SiteStation, 5, 7), levels = c("Ind", "Dev", "Rip", "Spe")), 
         Site = factor(substr(SiteStation, 1, 3), levels = c("LWL", "LWR")), 
         Helper = case_when(is.na(Value) ~ "*", TRUE ~ NA))
#
#
#
####RECRUITMENT DATA
names(Rcrt_df) <- gsub("\\.", "", names(Rcrt_df))
Recruits <- Rcrt_df %>% 
  dplyr::select(contains("LW")) %>% 
  filter(LWL_RetDate >= Start_date & LWL_RetDate <= End_date) %>% 
  dplyr::select(-LWR_RetDate)  %>% 
  rename("RetDate" = LWL_RetDate) %>% 
  gather(SiteStation, Value, -RetDate) %>% 
  mutate(Site = factor(substr(SiteStation, 1, 3), levels = c("LWL", "LWR")), 
         Station = as.factor(substr(SiteStation, 4, 4)), 
         Measure = case_when(grepl("Mean", SiteStation) ~ "Mean", 
                             grepl("SD", SiteStation) ~ "SD", 
                             TRUE ~ NA), 
         SiteStation = substr(SiteStation, 1, 4)) %>%  
  spread(Measure, Value) %>% 
  mutate(Helper = case_when(is.na(Mean) ~ "*", TRUE ~ NA))
#
#
#
####SEDIMENT DATA
names(Sedi_sta) <- gsub("\\.", "", names(Sedi_sta))
names(Sedi_pos) <- gsub("\\.", "", names(Sedi_pos))
Sed_sta_rate <- Sedi_sta %>% 
  dplyr::select(contains("Ret") | contains("Rate")) %>% 
  filter(LWL_RetDate >= Start_date & LWL_RetDate <= End_date) %>% 
  rename("RetDate" = LWL_RetDate) %>% 
  dplyr::select(-LWR_RetDate) %>% 
  gather(SiteStation, Value, -RetDate) %>% 
  mutate(Site = factor(substr(SiteStation, 1, 3), levels = c("LWL", "LWR")), 
         Station = as.factor(substr(SiteStation, 4, 4)), 
         Measure = case_when(grepl("Mean", SiteStation) ~ "Mean", 
                             grepl("SD", SiteStation) ~ "SD", 
                             TRUE ~ NA)) %>% 
  dplyr::select(-SiteStation) %>% 
  spread(Measure, Value) %>% 
  mutate(Helper = case_when(is.na(Mean) ~ "*", 
                            TRUE ~ NA),
         SiteStation = as.factor(paste0(Site, Station)))
Sed_sta_org <- Sedi_sta %>% 
  dplyr::select(contains("Ret") | contains("Pct")) %>% 
  filter(LWL_RetDate >= Start_date & LWL_RetDate <= End_date) %>% 
  rename("RetDate" = LWL_RetDate) %>% 
  dplyr::select(-LWR_RetDate) %>% 
  gather(SiteStation, Value, -RetDate) %>% 
  mutate(Site = factor(substr(SiteStation, 1, 3), levels = c("LWL", "LWR")), 
         Station = as.factor(substr(SiteStation, 4, 4)), 
         Measure = case_when(grepl("Mean", SiteStation) ~ "Mean", 
                             grepl("SD", SiteStation) ~ "SD", 
                             TRUE ~ NA)) %>% 
  dplyr::select(-SiteStation) %>% 
  spread(Measure, Value) %>% 
  mutate(Helper = case_when(is.na(Mean) ~ "*", 
                            TRUE ~ NA),
         SiteStation = as.factor(paste0(Site, Station)))
Sed_sta_wt <- Sedi_sta %>% 
  dplyr::select(contains("Ret") | contains("Wt")) %>% 
  filter(LWL_RetDate >= Start_date & LWL_RetDate <= End_date) %>% 
  rename("RetDate" = LWL_RetDate) %>% 
  dplyr::select(-LWR_RetDate) %>% 
  gather(SiteStation, Value, -RetDate) %>% 
  mutate(Site = factor(substr(SiteStation, 1, 3), levels = c("LWL", "LWR")), 
         Station = as.factor(substr(SiteStation, 4, 4)), 
         Measure = case_when(grepl("Mean", SiteStation) ~ "Mean", 
                             grepl("SD", SiteStation) ~ "SD", 
                             TRUE ~ NA)) %>% 
  dplyr::select(-SiteStation) %>% 
  spread(Measure, Value) %>% 
  mutate(Helper = case_when(is.na(Mean) ~ "*", TRUE ~ NA),
         SiteStation = as.factor(paste0(Site, Station)))
#
Sedi_positions <- Sedi_pos %>% 
  dplyr::select(-AnalysisDate) %>% 
  rename("RetDate" = North_RetDate) %>% 
  filter(RetDate >= Start_date & RetDate <= End_date) %>% 
  gather(Info, Value, -RetDate) %>% 
  mutate(Position = factor(substr(Info, 1, 5)), 
         Measure = case_when(grepl("Mean", Info) ~ "Mean", 
                             grepl("SD", Info) ~ "SD", 
                             TRUE ~ NA), 
         Parameter = case_when(grepl("Rate", Info) ~ "Rate", 
                               grepl("Pct", Info) ~ "OrgContent", 
                               grepl("Wt", Info) ~ "OrgWt", 
                               TRUE ~ NA)) %>% 
  dplyr::select(-Info)  %>% 
  spread(Measure, Value) %>% 
  mutate(Helper = case_when(is.na(Mean) ~ "*", 
                            TRUE ~ NA))
#
#
```

```{r Missing Data summary}
#
##Water quality 
WQ_check <- full_join(WQ_Sal_s %>% 
                        filter(LWL_RetDate_Sal > Start_date & LWL_RetDate_Sal < End_date) %>% 
                        mutate(MonYr = substr(LWL_RetDate_Sal, 1, 7)) %>% 
                        dplyr::select(MonYr, everything(), -matches("RetDate")) %>% 
                        rename_with(~str_remove(., "_Sal")) %>% 
                        gather("Station", "Salinity", -MonYr),
                      WQ_Tem_s %>% 
                        filter(LWL_RetDate_Temp > Start_date & LWL_RetDate_Temp < End_date) %>% 
                        mutate(MonYr = substr(LWL_RetDate_Temp, 1, 7)) %>% 
                        dplyr::select(MonYr, everything(), -matches("RetDate")) %>% 
                        rename_with(~str_remove(., "_Temp")) %>% 
                        gather("Station", "Temperature", -MonYr)) %>%
  full_join(WQ_DO_s %>% 
              filter(LWL_RetDate_DO > Start_date & LWL_RetDate_DO < End_date) %>% 
              mutate(MonYr = substr(LWL_RetDate_DO, 1, 7)) %>% 
              dplyr::select(MonYr, everything(), -matches("RetDate")) %>% 
              rename_with(~str_remove(., "_DO")) %>% 
              gather("Station", "DO", -MonYr)) %>%
  full_join(WQ_pH_s %>% 
              filter(LWL_RetDate_pH > Start_date & LWL_RetDate_pH < End_date) %>% 
              mutate(MonYr = substr(LWL_RetDate_pH, 1, 7)) %>% 
              dplyr::select(MonYr, everything(), -matches("RetDate")) %>% 
              rename_with(~str_remove(., "_pH")) %>% 
              gather("Station", "pH", -MonYr)) %>%
  full_join(WQ_Secchi_s %>% 
              filter(LWL_RetDate_SP > Start_date & LWL_RetDate_SP < End_date) %>% 
              mutate(MonYr = substr(LWL_RetDate_SP, 1, 7)) %>% 
              dplyr::select(MonYr, everything(), -matches("RetDate")) %>% 
              rename_with(~str_remove(., "_SP")) %>% 
              gather("Station", "Secchi", -MonYr)) %>%
  filter(is.na(Temperature) | is.na(Salinity) | is.na(DO) | is.na(pH) | is.na(Secchi)) %>%
  filter(Station == "LWL" | Station == "LWR")
#
#
#
##Survey - Counts_df, SH_df
Survey_check <- Counts_df %>% 
                        filter(AnalysisDate > Start_date & AnalysisDate < End_date) %>% 
                        dplyr::select(Survey, contains("LiveMean")) %>% 
                        filter(str_detect(Survey, "Spring|Fall")) %>% 
                        rename_with(~str_remove(., "_LiveMean")) %>% 
                        gather("Station", "LiveCount", -Survey) %>% 
  filter(grepl("LW", Station)) %>%
  filter(is.na(LiveCount)) %>% 
  dplyr::select(Survey, Station)
#
SH_check <- SH_df %>% 
  filter(AnalysisDate > Start_date & AnalysisDate < End_date) %>% 
  dplyr::select(Survey, contains("Mean")) %>%                     
  filter(str_detect(Survey, "Spring|Fall")) %>% 
  rename_with(~str_remove(., "_SHMean")) %>% 
  gather("Station", "SH", -Survey) %>% 
  filter(grepl("LW", Station)) %>%
  filter(is.na(SH)) %>% 
  dplyr::select(Survey, Station)
#
#
#
##Dermo
Dermo_check <- Dermo_df %>% 
  filter(LWL_RetDate > Start_date & LWL_RetDate < End_date) %>% 
  mutate(MonYr = substr(LWL_RetDate, 1, 7)) %>% 
  dplyr::select(MonYr, contains("Mean")) %>% 
  rename_with(~str_remove(., "_Mean")) %>% 
  gather("Station", "Dermo", -MonYr)  %>% 
  filter(grepl("LW", Station)) %>%
  filter(is.na(Dermo)) %>% 
  dplyr::select(MonYr, Station)
#
#
#
##Repro
Repro_check <- Repro_df %>% 
  filter(LWL_RetDate > Start_date & LWL_RetDate < End_date) %>% 
  mutate(MonYr = substr(LWL_RetDate, 1, 7)) %>% 
  dplyr::select(MonYr, contains("Dev")) %>% 
  rename_with(~str_remove(., "_Dev")) %>% 
  gather("Station", "Repro", -MonYr) %>% 
  filter(grepl("LW", Station)) %>%
  filter(is.na(Repro)) %>% 
  dplyr::select(MonYr, Station)
#
#
#
##Recruitment
Rcrt_check <- Rcrt_df %>% 
  filter(LWL_RetDate > Start_date & LWL_RetDate < End_date) %>% 
  mutate(MonYr = substr(LWL_RetDate, 1, 7)) %>% 
  dplyr::select(MonYr, contains("Mean")) %>% 
  rename_with(~str_remove(., "_Mean")) %>% 
  gather("Station", "Spat", -MonYr) %>% 
  filter(grepl("LW", Station)) %>%
  filter(is.na(Spat)) %>% 
  dplyr::select(MonYr, Station)
#
#
#
##Sediment
Rate_pos_check <- Sedi_pos %>%
  filter(AnalysisDate > Start_date & AnalysisDate < End_date) %>% 
  mutate(MonYr = substr(AnalysisDate, 1, 7)) %>% 
  dplyr::select(MonYr, contains("RateMean")) %>% 
  gather("Position", "RateMean", -MonYr)  %>% 
  filter(is.na(RateMean)) %>% 
  dplyr::select(MonYr, Position)
Rate_sta_check <- Sedi_sta %>% 
  filter(AnalysisDate > Start_date & AnalysisDate < End_date) %>% 
  mutate(MonYr = substr(AnalysisDate, 1, 7)) %>% 
  dplyr::select(MonYr, contains("RateMean")) %>%
  gather("Station", "RateMean", -MonYr)  %>% 
  separate(Station, into = c("Site", "Type"), sep = "_") %>% 
  filter(is.na(RateMean)) %>% 
  dplyr::select(MonYr, Site, Type)
#
Org_pos_check <- Sedi_pos %>%
  filter(AnalysisDate > Start_date & AnalysisDate < End_date) %>% 
  mutate(MonYr = substr(AnalysisDate, 1, 7)) %>% 
  dplyr::select(MonYr, contains("OrganicMean")) %>% 
  gather("Position", "OrganicMean", -MonYr)  %>% 
  filter(is.na(OrganicMean)) %>% 
  dplyr::select(MonYr, Position)
Org_sta_check <- Sedi_sta %>% 
  filter(AnalysisDate > Start_date & AnalysisDate < End_date) %>% 
  mutate(MonYr = substr(AnalysisDate, 1, 7)) %>% 
  dplyr::select(MonYr, contains("OrganicMean")) %>%
  gather("Station", "OrganicMean", -MonYr)  %>% 
  separate(Station, into = c("Site", "Type"), sep = "_") %>% 
  filter(is.na(OrganicMean)) %>% 
  dplyr::select(MonYr, Site, Type)
#
#
#
```

The following figures are presented for the final report covering `r Start_date %>% format("%B %Y")` through `r End_date %>% format("%B %Y")`.
\
\
**PBC missing data**

Any samples listed below were missing during the monitoring period:
\
\
*Water quality*
\
`r if(nrow(WQ_check) > 0) {flextable(WQ_check) %>% align(align = "center", part = "all")  %>% autofit() %>% font(fontname = "Arial", part = "all")} else {paste("No missing water quality data.")}`
\
\
*Survey*
\
`r if(nrow(Survey_check) > 0) {flextable(Survey_check) %>% align(align = "center", part = "all")  %>% autofit() %>% font(fontname = "Arial", part = "all")} else {paste("No missing survey count data.")}`\
`r if(nrow(SH_check) > 0) {flextable(SH_check) %>% align(align = "center", part = "all")  %>% autofit() %>% font(fontname = "Arial", part = "all")} else {paste("No missing survey shell height data.")}`
\
\
*Dermo*
\
`r if(nrow(Dermo_check) > 0) {flextable(Dermo_check) %>% align(align = "center", part = "all")  %>% autofit() %>% font(fontname = "Arial", part = "all")} else {paste("No missing dermo data.")}`
\
\
*Repro - site based data*
\
`r if(nrow(Repro_check) > 0) {flextable(Repro_check) %>% align(align = "center", part = "all")  %>% autofit() %>% font(fontname = "Arial", part = "all")} else {paste("No missing repro data.")}`
\
\
*Recruitment*
\
`r if(nrow(Rcrt_check) > 0) {flextable(Rcrt_check) %>% align(align = "center", part = "all")  %>% autofit() %>% font(fontname = "Arial", part = "all")} else {paste("No missing recruitment data.")}`
\
\
*Sediment*
\
Sedimentation rate\
`r if(nrow(Rate_pos_check) > 0) {flextable(Rate_pos_check) %>% align(align = "center", part = "all")  %>% autofit() %>% font(fontname = "Arial", part = "all")} else {paste("No missing sedimentation rate data per North or South station grouping.")}`\
`r if(nrow(Rate_sta_check) > 0) {flextable(Rate_sta_check) %>% align(align = "center", part = "all")  %>% autofit() %>% font(fontname = "Arial", part = "all")} else {paste("No missing sedimentation rate data per station.")}`\
Percent organic weight\
`r if(nrow(Org_pos_check) > 0) {flextable(Org_pos_check) %>% align(align = "center", part = "all")  %>% autofit() %>% font(fontname = "Arial", part = "all")} else {paste("No missing percent organic weight data per North or South station grouping.")}`\
`r if(nrow(Org_sta_check) > 0) {flextable(Org_sta_check) %>% align(align = "center", part = "all")  %>% autofit() %>% font(fontname = "Arial", part = "all")} else {paste("No missing percent organic weight data per station.")}`
\
\
\newpage

```{r Salinity Figure, fig.cap = "**Figure 4.**  Monthly salinity recorded at natural reef stations (top) and at restored reef stations (bottom) in Lake Worth Lagoon and the mean daily flow rate at the S155 structure as recorded by the South Florida Water Management District. Pale green bar denotes salinity optima band.", fig.height = 5, fig.width = 8, fig.fullwidth=TRUE}
#
Sal_plot <- ggarrange(
  #LWL
  ggplot() +
    geom_area(data = LW_Flow %>% filter(Site == "LWL"), aes(Date, Rescale), fill = rgb(156, 156, 156, maxColorValue = 255))+
    geom_rect(aes(xmin = -Inf, xmax = Inf, ymin = 10, ymax = 20), alpha = 0.4, inherit.aes = FALSE, fill = "palegreen")+
    geom_line(data = PBC_Sal %>% filter(Site == "LWL"), aes(RetDate, Salinity, color = Station), linewidth = 0.7) +
    geom_point(data = PBC_Sal %>% filter(Site == "LWL"), aes(RetDate, Salinity, fill = Station, shape = Station), size = 3) +
    labs(title = "Lake Worth-Natural") +
    scale_x_date("", expand= c(0,0), date_breaks = "2 months", date_labels = "%b %Y", limits = c(Start_date %m-% days(5), End_date %m-% days(5)))+
    scale_y_continuous("Salinity", expand = c(0,0), 
                       sec.axis = sec_axis(~.*(flow_max/40), 
                                           name = "Flow (cfs)", 
                                           breaks = flow_breaks)) +
    coord_cartesian(ylim = c(0, 40))+
    scale_fill_manual("", labels = c("1" = "Station 1", "2" = "Station 2", "3" = "Station 3", "4" = "Station 4", "5" = "Flow"), values = c("1" = rgb(0, 0, 228, maxColorValue = 255), "2" = rgb(245, 0, 0, maxColorValue = 255), "3" = rgb(0, 118, 0, maxColorValue = 255), "4" = rgb(102, 0, 102, maxColorValue = 255), "5" = rgb(156, 156, 156, maxColorValue = 255)), breaks = c("5", "1", "2", "3", "4")) +
    scale_color_manual("", labels = c("1" = "Station 1", "2" = "Station 2", "3" = "Station 3", "4" = "Staion 4", "5" = "Flow"), values = c("1" = rgb(0, 0, 228, maxColorValue = 255), "2" = rgb(245, 0, 0, maxColorValue = 255), "3" = rgb(0, 118, 0, maxColorValue = 255), "4" = rgb(102, 0, 102, maxColorValue = 255), "5" = "white"), breaks = c("5", "1", "2", "3", "4")) + 
    scale_shape_manual("", labels = c("1" = "Station 1", "2" = "Station 2", "3" = "Station 3", "4" = "Station 4", "5" = "Flow"), values = c("1" = 21, "2" = 21, "3" = 21, "4" = 21, "5" = 22), breaks = c("5", "1", "2", "3", "4"))+
    BaseForm + FacetForm +  PlotTitle + theme(legend.position = "none")+
  rremove("y.title") + rremove("x.text"),
  NULL,
  #LWR
  ggplot() +
    geom_area(data = LW_Flow %>% filter(Site == "LWR"), aes(Date, Rescale), fill = rgb(156, 156, 156, maxColorValue = 255))+
    geom_rect(aes(xmin = -Inf, xmax = Inf, ymin = 10, ymax = 20), alpha = 0.4, inherit.aes = FALSE, fill = "palegreen")+
    geom_line(data = PBC_Sal %>% filter(Site == "LWR"), aes(RetDate, Salinity, color = Station), linewidth = 0.7) +
    geom_point(data = PBC_Sal %>% filter(Site == "LWR"), aes(RetDate, Salinity, fill = Station, shape = Station), size = 3) +
    labs(title = "Lake Worth-Restoration") +
    scale_x_date("", expand= c(0,0), date_breaks = "2 months", date_labels = "%b %Y", limits = c(Start_date %m-% days(5), End_date %m-% days(5)))+
    scale_y_continuous("Salinity", expand = c(0,0), 
                       sec.axis = sec_axis(~.*(flow_max/40), 
                                           name = "Flow (cfs)", 
                                           breaks = flow_breaks)) +
    coord_cartesian(ylim = c(0, 40))+
    scale_fill_manual("", labels = c("1" = "Station 1", "2" = "Station 2", "3" = "Station 3", "4" = "Station 4", "5" = "Flow"), values = c("1" = rgb(0, 0, 228, maxColorValue = 255), "2" = rgb(245, 0, 0, maxColorValue = 255), "3" = rgb(0, 118, 0, maxColorValue = 255), "4" = rgb(102, 0, 102, maxColorValue = 255), "5" = rgb(156, 156, 156, maxColorValue = 255)), breaks = c("5", "1", "2", "3", "4")) +
    scale_color_manual("", labels = c("1" = "Station 1", "2" = "Station 2", "3" = "Station 3", "4" = "Staion 4", "5" = "Flow"), values = c("1" = rgb(0, 0, 228, maxColorValue = 255), "2" = rgb(245, 0, 0, maxColorValue = 255), "3" = rgb(0, 118, 0, maxColorValue = 255), "4" = rgb(102, 0, 102, maxColorValue = 255), "5" = "white"), breaks = c("5", "1", "2", "3", "4")) + 
    scale_shape_manual("", labels = c("1" = "Station 1", "2" = "Station 2", "3" = "Station 3", "4" = "Station 4", "5" = "Flow"), values = c("1" = 21, "2" = 21, "3" = 21, "4" = 21, "5" = 22), breaks = c("5", "1", "2", "3", "4"))+
    BaseForm + FacetForm + PlotTitle + theme(legend.position = "none")+
  rremove("y.title") + rremove("x.title"),
  nrow =  3, heights = c(0.9, -0.05, 1.1))
#
annotate_figure(Sal_plot, 
                left = text_grob("Salinity", rot = 90, family = "serif", color = "black", size = 17),
                right = text_grob("Flow (cfs)", rot = 270, family = "serif", color = "black", size = 17))
#
#
```

```{r Temperature Figure, fig.cap = "**Figure 5.**  Monthly temperature recorded at natural reef stations (top) and at restored reef stations (bottom) in Lake Worth Lagoon and the mean daily flow rate at the S155 structure as recorded by the South Florida Water Management District.", fig.height = 5, fig.width = 8, fig.fullwidth=TRUE}
#max(LW_Flow$LWSum) - round to nearest divisible by 4
Temp_plot <- ggarrange(
  #LWL
  ggplot() +
    geom_area(data = LW_Flow %>% filter(Site == "LWL"), aes(Date, Rescale), fill = rgb(156, 156, 156, maxColorValue = 255))+
geom_line(data = PBC_Temp %>% filter(Site == "LWL"), aes(RetDate, Temperature, color = Station), linewidth = 0.7) +
    geom_point(data = PBC_Temp %>% filter(Site == "LWL"), aes(RetDate, Temperature, fill = Station, shape = Station), size = 3) +
    labs(title = "Lake Worth-Natural") +
    scale_x_date("", expand= c(0,0), date_breaks = "2 months", date_labels = "%b %Y", limits = c(Start_date %m-% days(5), End_date %m-% days(5)))+
    scale_y_continuous("Temperature (\u00B0C)", expand = c(0,0), 
                       sec.axis = sec_axis(~.*(flow_max/40), 
                                           name = "Flow (cfs)", 
                                           breaks = flow_breaks)) +
    coord_cartesian(ylim = c(0, 40))+
    scale_fill_manual("", labels = c("1" = "Station 1", "2" = "Station 2", "3" = "Station 3", "4" = "Station 4", "5" = "Flow"), values = c("1" = rgb(0, 0, 228, maxColorValue = 255), "2" = rgb(245, 0, 0, maxColorValue = 255), "3" = rgb(0, 118, 0, maxColorValue = 255), "4" = rgb(102, 0, 102, maxColorValue = 255), "5" = rgb(156, 156, 156, maxColorValue = 255)), breaks = c("5", "1", "2", "3", "4")) +
    scale_color_manual("", labels = c("1" = "Station 1", "2" = "Station 2", "3" = "Station 3", "4" = "Staion 4", "5" = "Flow"), values = c("1" = rgb(0, 0, 228, maxColorValue = 255), "2" = rgb(245, 0, 0, maxColorValue = 255), "3" = rgb(0, 118, 0, maxColorValue = 255), "4" = rgb(102, 0, 102, maxColorValue = 255), "5" = "white"), breaks = c("5", "1", "2", "3", "4")) + 
    scale_shape_manual("", labels = c("1" = "Station 1", "2" = "Station 2", "3" = "Station 3", "4" = "Station 4", "5" = "Flow"), values = c("1" = 21, "2" = 21, "3" = 21, "4" = 21, "5" = 22), breaks = c("5", "1", "2", "3", "4"))+
    BaseForm + FacetForm +  PlotTitle + theme(legend.position = "none")+
  rremove("y.title") + rremove("x.text"),
  NULL,
  #LWR
  ggplot() +
    geom_area(data = LW_Flow %>% filter(Site == "LWR"), aes(Date, Rescale), fill = rgb(156, 156, 156, maxColorValue = 255))+
  geom_line(data = PBC_Temp %>% filter(Site == "LWR"), aes(RetDate, Temperature, color = Station), linewidth = 0.7) +
    geom_point(data = PBC_Temp %>% filter(Site == "LWR"), aes(RetDate, Temperature, fill = Station, shape = Station), size = 3) +
    labs(title = "Lake Worth-Restoration") +
    scale_x_date("", expand= c(0,0), date_breaks = "2 months", date_labels = "%b %Y", limits = c(Start_date %m-% days(5), End_date %m-% days(5)))+
    scale_y_continuous("Temperature (\u00B0C)", expand = c(0,0), 
                       sec.axis = sec_axis(~.*(flow_max/40), 
                                           name = "Flow (cfs)", 
                                           breaks = flow_breaks)) +
    coord_cartesian(ylim = c(0, 40))+
    scale_fill_manual("", labels = c("1" = "Station 1", "2" = "Station 2", "3" = "Station 3", "4" = "Station 4", "5" = "Flow"), values = c("1" = rgb(0, 0, 228, maxColorValue = 255), "2" = rgb(245, 0, 0, maxColorValue = 255), "3" = rgb(0, 118, 0, maxColorValue = 255), "4" = rgb(102, 0, 102, maxColorValue = 255), "5" = rgb(156, 156, 156, maxColorValue = 255)), breaks = c("5", "1", "2", "3", "4")) +
    scale_color_manual("", labels = c("1" = "Station 1", "2" = "Station 2", "3" = "Station 3", "4" = "Staion 4", "5" = "Flow"), values = c("1" = rgb(0, 0, 228, maxColorValue = 255), "2" = rgb(245, 0, 0, maxColorValue = 255), "3" = rgb(0, 118, 0, maxColorValue = 255), "4" = rgb(102, 0, 102, maxColorValue = 255), "5" = "white"), breaks = c("5", "1", "2", "3", "4")) + 
    scale_shape_manual("", labels = c("1" = "Station 1", "2" = "Station 2", "3" = "Station 3", "4" = "Station 4", "5" = "Flow"), values = c("1" = 21, "2" = 21, "3" = 21, "4" = 21, "5" = 22), breaks = c("5", "1", "2", "3", "4"))+
    BaseForm + FacetForm + PlotTitle + theme(legend.position = "none")+
  rremove("y.title")  + rremove("x.title"),
  nrow =  3, heights = c(0.9, -0.05, 1.1))
#
annotate_figure(Temp_plot, 
                left = text_grob("Temperature (\u00B0C)", rot = 90, family = "serif", color = "black", size = 17),
                right = text_grob("Flow (cfs)", rot = 270, family = "serif", color = "black", size = 17))
#
#
```

```{r Dissolved oxygen Figure, fig.cap = "**Figure 6.**  Monthly dissolved oxygen concentration recorded at natural reef stations (top) and at restored reef stations (bottom) in Lake Worth Lagoon and the mean daily flow rate at the S155 structure as recorded by the South Florida Water Management District.", fig.height = 5, fig.width = 8, fig.fullwidth=TRUE}
#max(LW_Flow$LWSum) - round to nearest divisible by 4
DO_plot <- ggarrange(
  #LWL
  ggplot() +
    geom_area(data = LW_Flow %>% filter(Site == "LWL"), aes(Date, Rescale16), fill = rgb(156, 156, 156, maxColorValue = 255))+
geom_line(data = PBC_DO %>% filter(Site == "LWL"), aes(RetDate, DO, color = Station), linewidth = 0.7) +
    geom_point(data = PBC_DO %>% filter(Site == "LWL"), aes(RetDate, DO, fill = Station, shape = Station), size = 3) +
    labs(title = "Lake Worth-Natural") +
    scale_x_date("", expand= c(0,0), date_breaks = "2 months", date_labels = "%b %Y", limits = c(Start_date %m-% days(5), End_date %m-% days(5)))+
    scale_y_continuous("Dissolved oxygen (mg/L)", expand = c(0,0), 
                       sec.axis = sec_axis(~.*(flow_max/16), 
                                           name = "Flow (cfs)", 
                                           breaks = flow_breaks)) +
    coord_cartesian(ylim = c(0, 16))+
    scale_fill_manual("", labels = c("1" = "Station 1", "2" = "Station 2", "3" = "Station 3", "4" = "Station 4", "5" = "Flow"), values = c("1" = rgb(0, 0, 228, maxColorValue = 255), "2" = rgb(245, 0, 0, maxColorValue = 255), "3" = rgb(0, 118, 0, maxColorValue = 255), "4" = rgb(102, 0, 102, maxColorValue = 255), "5" = rgb(156, 156, 156, maxColorValue = 255)), breaks = c("5", "1", "2", "3", "4")) +
    scale_color_manual("", labels = c("1" = "Station 1", "2" = "Station 2", "3" = "Station 3", "4" = "Staion 4", "5" = "Flow"), values = c("1" = rgb(0, 0, 228, maxColorValue = 255), "2" = rgb(245, 0, 0, maxColorValue = 255), "3" = rgb(0, 118, 0, maxColorValue = 255), "4" = rgb(102, 0, 102, maxColorValue = 255), "5" = "white"), breaks = c("5", "1", "2", "3", "4")) + 
    scale_shape_manual("", labels = c("1" = "Station 1", "2" = "Station 2", "3" = "Station 3", "4" = "Station 4", "5" = "Flow"), values = c("1" = 21, "2" = 21, "3" = 21, "4" = 21, "5" = 22), breaks = c("5", "1", "2", "3", "4"))+
    BaseForm + FacetForm +  PlotTitle + theme(legend.position = "none")+
  rremove("y.title") + rremove("x.text"),
  NULL,
  #LWR
  ggplot() +
    geom_area(data = LW_Flow %>% filter(Site == "LWR"), aes(Date, Rescale16), fill = rgb(156, 156, 156, maxColorValue = 255))+
  geom_line(data = PBC_DO %>% filter(Site == "LWR"), aes(RetDate, DO, color = Station), linewidth = 0.7) +
    geom_point(data = PBC_DO %>% filter(Site == "LWR"), aes(RetDate, DO, fill = Station, shape = Station), size = 3) +
    labs(title = "Lake Worth-Restoration") +
    scale_x_date("", expand= c(0,0), date_breaks = "2 months", date_labels = "%b %Y", limits = c(Start_date %m-% days(5), End_date %m-% days(5)))+
    scale_y_continuous("Dissolved oxygen (mg/L)", expand = c(0,0), 
                       sec.axis = sec_axis(~.*(flow_max/16), 
                                           name = "Flow (cfs)", 
                                           breaks = flow_breaks)) +
    coord_cartesian(ylim = c(0, 16))+
    scale_fill_manual("", labels = c("1" = "Station 1", "2" = "Station 2", "3" = "Station 3", "4" = "Station 4", "5" = "Flow"), values = c("1" = rgb(0, 0, 228, maxColorValue = 255), "2" = rgb(245, 0, 0, maxColorValue = 255), "3" = rgb(0, 118, 0, maxColorValue = 255), "4" = rgb(102, 0, 102, maxColorValue = 255), "5" = rgb(156, 156, 156, maxColorValue = 255)), breaks = c("5", "1", "2", "3", "4")) +
    scale_color_manual("", labels = c("1" = "Station 1", "2" = "Station 2", "3" = "Station 3", "4" = "Staion 4", "5" = "Flow"), values = c("1" = rgb(0, 0, 228, maxColorValue = 255), "2" = rgb(245, 0, 0, maxColorValue = 255), "3" = rgb(0, 118, 0, maxColorValue = 255), "4" = rgb(102, 0, 102, maxColorValue = 255), "5" = "white"), breaks = c("5", "1", "2", "3", "4")) + 
    scale_shape_manual("", labels = c("1" = "Station 1", "2" = "Station 2", "3" = "Station 3", "4" = "Station 4", "5" = "Flow"), values = c("1" = 21, "2" = 21, "3" = 21, "4" = 21, "5" = 22), breaks = c("5", "1", "2", "3", "4"))+
    BaseForm + FacetForm + PlotTitle + theme(legend.position = "none")+
  rremove("y.title")  + rremove("x.title"),
  nrow =  3, heights = c(0.9, -0.05, 1.1))
#
annotate_figure(DO_plot, 
                left = text_grob("Dissolved oxygen (mg/L)", rot = 90, family = "serif", color = "black", size = 17),
                right = text_grob("Flow (cfs)", rot = 270, family = "serif", color = "black", size = 17))
#
#
```

```{r pH Figure, fig.cap = "**Figure 7.**  Monthly pH recorded at natural reef stations (top) and at restored reef stations (bottom) in Lake Worth Lagoon and the mean daily flow rate at the S155 structure as recorded by the South Florida Water Management District.", fig.height = 5, fig.width = 8, fig.fullwidth=TRUE}
#max(LW_Flow$LWSum) - round to nearest divisible by 4
pH_plot <- ggarrange(
  #LWL
  ggplot() +
    geom_area(data = LW_Flow %>% filter(Site == "LWL"), aes(Date, Rescale10), fill = rgb(156, 156, 156, maxColorValue = 255))+
geom_line(data = PBC_pH %>% filter(Site == "LWL"), aes(RetDate, pH, color = Station), linewidth = 0.7) +
    geom_point(data = PBC_pH %>% filter(Site == "LWL"), aes(RetDate, pH, fill = Station, shape = Station), size = 3) +
    labs(title = "Lake Worth-Natural") +
    scale_x_date("", expand= c(0,0), date_breaks = "2 months", date_labels = "%b %Y", limits = c(Start_date %m-% days(5), End_date %m-% days(5)))+
    scale_y_continuous("pH", expand = c(0,0), 
                       sec.axis = sec_axis(~(.-7)*(flow_max/(10-7)), 
                                           name = "Flow (cfs)", 
                                           breaks = flow_breaks)) +
    coord_cartesian(ylim = c(7, 10))+
    scale_fill_manual("", labels = c("1" = "Station 1", "2" = "Station 2", "3" = "Station 3", "4" = "Station 4", "5" = "Flow"), values = c("1" = rgb(0, 0, 228, maxColorValue = 255), "2" = rgb(245, 0, 0, maxColorValue = 255), "3" = rgb(0, 118, 0, maxColorValue = 255), "4" = rgb(102, 0, 102, maxColorValue = 255), "5" = rgb(156, 156, 156, maxColorValue = 255)), breaks = c("5", "1", "2", "3", "4")) +
    scale_color_manual("", labels = c("1" = "Station 1", "2" = "Station 2", "3" = "Station 3", "4" = "Staion 4", "5" = "Flow"), values = c("1" = rgb(0, 0, 228, maxColorValue = 255), "2" = rgb(245, 0, 0, maxColorValue = 255), "3" = rgb(0, 118, 0, maxColorValue = 255), "4" = rgb(102, 0, 102, maxColorValue = 255), "5" = "white"), breaks = c("5", "1", "2", "3", "4")) + 
    scale_shape_manual("", labels = c("1" = "Station 1", "2" = "Station 2", "3" = "Station 3", "4" = "Station 4", "5" = "Flow"), values = c("1" = 21, "2" = 21, "3" = 21, "4" = 21, "5" = 22), breaks = c("5", "1", "2", "3", "4"))+
    BaseForm + FacetForm +  PlotTitle + theme(legend.position = "none")+
  rremove("y.title") + rremove("x.text"),
  NULL,
  #LWR
  ggplot() +
    geom_area(data = LW_Flow %>% filter(Site == "LWR"), aes(Date, Rescale10), fill = rgb(156, 156, 156, maxColorValue = 255))+
  geom_line(data = PBC_pH %>% filter(Site == "LWR"), aes(RetDate, pH, color = Station), linewidth = 0.7) +
    geom_point(data = PBC_pH %>% filter(Site == "LWR"), aes(RetDate, pH, fill = Station, shape = Station), size = 3) +
    labs(title = "Lake Worth-Restoration") +
    scale_x_date("", expand= c(0,0), date_breaks = "2 months", date_labels = "%b %Y", limits = c(Start_date %m-% days(5), End_date %m-% days(5)))+
        scale_y_continuous("pH", expand = c(0,0), 
                           sec.axis = sec_axis(~(.-7)*(flow_max/(10-7)), 
                                               name = "Flow (cfs)", 
                                               breaks = flow_breaks)) +
    coord_cartesian(ylim = c(7, 10))+
    scale_fill_manual("", labels = c("1" = "Station 1", "2" = "Station 2", "3" = "Station 3", "4" = "Station 4", "5" = "Flow"), values = c("1" = rgb(0, 0, 228, maxColorValue = 255), "2" = rgb(245, 0, 0, maxColorValue = 255), "3" = rgb(0, 118, 0, maxColorValue = 255), "4" = rgb(102, 0, 102, maxColorValue = 255), "5" = rgb(156, 156, 156, maxColorValue = 255)), breaks = c("5", "1", "2", "3", "4")) +
    scale_color_manual("", labels = c("1" = "Station 1", "2" = "Station 2", "3" = "Station 3", "4" = "Staion 4", "5" = "Flow"), values = c("1" = rgb(0, 0, 228, maxColorValue = 255), "2" = rgb(245, 0, 0, maxColorValue = 255), "3" = rgb(0, 118, 0, maxColorValue = 255), "4" = rgb(102, 0, 102, maxColorValue = 255), "5" = "white"), breaks = c("5", "1", "2", "3", "4")) + 
    scale_shape_manual("", labels = c("1" = "Station 1", "2" = "Station 2", "3" = "Station 3", "4" = "Station 4", "5" = "Flow"), values = c("1" = 21, "2" = 21, "3" = 21, "4" = 21, "5" = 22), breaks = c("5", "1", "2", "3", "4"))+
    BaseForm + FacetForm + PlotTitle + theme(legend.position = "none")+
  rremove("y.title")  + rremove("x.title"),
  nrow =  3, heights = c(0.9, -0.05, 1.1))
#
annotate_figure(pH_plot, 
                left = text_grob("pH", rot = 90, family = "serif", color = "black", size = 17),
                right = text_grob("Flow (cfs)", rot = 270, family = "serif", color = "black", size = 17))
#
#
```

```{r Secchi Figure, fig.cap = "**Figure 8.**  Monthly percent Secchi pentetration recorded at natural reef stations (top) and at restored reef stations (bottom) in Lake Worth Lagoon.", fig.height = 5, fig.width = 8, fig.fullwidth=TRUE}
SP_plot <- ggarrange(
  PBC_SP %>% filter(Site == "LWL") %>%
    ggplot(aes(RetDate, SP, fill = Station)) + 
    geom_col(position = position_dodge(13), width = 10, color = "black") + 
    labs(title = "Lake Worth-Natural") +
    scale_y_reverse("% Secchi Penetration", expand = c(0,0), limits = c(100, 0), breaks = seq(0, 100, by = 20)) +
    scale_x_date("", expand= c(0,0), date_breaks = "2 months", date_labels = "%b %Y", limits = c(Start_date %m-% days(5), End_date %m-% days(5)))+
    Station_fill + BaseForm + FacetForm + PlotTitle + theme(legend.position = "none") +
  rremove("y.title") + rremove("x.text"),
  NULL,
  PBC_SP %>% filter(Site == "LWR") %>%
    ggplot(aes(RetDate, SP, fill = Station)) + 
    geom_col(position = position_dodge(13), width = 10, color = "black") + 
    labs(title = "Lake Worth-Restoration") +
    scale_y_reverse("% Secchi Penetration", expand = c(0,0), limits = c(100, 0), breaks = seq(0, 100, by = 20)) +
    scale_x_date("", expand= c(0,0), date_breaks = "2 months", date_labels = "%b %Y", limits = c(Start_date %m-% days(5), End_date %m-% days(5)))+
    Station_fill + BaseForm + FacetForm + PlotTitle + theme(legend.position = "none") +
  rremove("y.title"),
  nrow =  3, heights = c(0.9, -0.05, 1.1))
#
annotate_figure(SP_plot, left = text_grob("% Secchi Penetration", rot = 90, family = "serif", color = "black", size = 17))
#
#
#
```

```{r Survey table, results='asis'}
cat("<br>
    <br>
    <br>")
Survey_table <- Counts_df %>% 
  dplyr::select(Survey, contains("LiveMean")) %>% 
  dplyr::select(Survey, contains("LW")) %>% 
  drop_na() %>% 
  pivot_longer(c(-Survey),
    names_to = "SiteStation",
    values_to = "Mean") %>%
  mutate(
    Type = case_when(substr(SiteStation, 3, 3) == "L" ~ "Natural",
                     TRUE ~ "Restored"),
    Station = substr(SiteStation, 4, 4)) %>%
  left_join(StationInfo) %>%
  group_by(Group, Type, Station, StationName) %>%
  summarise(
    Minimum = round(min(Mean), 2),
    Maximum = round(max(Mean), 2),
    Mean = round(mean(Mean), 2),
    .groups = "drop"
  ) %>%
  dplyr::select(
    Group,
    Type,
    Station,
    StationName,
    Minimum,
    Maximum,
    Mean)


Survey_table %>%
  flextable() %>%
  # Font
  font(fontname = "Times New Roman", part = "all") %>%
  fontsize(size = 10, part = "all") %>%
  # Remove all default borders
  border_remove() %>%
  # Header formatting
  bold(part = "header") %>%
  # Alignment
  align(
    j = c("Group",
          "Type",
          "Station",
          "StationName"),
    align = "left",
    part = "all") %>%
  align(
    j = c("Minimum",
          "Maximum",
          "Mean"),
    align = "center",
    part = "all") %>%
  # Number formatting
  colformat_num(
    j = c("Minimum",
          "Maximum",
          "Mean"),
    digits = 2) %>%
  # Header borders
  hline_top(border = fp_border(color = "black",
                               width = 1.5),
            part = "header") %>%
  hline_bottom(border = fp_border(color = "black",
                                  width = 1.5),
              part = "header") %>%
  # Bottom border of table
  hline_bottom(border = fp_border(color = "black",
                                  width = 1.5),
               part = "body") %>%
  # Table overall width
  #set_table_properties(width = 6.5, layout = "fixed" ) %>%
  # Caption
  set_caption(
    caption = "**Table 4.** Minimum, maximum, and mean live oyster density (oysters/m2) at each of the Lake Worth monitoring stations throughout the monitoring period.") %>%
  # Automatically size columns
  autofit()
cat("<br>
    <br>
    <br>")
```

```{r Natural Survey Figure, fig.cap = "**Figure 9.**  Mean semi-annual number (± S.D.) of live oysters (colored bars) present at natural reef stations in Lake Worth Lagoon and the mean daily flow rate (gray fill) at the S155 structure as recorded by the South Florida Water Management District. Please note the differences in the y-axis range among station plots.", fig.height = 8.5, fig.width = 8, fig.fullwidth=TRUE}
#
Nat_Live_list <- list()
for(i in seq_along(LWL_stations)){
  #
  Working_site <- paste(LWL_stations[i])
  df_temp <- Counts %>% 
    filter(grepl("Live", SiteStation) & grepl(Working_site, SiteStation)) %>% 
    rowwise() %>% 
    mutate(Upper = sum(Mean, SD, na.rm = TRUE))
  df_temp$HelperLocation <- (ceiling((max(df_temp$Upper, na.rm = T)*1.05)*10)/10)/5
  max_upper <- (ceiling((max(df_temp$Upper, na.rm = T)*1.05)*10)/10) #*1.05 adds 5% buffer to top if needed, *10 & /10 rounds up to nearest 0.1
  # Automatically determine a "pretty" y-axis range
  y_breaks <- pretty(c(0, max_upper))
  y_max <- max(y_breaks)
  temp_flow <- LW_Flow %>% 
    dplyr::select(Date, Site, LWSum) %>%
    mutate(Rescale = LWSum / flow_max * y_max)
  #flow_scale <- flow_max/y_max
  #
  Nat_Live_list[[i]] <- df_temp %>% 
    ggplot(aes(AnalysisDate, Mean, fill = Station)) + 
        geom_area(data = temp_flow %>% filter(Site == "LWL"), aes(Date, Rescale, group = 1), fill = rgb(156, 156, 156, maxColorValue = 255), inherit.aes = FALSE)+
    geom_errorbar(aes(ymin = Mean, ymax = Mean + SD), 
                  color = "black", position = position_dodge(40), width = 17) +
    geom_col(position = position_dodge(40), width = 25, color = "black") + 
    scale_x_date("Survey", 
                 expand= c(0,0), labels = Surveys$Survey, breaks = Surveys$AnalysisDate, limits = c(Start_date, End_date))+
    scale_y_continuous(expression("Live oysters / m"^2), 
                       expand = c(0,0), limits = c(0, y_max), breaks = y_breaks,
                       sec.axis = sec_axis(
                         local({
                           flow_scale <- flow_max/y_max
                           ~.*(flow_scale)}),
                       breaks = flow_breaks))+
       #coord_cartesian(ylim = c(0, y_max))+
    ggtitle(paste0(case_when(substr(Working_site, 4, 4) == "1" ~ "Station 1", 
                             substr(Working_site, 4, 4) == "2" ~ "Station 2", 
                             TRUE ~ "Station 3"))) + 
    Station_fill + Station_color + BaseForm + PlotTitle + 
    Xnudge + theme(legend.position = "none")
}
rm(i, Working_site, df_temp, max_upper, y_breaks, y_max, temp_flow, flow_scale)
#
Nat_live_fig <- gridExtra::arrangeGrob(
  textGrob(expression("Live oysters / m"^2), rot = 90, 
                  gp = gpar(fontfamily = "serif", col = "black", fontsize = 17)),
  gridExtra::arrangeGrob(
    ggplotGrob(Nat_Live_list[[1]] + rremove("x.title") + rremove("x.text") + rremove("y.title")), 
    ggplotGrob(Nat_Live_list[[2]] + rremove("x.title") + rremove("x.text") + rremove("y.title")), 
    ggplotGrob(Nat_Live_list[[3]] + rremove("x.title") + rremove("y.title")),
    ncol = 1, heights = c(0.9, 0.9, 1.1)),
  textGrob("Flow (cfs)", rot = 270, 
                   gp = gpar(fontfamily = "serif", col = "black", fontsize = 17)),
  ncol = 3,
  widths = c(1.5, 20, 1.5)
  )
#
grid::grid.draw(Nat_live_fig)
#
#
```

```{r Restoration Survey Figure, fig.cap = "**Figure 10.**  Mean semi-annual number (± S.D.) of live oysters (colored bars) present at restoration reef stations in Lake Worth Lagoon and the mean daily flow rate (gray fill) at the S155 structure as recorded by the South Florida Water Management District. Please note the differences in the y-axis range among station plots.", fig.height = 8.5, fig.width = 8, fig.fullwidth=TRUE}
#
Res_Live_list <- list()
for(i in seq_along(LWR_stations)){
  #
  Working_site <- paste(LWR_stations[i])
  df_temp <- Counts %>% 
    filter(grepl("Live", SiteStation) & grepl(Working_site, SiteStation)) %>% 
    rowwise() %>% 
    mutate(Upper = sum(Mean, SD, na.rm = TRUE))
  df_temp$HelperLocation <- (ceiling((max(df_temp$Upper, na.rm = T)*1.05)*10)/10)/5
  max_upper <- (ceiling((max(df_temp$Upper, na.rm = T)*1.05)*10)/10) #*1.05 adds 5% buffer to top if needed, *10 & /10 rounds up to nearest 0.1
  # Automatically determine a "pretty" y-axis range
  y_breaks <- pretty(c(0, max_upper))
  y_max <- max(y_breaks)
  temp_flow <- LW_Flow %>% 
    dplyr::select(Date, Site, LWSum) %>%
    mutate(Rescale = LWSum / flow_max * y_max)
  #flow_scale <- flow_max/y_max
  #
  Res_Live_list[[i]] <- df_temp %>% 
    ggplot(aes(AnalysisDate, Mean, fill = Station)) + 
        geom_area(data = temp_flow %>% filter(Site == "LWR"), aes(Date, Rescale, group = 1), fill = rgb(156, 156, 156, maxColorValue = 255), inherit.aes = FALSE)+
    geom_errorbar(aes(ymin = Mean, ymax = Mean + SD), 
                  color = "black", position = position_dodge(40), width = 17) +
    geom_col(position = position_dodge(40), width = 25, color = "black") + 
    scale_x_date("Survey", 
                 expand= c(0,0), labels = Surveys$Survey, breaks = Surveys$AnalysisDate, limits = c(Start_date, End_date))+
    scale_y_continuous(expression("Live oysters / m"^2), 
                       expand = c(0,0), limits = c(0, y_max), breaks = y_breaks,
                       sec.axis = sec_axis(
                         local({
                           flow_scale <- flow_max/y_max
                           ~.*(flow_scale)}),
                       breaks = flow_breaks))+
       #coord_cartesian(ylim = c(0, y_max))+
    ggtitle(paste0(case_when(substr(Working_site, 4, 4) == "2" ~ "Station 2", 
                             substr(Working_site, 4, 4) == "3" ~ "Station 3", 
                             TRUE ~ "Station 4"))) + 
    Station_fill + Station_color + BaseForm + PlotTitle + 
    Xnudge + theme(legend.position = "none")
}
rm(i, Working_site, df_temp, max_upper, y_breaks, y_max, temp_flow, flow_scale)
#
Res_live_fig <- gridExtra::arrangeGrob(
  textGrob(expression("Live oysters / m"^2), rot = 90, 
                  gp = gpar(fontfamily = "serif", col = "black", fontsize = 17)),
  gridExtra::arrangeGrob(
    ggplotGrob(Res_Live_list[[1]] + rremove("x.title") + rremove("x.text") + rremove("y.title")), 
    ggplotGrob(Res_Live_list[[2]] + rremove("x.title") + rremove("x.text") + rremove("y.title")), 
    ggplotGrob(Res_Live_list[[3]] + rremove("x.title") + rremove("y.title")),
    ncol = 1, heights = c(0.9, 0.9, 1.1)),
  textGrob("Flow (cfs)", rot = 270, 
                   gp = gpar(fontfamily = "serif", col = "black", fontsize = 17)),
  ncol = 3,
  widths = c(1.5, 20, 1.5)
  )
#
grid::grid.draw(Res_live_fig)
#
#
```

```{r Natural Dead Ratio Figure, fig.cap = "**Figure 11.**  Mean semi-annual ratio (± S.D.) of dead oysters (colored bars) present at natural reef stations in Lake Worth Lagoon and the mean daily flow rate (gray fill) at the S155 structure as recorded by the South Florida Water Management District. Please note the differences in the y-axis range among station plots.", fig.height = 8.5, fig.width = 8, fig.fullwidth=TRUE}
#
Nat_Dead_list <- list()
for(i in seq_along(LWL_stations)){
  #
  Working_site <- paste(LWL_stations[i])
  df_temp <- Counts %>% 
    filter(grepl("Dead", SiteStation) & grepl(Working_site, SiteStation)) %>% 
    rowwise() %>% 
    mutate(Upper = sum(Mean, SD, na.rm = TRUE))
  df_temp$HelperLocation <- (ceiling((max(df_temp$Upper, na.rm = T)*1.05)*10)/10)/5
  max_upper <- (ceiling((max(df_temp$Upper, na.rm = T)*1.05)*10)/10) #*1.05 adds 5% buffer to top if needed, *10 & /10 rounds up to nearest 0.1
  # Automatically determine a "pretty" y-axis range
  y_breaks <- pretty(c(0, max_upper))
  y_max <- max(y_breaks)
  temp_flow <- LW_Flow %>% 
    dplyr::select(Date, Site, LWSum) %>%
    mutate(Rescale = LWSum / flow_max * y_max)
  #flow_scale <- flow_max/y_max
  #
  Nat_Dead_list[[i]] <- df_temp %>% 
    ggplot(aes(AnalysisDate, Mean, fill = Station)) + 
        geom_area(data = temp_flow %>% filter(Site == "LWL"), aes(Date, Rescale, group = 1), fill = rgb(156, 156, 156, maxColorValue = 255), inherit.aes = FALSE)+
    geom_errorbar(aes(ymin = Mean, ymax = Mean + SD), 
                  color = "black", position = position_dodge(40), width = 17) +
    geom_col(position = position_dodge(40), width = 25, color = "black") + 
    scale_x_date("Survey", 
                 expand= c(0,0), labels = Surveys$Survey, breaks = Surveys$AnalysisDate, limits = c(Start_date, End_date))+
    scale_y_continuous("Ratio of Dead Oysters", 
                       expand = c(0,0), limits = c(0, y_max), breaks = y_breaks,
                       sec.axis = sec_axis(
                         local({
                           flow_scale <- flow_max/y_max
                           ~.*(flow_scale)}),
                       breaks = flow_breaks))+
       #coord_cartesian(ylim = c(0, y_max))+
    ggtitle(paste0(case_when(substr(Working_site, 4, 4) == "1" ~ "Station 1", 
                             substr(Working_site, 4, 4) == "2" ~ "Station 2", 
                             TRUE ~ "Station 3"))) + 
    Station_fill + Station_color + BaseForm + PlotTitle + 
    Xnudge + theme(legend.position = "none")
}
rm(i, Working_site, df_temp, max_upper, y_breaks, y_max, temp_flow, flow_scale)
#
Nat_dead_fig <- gridExtra::arrangeGrob(
  textGrob("Ratio of Dead Oysters", rot = 90, 
                  gp = gpar(fontfamily = "serif", col = "black", fontsize = 17)),
  gridExtra::arrangeGrob(
    ggplotGrob(Nat_Dead_list[[1]] + rremove("x.title") + rremove("x.text") + rremove("y.title")), 
    ggplotGrob(Nat_Dead_list[[2]] + rremove("x.title") + rremove("x.text") + rremove("y.title")), 
    ggplotGrob(Nat_Dead_list[[3]] + rremove("x.title") + rremove("y.title")),
    ncol = 1, heights = c(0.9, 0.9, 1.1)),
  textGrob("Flow (cfs)", rot = 270, 
                   gp = gpar(fontfamily = "serif", col = "black", fontsize = 17)),
  ncol = 3,
  widths = c(1.5, 20, 1.5)
  )
#
grid::grid.draw(Nat_dead_fig)
#
#
```

```{r Restoration Dead Ratio Figure, fig.cap = "**Figure 12.**  Mean semi-annual ratio (± S.D.) of dead oysters (colored bars) present at restoration reef stations in Lake Worth Lagoon and the mean daily flow rate (gray fill) at the S155 structure as recorded by the South Florida Water Management District. Please note the differences in the y-axis range among station plots.", fig.height = 8.5, fig.width = 8, fig.fullwidth=TRUE}
#
Res_Dead_list <- list()
for(i in seq_along(LWR_stations)){
  #
  Working_site <- paste(LWR_stations[i])
  df_temp <- Counts %>% 
    filter(grepl("Dead", SiteStation) & grepl(Working_site, SiteStation)) %>% 
    rowwise() %>% 
    mutate(Upper = sum(Mean, SD, na.rm = TRUE))
  df_temp$HelperLocation <- (ceiling((max(df_temp$Upper, na.rm = T)*1.05)*10)/10)/5
  max_upper <- (ceiling((max(df_temp$Upper, na.rm = T)*1.05)*10)/10) #*1.05 adds 5% buffer to top if needed, *10 & /10 rounds up to nearest 0.1
  # Automatically determine a "pretty" y-axis range
  y_breaks <- pretty(c(0, max_upper))
  y_max <- max(y_breaks)
  temp_flow <- LW_Flow %>% 
    dplyr::select(Date, Site, LWSum) %>%
    mutate(Rescale = LWSum / flow_max * y_max)
  #flow_scale <- flow_max/y_max
  #
  Res_Dead_list[[i]] <- df_temp %>% 
    ggplot(aes(AnalysisDate, Mean, fill = Station)) + 
        geom_area(data = temp_flow %>% filter(Site == "LWR"), aes(Date, Rescale, group = 1), fill = rgb(156, 156, 156, maxColorValue = 255), inherit.aes = FALSE)+
    geom_errorbar(aes(ymin = Mean, ymax = Mean + SD), 
                  color = "black", position = position_dodge(40), width = 17) +
    geom_col(position = position_dodge(40), width = 25, color = "black") + 
    scale_x_date("Survey", 
                 expand= c(0,0), labels = Surveys$Survey, breaks = Surveys$AnalysisDate, limits = c(Start_date, End_date))+
    scale_y_continuous("Ratio of Dead Oysters", 
                       expand = c(0,0), limits = c(0, y_max), breaks = y_breaks,
                       sec.axis = sec_axis(
                         local({
                           flow_scale <- flow_max/y_max
                           ~.*(flow_scale)}),
                       breaks = flow_breaks))+
       #coord_cartesian(ylim = c(0, y_max))+
    ggtitle(paste0(case_when(substr(Working_site, 4, 4) == "2" ~ "Station 2", 
                             substr(Working_site, 4, 4) == "3" ~ "Station 3", 
                             TRUE ~ "Station 4"))) + 
    Station_fill + Station_color + BaseForm + PlotTitle + 
    Xnudge + theme(legend.position = "none")
}
rm(i, Working_site, df_temp, max_upper, y_breaks, y_max, temp_flow, flow_scale)
#
Res_dead_fig <- gridExtra::arrangeGrob(
  textGrob("Ratio of Dead Oysters", rot = 90, 
                  gp = gpar(fontfamily = "serif", col = "black", fontsize = 17)),
  gridExtra::arrangeGrob(
    ggplotGrob(Res_Dead_list[[1]] + rremove("x.title") + rremove("x.text") + rremove("y.title")), 
    ggplotGrob(Res_Dead_list[[2]] + rremove("x.title") + rremove("x.text") + rremove("y.title")), 
    ggplotGrob(Res_Dead_list[[3]] + rremove("x.title") + rremove("y.title")),
    ncol = 1, heights = c(0.9, 0.9, 1.1)),
  textGrob("Flow (cfs)", rot = 270, 
                   gp = gpar(fontfamily = "serif", col = "black", fontsize = 17)),
  ncol = 3,
  widths = c(1.5, 20, 1.5)
  )
#
grid::grid.draw(Res_dead_fig)
#
#
```

```{r Natural Shell Heights Figure, fig.cap = "**Figure 13.**  Mean semi-annual shell height (± S.D.) of live oysters (colored bars) present at natural reef stations in Lake Worth Lagoon and the mean daily flow rate (gray fill) at the S155 structure as recorded by the South Florida Water Management District. Please note the differences in the y-axis range among station plots.", fig.height = 8.5, fig.width = 8, fig.fullwidth=TRUE}
#
Nat_SH_list <- list()
for(i in seq_along(LWL_stations)){
  #
  Working_site <- paste(LWL_stations[i])
  df_temp <- SHs %>% 
    filter(grepl(Working_site, SiteStation)) %>% 
    rowwise() %>% 
    mutate(Upper = sum(Mean, SD, na.rm = TRUE))
  df_temp$HelperLocation <- (ceiling((max(df_temp$Upper, na.rm = T)*1.05)*10)/10)/5
  max_upper <- (ceiling((max(df_temp$Upper, na.rm = T)*1.05)*10)/10) #*1.05 adds 5% buffer to top if needed, *10 & /10 rounds up to nearest 0.1
  # Automatically determine a "pretty" y-axis range
  y_breaks <- pretty(c(0, max_upper))
  y_max <- max(y_breaks)
  temp_flow <- LW_Flow %>% 
    dplyr::select(Date, Site, LWSum) %>%
    mutate(Rescale = LWSum / flow_max * y_max)
  #flow_scale <- flow_max/y_max
  #
  Nat_SH_list[[i]] <- df_temp %>% 
    ggplot(aes(AnalysisDate, Mean, fill = Station)) + 
        geom_area(data = temp_flow %>% filter(Site == "LWL"), aes(Date, Rescale, group = 1), fill = rgb(156, 156, 156, maxColorValue = 255), inherit.aes = FALSE)+
    geom_errorbar(aes(ymin = Mean, ymax = Mean + SD), 
                  color = "black", position = position_dodge(40), width = 17) +
    geom_col(position = position_dodge(40), width = 25, color = "black") + 
    scale_x_date("Survey", 
                 expand= c(0,0), labels = Surveys$Survey, breaks = Surveys$AnalysisDate, limits = c(Start_date, End_date))+
    scale_y_continuous("Shell height (mm)", 
                       expand = c(0,0), limits = c(0, y_max), breaks = y_breaks,
                       sec.axis = sec_axis(
                         local({
                           flow_scale <- flow_max/y_max
                           ~.*(flow_scale)}),
                       breaks = flow_breaks))+
       #coord_cartesian(ylim = c(0, y_max))+
    ggtitle(paste0(case_when(substr(Working_site, 4, 4) == "1" ~ "Station 1", 
                             substr(Working_site, 4, 4) == "2" ~ "Station 2", 
                             TRUE ~ "Station 3"))) + 
    Station_fill + Station_color + BaseForm + PlotTitle + 
    Xnudge + theme(legend.position = "none")
}
rm(i, Working_site, df_temp, max_upper, y_breaks, y_max, temp_flow, flow_scale)
#
Nat_SH_fig <- gridExtra::arrangeGrob(
  textGrob("Shell height (mm)", rot = 90, 
                  gp = gpar(fontfamily = "serif", col = "black", fontsize = 17)),
  gridExtra::arrangeGrob(
    ggplotGrob(Nat_SH_list[[1]] + rremove("x.title") + rremove("x.text") + rremove("y.title")), 
    ggplotGrob(Nat_SH_list[[2]] + rremove("x.title") + rremove("x.text") + rremove("y.title")), 
    ggplotGrob(Nat_SH_list[[3]] + rremove("x.title") + rremove("y.title")),
    ncol = 1, heights = c(0.9, 0.9, 1.1)),
  textGrob("Flow (cfs)", rot = 270, 
                   gp = gpar(fontfamily = "serif", col = "black", fontsize = 17)),
  ncol = 3,
  widths = c(1.5, 20, 1.5)
  )
#
grid::grid.draw(Nat_SH_fig)
#
#
```

```{r Restoration Shell Height Figure, fig.cap = "**Figure 14.**  Mean semi-annual shell height (± S.D.) of live oysters (colored bars) present at restoration reef stations in Lake Worth Lagoon and the mean daily flow rate (gray fill) at the S155 structure as recorded by the South Florida Water Management District. Please note the differences in the y-axis range among station plots.", fig.height = 8.5, fig.width = 8, fig.fullwidth=TRUE}
#
Res_SH_list <- list()
for(i in seq_along(LWR_stations)){
  #
  Working_site <- paste(LWR_stations[i])
  df_temp <- SHs %>% 
    filter(grepl(Working_site, SiteStation)) %>% 
    rowwise() %>% 
    mutate(Upper = sum(Mean, SD, na.rm = TRUE))
  df_temp$HelperLocation <- (ceiling((max(df_temp$Upper, na.rm = T)*1.05)*10)/10)/5
  max_upper <- (ceiling((max(df_temp$Upper, na.rm = T)*1.05)*10)/10) #*1.05 adds 5% buffer to top if needed, *10 & /10 rounds up to nearest 0.1
  # Automatically determine a "pretty" y-axis range
  y_breaks <- pretty(c(0, max_upper))
  y_max <- max(y_breaks)
  temp_flow <- LW_Flow %>% 
    dplyr::select(Date, Site, LWSum) %>%
    mutate(Rescale = LWSum / flow_max * y_max)
  #flow_scale <- flow_max/y_max
  #
  Res_SH_list[[i]] <- df_temp %>% 
    ggplot(aes(AnalysisDate, Mean, fill = Station)) + 
        geom_area(data = temp_flow %>% filter(Site == "LWR"), aes(Date, Rescale, group = 1), fill = rgb(156, 156, 156, maxColorValue = 255), inherit.aes = FALSE)+
    geom_errorbar(aes(ymin = Mean, ymax = Mean + SD), 
                  color = "black", position = position_dodge(40), width = 17) +
    geom_col(position = position_dodge(40), width = 25, color = "black") + 
    scale_x_date("Survey", 
                 expand= c(0,0), labels = Surveys$Survey, breaks = Surveys$AnalysisDate, limits = c(Start_date, End_date))+
    scale_y_continuous("Shell height (mm)", 
                       expand = c(0,0), limits = c(0, y_max), breaks = y_breaks,
                       sec.axis = sec_axis(
                         local({
                           flow_scale <- flow_max/y_max
                           ~.*(flow_scale)}),
                       breaks = flow_breaks))+
       #coord_cartesian(ylim = c(0, y_max))+
    ggtitle(paste0(case_when(substr(Working_site, 4, 4) == "2" ~ "Station 2", 
                             substr(Working_site, 4, 4) == "3" ~ "Station 3", 
                             TRUE ~ "Station 4"))) + 
    Station_fill + Station_color + BaseForm + PlotTitle + 
    Xnudge + theme(legend.position = "none")
}
rm(i, Working_site, df_temp, max_upper, y_breaks, y_max, temp_flow, flow_scale)
#
Res_SH_fig <- gridExtra::arrangeGrob(
  textGrob("Shell height (mm)", rot = 90, 
                  gp = gpar(fontfamily = "serif", col = "black", fontsize = 17)),
  gridExtra::arrangeGrob(
    ggplotGrob(Res_SH_list[[1]] + rremove("x.title") + rremove("x.text") + rremove("y.title")), 
    ggplotGrob(Res_SH_list[[2]] + rremove("x.title") + rremove("x.text") + rremove("y.title")), 
    ggplotGrob(Res_SH_list[[3]] + rremove("x.title") + rremove("y.title")),
    ncol = 1, heights = c(0.9, 0.9, 1.1)),
  textGrob("Flow (cfs)", rot = 270, 
                   gp = gpar(fontfamily = "serif", col = "black", fontsize = 17)),
  ncol = 3,
  widths = c(1.5, 20, 1.5)
  )
#
grid::grid.draw(Res_SH_fig)
#
#
```

```{r Natural Dermo Prevalence Figure, fig.cap = "**Figure 15.**  Monthly prevalence (%) of oysters infected with *Perkinsus marinus* (dermo; colored bars) at natural reef stations in Lake Worth Lagoon and the mean daily flow rate (gray fill) at the S155 structure as recorded by the South Florida Water Management District.", fig.height = 8.5, fig.width = 8, fig.fullwidth=TRUE}
#
temp_flow <- LW_Flow %>% 
    dplyr::select(Date, Site, LWSum) %>%
    mutate(Rescale = LWSum / flow_max * 100)
#
Nat_dermoP <- ggarrange(
  DermoP %>% filter(Site == "LWL" & Station == "1") %>%
    ggplot(aes(RetDate, Value, fill = Station)) + 
    geom_area(data = temp_flow %>% filter(Site == "LWL"), aes(Date, Rescale), fill = rgb(156, 156, 156, maxColorValue = 255))+
    geom_col(position = position_dodge(12), width = 9, color = "black") +
    geom_text(aes(y = 20, label = Helper, color = Station), position = position_dodge(12), size = 9)+
    labs(title = "Station 1") +
    scale_y_continuous("% Dermo Prevalence", expand = c(0,0), 
                       sec.axis = sec_axis(~.*(flow_max/100),
                       breaks = flow_breaks))+
    coord_cartesian(ylim = c(0, 100))+
    scale_x_date("", expand= c(0,0), date_breaks = "2 months", date_labels = "%b %Y", limits = c(Start_date %m-% days(5), End_date %m-% days(5)))+ 
    Station_fill + Station_color + BaseForm + theme(legend.position = "none") + PlotTitle +
  rremove("y.title") + rremove("x.text"),
  NULL,
  DermoP %>% filter(Site == "LWL" & Station == "2") %>%
    ggplot(aes(RetDate, Value, fill = Station)) + 
    geom_area(data = temp_flow %>% filter(Site == "LWL"), aes(Date, Rescale), fill = rgb(156, 156, 156, maxColorValue = 255))+
    geom_col(position = position_dodge(12), width = 9, color = "black") +
    geom_text(aes(y = 20, label = Helper, color = Station), position = position_dodge(12), size = 9)+
    labs(title = "Station 2") +
    scale_y_continuous("% Dermo Prevalence", expand = c(0,0), 
                       sec.axis = sec_axis(~.*(flow_max/100),
                       breaks = flow_breaks))+
    coord_cartesian(ylim = c(0, 100))+
    scale_x_date("", expand= c(0,0), date_breaks = "2 months", date_labels = "%b %Y", limits = c(Start_date %m-% days(5), End_date %m-% days(5)))+ 
    Station_fill + Station_color + BaseForm + theme(legend.position = "none") + PlotTitle +
  rremove("y.title") + rremove("x.text"),
  NULL,
  DermoP %>% filter(Site == "LWL" & Station == "3") %>%
    ggplot(aes(RetDate, Value, fill = Station)) + 
    geom_area(data = temp_flow %>% filter(Site == "LWL"), aes(Date, Rescale), fill = rgb(156, 156, 156, maxColorValue = 255))+
    geom_col(position = position_dodge(12), width = 9, color = "black") +
    geom_text(aes(y = 20, label = Helper, color = Station), position = position_dodge(12), size = 9)+
    labs(title = "Station 3") +
    scale_y_continuous("% Dermo Prevalence", expand = c(0,0), 
                       sec.axis = sec_axis(~.*(flow_max/100),
                       breaks = flow_breaks))+
    coord_cartesian(ylim = c(0, 100))+
    scale_x_date("", expand= c(0,0), date_breaks = "2 months", date_labels = "%b %Y", limits = c(Start_date %m-% days(5), End_date %m-% days(5)))+ 
    Station_fill + Station_color + BaseForm + theme(legend.position = "none") + PlotTitle +
  rremove("y.title")  + rremove("x.title"),
  nrow =  5, heights = c(1, -0.1, 1, -0.1, 1))
#
rm(temp_flow)
#
annotate_figure(Nat_dermoP, 
                left = text_grob("% Dermo Prevalence", rot = 90, family = "serif", color = "black", size = 17),
                right = text_grob("Flow (cfs)", rot = 270, family = "serif", color = "black", size = 17))
#
#
```

```{r Restoration Dermo Prevalence Figure, fig.cap = "**Figure 16.**  Monthly prevalence (%) of oysters infected with *Perkinsus marinus* (dermo; colored bars) at restoration reef stations in Lake Worth Lagoon and the mean daily flow rate (gray fill) at the S155 structure as recorded by the South Florida Water Management District.", fig.height = 8.5, fig.width = 8, fig.fullwidth=TRUE}
#
temp_flow <- LW_Flow %>% 
    dplyr::select(Date, Site, LWSum) %>%
    mutate(Rescale = LWSum / flow_max * 100)
#
Res_dermoP <- ggarrange(
  DermoP %>% filter(Site == "LWR" & Station == "2") %>%
    ggplot(aes(RetDate, Value, fill = Station)) + 
    geom_area(data = temp_flow %>% filter(Site == "LWR"), aes(Date, Rescale), fill = rgb(156, 156, 156, maxColorValue = 255))+
    geom_col(position = position_dodge(12), width = 9, color = "black") +
    geom_text(aes(y = 20, label = Helper, color = Station), position = position_dodge(12), size = 9)+
    labs(title = "Station 2") +
    scale_y_continuous("% Dermo Prevalence", expand = c(0,0), 
                       sec.axis = sec_axis(~.*(flow_max/100),
                       breaks = flow_breaks))+
    coord_cartesian(ylim = c(0, 100))+
    scale_x_date("", expand= c(0,0), date_breaks = "2 months", date_labels = "%b %Y", limits = c(Start_date %m-% days(5), End_date %m-% days(5)))+ 
    Station_fill + Station_color + BaseForm + theme(legend.position = "none") + PlotTitle +
  rremove("y.title") + rremove("x.text"),
  NULL,
  DermoP %>% filter(Site == "LWR" & Station == "3") %>%
    ggplot(aes(RetDate, Value, fill = Station)) + 
    geom_area(data = temp_flow %>% filter(Site == "LWR"), aes(Date, Rescale), fill = rgb(156, 156, 156, maxColorValue = 255))+
    geom_col(position = position_dodge(12), width = 9, color = "black") +
    geom_text(aes(y = 20, label = Helper, color = Station), position = position_dodge(12), size = 9)+
    labs(title = "Station 3") +
    scale_y_continuous("% Dermo Prevalence", expand = c(0,0), 
                       sec.axis = sec_axis(~.*(flow_max/100),
                       breaks = flow_breaks))+
    coord_cartesian(ylim = c(0, 100))+
    scale_x_date("", expand= c(0,0), date_breaks = "2 months", date_labels = "%b %Y", limits = c(Start_date %m-% days(5), End_date %m-% days(5)))+ 
    Station_fill + Station_color + BaseForm + theme(legend.position = "none") + PlotTitle +
  rremove("y.title") + rremove("x.text"),
  NULL,
  DermoP %>% filter(Site == "LWR" & Station == "4") %>%
    ggplot(aes(RetDate, Value, fill = Station)) + 
    geom_area(data = temp_flow %>% filter(Site == "LWR"), aes(Date, Rescale), fill = rgb(156, 156, 156, maxColorValue = 255))+
    geom_col(position = position_dodge(12), width = 9, color = "black") +
    geom_text(aes(y = 20, label = Helper, color = Station), position = position_dodge(12), size = 9)+
    labs(title = "Station 4") +
    scale_y_continuous("% Dermo Prevalence", expand = c(0,0), 
                       sec.axis = sec_axis(~.*(flow_max/100),
                       breaks = flow_breaks))+
    coord_cartesian(ylim = c(0, 100))+
    scale_x_date("", expand= c(0,0), date_breaks = "2 months", date_labels = "%b %Y", limits = c(Start_date %m-% days(5), End_date %m-% days(5)))+ 
    Station_fill + Station_color + BaseForm + theme(legend.position = "none") + PlotTitle +
  rremove("y.title") + rremove("x.title"),
  nrow =  5, heights = c(1, -0.1, 1, -0.1, 1))
#
rm(temp_flow)
#
annotate_figure(Res_dermoP, 
                left = text_grob("% Dermo Prevalence", rot = 90, family = "serif", color = "black", size = 17),
                right = text_grob("Flow (cfs)", rot = 270, family = "serif", color = "black", size = 17))
#
#
```

```{r Natural Dermo Intensity Figure, fig.cap = "**Figure 17.**  Mean monthly infection intensity (± S.D.) of oysters infected with *Perkinsus marinus* (dermo; colored bars) at natural reef stations in Lake Worth Lagoon and the mean daily flow rate (gray fill) at the S155 structure as recorded by the South Florida Water Management District.", fig.height = 8.5, fig.width = 8, fig.fullwidth=TRUE}
#
temp_flow <- LW_Flow %>% 
    dplyr::select(Date, Site, LWSum) %>%
    mutate(Rescale = LWSum / flow_max * 5)
#
Nat_dermoI <- ggarrange(
  DermoI %>% filter(Site == "LWL" & Station == "1") %>%
    ggplot(aes(RetDate, Mean, fill = Station)) + 
    geom_area(data = temp_flow %>% filter(Site == "LWL"), aes(Date, Rescale), fill = rgb(156, 156, 156, maxColorValue = 255))+
    geom_col(position = position_dodge(12), width = 9, color = "black") +
    geom_errorbar(aes(ymin = Mean, ymax = Mean + SD), color = "black", position = position_dodge(12), width = 11) +
    geom_text(aes(y = 20, label = Helper, color = Station), position = position_dodge(12), size = 9)+
    labs(title = "Station 1") +
    scale_y_continuous("Dermo Infection Intensity", expand = c(0,0), 
                       sec.axis = sec_axis(~.*(flow_max/5),
                       breaks = flow_breaks))+
    coord_cartesian(ylim = c(0, 5))+
    scale_x_date("", expand= c(0,0), date_breaks = "2 months", date_labels = "%b %Y", limits = c(Start_date %m-% days(5), End_date %m-% days(5)))+ 
    Station_fill + Station_color + BaseForm + theme(legend.position = "none") + PlotTitle +
  rremove("y.title") + rremove("x.text"),
  NULL,
  DermoI %>% filter(Site == "LWL" & Station == "2") %>%
    ggplot(aes(RetDate, Mean, fill = Station)) + 
    geom_area(data = temp_flow %>% filter(Site == "LWL"), aes(Date, Rescale), fill = rgb(156, 156, 156, maxColorValue = 255))+
    geom_col(position = position_dodge(12), width = 9, color = "black") +
    geom_errorbar(aes(ymin = Mean, ymax = Mean + SD), color = "black", position = position_dodge(12), width = 11) +
    geom_text(aes(y = 20, label = Helper, color = Station), position = position_dodge(12), size = 9)+
    labs(title = "Station 2") +
    scale_y_continuous("Dermo Infection Intensity", expand = c(0,0), 
                       sec.axis = sec_axis(~.*(flow_max/5),
                       breaks = flow_breaks))+
    coord_cartesian(ylim = c(0, 5))+
    scale_x_date("", expand= c(0,0), date_breaks = "2 months", date_labels = "%b %Y", limits = c(Start_date %m-% days(5), End_date %m-% days(5)))+ 
    Station_fill + Station_color + BaseForm + theme(legend.position = "none") + PlotTitle +
  rremove("y.title") + rremove("x.text"),
  NULL,
  DermoI %>% filter(Site == "LWL" & Station == "3") %>%
    ggplot(aes(RetDate, Mean, fill = Station)) + 
    geom_area(data = temp_flow %>% filter(Site == "LWL"), aes(Date, Rescale), fill = rgb(156, 156, 156, maxColorValue = 255))+
    geom_col(position = position_dodge(12), width = 9, color = "black") +
    geom_errorbar(aes(ymin = Mean, ymax = Mean + SD), color = "black", position = position_dodge(12), width = 11) +
    geom_text(aes(y = 20, label = Helper, color = Station), position = position_dodge(12), size = 9)+
    labs(title = "Station 3") +
    scale_y_continuous("Dermo Infection Intensity", expand = c(0,0), 
                       sec.axis = sec_axis(~.*(flow_max/5),
                       breaks = flow_breaks))+
    coord_cartesian(ylim = c(0, 5))+
    scale_x_date("", expand= c(0,0), date_breaks = "2 months", date_labels = "%b %Y", limits = c(Start_date %m-% days(5), End_date %m-% days(5)))+ 
    Station_fill + Station_color + BaseForm + theme(legend.position = "none") + PlotTitle +
  rremove("y.title")  + rremove("x.title"),
  nrow =  5, heights = c(1, -0.1, 1, -0.1, 1))
#
rm(temp_flow)
#
annotate_figure(Nat_dermoI, 
                left = text_grob("Dermo Infection Intensity", rot = 90, family = "serif", color = "black", size = 17),
                right = text_grob("Flow (cfs)", rot = 270, family = "serif", color = "black", size = 17))
#
#
```

```{r Restoration Dermo Intensity Figure, fig.cap = "**Figure 18.**  Mean monthly infection intensity (± S.D.) of oysters infected with *Perkinsus marinus* (dermo; colored bars) at restoration reef stations in Lake Worth Lagoon and the mean daily flow rate (gray fill) at the S155 structure as recorded by the South Florida Water Management District.", fig.height = 8.5, fig.width = 8, fig.fullwidth=TRUE}
#
temp_flow <- LW_Flow %>% 
    dplyr::select(Date, Site, LWSum) %>%
    mutate(Rescale = LWSum / flow_max * 5)
#
Res_dermoI <- ggarrange(
  DermoI %>% filter(Site == "LWR" & Station == "2") %>%
    ggplot(aes(RetDate, Mean, fill = Station)) + 
    geom_area(data = temp_flow %>% filter(Site == "LWR"), aes(Date, Rescale), fill = rgb(156, 156, 156, maxColorValue = 255))+
    geom_col(position = position_dodge(12), width = 9, color = "black") +
    geom_errorbar(aes(ymin = Mean, ymax = Mean + SD), color = "black", position = position_dodge(12), width = 11) +
    geom_text(aes(y = 20, label = Helper, color = Station), position = position_dodge(12), size = 9)+
    labs(title = "Station 2") +
    scale_y_continuous("Dermo Infection Intensity", expand = c(0,0), 
                       sec.axis = sec_axis(~.*(flow_max/5),
                       breaks = flow_breaks))+
    coord_cartesian(ylim = c(0, 5))+
    scale_x_date("", expand= c(0,0), date_breaks = "2 months", date_labels = "%b %Y", limits = c(Start_date %m-% days(5), End_date %m-% days(5)))+ 
    Station_fill + Station_color + BaseForm + theme(legend.position = "none") + PlotTitle +
  rremove("y.title") + rremove("x.text"),
  NULL,
  DermoI %>% filter(Site == "LWR" & Station == "3") %>%
    ggplot(aes(RetDate, Mean, fill = Station)) + 
    geom_area(data = temp_flow %>% filter(Site == "LWR"), aes(Date, Rescale), fill = rgb(156, 156, 156, maxColorValue = 255))+
    geom_col(position = position_dodge(12), width = 9, color = "black") +
    geom_errorbar(aes(ymin = Mean, ymax = Mean + SD), color = "black", position = position_dodge(12), width = 11) +
    geom_text(aes(y = 20, label = Helper, color = Station), position = position_dodge(12), size = 9)+
    labs(title = "Station 3") +
    scale_y_continuous("Dermo Infection Intensity", expand = c(0,0), 
                       sec.axis = sec_axis(~.*(flow_max/5),
                       breaks = flow_breaks))+
    coord_cartesian(ylim = c(0, 5))+
    scale_x_date("", expand= c(0,0), date_breaks = "2 months", date_labels = "%b %Y", limits = c(Start_date %m-% days(5), End_date %m-% days(5)))+ 
    Station_fill + Station_color + BaseForm + theme(legend.position = "none") + PlotTitle +
  rremove("y.title") + rremove("x.text"),
  NULL,
  DermoI %>% filter(Site == "LWR" & Station == "4") %>%
    ggplot(aes(RetDate, Mean, fill = Station)) + 
    geom_area(data = temp_flow %>% filter(Site == "LWR"), aes(Date, Rescale), fill = rgb(156, 156, 156, maxColorValue = 255))+
    geom_col(position = position_dodge(12), width = 9, color = "black") +
    geom_errorbar(aes(ymin = Mean, ymax = Mean + SD), color = "black", position = position_dodge(12), width = 11) +
    geom_text(aes(y = 20, label = Helper, color = Station), position = position_dodge(12), size = 9)+
    labs(title = "Station 4") +
    scale_y_continuous("Dermo Infection Intensity", expand = c(0,0), 
                       sec.axis = sec_axis(~.*(flow_max/5),
                       breaks = flow_breaks))+
    coord_cartesian(ylim = c(0, 5))+
    scale_x_date("", expand= c(0,0), date_breaks = "2 months", date_labels = "%b %Y", limits = c(Start_date %m-% days(5), End_date %m-% days(5)))+ 
    Station_fill + Station_color + BaseForm + theme(legend.position = "none") + PlotTitle +
  rremove("y.title") + rremove("x.title"),
  nrow =  5, heights = c(1, -0.1, 1, -0.1, 1))
#
rm(temp_flow)
#
annotate_figure(Res_dermoI, 
                left = text_grob("Dermo Infection Intensity", rot = 90, family = "serif", color = "black", size = 17),
                right = text_grob("Flow (cfs)", rot = 270, family = "serif", color = "black", size = 17))
#
#
```

```{r Repro Figure, fig.cap = "**Figure 19.**  Monthly reproductive development of oysters collected from natural reef stations (top) and restored reef stations (bottom) in Lake Worth Lagoon.", fig.height = 7, fig.width = 8, fig.fullwidth=TRUE}
#
ggarrange(
    Repro_PBC %>% filter(Site == "LWL") %>%
        ggplot(aes(RetDate, Value, fill = Stage)) + 
        geom_bar(position = position_fill(reverse = TRUE), stat = "identity", width = 12, color = "black") + 
        labs(title = "Lake Worth-Natural") +
        scale_y_continuous("Frequency", expand = c(0,0), labels = label_percent(suffix = "")) +
        scale_x_date("", expand= c(0,0), date_breaks = "1 month", date_labels = "%b", limits = c(Start_date %m-% days(5), End_date %m-% days(5)))+
        Stage_fill + BaseForm + Legend + PlotTitle,
    NULL,
    Repro_PBC %>% filter(Site == "LWR") %>%
        ggplot(aes(RetDate, Value, fill = Stage)) + 
        geom_bar(position = position_fill(reverse = TRUE), stat = "identity", width = 12, color = "black") + 
        labs(title = "Lake Worth-Restoration") +
        scale_y_continuous("Frequency", expand = c(0,0), labels = label_percent(suffix = "")) +
        scale_x_date("", expand= c(0,0), date_breaks = "1 month", date_labels = "%b", limits = c(Start_date %m-% days(5), End_date %m-% days(5)))+
        Stage_fill + BaseForm + PlotTitle + theme(legend.position = "none"),
    nrow =  3, heights = c(1, -0.05, 1))
#
```

```{r Natural Recruitment Figure, fig.cap = "**Figure 20.**  Mean monthly number (± S.D.) of oyster spat recruits (colored bars) collected per shell from natural reef stations in Lake Worth Lagoon and the mean daily flow rate (gray fill) at the S155 structure as recorded by the South Florida Water Management District. Please note the differences in the y-axis range among station plots.", fig.height = 8.5, fig.width = 8, fig.fullwidth=TRUE}
#
Nat_Rcrt_list <- list()
for(i in seq_along(LWL_stations)){
  #
  Working_site <- paste(LWL_stations[i])
  df_temp <- Recruits %>% 
    filter(grepl(Working_site, SiteStation)) %>% 
    rowwise() %>% 
    mutate(Upper = sum(Mean, SD, na.rm = TRUE))
  df_temp$HelperLocation <- (ceiling((max(df_temp$Upper, na.rm = T)*1.05)*10)/10)/5
  max_upper <- (ceiling((max(df_temp$Upper, na.rm = T)*1.05)*10)/10) #*1.05 adds 5% buffer to top if needed, *10 & /10 rounds up to nearest 0.1
  # Automatically determine a "pretty" y-axis range
  y_breaks <- pretty(c(0, max_upper))
  y_max <- max(y_breaks)
  temp_flow <- LW_Flow %>% 
    dplyr::select(Date, Site, LWSum) %>%
    mutate(Rescale = LWSum / flow_max * y_max)
  #flow_scale <- flow_max/y_max
  #
  Nat_Rcrt_list[[i]] <- df_temp %>% 
    ggplot(aes(RetDate, Mean, fill = Station)) + 
        geom_area(data = temp_flow %>% filter(Site == "LWL"), aes(Date, Rescale, group = 1), fill = rgb(156, 156, 156, maxColorValue = 255), inherit.aes = FALSE)+
    geom_errorbar(aes(ymin = Mean, ymax = Mean + SD), 
                  color = "black", position = position_dodge(40), width = 17) +
    geom_col(position = position_dodge(40), width = 15, color = "black") + 
    scale_x_date("", expand= c(0,0), date_breaks = "2 months", date_labels = "%b %Y", limits = c(Start_date %m-% days(5), End_date %m-% days(5)))+
    scale_y_continuous("Spat / Shell", 
                       expand = c(0,0), limits = c(0, y_max), breaks = y_breaks,
                       sec.axis = sec_axis(
                         local({
                           flow_scale <- flow_max/y_max
                           ~.*(flow_scale)}),
                       breaks = flow_breaks))+
       #coord_cartesian(ylim = c(0, y_max))+
    ggtitle(paste0(case_when(substr(Working_site, 4, 4) == "1" ~ "Station 1", 
                             substr(Working_site, 4, 4) == "2" ~ "Station 2", 
                             TRUE ~ "Station 3"))) + 
    Station_fill + Station_color + BaseForm + PlotTitle + 
    Xnudge + theme(legend.position = "none")
}
rm(i, Working_site, df_temp, max_upper, y_breaks, y_max, temp_flow, flow_scale)
#
Nat_rcrt_fig <- gridExtra::arrangeGrob(
  textGrob("Spat / Shell", rot = 90, 
                  gp = gpar(fontfamily = "serif", col = "black", fontsize = 17)),
  gridExtra::arrangeGrob(
    ggplotGrob(Nat_Rcrt_list[[1]] + rremove("x.title") + rremove("x.text") + rremove("y.title")), 
    ggplotGrob(Nat_Rcrt_list[[2]] + rremove("x.title") + rremove("x.text") + rremove("y.title")), 
    ggplotGrob(Nat_Rcrt_list[[3]] + rremove("x.title") + rremove("y.title")),
    ncol = 1, heights = c(0.9, 0.9, 1.1)),
  textGrob("Flow (cfs)", rot = 270, 
                   gp = gpar(fontfamily = "serif", col = "black", fontsize = 17)),
  ncol = 3,
  widths = c(1.5, 20, 1.5)
  )
#
grid::grid.draw(Nat_rcrt_fig)
#
#
```

```{r Restoration Recruitment Figure, fig.cap = "**Figure 21.**  Mean monthly number (± S.D.) of oyster spat recruits (colored bars) collected per shell from restoration reef stations in Lake Worth Lagoon and the mean daily flow rate (gray fill) at the S155 structure as recorded by the South Florida Water Management District. Please note the differences in the y-axis range among station plots.", fig.height = 8.5, fig.width = 8, fig.fullwidth=TRUE}
#
Res_Rcrt_list <- list()
for(i in seq_along(LWR_stations)){
  #
  Working_site <- paste(LWR_stations[i])
  df_temp <- Recruits %>% 
    filter(grepl(Working_site, SiteStation)) %>% 
    rowwise() %>% 
    mutate(Upper = sum(Mean, SD, na.rm = TRUE))
  df_temp$HelperLocation <- (ceiling((max(df_temp$Upper, na.rm = T)*1.05)*10)/10)/5
  max_upper <- (ceiling((max(df_temp$Upper, na.rm = T)*1.05)*10)/10) #*1.05 adds 5% buffer to top if needed, *10 & /10 rounds up to nearest 0.1
  # Automatically determine a "pretty" y-axis range
  y_breaks <- pretty(c(0, max_upper))
  y_max <- max(y_breaks)
  temp_flow <- LW_Flow %>% 
    dplyr::select(Date, Site, LWSum) %>%
    mutate(Rescale = LWSum / flow_max * y_max)
  #flow_scale <- flow_max/y_max
  #
  Res_Rcrt_list[[i]] <- df_temp %>% 
    ggplot(aes(RetDate, Mean, fill = Station)) + 
        geom_area(data = temp_flow %>% filter(Site == "LWR"), aes(Date, Rescale, group = 1), fill = rgb(156, 156, 156, maxColorValue = 255), inherit.aes = FALSE)+
    geom_errorbar(aes(ymin = Mean, ymax = Mean + SD), 
                  color = "black", position = position_dodge(40), width = 17) +
    geom_col(position = position_dodge(40), width = 15, color = "black") + 
    scale_x_date("", expand= c(0,0), date_breaks = "2 months", date_labels = "%b %Y", limits = c(Start_date %m-% days(5), End_date %m-% days(5)))+
    scale_y_continuous("Spat / Shell", 
                       expand = c(0,0), limits = c(0, y_max), breaks = y_breaks,
                       sec.axis = sec_axis(
                         local({
                           flow_scale <- flow_max/y_max
                           ~.*(flow_scale)}),
                       breaks = flow_breaks))+
       #coord_cartesian(ylim = c(0, y_max))+
    ggtitle(paste0(case_when(substr(Working_site, 4, 4) == "4" ~ "Station 4", 
                             substr(Working_site, 4, 4) == "2" ~ "Station 2", 
                             TRUE ~ "Station 3"))) + 
    Station_fill + Station_color + BaseForm + PlotTitle + 
    Xnudge + theme(legend.position = "none")
}
rm(i, Working_site, df_temp, max_upper, y_breaks, y_max, temp_flow, flow_scale)
#
Res_rcrt_fig <- gridExtra::arrangeGrob(
  textGrob("Spat / Shell", rot = 90, 
                  gp = gpar(fontfamily = "serif", col = "black", fontsize = 17)),
  gridExtra::arrangeGrob(
    ggplotGrob(Res_Rcrt_list[[1]] + rremove("x.title") + rremove("x.text") + rremove("y.title")), 
    ggplotGrob(Res_Rcrt_list[[2]] + rremove("x.title") + rremove("x.text") + rremove("y.title")), 
    ggplotGrob(Res_Rcrt_list[[3]] + rremove("x.title") + rremove("y.title")),
    ncol = 1, heights = c(0.9, 0.9, 1.1)),
  textGrob("Flow (cfs)", rot = 270, 
                   gp = gpar(fontfamily = "serif", col = "black", fontsize = 17)),
  ncol = 3,
  widths = c(1.5, 20, 1.5)
  )
#
grid::grid.draw(Res_rcrt_fig)
#
#
```

```{r Natural Sedimentation Figure, fig.cap = "**Figure 22.**  Mean monthly sedimentation rate (± S.D.; colored bars) at natural reef stations in Lake Worth Lagoon and the mean daily flow rate (gray fill) at the S155 structure as recorded by the South Florida Water Management District. Please note the differences in the y-axis range among station plots.", fig.height = 8.5, fig.width = 8, fig.fullwidth=TRUE}
#
Nat_Sedi_list <- list()
for(i in seq_along(LWL_stations)){
  #
  Working_site <- paste(LWL_stations[i])
  df_temp <- Sed_sta_rate %>% 
    filter(grepl(Working_site, SiteStation)) %>% 
    rowwise() %>% 
    mutate(Upper = sum(Mean, SD, na.rm = TRUE))
  df_temp$HelperLocation <- (ceiling((max(df_temp$Upper, na.rm = T)*1.05)*10)/10)/5
  max_upper <- (ceiling((max(df_temp$Upper, na.rm = T)*1.05)*10)/10) #*1.05 adds 5% buffer to top if needed, *10 & /10 rounds up to nearest 0.1
  # Automatically determine a "pretty" y-axis range
  y_breaks <- pretty(c(0, max_upper))
  y_max <- max(y_breaks)
  temp_flow <- LW_Flow %>% 
    dplyr::select(Date, Site, LWSum) %>%
    mutate(Rescale = LWSum / flow_max * y_max)
  #flow_scale <- flow_max/y_max
  #
  Nat_Sedi_list[[i]] <- df_temp %>% 
    ggplot(aes(RetDate, Mean, fill = Station)) + 
        geom_area(data = temp_flow %>% filter(Site == "LWL"), aes(Date, Rescale, group = 1), fill = rgb(156, 156, 156, maxColorValue = 255), inherit.aes = FALSE)+
    geom_text(aes(y = HelperLocation, label = Helper, color = Station), position = position_dodge(40), size = 9) +
    geom_errorbar(aes(ymin = Mean, ymax = Mean + SD), 
                  color = "black", position = position_dodge(40), width = 17) +
    geom_col(position = position_dodge(40), width = 15, color = "black") + 
    #Adding pattern to indicate estimated values:
    geom_col_pattern(aes(pattern = ifelse(format(RetDate, "%Y-%m") == "2025-05" | format(RetDate, "%Y-%m") == "2025-09", "stripe", NA)), pattern_density = 0.4, pattern_fill = "white", position = position_dodge(40), width = 15, color = "black", show.legend = FALSE)+
    scale_x_date("", expand= c(0,0), date_breaks = "2 months", date_labels = "%b %Y", limits = c(Start_date %m-% days(5), End_date %m-% days(5)))+
    scale_y_continuous("Sedimentation Rate (g/month)", 
                       expand = c(0,0), limits = c(0, y_max), breaks = y_breaks,
                       sec.axis = sec_axis(
                         local({
                           flow_scale <- flow_max/y_max
                           ~.*(flow_scale)}),
                       breaks = flow_breaks))+
       #coord_cartesian(ylim = c(0, y_max))+
    ggtitle(paste0(case_when(substr(Working_site, 4, 4) == "1" ~ "Station 1", 
                             substr(Working_site, 4, 4) == "2" ~ "Station 2", 
                             TRUE ~ "Station 3"))) + 
    Station_fill + Station_color + BaseForm + PlotTitle + 
    Xnudge + theme(legend.position = "none")
}
rm(i, Working_site, df_temp, max_upper, y_breaks, y_max, temp_flow, flow_scale)
#
g1 <- ggplotGrob(Nat_Sedi_list[[1]] + rremove("x.title") + rremove("x.text") + rremove("y.title")) 
g2 <- ggplotGrob(Nat_Sedi_list[[2]] + rremove("x.title") + rremove("x.text") + rremove("y.title"))
g3 <- ggplotGrob(Nat_Sedi_list[[3]] + rremove("x.title") + rremove("y.title"))
max_widths <- grid::unit.pmax(
  g1$widths,
  g2$widths,
  g3$widths
)

g1$widths <- max_widths
g2$widths <- max_widths
g3$widths <- max_widths
#
Nat_sedi_fig <- gridExtra::arrangeGrob(
  textGrob("Sedimentation Rate (g/month)", rot = 90, 
                  gp = gpar(fontfamily = "serif", col = "black", fontsize = 17)),
  gridExtra::arrangeGrob(
    g1, g2, g3,
    ncol = 1, heights = c(0.9, 0.9, 1.1)),
  textGrob("Flow (cfs)", rot = 270, 
                   gp = gpar(fontfamily = "serif", col = "black", fontsize = 17)),
  ncol = 3,
  widths = c(1.5, 20, 1.5)
  )
#
grid::grid.draw(Nat_sedi_fig)
#
#
```

```{r Restoration Sedimentation Figure, fig.cap = "**Figure 23.**  Mean monthly sedimentation rate (± S.D.; colored bars) at restoration reef stations in Lake Worth Lagoon and the mean daily flow rate (gray fill) at the S155 structure as recorded by the South Florida Water Management District. Please note the differences in the y-axis range among station plots.", fig.height = 8.5, fig.width = 8, fig.fullwidth=TRUE}
#
Res_Sedi_list <- list()
for(i in seq_along(LWR_stations)){
  #
  Working_site <- paste(LWR_stations[i])
  df_temp <- Sed_sta_rate %>% 
    filter(grepl(Working_site, SiteStation)) %>% 
    rowwise() %>% 
    mutate(Upper = sum(Mean, SD, na.rm = TRUE))
  df_temp$HelperLocation <- (ceiling((max(df_temp$Upper, na.rm = T)*1.05)*10)/10)/5
  max_upper <- (ceiling((max(df_temp$Upper, na.rm = T)*1.05)*10)/10) #*1.05 adds 5% buffer to top if needed, *10 & /10 rounds up to nearest 0.1
  # Automatically determine a "pretty" y-axis range
  y_breaks <- pretty(c(0, max_upper))
  y_max <- max(y_breaks)
  temp_flow <- LW_Flow %>% 
    dplyr::select(Date, Site, LWSum) %>%
    mutate(Rescale = LWSum / flow_max * y_max)
  #flow_scale <- flow_max/y_max
  #
  Res_Sedi_list[[i]] <- df_temp %>% 
    ggplot(aes(RetDate, Mean, fill = Station)) + 
        geom_area(data = temp_flow %>% filter(Site == "LWR"), aes(Date, Rescale, group = 1), fill = rgb(156, 156, 156, maxColorValue = 255), inherit.aes = FALSE)+
    geom_text(aes(y = HelperLocation, label = Helper, color = Station), position = position_dodge(40), size = 9) +
    geom_errorbar(aes(ymin = Mean, ymax = Mean + SD), 
                  color = "black", position = position_dodge(40), width = 17) +
    geom_col(position = position_dodge(40), width = 15, color = "black") + 
    #Adding pattern to indicate estimated values:
    geom_col_pattern(aes(pattern = ifelse(format(RetDate, "%Y-%m") == "2025-05" | format(RetDate, "%Y-%m") == "2025-09", "stripe", NA)), pattern_density = 0.4, pattern_fill = "white", position = position_dodge(40), width = 15, color = "black", show.legend = FALSE)+
    scale_x_date("", expand= c(0,0), date_breaks = "2 months", date_labels = "%b %Y", limits = c(Start_date %m-% days(5), End_date %m-% days(5)))+
    scale_y_continuous("Sedimentation Rate (g/month)", 
                       expand = c(0,0), limits = c(0, y_max), breaks = y_breaks,
                       sec.axis = sec_axis(
                         local({
                           flow_scale <- flow_max/y_max
                           ~.*(flow_scale)}),
                       breaks = flow_breaks))+
       #coord_cartesian(ylim = c(0, y_max))+
    ggtitle(paste0(case_when(substr(Working_site, 4, 4) == "4" ~ "Station 4", 
                             substr(Working_site, 4, 4) == "2" ~ "Station 2", 
                             TRUE ~ "Station 3"))) + 
    Station_fill + Station_color + BaseForm + PlotTitle + 
    Xnudge + theme(legend.position = "none")
}
rm(i, Working_site, df_temp, max_upper, y_breaks, y_max, temp_flow, flow_scale)
#
g1 <- ggplotGrob(Res_Sedi_list[[1]] + rremove("x.title") + rremove("x.text") + rremove("y.title")) 
g2 <- ggplotGrob(Res_Sedi_list[[2]] + rremove("x.title") + rremove("x.text") + rremove("y.title"))
g3 <- ggplotGrob(Res_Sedi_list[[3]] + rremove("x.title") + rremove("y.title"))
max_widths <- grid::unit.pmax(
  g1$widths,
  g2$widths,
  g3$widths
)

g1$widths <- max_widths
g2$widths <- max_widths
g3$widths <- max_widths
#
Res_sedi_fig <- gridExtra::arrangeGrob(
  textGrob("Sedimentation Rate (g/month)", rot = 90, 
                  gp = gpar(fontfamily = "serif", col = "black", fontsize = 17)),
  gridExtra::arrangeGrob(
    g1, g2, g3,
    ncol = 1, heights = c(0.9, 0.9, 1.1)),
  textGrob("Flow (cfs)", rot = 270, 
                   gp = gpar(fontfamily = "serif", col = "black", fontsize = 17)),
  ncol = 3,
  widths = c(1.5, 20, 1.5)
  )
#
grid::grid.draw(Res_sedi_fig)
#
#
```

```{r Natural Organic Figure, fig.cap = "**Figure 24.**  Mean monthly organic content (%) of sediment (colored bars) at natural reef stations in Lake Worth Lagoon and the mean daily flow rate (gray fill) at the S155 structure as recorded by the South Florida Water Management District. Please note the differences in the y-axis range among station plots.", fig.height = 8.5, fig.width = 8, fig.fullwidth=TRUE}
#
Nat_Orgc_list <- list()
for(i in seq_along(LWL_stations)){
  #
  Working_site <- paste(LWL_stations[i])
  df_temp <- Sed_sta_org %>% 
    filter(grepl(Working_site, SiteStation)) %>% 
    rowwise() %>% 
    mutate(Upper = sum(Mean, SD, na.rm = TRUE))
  df_temp$HelperLocation <- (ceiling((max(df_temp$Upper, na.rm = T)*1.05)*10)/10)/5
  max_upper <- (ceiling((max(df_temp$Upper, na.rm = T)*1.05)*10)/10) #*1.05 adds 5% buffer to top if needed, *10 & /10 rounds up to nearest 0.1
  # Automatically determine a "pretty" y-axis range
  y_breaks <- pretty(c(0, max_upper))
  y_max <- max(y_breaks)
  temp_flow <- LW_Flow %>% 
    dplyr::select(Date, Site, LWSum) %>%
    mutate(Rescale = LWSum / flow_max * y_max)
  #flow_scale <- flow_max/y_max
  #
  Nat_Orgc_list[[i]] <- df_temp %>% 
    ggplot(aes(RetDate, Mean, fill = Station)) + 
        geom_area(data = temp_flow %>% filter(Site == "LWL"), aes(Date, Rescale, group = 1), fill = rgb(156, 156, 156, maxColorValue = 255), inherit.aes = FALSE)+
    geom_text(aes(y = HelperLocation, label = Helper, color = Station), position = position_dodge(40), size = 9) +
    geom_errorbar(aes(ymin = Mean, ymax = Mean + SD), 
                  color = "black", position = position_dodge(40), width = 17) +
    geom_col(position = position_dodge(40), width = 15, color = "black") + 
    #Adding pattern to indicate estimated values:
    geom_col_pattern(aes(pattern = ifelse(format(RetDate, "%Y-%m") == "2025-05" | format(RetDate, "%Y-%m") == "2025-09", "stripe", NA)), pattern_density = 0.4, pattern_fill = "white", position = position_dodge(40), width = 15, color = "black", show.legend = FALSE)+
    scale_x_date("", expand= c(0,0), date_breaks = "2 months", date_labels = "%b %Y", limits = c(Start_date %m-% days(5), End_date %m-% days(5)))+
    scale_y_continuous("Organic Content (%)", 
                       expand = c(0,0), limits = c(0, y_max), breaks = y_breaks,
                       sec.axis = sec_axis(
                         local({
                           flow_scale <- flow_max/y_max
                           ~.*(flow_scale)}),
                       breaks = flow_breaks))+
       #coord_cartesian(ylim = c(0, y_max))+
    ggtitle(paste0(case_when(substr(Working_site, 4, 4) == "1" ~ "Station 1", 
                             substr(Working_site, 4, 4) == "2" ~ "Station 2", 
                             TRUE ~ "Station 3"))) + 
    Station_fill + Station_color + BaseForm + PlotTitle + 
    Xnudge + theme(legend.position = "none")
}
rm(i, Working_site, df_temp, max_upper, y_breaks, y_max, temp_flow, flow_scale)
#
g1 <- ggplotGrob(Nat_Orgc_list[[1]] + rremove("x.title") + rremove("x.text") + rremove("y.title")) 
g2 <- ggplotGrob(Nat_Orgc_list[[2]] + rremove("x.title") + rremove("x.text") + rremove("y.title"))
g3 <- ggplotGrob(Nat_Orgc_list[[3]] + rremove("x.title") + rremove("y.title"))
max_widths <- grid::unit.pmax(
  g1$widths,
  g2$widths,
  g3$widths
)

g1$widths <- max_widths
g2$widths <- max_widths
g3$widths <- max_widths
#
Nat_Orgc_fig <- gridExtra::arrangeGrob(
  textGrob("Organic Content (%)", rot = 90, 
                  gp = gpar(fontfamily = "serif", col = "black", fontsize = 17)),
  gridExtra::arrangeGrob(
    g1, g2, g3,
    ncol = 1, heights = c(0.9, 0.9, 1.1)),
  textGrob("Flow (cfs)", rot = 270, 
                   gp = gpar(fontfamily = "serif", col = "black", fontsize = 17)),
  ncol = 3,
  widths = c(1.5, 20, 1.5)
  )
#
grid::grid.draw(Nat_Orgc_fig)
#
#
```

```{r Restoration Organic Figure, fig.cap = "**Figure 25.**  Mean monthly organic content (%) of sediment (colored bars) at restoration reef stations in Lake Worth Lagoon and the mean daily flow rate (gray fill) at the S155 structure as recorded by the South Florida Water Management District. Please note the differences in the y-axis range among station plots.", fig.height = 8.5, fig.width = 8, fig.fullwidth=TRUE}
#
Res_Orgc_list <- list()
for(i in seq_along(LWR_stations)){
  #
  Working_site <- paste(LWR_stations[i])
  df_temp <- Sed_sta_org %>% 
    filter(grepl(Working_site, SiteStation)) %>% 
    rowwise() %>% 
    mutate(Upper = sum(Mean, SD, na.rm = TRUE))
  df_temp$HelperLocation <- (ceiling((max(df_temp$Upper, na.rm = T)*1.05)*10)/10)/5
  max_upper <- (ceiling((max(df_temp$Upper, na.rm = T)*1.05)*10)/10) #*1.05 adds 5% buffer to top if needed, *10 & /10 rounds up to nearest 0.1
  # Automatically determine a "pretty" y-axis range
  y_breaks <- pretty(c(0, max_upper))
  y_max <- max(y_breaks)
  temp_flow <- LW_Flow %>% 
    dplyr::select(Date, Site, LWSum) %>%
    mutate(Rescale = LWSum / flow_max * y_max)
  #flow_scale <- flow_max/y_max
  #
  Res_Orgc_list[[i]] <- df_temp %>% 
    ggplot(aes(RetDate, Mean, fill = Station)) + 
        geom_area(data = temp_flow %>% filter(Site == "LWR"), aes(Date, Rescale, group = 1), fill = rgb(156, 156, 156, maxColorValue = 255), inherit.aes = FALSE)+
    geom_text(aes(y = HelperLocation, label = Helper, color = Station), position = position_dodge(40), size = 9) +
    geom_errorbar(aes(ymin = Mean, ymax = Mean + SD), 
                  color = "black", position = position_dodge(40), width = 17) +
    geom_col(position = position_dodge(40), width = 15, color = "black") + 
    #Adding pattern to indicate estimated values:
    geom_col_pattern(aes(pattern = ifelse(format(RetDate, "%Y-%m") == "2025-05" | format(RetDate, "%Y-%m") == "2025-09", "stripe", NA)), pattern_density = 0.4, pattern_fill = "white", position = position_dodge(40), width = 15, color = "black", show.legend = FALSE)+
    scale_x_date("", expand= c(0,0), date_breaks = "2 months", date_labels = "%b %Y", limits = c(Start_date %m-% days(5), End_date %m-% days(5)))+
    scale_y_continuous("Organic Content (%)", 
                       expand = c(0,0), limits = c(0, y_max), breaks = y_breaks,
                       sec.axis = sec_axis(
                         local({
                           flow_scale <- flow_max/y_max
                           ~.*(flow_scale)}),
                       breaks = flow_breaks))+
       #coord_cartesian(ylim = c(0, y_max))+
    ggtitle(paste0(case_when(substr(Working_site, 4, 4) == "4" ~ "Station 4", 
                             substr(Working_site, 4, 4) == "2" ~ "Station 2", 
                             TRUE ~ "Station 3"))) + 
    Station_fill + Station_color + BaseForm + PlotTitle + 
    Xnudge + theme(legend.position = "none")
}
rm(i, Working_site, df_temp, max_upper, y_breaks, y_max, temp_flow, flow_scale)
#
g1 <- ggplotGrob(Res_Orgc_list[[1]] + rremove("x.title") + rremove("x.text") + rremove("y.title")) 
g2 <- ggplotGrob(Res_Orgc_list[[2]] + rremove("x.title") + rremove("x.text") + rremove("y.title"))
g3 <- ggplotGrob(Res_Orgc_list[[3]] + rremove("x.title") + rremove("y.title"))
max_widths <- grid::unit.pmax(
  g1$widths,
  g2$widths,
  g3$widths
)

g1$widths <- max_widths
g2$widths <- max_widths
g3$widths <- max_widths
#
Res_Orgc_fig <- gridExtra::arrangeGrob(
  textGrob("Organic Content (%)", rot = 90, 
                  gp = gpar(fontfamily = "serif", col = "black", fontsize = 17)),
  gridExtra::arrangeGrob(
    g1, g2, g3,
    ncol = 1, heights = c(0.9, 0.9, 1.1)),
  textGrob("Flow (cfs)", rot = 270, 
                   gp = gpar(fontfamily = "serif", col = "black", fontsize = 17)),
  ncol = 3,
  widths = c(1.5, 20, 1.5)
  )
#
grid::grid.draw(Res_Orgc_fig)
#
#
```

```{r Natural Organic Weight Figure, fig.cap = "**Figure 26.**  Mean monthly organic weight (± S.D.) of sediment (colored bars) collected at natural reef stations in Lake Worth Lagoon and the mean daily flow rate (gray fill) at the S155 structure as recorded by the South Florida Water Management District. Please note the differences in the y-axis range among station plots.", fig.height = 8.5, fig.width = 8, fig.fullwidth=TRUE}
#
Nat_Orgw_list <- list()
for(i in seq_along(LWL_stations)){
  #
  Working_site <- paste(LWL_stations[i])
  df_temp <- Sed_sta_wt %>% 
    filter(grepl(Working_site, SiteStation)) %>% 
    rowwise() %>% 
    mutate(Upper = sum(Mean, SD, na.rm = TRUE))
  df_temp$HelperLocation <- (ceiling((max(df_temp$Upper, na.rm = T)*1.05)*10)/10)/5
  max_upper <- (ceiling((max(df_temp$Upper, na.rm = T)*1.05)*10)/10) #*1.05 adds 5% buffer to top if needed, *10 & /10 rounds up to nearest 0.1
  # Automatically determine a "pretty" y-axis range
  y_breaks <- pretty(c(0, max_upper))
  y_max <- max(y_breaks)
  temp_flow <- LW_Flow %>% 
    dplyr::select(Date, Site, LWSum) %>%
    mutate(Rescale = LWSum / flow_max * y_max)
  #flow_scale <- flow_max/y_max
  #
  Nat_Orgw_list[[i]] <- df_temp %>% 
    ggplot(aes(RetDate, Mean, fill = Station)) + 
        geom_area(data = temp_flow %>% filter(Site == "LWL"), aes(Date, Rescale, group = 1), fill = rgb(156, 156, 156, maxColorValue = 255), inherit.aes = FALSE)+
    geom_text(aes(y = HelperLocation, label = Helper, color = Station), position = position_dodge(40), size = 9) +
    geom_errorbar(aes(ymin = Mean, ymax = Mean + SD), 
                  color = "black", position = position_dodge(40), width = 17) +
    geom_col(position = position_dodge(40), width = 15, color = "black") + 
    #Adding pattern to indicate estimated values:
    geom_col_pattern(aes(pattern = ifelse(format(RetDate, "%Y-%m") == "2025-05" | format(RetDate, "%Y-%m") == "2025-09", "stripe", NA)), pattern_density = 0.4, pattern_fill = "white", position = position_dodge(40), width = 15, color = "black", show.legend = FALSE)+
    scale_x_date("", expand= c(0,0), date_breaks = "2 months", date_labels = "%b %Y", limits = c(Start_date %m-% days(5), End_date %m-% days(5)))+
    scale_y_continuous("Organic Weight (g/month)", 
                       expand = c(0,0), limits = c(0, y_max), breaks = y_breaks,
                       sec.axis = sec_axis(
                         local({
                           flow_scale <- flow_max/y_max
                           ~.*(flow_scale)}),
                       breaks = flow_breaks))+
       #coord_cartesian(ylim = c(0, y_max))+
    ggtitle(paste0(case_when(substr(Working_site, 4, 4) == "1" ~ "Station 1", 
                             substr(Working_site, 4, 4) == "2" ~ "Station 2", 
                             TRUE ~ "Station 3"))) + 
    Station_fill + Station_color + BaseForm + PlotTitle + 
    Xnudge + theme(legend.position = "none")
}
rm(i, Working_site, df_temp, max_upper, y_breaks, y_max, temp_flow, flow_scale)
#
g1 <- ggplotGrob(Nat_Orgw_list[[1]] + rremove("x.title") + rremove("x.text") + rremove("y.title")) 
g2 <- ggplotGrob(Nat_Orgw_list[[2]] + rremove("x.title") + rremove("x.text") + rremove("y.title"))
g3 <- ggplotGrob(Nat_Orgw_list[[3]] + rremove("x.title") + rremove("y.title"))
max_widths <- grid::unit.pmax(
  g1$widths,
  g2$widths,
  g3$widths
)

g1$widths <- max_widths
g2$widths <- max_widths
g3$widths <- max_widths
#
Nat_Orgw_fig <- gridExtra::arrangeGrob(
  textGrob("Organic Weight (g/month)", rot = 90, 
                  gp = gpar(fontfamily = "serif", col = "black", fontsize = 17)),
  gridExtra::arrangeGrob(
    g1, g2, g3,
    ncol = 1, heights = c(0.9, 0.9, 1.1)),
  textGrob("Flow (cfs)", rot = 270, 
                   gp = gpar(fontfamily = "serif", col = "black", fontsize = 17)),
  ncol = 3,
  widths = c(1.5, 20, 1.5)
  )
#
grid::grid.draw(Nat_Orgw_fig)
#
#
```

```{r Restoration Organic Weight Figure, fig.cap = "**Figure 27.**  Mean monthly organic weight (± S.D.) of sediment (colored bars) collected at restoration reef stations in Lake Worth Lagoon and the mean daily flow rate (gray fill) at the S155 structure as recorded by the South Florida Water Management District. Please note the differences in the y-axis range among station plots.", fig.height = 8.5, fig.width = 8, fig.fullwidth=TRUE}
#
Res_Orgw_list <- list()
for(i in seq_along(LWR_stations)){
  #
  Working_site <- paste(LWR_stations[i])
  df_temp <- Sed_sta_wt %>% 
    filter(grepl(Working_site, SiteStation)) %>% 
    rowwise() %>% 
    mutate(Upper = sum(Mean, SD, na.rm = TRUE))
  df_temp$HelperLocation <- (ceiling((max(df_temp$Upper, na.rm = T)*1.05)*10)/10)/5
  max_upper <- (ceiling((max(df_temp$Upper, na.rm = T)*1.05)*10)/10) #*1.05 adds 5% buffer to top if needed, *10 & /10 rounds up to nearest 0.1
  # Automatically determine a "pretty" y-axis range
  y_breaks <- pretty(c(0, max_upper))
  y_max <- max(y_breaks)
  temp_flow <- LW_Flow %>% 
    dplyr::select(Date, Site, LWSum) %>%
    mutate(Rescale = LWSum / flow_max * y_max)
  #flow_scale <- flow_max/y_max
  #
  Res_Orgw_list[[i]] <- df_temp %>% 
    ggplot(aes(RetDate, Mean, fill = Station)) + 
        geom_area(data = temp_flow %>% filter(Site == "LWR"), aes(Date, Rescale, group = 1), fill = rgb(156, 156, 156, maxColorValue = 255), inherit.aes = FALSE)+
    geom_text(aes(y = HelperLocation, label = Helper, color = Station), position = position_dodge(40), size = 9) +
    geom_errorbar(aes(ymin = Mean, ymax = Mean + SD), 
                  color = "black", position = position_dodge(40), width = 17) +
    geom_col(position = position_dodge(40), width = 15, color = "black") + 
    #Adding pattern to indicate estimated values:
    geom_col_pattern(aes(pattern = ifelse(format(RetDate, "%Y-%m") == "2025-05" | format(RetDate, "%Y-%m") == "2025-09", "stripe", NA)), pattern_density = 0.4, pattern_fill = "white", position = position_dodge(40), width = 15, color = "black", show.legend = FALSE)+
    scale_x_date("", expand= c(0,0), date_breaks = "2 months", date_labels = "%b %Y", limits = c(Start_date %m-% days(5), End_date %m-% days(5)))+
    scale_y_continuous("Organic Weight (g/month)", 
                       expand = c(0,0), limits = c(0, y_max), breaks = y_breaks,
                       sec.axis = sec_axis(
                         local({
                           flow_scale <- flow_max/y_max
                           ~.*(flow_scale)}),
                       breaks = flow_breaks))+
       #coord_cartesian(ylim = c(0, y_max))+
    ggtitle(paste0(case_when(substr(Working_site, 4, 4) == "4" ~ "Station 4", 
                             substr(Working_site, 4, 4) == "2" ~ "Station 2", 
                             TRUE ~ "Station 3"))) + 
    Station_fill + Station_color + BaseForm + PlotTitle + 
    Xnudge + theme(legend.position = "none")
}
rm(i, Working_site, df_temp, max_upper, y_breaks, y_max, temp_flow, flow_scale)
#
g1 <- ggplotGrob(Res_Orgw_list[[1]] + rremove("x.title") + rremove("x.text") + rremove("y.title")) 
g2 <- ggplotGrob(Res_Orgw_list[[2]] + rremove("x.title") + rremove("x.text") + rremove("y.title"))
g3 <- ggplotGrob(Res_Orgw_list[[3]] + rremove("x.title") + rremove("y.title"))
max_widths <- grid::unit.pmax(
  g1$widths,
  g2$widths,
  g3$widths
)

g1$widths <- max_widths
g2$widths <- max_widths
g3$widths <- max_widths
#
Res_Orgw_fig <- gridExtra::arrangeGrob(
  textGrob("Organic Weight (g/month)", rot = 90, 
                  gp = gpar(fontfamily = "serif", col = "black", fontsize = 17)),
  gridExtra::arrangeGrob(
    g1, g2, g3,
    ncol = 1, heights = c(0.9, 0.9, 1.1)),
  textGrob("Flow (cfs)", rot = 270, 
                   gp = gpar(fontfamily = "serif", col = "black", fontsize = 17)),
  ncol = 3,
  widths = c(1.5, 20, 1.5)
  )
#
grid::grid.draw(Res_Orgw_fig)
#
#
```

```{r Sediment Position Figure, fig.cap = "**Figure 28.**  Mean monthly sedimentation rate (± S.D.), organic content (%), and organic weight (± S.D.) of sediment at stations north (blue bars) and south (red bars) of C-51 in Lake Worth Lagoon and the mean daily flow rate (gray fill) at the S155 structure as recorded by the South Florida Water Management District.", fig.height = 10, fig.width = 8, fig.fullwidth=TRUE}
#
Posi_list <- list()
for(i in seq_along(Sediment_list)){
  #
  Working_param <- paste(Sediment_list[i])
  df_temp <- Sedi_positions %>% 
    filter(grepl(Working_param, Parameter)) %>% 
    rowwise() %>% 
    mutate(Upper = sum(Mean, SD, na.rm = TRUE))
  df_temp$HelperLocation <- (ceiling((max(df_temp$Upper, na.rm = T)*1.05)*10)/10)/5
  max_upper <- ceiling(max(df_temp$Upper, na.rm = T)*1.05) #*1.05 adds 5% buffer to top if needed
  #
  # Automatically determine a "pretty" y-axis range
  y_breaks <- pretty(c(0, max_upper))
  y_max <- max(y_breaks)
  temp_flow <- LW_Flow %>% 
    dplyr::select(Date, Site, LWSum) %>%
    mutate(Rescale = LWSum / flow_max * y_max)
  #
  Posi_list[[i]] <- df_temp %>% 
    ggplot(aes(RetDate, Mean, fill = Position))+ 
    geom_area(data = temp_flow %>% filter(Site == "LWL"), aes(Date, Rescale, group = 1), fill = rgb(156, 156, 156, maxColorValue = 255), inherit.aes = FALSE)+
    geom_errorbar(aes(ymin = Mean, ymax = Mean + SD), 
                  color = "black", position = position_dodge(19), width = 14) +
    geom_col(position = position_dodge(19), width = 17, color = "black") +
    #Adding pattern to indicate estimated values:
    geom_col_pattern(aes(pattern = ifelse(format(RetDate, "%Y-%m") == "2025-05" | format(RetDate, "%Y-%m") == "2025-09", "stripe", NA)), pattern_density = 0.4, pattern_fill = "white", position = position_dodge(19), width = 17, color = "black", show.legend = FALSE)+
    geom_text(aes(y = HelperLocation, label = Helper, fill = Position), 
              position = position_dodge(15), size = 9) +
    scale_x_date("", expand= c(0,0), date_breaks = "2 months", date_labels = "%b %Y", limits = c(Start_date %m-% days(5), End_date %m-% days(5)))+
    scale_y_continuous(case_when(Working_param == "Rate" ~ "Sedimentation\nRate (g/month)", 
                                 Working_param == "OrgContent" ~ "Organic\nContent (%)", 
                                 Working_param == "OrgWt" ~ "Organic Weight\n(g/month)", 
                                 TRUE ~ "Something is missing."), 
                       expand = c(0,0), limits = c(0, y_max), 
                       sec.axis = sec_axis(
                         local({
                           flow_scale <- flow_max/y_max
                           ~.*(flow_scale)}),
                         breaks = flow_breaks))+
    Position_fill + Position_color + BaseForm + PlotTitle + 
    theme(axis.title.y = element_text(size = 14),
          legend.position = "none")
}

rm(i, Working_site, df_temp, max_upper, y_breaks, y_max, temp_flow, flow_scale)
#
g1 <- ggplotGrob(Posi_list[[1]] + rremove("x.title") + rremove("x.text")) 
g2 <- ggplotGrob(Posi_list[[2]] + rremove("x.title") + rremove("x.text"))
g3 <- ggplotGrob(Posi_list[[3]] + rremove("x.title"))
max_widths <- grid::unit.pmax(
  g1$widths,
  g2$widths,
  g3$widths
)

g1$widths <- max_widths
g2$widths <- max_widths
g3$widths <- max_widths
#
Posi_fig <- gridExtra::arrangeGrob(
  gridExtra::arrangeGrob(
    g1, g2, g3,
    ncol = 1, heights = c(0.9, 0.9, 1.1)),
  textGrob("Flow (cfs)", rot = 270, 
                   gp = gpar(fontfamily = "serif", col = "black", fontsize = 17)),
  ncol = 2,
  widths = c(20, 1.5)
  )
#
grid::grid.draw(Posi_fig)
#
#
```

**PBC Appendix Tables and Figures**

Supplementary tables and figures of survey, recruitment, and reproductive activity data from 2015 through 2023. Figures are presented in the same format as the main in-text figures.
\
\

```{r A1 table}
#
A1tab <- full_join(
  PBC_Sal %>% 
    mutate(Month = month(RetDate, label = TRUE, abbr = TRUE),
           StaCode = paste0(Site, Station)) %>%
    group_by(Month, StaCode) %>% 
    summarise(Salinity = mean(Salinity, na.rm = T)) %>% 
    pivot_wider(names_from = StaCode, values_from = Salinity) %>%
    dplyr::select(LWR4, LWL1, LWL2, LWR2, LWR3, LWL3),
  PBC_Sal %>% 
    mutate(Month = month(RetDate, label = TRUE, abbr = TRUE)) %>%
    group_by(Month) %>% 
    summarise(`Monthly Ave` = mean(Salinity, na.rm = T))) %>%
  ungroup() %>%
  drop_na() %>%
  bind_rows(
    summarise(.,
              Month = "Station Ave",
              across(where(is.numeric), ~ mean(.x, na.rm = TRUE)))) #%>%
  #mutate(
   # across(where(is.numeric), ~ format(round(.x, 1), trim = TRUE, nsmall = 0)))
#
A1tab %>%
  flextable() %>%
  # Font
  font(fontname = "Times New Roman", part = "all") %>%
  fontsize(size = 10, part = "all") %>%
  # Remove all default borders
  border_remove() %>%
  # Header formatting
  bold(part = "header") %>%
  # Alignment
  align(
    j = c("Month"),
    align = "left",
    part = "all") %>%
  align(
    j = c("LWR4",
          "LWL1",
          "LWL2",
          "LWR2",
          "LWR3",
          "LWL3",
          "Monthly Ave"),
    align = "center",
    part = "all") %>%
  # All borders
  border_inner_h(border = fp_border(color = "black", width = 1), part = "all") %>%
  border_inner_v(border = fp_border(color = "black", width = 1), part = "all") %>%
  # Header and bottom borders
  hline_top(border = fp_border(color = "black", width = 2), part = "header") %>%
  hline_bottom(border = fp_border(color = "black", width = 2), part = "header") %>%
  hline_bottom(border = fp_border(color = "black", width = 2), part = "body") %>%
  # Bold values
  bold(j = 1, part = "body") %>%
  bold(i = 13, part = "body") %>%
  # Color cells - green
  {ft <- .
    num_cols <- names(A1tab)[sapply(A1tab, is.numeric)]
    for (col in num_cols) {
      vals <- as.numeric(A1tab[[col]])
      ft <- bg(ft,
        i = which(A1tab[[col]] >= 10 & A1tab[[col]] <= 20),
        j = col,
        bg = "#C5F3C5")}
    ft} %>%
  # Color cells - tan
  {ft <- .
    num_cols <- names(A1tab)[sapply(A1tab, is.numeric)]
    for (col in num_cols) {
      vals <- as.numeric(A1tab[[col]])
      ft <- bg(ft,
        i = which(A1tab[[col]] > 20),
        j = col,
        bg = "#FAE2B2")}
    ft} %>%
  # Color cells - blue
  {ft <- .
    num_cols <- names(A1tab)[sapply(A1tab, is.numeric)]
    for (col in num_cols) {
      vals <- as.numeric(A1tab[[col]])
      ft <- bg(ft,
        i = which(A1tab[[col]] < 10),
        j = col,
        bg = "#B8E3E9")}
    ft} %>%
  # Number formatting
  colformat_double(
    j = names(A1tab)[sapply(A1tab, is.numeric)],
    digits = 1) %>%
  # Caption
  set_caption(
    caption = "Table A1. Average monthly salinity at natural reef (LWL) and restored reef (LWR) monitoring stations in Lake Worth Lagoon. Stations are arranged north to south (left to right) with relative proximity to C-51 denoted by the C-51 column in the table. Salinities are designated as falling within the target range of 10-20 (green) or above the target range (orange).") %>%
  # Automatically size columns
  autofit()
#
#
```