---
title: "PBC Monthly Report - `r params$Year`-`r params$Month`"
output: 
  word_document:
      reference_docx: Monthly-Reports-template.docx
params: 
  Month: "06"  #Enter 2-digit month
  Year: "2024" #Enter 4-digit year
  
knit: (function(inputFile, encoding) {
  rmarkdown::render(
    input = inputFile, encoding = encoding,
    output_file = paste0(substr(inputFile, 1, nchar(inputFile)-14), " - ", with(rmarkdown::yaml_front_matter(inputFile), paste(params$Year, params$Month)),'.docx')) 
      })
---

```{r VariableSet, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

Author <- c("E Levine") #Change to your name
Database <- "Oysters_24-06-28_test"  #Set the local database to use
Server = "localhost\\ERICALOCALSQL" #Set the local Server to use


#Don't modify code in rest of section
Estuaries <- c("LW")
LocationIDs <- c("0235", "0236", "0237", "0240", "0241", "0312")
Month <- params$Month 
Year <- params$Year   
Survey <- ifelse(as.numeric(Month) > 11 | as.numeric(Month) < 3, paste0("Winter", Year),
                 ifelse(as.numeric(Month) > 2 & as.numeric(Month) < 6, paste0("Spring", Year),
                        ifelse(as.numeric(Month) > 5 & as.numeric(Month) < 9, paste0("Summer", Year), paste0("Fall", Year))))
```

```{r PackageLoad & VarSet, echo = FALSE, warning = FALSE, message = FALSE}
# Load necessary R packages
if (!require("pacman")) {install.packages("pacman")}
pacman::p_load(odbc, DBI, dbplyr,
  tidyverse, dplyr,  #DF manipulation
  #readxl,          #Excel
  lubridate,         #Dates
  knitr, here,
  flextable,
  install = TRUE)

MonYr <- paste(month.abb[as.numeric(Month)], Year, sep = " ")
ReportStart <- as.Date(paste(Year, Month, "01", sep = "-")) - months(1)
ReportEnd <- as.Date(format(ceiling_date(ReportStart %m+% months(2)) - days(1), "%Y-%m-%d"))
NorthStations <- c("0312", "0235", "0236")
SouthStations <- c("0240", "0241", "0237")
NS_Order <- c('LWR4', 'LWL1', 'LWL2', 'LWR2', 'LWR3', 'LWL3')
```

```{r DatabaseDownload}
# Connect to Local database server and pull all necessary data, then close connection 
con <- dbConnect(odbc(),
                    Driver = "SQL Server", 
                    Server = Server,
                    Database = Database,
                    Authentication = "ActiveDirectoryIntegrated")

dboFixedLocations <- tbl(con,in_schema("dbo", "FixedLocations")) %>%
  collect() %>% 
  filter(Estuary %in% Estuaries)
hsdbSampleEventWQ <- tbl(con,in_schema("hsdb", "SampleEventWQ")) %>%
  collect() %>%
  filter(substring(SampleEventID, 1, 2) %in% Estuaries)
dboSampleEventWQ <- tbl(con,in_schema("dbo", "SampleEventWQ")) %>%
  collect() %>%
  filter(substring(SampleEventID, 1, 2) %in% Estuaries)
hsdbRecruitment <- tbl(con,in_schema("hsdb", "Recruitment")) %>%
  collect() %>%
  filter(substring(SampleEventID, 1, 2) %in% Estuaries)
dboRecruitment <- tbl(con,in_schema("dbo", "Recruitment")) %>%
  collect() %>%
  filter(substring(SampleEventID, 1, 2) %in% Estuaries)
hsdbDermo <- tbl(con,in_schema("hsdb", "Dermo")) %>%
  collect() %>%
  filter(substring(SampleEventID, 1, 2) %in% Estuaries)
dboDermo <- tbl(con,in_schema("dbo", "Dermo")) %>%
  collect() %>%
  filter(substring(SampleEventID, 1, 2) %in% Estuaries) %>%
  mutate(DermoMantle = as.numeric(DermoMantle),
         DermoGill = as.numeric(DermoGill))
hsdbSediment <- tbl(con,in_schema("hsdb", "SedimentTrap")) %>%
  collect() %>%
  filter(substring(SampleEventID, 1, 2) %in% Estuaries)
dboSediment <- tbl(con,in_schema("dbo", "SedimentTrap")) %>%
  collect() %>%
  filter(substring(SampleEventID, 1, 2) %in% Estuaries)

if(Month == "03" | Month == "06" | Month == "09" | Month == "12"){
  hsdbSurvey <- tbl(con,in_schema("hsdb", "SurveyQuadrat")) %>%
    collect() %>%
    filter(substring(SampleEventID, 1, 2) %in% Estuaries)
  dboSurvey <- tbl(con,in_schema("dbo", "SurveyQuadrat")) %>%
    collect() %>%
    filter(substring(SampleEventID, 1, 2) %in% Estuaries)} else {hsdbSurvey <- "Survey was not conducted."}
DBI::dbDisconnect(con)
```

```{r DataFilters and Summaries}
# Filter data frames so that only data collected for inclusion in the CERP Monthly Report are present.
FixedLocations1 <- dboFixedLocations %>% 
  mutate(StationNumber = as.numeric(StationNumber)) %>% 
  filter(FixedLocationID %in% LocationIDs) %>% #Only need SLC stations (0255-0257), CR2 (0231), and CR3 (0232)
  select(FixedLocationID,
         Estuary,
         SectionName, 
         StationNumber) %>% 
  distinct()  

### WATER QUALITY ###
WQ1 <- union(hsdbSampleEventWQ, dboSampleEventWQ) %>% 
  mutate(RetDate = as.Date(substring(SampleEventID, 8, 15), format = "%Y%m%d"), 
         FixedLocationID = substring(SampleEventID, 19, 22), 
         AnalysisDate = as.Date(floor_date(RetDate, unit = "month")),
         Plot_Date = as.Date(AnalysisDate + 14),
         SecchiPercent = (Secchi / Depth) * 100) %>%
  select(SampleEventWQID,
         FixedLocationID,
         SampleEventID,
         RetDate,
         AnalysisDate,
         Plot_Date,
         Temperature,
         Salinity,
         DissolvedOxygen,
         pH,
         SecchiPercent) %>% 
  drop_na(Temperature) %>%
  filter(RetDate >= ReportStart & RetDate < ReportEnd & FixedLocationID %in% LocationIDs) %>%
  left_join(FixedLocations1, by = c("FixedLocationID")) 

LWL_WQStats <- WQ1 %>% 
  filter(str_detect(SampleEventWQID, 'COLL') & SectionName == "L") %>%
  group_by(AnalysisDate, 
           Plot_Date, 
           RetDate,
           Estuary,  
           SectionName) %>% 
  summarise(SalMean = mean(Salinity, na.rm = TRUE),
            SalSD = sd(Salinity, na.rm = T))

LWR_WQStats <- WQ1 %>% 
  filter(str_detect(SampleEventWQID, 'COLL') & SectionName == "R") %>%
  group_by(AnalysisDate, 
           Plot_Date,  
           RetDate,
           Estuary,  
           SectionName) %>% 
  summarise(SalMean = mean(Salinity, na.rm = TRUE),
            SalSD = sd(Salinity, na.rm = T))


### RECRITMENT ###
R1 <- union(hsdbRecruitment, dboRecruitment) %>% 
  filter(ShellPosition %in% c(2,3,4,5,8,9,10,11)) %>%
  mutate(DeployedDate = as.Date(DeployedDate), 
         RetDate = as.Date(substring(SampleEventID, 8, 15), format = "%Y%m%d"), 
         FixedLocationID = substring(ShellID, 19, 22), 
         NumDays = as.numeric(RetDate-DeployedDate),
         BottomMonth= NumBottom/(NumDays/28),
         AnalysisDate = as.Date(floor_date(RetDate, unit = "month")),
         Plot_Date = as.Date(AnalysisDate + 14)) %>%
  select(ShellID,
         FixedLocationID,
         SampleEventID,
         DeployedDate,
         RetDate,
         AnalysisDate,
         Plot_Date,
         NumDays,
         ShellPosition,
         NumBottom,
         BottomMonth) %>% 
  filter(RetDate >= ReportStart & RetDate < ReportEnd) %>%
  left_join(FixedLocations1, by = c("FixedLocationID"))

LWL_RecruitStats <-  R1 %>% 
  filter(SectionName == "L") %>%
  group_by(AnalysisDate, Plot_Date, RetDate, Estuary, SectionName) %>%
   summarise(RcrtMean = mean(BottomMonth, na.rm = TRUE), 
            RcrtSD= sd(BottomMonth, na.rm = TRUE))

LWR_RecruitStats <-  R1 %>% 
  filter(SectionName == "R") %>%
  group_by(AnalysisDate, Plot_Date, RetDate, Estuary, SectionName) %>%
   summarise(RcrtMean = mean(BottomMonth, na.rm = TRUE), 
            RcrtSD= sd(BottomMonth, na.rm = TRUE))

### DERMO ###
Dermo1 <- union((hsdbDermo %>% dplyr::select(-OldSampleNumber)), dboDermo) %>% 
  mutate(FixedLocationID = substring(SampleEventID, 19, 22), 
         RetDate = as.Date(substring(SampleEventID, 8, 15), format = "%Y%m%d"),
         AnalysisDate = as.Date(floor_date(RetDate, unit = "month")),
         Plot_Date = as.Date(AnalysisDate + 14),
         DermoSum = as.numeric(ifelse(rowSums(select(., contains("Dermo"))) >0, 1, 0))) %>%
  select(OysterID,
         FixedLocationID,
         SampleEventID,
         RetDate,
         AnalysisDate,
         Plot_Date,
         DermoMantle,
         DermoGill,
         DermoSum) %>% 
  filter(RetDate >= ReportStart & RetDate < ReportEnd & FixedLocationID %in% LocationIDs) %>%
  left_join(FixedLocations1, by = c("FixedLocationID"))

LWL_DermoStats <- Dermo1 %>%
  filter(SectionName == "L") %>%
  group_by(AnalysisDate, 
           Plot_Date,  
           RetDate,
           Estuary,  
           SectionName) %>% 
  summarise(DermoPct = (sum(DermoSum, na.rm = TRUE)/n())*100)

LWR_DermoStats <- Dermo1 %>%
  filter(SectionName == "R") %>%
  group_by(AnalysisDate, 
           Plot_Date,  
           RetDate,
           Estuary,  
           SectionName) %>% 
  summarise(DermoPct = (sum(DermoSum, na.rm = TRUE)/n())*100)


### SURVEY ###
if(Month == "03" | Month == "06" | Month == "09" | Month == "12"){
Survey1 <- union(hsdbSurvey, dboSurvey) %>% 
  mutate(FixedLocationID = substring(SampleEventID, 19, 22), 
         RetDate = as.Date(substring(SampleEventID, 8, 15), format = "%Y%m%d"),
         AnalysisDate = as.Date(floor_date(RetDate, unit = "month")),
         Plot_Date = as.Date(AnalysisDate + 14),
         Live = NumLive * 4,
         Dead = NumDead * 4) %>%
  select(QuadratID,
         FixedLocationID,
         SampleEventID,
         RetDate,
         AnalysisDate,
         Plot_Date,
         QuadratNumber,
         Live,
         Dead) %>% 
  filter(RetDate >= ReportStart & RetDate < ReportEnd & FixedLocationID %in% LocationIDs) %>%
  left_join(FixedLocations1, by = c("FixedLocationID"))
}else{Survey1 <- "Survey was not conducted."}

if(Month == "03" | Month == "06" | Month == "09" | Month == "12"){
  LWL_SurveyStats <- Survey1 %>%
    filter(SectionName == "L") %>%
    group_by(AnalysisDate, 
             Plot_Date,  
             RetDate,
             Estuary,  
             SectionName) %>%
    summarise(LiveMean = mean(Live, na.rm = T),
              LiveSD = sd(Live, na.rm = T),
              DeadMean = mean(Dead, na.rm = T),
              DeadSD = sd(Dead, na.rm = T))
}else{LWL_SurveyStats <- "Survey was not conducted."}

if(Month == "03" | Month == "06" | Month == "09" | Month == "12"){
  LWR_SurveyStats <- Survey1 %>%
    filter(SectionName == "R") %>%
    group_by(AnalysisDate, 
             Plot_Date,  
             RetDate,
             Estuary,  
             SectionName) %>%
    summarise(LiveMean = mean(Live, na.rm = T),
              LiveSD = sd(Live, na.rm = T),
              DeadMean = mean(Dead, na.rm = T),
              DeadSD = sd(Dead, na.rm = T))
}else{LWR_SurveyStats <- "Survey was not conducted."}

### SEDIMENT TRAPS ###
Sedi1 <- union(hsdbSediment, dboSediment) %>% 
  mutate(Proportion = (CrucibleDW-TareCrucible)/((PanDryWeight - PanTareWeight) + (FilterDryWeight - FilterTareWeight)))%>%
  mutate(DeployedDate = as.Date(DeployedDate), 
         RetDate = as.Date(substring(SampleEventID, 8, 15), format = "%Y%m%d"), 
         NumDays = as.numeric(RetDate-DeployedDate),
         FixedLocationID = substring(SampleEventID, 19, 22), 
         AnalysisDate = as.Date(floor_date(RetDate, unit = "month")),
         Plot_Date = as.Date(AnalysisDate + 14),
         Position = case_when(FixedLocationID %in% NorthStations ~ "North",
                             FixedLocationID %in% SouthStations ~ "South",
                             TRUE ~ NA),
          Proportion = (CrucibleDW-TareCrucible)/((PanDryWeight-PanTareWeight)+(FilterDryWeight-FilterTareWeight)),
         TotalDW = (PanDryWeight - PanTareWeight) + (FilterDryWeight - FilterTareWeight),
         TotalAsh = (AshWeight - TareCrucible)*(1/Proportion),
         OrganicWt = TotalDW - TotalAsh, 
         PctOrganic = (OrganicWt/TotalDW) * 100) %>%
  select(CupSampleID,
         FixedLocationID,
         SampleEventID,
         DeployedDate,
         RetDate,
         AnalysisDate,
         Plot_Date,
         NumDays,
         Position,
         Proportion,
         TotalDW,
         TotalAsh,
         OrganicWt,
         PctOrganic) %>% 
  filter(RetDate >= ReportStart & RetDate < ReportEnd) %>%
  left_join(FixedLocations1, by = c("FixedLocationID"))

LW_SediStats <- Sedi1 %>%
  group_by(AnalysisDate, 
           Plot_Date,  
           RetDate,
           FixedLocationID,
           Estuary,  
           SectionName, 
           StationNumber,
           Position) %>%
  summarise(MonthRate = mean(TotalDW/(NumDays/28), na.rm = T),
            MeanOrganic = mean(PctOrganic, na.rm = T),
            MonthOrgWt = mean(OrganicWt/(NumDays/28), na.rm = T))

```

```{r Data summary tables}
#Output tables for LWL and LWR - combining WQ, Rcrt, Dermo, and Survey
LWL_Summary <- left_join(
  left_join(
    left_join(LWL_WQStats %>% ungroup() %>% dplyr::select(AnalysisDate, SalMean, SalSD),
              LWL_RecruitStats %>% ungroup() %>% dplyr::select(AnalysisDate, RcrtMean, RcrtSD)),
    LWL_DermoStats %>% ungroup() %>% dplyr::select(AnalysisDate, DermoPct)),
  #Add in survey data or placeholder if no survey conducted
  if(Month == "03" | Month == "06" | Month == "09" | Month == "12"){
    LWL_SurveyStats %>% ungroup() %>% dplyr::select(AnalysisDate, LiveMean:DeadSD) %>%
      mutate(Season = case_when(month(AnalysisDate) > 4 & month(AnalysisDate) < 10 ~ "WetSeason", TRUE ~ "DrySeason"), .before = LiveMean)
    }else{
      data.frame(AnalysisDate = LWL_WQStats$AnalysisDate, Survey = NA)
      }) %>%
  mutate(across(where(is.numeric), round, 2))


LWR_Summary <- left_join(
  left_join(
    left_join(LWR_WQStats %>% ungroup() %>% dplyr::select(AnalysisDate, SalMean, SalSD),
              LWR_RecruitStats %>% ungroup() %>% dplyr::select(AnalysisDate, RcrtMean, RcrtSD)),
    LWR_DermoStats %>% ungroup() %>% dplyr::select(AnalysisDate, DermoPct)),
  #Add in survey data or placeholder if no survey conducted
  if(Month == "03" | Month == "06" | Month == "09" | Month == "12"){
    LWR_SurveyStats %>% ungroup() %>% dplyr::select(AnalysisDate, LiveMean:DeadSD) %>%
      mutate(Season = case_when(month(AnalysisDate) > 4 & month(AnalysisDate) < 10 ~ "WetSeason", TRUE ~ "DrySeason"), .before = LiveMean)
    }else{
      data.frame(AnalysisDate = LWL_WQStats$AnalysisDate, Survey = NA)
      }) %>%
  mutate(across(where(is.numeric), round, 2))

##Output table for sediment traps - divided by North and South of C-51
Sedi_summary <- LW_SediStats %>% group_by(AnalysisDate, RetDate, Position) %>%
  summarise(Rate = mean(MonthRate, na.rm = T),
            OrganicPct = mean(MeanOrganic, na.rm = T),
            RateOrganicWt = mean(MonthOrgWt, na.rm = T)) %>%
  mutate(across(where(is.numeric), round, 2))

```

```{r Surevy Text}
#Text for survey section of monthly report
LWL_Srvy_note <- if(Month == "03" | Month == "09") {paste0("During the biannual ", if(Month == "03") {paste("spring")} else {paste("fall")}, " survey there were approximately ", round(LWL_SurveyStats$LiveMean,0), " live and ", round(LWL_SurveyStats$DeadMean,0), " dead oysters per 1 m2 quadrat.")} else {paste("Survey was not conducted this month")}

LWR_Srvy_note <- if(Month == "03" | Month == "09") {paste0("During the biannual ", if(Month == "03") {paste("spring")} else {paste("fall")}, " survey there were approximately ", round(LWR_SurveyStats$LiveMean,0), " live and ", round(LWR_SurveyStats$DeadMean,0), " dead oysters per 1 m2 quadrat.")} else {paste("Survey was not conducted this month")}

```

```{r ReportText}
#Report Text in area below
```

## Report summary
This monthly report was compiled by `r Author` on `r format(Sys.Date(), "%d %B %Y")` and summarizes data for **Palm Beach County** sites in **`r MonYr`**. Analysis covers data occurring between *`r format(ReportStart, "%d %B %Y")`* and *`r format(ReportEnd,  "%d %B %Y")`* at natural reef and restored reef stations.\

## Lake Worth Lagoon summary

Here is the monthly report with the data collected from the Lake Worth Lagoon stations on `r max(LWL_WQStats$RetDate) %>% format("%B %d, %Y")`:

*	Mean salinity 
`r if((LWL_WQStats %>% filter(RetDate == min(LWL_WQStats$RetDate)))$SalMean > (LWL_WQStats %>% filter(RetDate == max(LWL_WQStats$RetDate)))$SalMean) {paste("decreased")} else if ((LWL_WQStats %>% filter(RetDate == min(LWL_WQStats$RetDate)))$SalMean < (LWL_WQStats %>% filter(RetDate == max(LWL_WQStats$RetDate)))$SalMean) {paste("increased")} else {paste("stayed the same")}` 
from 
`r round((LWL_WQStats %>% filter(RetDate == min(LWL_WQStats$RetDate)))$SalMean,2)` 
in 
`r min(LWL_WQStats$RetDate) %>% format("%B")` 
to 
`r round((LWL_WQStats %>% filter(RetDate == max(LWL_WQStats$RetDate)))$SalMean,2)` 
in 
`r max(LWL_WQStats$RetDate) %>% format("%B")`.
*	The mean recruitment rate 
`r if((LWL_RecruitStats %>% filter(RetDate == min(LWL_RecruitStats$RetDate)))$RcrtMean > (LWL_RecruitStats %>% filter(RetDate == max(LWL_RecruitStats$RetDate)))$RcrtMean) {paste("decreased")} else if ((LWL_RecruitStats %>% filter(RetDate == min(LWL_RecruitStats$RetDate)))$RcrtMean < (LWL_RecruitStats %>% filter(RetDate == max(LWL_RecruitStats$RetDate)))$RcrtMean) {paste("increased")} else {paste("stayed the same")}` 
from 
`r round((LWL_RecruitStats %>% filter(RetDate == min(LWL_RecruitStats$RetDate)))$RcrtMean,2)` 
spat/shell in 
`r min(LWL_RecruitStats$RetDate) %>% format("%B")` 
to 
`r round((LWL_RecruitStats %>% filter(RetDate == max(LWL_RecruitStats$RetDate)))$RcrtMean,2)` 
spat/shell in 
`r max(LWL_RecruitStats$RetDate) %>% format("%B")`.
*	Dermo prevalence 
`r if((LWL_DermoStats %>% filter(RetDate == min(LWL_DermoStats$RetDate)))$DermoPct > (LWL_DermoStats %>% filter(RetDate == max(LWL_DermoStats$RetDate)))$DermoPct) {paste("decreased")} else if ((LWL_DermoStats %>% filter(RetDate == min(LWL_DermoStats$RetDate)))$DermoPct < (LWL_DermoStats %>% filter(RetDate == max(LWL_DermoStats$RetDate)))$DermoPct) {paste("increased")} else {paste("stayed the same")}` 
from
`r round((LWL_DermoStats %>% filter(RetDate == min(LWL_DermoStats$RetDate)))$DermoPct,2)`% 
in 
`r min(LWL_DermoStats$RetDate) %>% format("%B")` 
to 
`r round((LWL_DermoStats %>% filter(RetDate == max(LWL_DermoStats$RetDate)))$DermoPct,2)`% 
of the oysters sampled in
`r max(LWL_DermoStats$RetDate) %>% format("%B")`.
* `r if(Month == "03" | Month == "09") {paste(LWL_Srvy_note)} else {paste("Survey was not conducted this month")}`
\

## Lake Worth Restoration summary 

Here is the monthly report with data collected from the Lake Worth Restoration stations on `r max(LWR_WQStats$RetDate) %>% format("%B %d, %Y")`:

*	Mean salinity 
`r if((LWR_WQStats %>% filter(RetDate == min(LWR_WQStats$RetDate)))$SalMean > (LWR_WQStats %>% filter(RetDate == max(LWR_WQStats$RetDate)))$SalMean) {paste("decreased")} else if ((LWR_WQStats %>% filter(RetDate == min(LWR_WQStats$RetDate)))$SalMean < (LWR_WQStats %>% filter(RetDate == max(LWR_WQStats$RetDate)))$SalMean) {paste("increased")} else {paste("stayed the same")}` 
from 
`r round((LWR_WQStats %>% filter(RetDate == min(LWR_WQStats$RetDate)))$SalMean,2)` 
in 
`r min(LWR_WQStats$RetDate) %>% format("%B")` 
to 
`r round((LWR_WQStats %>% filter(RetDate == max(LWR_WQStats$RetDate)))$SalMean,2)` 
in 
`r max(LWR_WQStats$RetDate) %>% format("%B")`.
*	The mean recruitment rate 
`r if((LWR_RecruitStats %>% filter(RetDate == min(LWR_RecruitStats$RetDate)))$RcrtMean > (LWR_RecruitStats %>% filter(RetDate == max(LWR_RecruitStats$RetDate)))$RcrtMean) {paste("decreased")} else if ((LWR_RecruitStats %>% filter(RetDate == min(LWR_RecruitStats$RetDate)))$RcrtMean < (LWR_RecruitStats %>% filter(RetDate == max(LWR_RecruitStats$RetDate)))$RcrtMean) {paste("increased")} else {paste("stayed the same")}` 
from 
`r round((LWR_RecruitStats %>% filter(RetDate == min(LWR_RecruitStats$RetDate)))$RcrtMean,2)` 
spat/shell in 
`r min(LWR_RecruitStats$RetDate) %>% format("%B")` 
to 
`r round((LWR_RecruitStats %>% filter(RetDate == max(LWR_RecruitStats$RetDate)))$RcrtMean,2)` 
spat/shell in 
`r max(LWR_RecruitStats$RetDate) %>% format("%B")`.
*	Dermo prevalence 
`r if((LWR_DermoStats %>% filter(RetDate == min(LWR_DermoStats$RetDate)))$DermoPct > (LWR_DermoStats %>% filter(RetDate == max(LWR_DermoStats$RetDate)))$DermoPct) {paste("decreased")} else if ((LWR_DermoStats %>% filter(RetDate == min(LWR_DermoStats$RetDate)))$DermoPct < (LWR_DermoStats %>% filter(RetDate == max(LWR_DermoStats$RetDate)))$DermoPct) {paste("increased")} else {paste("stayed the same")}` 
from
`r round((LWR_DermoStats %>% filter(RetDate == min(LWR_DermoStats$RetDate)))$DermoPct,2)`% 
in 
`r min(LWR_DermoStats$RetDate) %>% format("%B")` 
to 
`r round((LWR_DermoStats %>% filter(RetDate == max(LWR_DermoStats$RetDate)))$DermoPct,2)`% 
of the oysters sampled in
`r max(LWR_DermoStats$RetDate) %>% format("%B")`.
* `r if(Month == "03" | Month == "09") {paste(LWL_Srvy_note)} else {paste("Survey was not conducted this month")}`
\

## Lake Worth sediment trap summary 

Here is the monthly report with sediment data collected from the Lake Worth Lagoon and Lake Worth Restoration stations on `r max(LWL_WQStats$RetDate) %>% format("%B %d, %Y")`:

* The mean monthly sedimentation rate at the stations north of the C-51 output 
`r if((Sedi_summary %>% filter(Position == "North" & RetDate == min(Sedi_summary$RetDate)))$Rate > (Sedi_summary %>% filter(Position == "North" & RetDate == max(Sedi_summary$RetDate)))$Rate) {paste("decreased")} else if ((Sedi_summary %>% filter(Position == "North" & RetDate == min(Sedi_summary$RetDate)))$Rate < (Sedi_summary %>% filter(Position == "North" & RetDate == max(Sedi_summary$RetDate)))$Rate) {paste("increased")} else {paste("stayed the same")}` 
from 
`r (Sedi_summary %>% filter(Position == "North" & RetDate == min(Sedi_summary$RetDate)))$Rate`
g/month in 
`r min(Sedi_summary$RetDate) %>% format("%B")` 
to 
`r (Sedi_summary %>% filter(Position == "North" & RetDate == max(Sedi_summary$RetDate)))$Rate`
g/month in
`r max(Sedi_summary$RetDate) %>% format("%B")`,
and the mean percent organic content
`r if((Sedi_summary %>% filter(Position == "North" & RetDate == min(Sedi_summary$RetDate)))$OrganicPct > (Sedi_summary %>% filter(Position == "North" & RetDate == max(Sedi_summary$RetDate)))$OrganicPct) {paste("decreased")} else if ((Sedi_summary %>% filter(Position == "North" & RetDate == min(Sedi_summary$RetDate)))$OrganicPct < (Sedi_summary %>% filter(Position == "North" & RetDate == max(Sedi_summary$RetDate)))$OrganicPct) {paste("increased")} else {paste("stayed the same")}` 
from 
`r (Sedi_summary %>% filter(Position == "North" & RetDate == min(Sedi_summary$RetDate)))$OrganicPct`%
in 
`r min(Sedi_summary$RetDate) %>% format("%B")` 
to 
`r (Sedi_summary %>% filter(Position == "North" & RetDate == max(Sedi_summary$RetDate)))$OrganicPct`%
in
`r max(Sedi_summary$RetDate) %>% format("%B")`.
The mean monthly organic weight 
`r if((Sedi_summary %>% filter(Position == "North" & RetDate == min(Sedi_summary$RetDate)))$RateOrganicWt > (Sedi_summary %>% filter(Position == "North" & RetDate == max(Sedi_summary$RetDate)))$RateOrganicWt) {paste("decreased")} else if ((Sedi_summary %>% filter(Position == "North" & RetDate == min(Sedi_summary$RetDate)))$RateOrganicWt < (Sedi_summary %>% filter(Position == "North" & RetDate == max(Sedi_summary$RetDate)))$RateOrganicWt) {paste("increased")} else {paste("stayed the same")}` 
from 
`r (Sedi_summary %>% filter(Position == "North" & RetDate == min(Sedi_summary$RetDate)))$RateOrganicWt`
g/month in 
`r min(Sedi_summary$RetDate) %>% format("%B")` 
to 
`r (Sedi_summary %>% filter(Position == "North" & RetDate == max(Sedi_summary$RetDate)))$RateOrganicWt`
g/month in
`r max(Sedi_summary$RetDate) %>% format("%B")`.

* The mean monthly sedimentation rate at the stations south of the C-51 output 
`r if((Sedi_summary %>% filter(Position == "South" & RetDate == min(Sedi_summary$RetDate)))$Rate > (Sedi_summary %>% filter(Position == "South" & RetDate == max(Sedi_summary$RetDate)))$Rate) {paste("decreased")} else if ((Sedi_summary %>% filter(Position == "South" & RetDate == min(Sedi_summary$RetDate)))$Rate < (Sedi_summary %>% filter(Position == "South" & RetDate == max(Sedi_summary$RetDate)))$Rate) {paste("increased")} else {paste("stayed the same")}` 
from 
`r (Sedi_summary %>% filter(Position == "South" & RetDate == min(Sedi_summary$RetDate)))$Rate`
g/month in 
`r min(Sedi_summary$RetDate) %>% format("%B")` 
to 
`r (Sedi_summary %>% filter(Position == "South" & RetDate == max(Sedi_summary$RetDate)))$Rate`
g/month in
`r max(Sedi_summary$RetDate) %>% format("%B")`,
and the mean percent organic content
`r if((Sedi_summary %>% filter(Position == "South" & RetDate == min(Sedi_summary$RetDate)))$OrganicPct > (Sedi_summary %>% filter(Position == "South" & RetDate == max(Sedi_summary$RetDate)))$OrganicPct) {paste("decreased")} else if ((Sedi_summary %>% filter(Position == "South" & RetDate == min(Sedi_summary$RetDate)))$OrganicPct < (Sedi_summary %>% filter(Position == "South" & RetDate == max(Sedi_summary$RetDate)))$OrganicPct) {paste("increased")} else {paste("stayed the same")}` 
from 
`r (Sedi_summary %>% filter(Position == "South" & RetDate == min(Sedi_summary$RetDate)))$OrganicPct`%
in 
`r min(Sedi_summary$RetDate) %>% format("%B")` 
to 
`r (Sedi_summary %>% filter(Position == "South" & RetDate == max(Sedi_summary$RetDate)))$OrganicPct`%
in
`r max(Sedi_summary$RetDate) %>% format("%B")`.
The mean monthly organic weight 
`r if((Sedi_summary %>% filter(Position == "South" & RetDate == min(Sedi_summary$RetDate)))$RateOrganicWt > (Sedi_summary %>% filter(Position == "South" & RetDate == max(Sedi_summary$RetDate)))$RateOrganicWt) {paste("decreased")} else if ((Sedi_summary %>% filter(Position == "South" & RetDate == min(Sedi_summary$RetDate)))$RateOrganicWt < (Sedi_summary %>% filter(Position == "South" & RetDate == max(Sedi_summary$RetDate)))$RateOrganicWt) {paste("increased")} else {paste("stayed the same")}` 
from 
`r (Sedi_summary %>% filter(Position == "South" & RetDate == min(Sedi_summary$RetDate)))$RateOrganicWt`
g/month in 
`r min(Sedi_summary$RetDate) %>% format("%B")` 
to 
`r (Sedi_summary %>% filter(Position == "South" & RetDate == max(Sedi_summary$RetDate)))$RateOrganicWt`
g/month in
`r max(Sedi_summary$RetDate) %>% format("%B")`.
\

```{r echo=FALSE, restults = 'asis'}
set_flextable_defaults(na_str = "--", nan_str = "--")

#Create base table
Sedi_table <- LW_SediStats %>% mutate(Month = format(RetDate, "%B"), Station = paste0(Estuary, SectionName, StationNumber), MonthRate = round(MonthRate, 2), MeanOrganic = round(MeanOrganic, 2), RateOrganicWt = round(MonthOrgWt, 2)) %>% rename("Monthly rate (g/month)" = MonthRate, "Mean % organic" = MeanOrganic, "Mean rate organic weight (g/month)" = RateOrganicWt) %>% mutate(Station = factor(Station, levels = NS_Order)) %>% pivot_wider(id_cols = Station, names_from = Month, values_from = c("Monthly rate (g/month)", "Mean % organic", "Mean rate organic weight (g/month)"), names_glue = "{Month}_{.value}") %>% arrange(Station)


flextable(Sedi_table) %>% separate_header() %>% align(align = "center", part = "all") %>% 
  hline(i = 3, border = officer::fp_border(style = "dashed")) %>% vline(j = c(1,3, 5), border = officer::fp_border(style = "solid")) %>% autofit() %>% font(fontname = "Arial", part = "all") %>% fontsize(size = 11, part = "all") 

```
