---
output: 
  word_document:
  toc: true
---

```{r VariableSet, echo = FALSE, warning = FALSE, message = FALSE}
# Set your variables
ReportEnd <- as.Date("2024-03-31")  # Report End Date
Database = "OysterLocalMD20240425"  # Set the local database to use
Server = "localhost\\LOCALSQL" # Set the local Server to use
```

```{r PackageLoad, echo = FALSE, warning = FALSE, message = FALSE}
# Load necessary R packages
library(tidyverse)
library(odbc)
library(DBI)
library(dbplyr)
library(lubridate)
library(knitr)
library(ggpubr)
library(patchwork) #Required for arranging multiple plots, more flexible
library(scales)
```

```{r ConfigureChunks, warning=FALSE, include=FALSE}
# Configure chunks
knitr::opts_chunk$set(
	echo = FALSE,
	fig.height = 10,
	fig.width = 8,
	message = FALSE,
	warning = FALSE
)

ReportStart <- floor_date(ReportEnd %m-% months(14), unit = "month") 
QuarterStart <- floor_date(ReportEnd %m-% months(2), unit = "month")
Estuaries <- c("AB", "SS")
```

```{r DatabaseDownload}
# Connect to Local database server and pull all necessary data, then close connection 
con <- dbConnect(odbc(),
                    Driver = "SQL Server", 
                    Server = Server,
                    Database = Database,
                    Authentication = "ActiveDirectoryIntegrated")

dboFixedLocations <- tbl(con,in_schema("dbo", "FixedLocations")) %>%
  collect() %>% 
  filter(Estuary %in% Estuaries)
hsdbSampleEventWQ <- tbl(con,in_schema("hsdb", "SampleEventWQ")) %>%
  collect() %>%
  filter(substring(SampleEventID, 1, 2) %in% Estuaries)
dboSampleEventWQ <- tbl(con,in_schema("dbo", "SampleEventWQ")) %>%
  collect() %>%
  filter(substring(SampleEventID, 1, 2) %in% Estuaries)
hsdbRecruitment <- tbl(con,in_schema("hsdb", "Recruitment")) %>%
  collect() %>%
  filter(substring(SampleEventID, 1, 2) %in% Estuaries)
dboRecruitment <- tbl(con,in_schema("dbo", "Recruitment")) %>%
  collect() %>%
  filter(substring(SampleEventID, 1, 2) %in% Estuaries)
hsdbSedimentTrap <- tbl(con,in_schema("hsdb", "SedimentTrap")) %>%
  collect() %>%
  filter(substring(SampleEventID, 1, 2) %in% Estuaries)
dboSedimentTrap <- tbl(con,in_schema("dbo", "SedimentTrap")) %>%
  collect() %>%
  filter(substring(SampleEventID, 1, 2) %in% Estuaries)
DBI::dbDisconnect(con)
```

```{r DataFilters}
# Filter data frames so that only data collected for inclusion in the NFWF Report are present.
FixedLocations1 <- dboFixedLocations %>% 
  mutate(StationNumber = as.numeric(StationNumber)) %>% 
  select(FixedLocationID,
         Estuary,
         SectionName, 
         StationNumber) %>% 
  distinct()  # NOTE This does not include Parcel Name which is needed for SBM

### WATER QUALITY ###
WQ1 <- union(hsdbSampleEventWQ, dboSampleEventWQ) %>% 
  mutate(RetDate = as.Date(substring(SampleEventID, 8, 15), format = "%Y%m%d"), 
         FixedLocationID = substring(SampleEventID, 19, 22), 
         AnalysisDate = as.Date(floor_date(RetDate, unit = "month")),
         Plot_Date = as.Date(AnalysisDate + 14),
         SecchiPercent = (Secchi / Depth) * 100) %>%
  select(SampleEventWQID,
         FixedLocationID,
         SampleEventID,
         RetDate,
         AnalysisDate,
         Plot_Date,
         Temperature,
         Salinity,
         DissolvedOxygen,
         pH,
         SecchiPercent) %>% 
  drop_na(Temperature) %>%
  filter(RetDate >= ReportStart & RetDate < ReportEnd) %>%
  left_join(FixedLocations1, by = c("FixedLocationID")) 

AB_WQStats <- WQ1 %>% 
  filter(str_detect(SampleEventWQID, 'RCRT|SDTP') & Estuary == "AB") %>%
  group_by(AnalysisDate, 
           Plot_Date, 
           Estuary, 
           StationNumber, 
           SectionName) %>% 
  summarise(TempMean = mean(Temperature, na.rm = TRUE),
            SalMean = mean(Salinity, na.rm = TRUE),
            DOMean = mean(DissolvedOxygen, na.rm = TRUE), 
            pHMean = mean(pH, na.rm = TRUE), 
            SecchiMean = mean(SecchiPercent, na.rm = TRUE))

SS_WQStats <- WQ1 %>% 
  filter(str_detect(SampleEventWQID, 'RCRT|SDTP') & Estuary == "SS") %>%
  group_by(AnalysisDate, 
           Plot_Date, 
           Estuary, 
           StationNumber, 
           SectionName) %>% 
  summarise(TempMean = mean(Temperature, na.rm = TRUE),
            SalMean = mean(Salinity, na.rm = TRUE),
            DOMean = mean(DissolvedOxygen, na.rm = TRUE), 
            pHMean = mean(pH, na.rm = TRUE), 
            SecchiMean = mean(SecchiPercent, na.rm = TRUE))

AB_WQText <- AB_WQStats %>%
  filter(Plot_Date >= QuarterStart & Plot_Date < ReportEnd)

SS_WQText <- SS_WQStats %>%
  filter(Plot_Date >= QuarterStart & Plot_Date < ReportEnd)

### RECRITMENT ###
R1 <- union(hsdbRecruitment, dboRecruitment) %>% 
  filter(ShellPosition %in% c(2,3,4,5,8,9,10,11)) %>%
  mutate(DeployedDate = as.Date(DeployedDate), 
         RetDate = as.Date(substring(SampleEventID, 8, 15), format = "%Y%m%d"), 
         FixedLocationID = substring(ShellID, 19, 22), 
         NumDays = as.numeric(RetDate-DeployedDate),
         BottomMonth= NumBottom/(NumDays/28),
         AnalysisDate = as.Date(floor_date(RetDate, unit = "month")),
         Plot_Date = as.Date(AnalysisDate + 14)) %>%
  select(ShellID,
         FixedLocationID,
         SampleEventID,
         DeployedDate,
         RetDate,
         AnalysisDate,
         Plot_Date,
         NumDays,
         ShellPosition,
         NumBottom,
         BottomMonth) %>% 
  filter(RetDate >= ReportStart & RetDate < ReportEnd) %>%
  left_join(FixedLocations1, by = c("FixedLocationID"))
  
AB_RecruitStats <- R1 %>% 
  filter(Estuary == "AB") %>%
  group_by(AnalysisDate, Plot_Date, Estuary, StationNumber, SectionName) %>% 
  summarise(RecMean = mean(BottomMonth, na.rm = TRUE), 
            SD= sd(BottomMonth, na.rm = TRUE),
            Upper = RecMean + SD)

SS_RecruitStats <- R1 %>% 
  filter(Estuary == "SS") %>%
  group_by(AnalysisDate, Plot_Date, Estuary, StationNumber, SectionName) %>% 
  summarise(RecMean = mean(BottomMonth, na.rm = TRUE), 
            SD= sd(BottomMonth, na.rm = TRUE),
            Upper = RecMean + SD)

AB_RecruitText <- AB_RecruitStats %>%
  filter(Plot_Date >= QuarterStart & Plot_Date < ReportEnd)

SS_RecruitText <- SS_RecruitStats %>%
  filter(Plot_Date >= QuarterStart & Plot_Date < ReportEnd)

# Creates data frames for each section in each estuary by listing the variations and looping through those variations
lv1 <- list("AB_W", "AB_C", "AB_E", "SS_N", "SS_C", "SS_S")
lv2 <- list("AB", "AB", "AB", "SS", "SS", "SS")
lv3 <- list("W", "C", "E", "N", "C", "S")

for (i in seq_along(lv1)) {
  df_name <- paste0(lv1[i], "_RecruitStats")
  df_source <- get(paste0(lv2[i], "_RecruitStats")) 
  assign(df_name, df_source %>%
           filter(SectionName == lv3[i]) %>%
           group_by(StationNumber),
         envir = .GlobalEnv)
}

### SEDIMENT TRAP ###
# Note that traps with excessive biota are excluded from analysis
ST1 <- union(hsdbSedimentTrap, dboSedimentTrap) %>% 
  filter(NumFish == 0 & NumCrabs < 2 & NumDrills < 2 & NumHermitCrabs < 5) %>%
  mutate(DeployedDate = as.Date(DeployedDate), 
         RetDate = as.Date(substring(SampleEventID, 8, 15), format = "%Y%m%d"), 
         FixedLocationID = substring(SampleEventID, 19, 22), 
         NumDays = as.numeric(RetDate-DeployedDate),
         AnalysisDate = as.Date(floor_date(RetDate, unit = "month")),
         Plot_Date = as.Date(AnalysisDate + 14),
         SedWeight = (FilterDryWeight + PanDryWeight) - (FilterTareWeight + PanTareWeight),
         SedRate = SedWeight / (NumDays/28)) %>%
  select(CupSampleID,
         FixedLocationID,
         SampleEventID,
         DeployedDate,
         RetDate,
         AnalysisDate,
         Plot_Date,
         NumDays,
         SedWeight,
         SedRate) %>% 
  filter(RetDate >= ReportStart & RetDate < ReportEnd) %>%
  left_join(FixedLocations1, by = c("FixedLocationID"))

AB_SedimentStats <- ST1 %>% 
  filter(Estuary == "AB") %>%
  group_by(AnalysisDate, Plot_Date, Estuary, StationNumber, SectionName) %>% 
  summarise(SedMean = mean(SedRate, na.rm = TRUE), 
            SD = sd(SedRate, na.rm = TRUE),
            Upper = SedMean + SD)

AB_SedimentText <- AB_SedimentStats %>%
  filter(Plot_Date >= QuarterStart & Plot_Date < ReportEnd)

```

```{r ReportText}
#Report Text in area below
```

APALACHICOLA BAY <br><br>
Data reported in this section is preliminary as it has not been subjected to the full QA/QC process.

Preliminary recruitment data is available through the end of `r format(max(AB_RecruitText$AnalysisDate), "%B %Y")`. Recruitment rates ranged from `r round(min(AB_RecruitText$RecMean, na.rm = TRUE), 1)` to `r round(max(AB_RecruitText$RecMean, na.rm = TRUE), 1)` spat per shell in the last quarter. The maximum rate of `r round(max(AB_RecruitText$RecMean, na.rm = TRUE), 1)` was observed at Station `r AB_RecruitText$StationNumber[which.max(AB_RecruitText$RecMean)]` during sampling in `r format(AB_RecruitText$AnalysisDate[which.max(AB_RecruitText$RecMean)], "%B %Y")` (Fig. 4). 

Preliminary sediment trap data is available through the end of `r format(max(AB_SedimentText$AnalysisDate), "%B %Y")`. Sediment rates ranged from `r round(min(AB_SedimentText$SedMean, na.rm = TRUE), 1)` to `r round(max(AB_SedimentText$SedMean, na.rm = TRUE), 1)` grams (dry weight) of sediment in the last quarter. The maximum rate of `r round(max(AB_SedimentText$SedMean, na.rm = TRUE), 1)` was observed at Station `r AB_SedimentText$StationNumber[which.max(AB_SedimentText$SedMean)]` during sampling in `r format(AB_SedimentText$AnalysisDate[which.max(AB_SedimentText$SedMean)], "%B %Y")` (Fig. 5). 

Preliminary water quality data is available through the end of `r format(max(AB_WQText$AnalysisDate), "%B %Y")`. Water temperature, salinity, dissolved oxygen concentration, pH, water depth and Secchi depth were recorded during sampling (Figs. 12 – 16). Over the past quarter, water temperatures ranged from `r round(min(AB_WQText$TempMean, na.rm = TRUE), 1)` to `r round(max(AB_WQText$TempMean, na.rm = TRUE), 1)`°C; Salinities ranged from `r round(min(AB_WQText$SalMean, na.rm = TRUE), 1)` to `r round(max(AB_WQText$SalMean, na.rm = TRUE), 1)`; dissolved oxygen  ranged from `r round(min(AB_WQText$DOMean, na.rm = TRUE), 1)` to `r round(max(AB_WQText$DOMean, na.rm = TRUE), 1)` mg/L; pH values ranged from `r round(min(AB_WQText$pHMean, na.rm = TRUE), 1)` to `r round(max(AB_WQText$pHMean, na.rm = TRUE), 1)`; and secchi penetration values (percentage of the water column through which the Secchi disk could be seen) ranged from `r round(min(AB_WQText$SecchiMean, na.rm = TRUE), 1)` to `r round(max(AB_WQText$SecchiMean, na.rm = TRUE), 1)`%.


SUWANNEE SOUND <br><br>
Data reported in this section is preliminary as it has not been subjected to the full QA/QC process.

Preliminary recruitment data is available through the end of `r format(max(SS_RecruitText$AnalysisDate), "%B %Y")`. Recruitment rates ranged from `r round(min(SS_RecruitText$RecMean, na.rm = TRUE), 1)` to `r round(max(SS_RecruitText$RecMean, na.rm = TRUE), 1)` spat per shell in the last quarter. The maximum rate of `r round(max(SS_RecruitText$RecMean, na.rm = TRUE), 1)` was observed at Station `r SS_RecruitText$StationNumber[which.max(SS_RecruitText$RecMean)]` during sampling in `r format(SS_RecruitText$AnalysisDate[which.max(SS_RecruitText$RecMean)], "%B %Y")` (Fig. 17). 

Preliminary water quality data is available through the end of `r format(max(SS_WQText$AnalysisDate), "%B %Y")`. Water temperature, salinity, dissolved oxygen concentration, pH, water depth and Secchi depth were recorded during sampling (Figs. 18 – 21). Over the past quarter, water temperatures ranged from `r round(min(SS_WQText$TempMean, na.rm = TRUE), 1)` to `r round(max(SS_WQText$TempMean, na.rm = TRUE), 1)`°C; Salinities ranged from `r round(min(SS_WQText$SalMean, na.rm = TRUE), 1)` to `r round(max(SS_WQText$SalMean, na.rm = TRUE), 1)`; dissolved oxygen  ranged from `r round(min(SS_WQText$DOMean, na.rm = TRUE), 1)` to `r round(max(SS_WQText$DOMean, na.rm = TRUE), 1)` mg/L; pH values ranged from `r round(min(SS_WQText$pHMean, na.rm = TRUE), 1)` to `r round(max(SS_WQText$pHMean, na.rm = TRUE), 1)`.



```{r FigureFormatting}
#Base formatting for figure consistency
BaseForm <- theme_classic() +
  theme(panel.border = element_rect(color = "black", fill = NA), #Add border
        plot.title = element_text(hjust = 0, vjust = -7, family = "serif", color = "black", size = 12), #Add plot title for section
        axis.title = element_text(family = "serif", color = "black", size = 12), #Adjust axis title and text
        axis.text = element_text(family = "serif", color = "black", size = 10),
        axis.line = element_line(color = "black"),
        axis.ticks.length.x = unit(0.20, "cm"),
        axis.ticks.length.y = unit(0.1, "cm"),
        legend.position = "top", legend.justification = "right",  legend.box.spacing = unit(0.05, "line"), #Adjust legend position
        legend.title = element_blank(), legend.key.height = unit(0.5, "line"), legend.key.width = unit(1, "lines"), #Adjust legend title and spacing
        legend.text = element_text(family = "serif", color = "black", size = 9)) #Adjust legend text

#Color and shape to station number
Stations <- c("1" = "Station 1", "2" = "Station 2", "3" = "Station 3", "4" = "Station 4", "5" = "Station 5",
              "6" = "Station 6", "7" = "Station 7", "8" = "Station 8", "9" = "Station 9", "10" = "Station 10",
              "11" = "Station 11", "12" = "Station 12", "13" = "Station 13", "14" = "Station 14", "15" = "Station 15")
Stat_pal <- c(rgb(0, 64, 0, maxColorValue = 255), rgb(0, 255, 0, maxColorValue = 255), rgb(0, 128, 0, maxColorValue = 255), rgb(192, 255, 0, maxColorValue = 255), rgb(64, 192, 0, maxColorValue = 255),
              rgb(128, 0, 0, maxColorValue = 255), rgb(192, 192, 0, maxColorValue = 255), rgb(96, 0, 0, maxColorValue = 255), rgb(255, 128, 0, maxColorValue = 255), rgb(128, 64, 0, maxColorValue = 255),
              rgb(0, 0, 128, maxColorValue = 255), rgb(0, 128, 255, maxColorValue = 255), rgb(0, 0, 96, maxColorValue = 255), rgb(0, 128, 128, maxColorValue = 255), rgb(0, 64, 128, maxColorValue = 255))
Station_fill <- scale_fill_manual("", labels = Stations, values = setNames(Stat_pal, 1:15), na.value = "#999999")
Station_color <- scale_color_manual("", labels = Stations, values = setNames(Stat_pal, 1:15), na.value = "#999999")
Station_shape <- scale_shape_manual("",labels = Stations, values = setNames(c(21, 25, 22, 23, 24, 21, 25, 22, 23, 24, 21, 25, 22, 23, 24), 1:15))
#
```

```{r RecruitmentFigures}
#Creating Recruitment figures per section for better customization
lv4 <- list("AB West", "AB Central", "AB East", "SS North", "SS Central", "SS South")
recruit_plot_list <- list()

for (i in seq_along(lv1)) {
  df_source <- get(paste0(lv1[i], "_RecruitStats")) 
  max_upper <- max(ungroup(df_source) %>%  
                     dplyr::select(Upper), na.rm = TRUE)

  recruit_plot_list[[i]] <- df_source %>% 
  ggplot(aes(x = as.POSIXct(Plot_Date), y = RecMean, fill = factor(StationNumber)))+ 
  geom_bar(stat = "identity", position = "dodge",  color = "black", width = 1565200) + 
  geom_errorbar(aes(as.POSIXct(Plot_Date), ymin = RecMean, ymax = Upper), position = position_dodge(), width = 1565200)+ 
  scale_x_datetime("", expand = c(0.005, 0), 
                   date_breaks = "1 month", date_labels = "%b %Y", 
                   guide = guide_axis(angle = 45))+
  scale_y_continuous("Spat / Shell", expand = c(0, 0),
                     limits = c(0, ceiling(max_upper * 1.05)), #Provides a 5% buffer to the top of bars
                     breaks = pretty(0:2 * ceiling(max(ungroup(df_source) %>% 
                                                       dplyr::select(Upper), na.rm = TRUE) / 2))) + 
  ggtitle(lv4[i]) + BaseForm + Station_fill
}
# You can access individual plots using recruit_plot_list[[i]]. For example: print(recruit_plot_list[1])
#print(recruit_plot_list)
```

```{r ABRecruitmentFigs, warning = FALSE, message = FALSE, fig.cap = "Figure 4. Monthly mean number (± S.D.) of spat (oyster recruits) per shell collected at stations in the West, Central, and East sections of Apalachicola Bay over the past fifteen months (five quarters). "}
recruit_plot_list[[1]] + rremove('x.text') + theme(plot.margin = unit(c(0,0.2,-0.5,0.1), "lines")) +
recruit_plot_list[[2]] + rremove('x.text')+ theme(plot.margin = unit(c(-0.5,0.2,-0.5,0.1), "lines")) +
recruit_plot_list[[3]] + theme(plot.margin = unit(c(-0.5,0.2,-0.5,0.1), "lines")) +
plot_layout(ncol = 1)
```

```{r SSRecruitmentFigs, warning = FALSE, message = FALSE, fig.cap = "Figure 17. Monthly mean number (± S.D.) of spat (oyster recruits) per shell collected at stations in the North, Central, and South sections of Suwannee Sound over the past fifteen months (five quarters). "}
recruit_plot_list[[4]] + rremove('x.text') + theme(plot.margin = unit(c(0,0.2,-0.5,0.1), "lines")) +
recruit_plot_list[[5]] + rremove('x.text')+ theme(plot.margin = unit(c(-0.5,0.2,-0.5,0.1), "lines")) +
recruit_plot_list[[6]] + theme(plot.margin = unit(c(-0.5,0.2,-0.5,0.1), "lines")) +
plot_layout(ncol = 1)
```

```{r SedimentFigure}
max_upper <- max(ungroup(AB_SedimentStats) %>%  
                     dplyr::select(Upper), na.rm = TRUE)

AB_SedimentPlot <- AB_SedimentStats %>% 
  ggplot(aes(x = as.POSIXct(Plot_Date), y = SedMean, fill = factor(StationNumber)))+ 
  geom_bar(stat = "identity", position = "dodge",  color = "black", width = 1565200) + 
  geom_errorbar(aes(as.POSIXct(Plot_Date), ymin = SedMean, ymax = Upper), position = position_dodge(), width = 1565200)+ 
  scale_x_datetime("", expand = c(0.005, 0), 
                   date_breaks = "1 month", date_labels = "%b %Y", 
                   guide = guide_axis(angle = 45))+
  scale_y_continuous("Sediment rate (g / month)", expand = c(0, 0),
                     limits = c(0, ceiling(max_upper * 1.05)), #Provides a 5% buffer to the top of bars
                     breaks = pretty(0:2 * ceiling(max(ungroup(AB_SedimentStats) %>% 
                                                       dplyr::select(Upper), na.rm = TRUE) / 2))) + 
  ggtitle("Apalachicola Bay Sedimentation") + BaseForm + Station_fill
#print(AB_SedimentPlot)
```

```{r ABSedimentFigure, warning = FALSE, message = FALSE, fig.cap = "Figure 5. Monthly mean grams (± S.D.) of sediment per trap per month collected at stations in Apalachicola Bay over the past fifteen months (five quarters). "}
ggarrange(AB_SedimentPlot + theme(plot.margin = unit(c(0,0.2,0,0.1), "lines")),
          nrow = 1, ncol = 1)
```

```{r TempFigs}
#Creating Temperature figures per section for better customization
wqtemp_plot_list <- list()

for (i in seq_along(lv2)) {
  df_source <- get(paste0(lv2[i], "_WQStats")) 
  wqtemp_plot_list[[i]] <- df_source %>% 
  filter(SectionName == lv3[i]) %>%
  ggplot(aes(x = as.POSIXct(Plot_Date), y = TempMean, color = as.factor(StationNumber), group = as.factor(StationNumber)))+ #Set base data to present
  geom_line(color = "black") + #Add connecting lines
  geom_point(aes(shape = as.factor(StationNumber), fill = as.factor(StationNumber)), color = "black", size = 2.5) +  #Then add points on top. Fill = inside color of shape; Color = outside line of shape    
  scale_x_datetime("", expand = c(0.035, 0), #Set axis title and remove spacing
                   date_breaks = "1 month", date_labels = "%b %Y", #Set axis breaks, label format
                   guide = guide_axis(angle = 45))+
  scale_y_continuous("Temperature (°C)", expand = c(0, 0),
                     limits = c(0, 40), pretty_breaks())+
  ggtitle(lv4[i]) + BaseForm + Station_color + Station_fill + Station_shape
}
# You can access individual plots using recruit_plot_list[[i]]. For example: print(recruit_plot_list[1])
#print(wqtemp_plot_list)
```

```{r ABTempFigs, warning = FALSE, message = FALSE, fig.cap = "Figure 12. Monthly mean temperature at recruitment and sedimentation monitoring stations in the West, Central, and East sections of Apalachicola Bay over the past fifteen months (five quarters). "}
wqtemp_plot_list[[1]] + rremove('x.text') + theme(plot.margin = unit(c(0,0.2,-0.5,0.1), "lines")) +
wqtemp_plot_list[[2]] + rremove('x.text')+ theme(plot.margin = unit(c(-0.5,0.2,-0.5,0.1), "lines")) +
wqtemp_plot_list[[3]] + theme(plot.margin = unit(c(-0.5,0.2,-0.5,0.1), "lines")) +
plot_layout(ncol = 1)
```

```{r SSTempFigs, warning = FALSE, message = FALSE, fig.cap = "Figure 18. Monthly mean temperature at recruitment monitoring stations in the North, Central, and South sections of Suwannee Sound over the past fifteen months (five quarters). "}
wqtemp_plot_list[[4]] + rremove('x.text') + theme(plot.margin = unit(c(0,0.2,-0.5,0.1), "lines")) +
wqtemp_plot_list[[5]] + rremove('x.text')+ theme(plot.margin = unit(c(-0.5,0.2,-0.5,0.1), "lines")) +
wqtemp_plot_list[[6]] + theme(plot.margin = unit(c(-0.5,0.2,-0.5,0.1), "lines")) +
plot_layout(ncol = 1)
```

```{r SalinityFigs}
#Creating Salinity figures per section for better customization
wqsal_plot_list <- list()

for (i in seq_along(lv2)) {
  df_source <- get(paste0(lv2[i], "_WQStats")) 
  wqsal_plot_list[[i]] <- df_source %>% 
  filter(SectionName == lv3[i]) %>%
  ggplot(aes(x = as.POSIXct(Plot_Date), y = SalMean, color = as.factor(StationNumber), group = as.factor(StationNumber)))+ #Set base data to present
  geom_line(color = "black") + #Add connecting lines
  geom_point(aes(shape = as.factor(StationNumber), fill = as.factor(StationNumber)), color = "black", size = 2.5) +  #Then add points on top. Fill = inside color of shape; Color = outside line of shape    
  scale_x_datetime("", expand = c(0.035, 0), #Set axis title and remove spacing
                   date_breaks = "1 month", date_labels = "%b %Y", #Set axis breaks, label format
                   guide = guide_axis(angle = 45))+
  scale_y_continuous("Salinity", expand = c(0, 0),
                     limits = c(0, 40), pretty_breaks())+
  ggtitle(lv4[i]) + BaseForm + Station_color + Station_fill + Station_shape
}
# You can access individual plots using recruit_plot_list[[i]]. For example: print(recruit_plot_list[1])
#print(wqsal_plot_list)
```

```{r ABSalinityFigs, warning = FALSE, message = FALSE, fig.cap = "Figure 13. Monthly mean salinity at recruitment and sedimentation monitoring stations in the West, Central, and East sections of Apalachicola Bay over the past fifteen months (five quarters). "}
wqsal_plot_list[[1]] + rremove('x.text') + theme(plot.margin = unit(c(0,0.2,-0.5,0.1), "lines")) +
wqsal_plot_list[[2]] + rremove('x.text')+ theme(plot.margin = unit(c(-0.5,0.2,-0.5,0.1), "lines")) +
wqsal_plot_list[[3]] + theme(plot.margin = unit(c(-0.5,0.2,-0.5,0.1), "lines")) +
plot_layout(ncol = 1)
```

```{r SSSalinityFigs, warning = FALSE, message = FALSE, fig.cap = "Figure 19. Monthly mean salinity at recruitment monitoring stations in the North, Central, and South sections of Suwannee Sound over the past fifteen months (five quarters). "}
wqsal_plot_list[[4]] + rremove('x.text') + theme(plot.margin = unit(c(0,0.2,-0.5,0.1), "lines")) +
wqsal_plot_list[[5]] + rremove('x.text')+ theme(plot.margin = unit(c(-0.5,0.2,-0.5,0.1), "lines")) +
wqsal_plot_list[[6]] + theme(plot.margin = unit(c(-0.5,0.2,-0.5,0.1), "lines")) +
plot_layout(ncol = 1)
```

```{r DOFigs}
#Creating Dissolved Oxygen figures per section for better customization
wqDO_plot_list <- list()

for (i in seq_along(lv2)) {
  df_source <- get(paste0(lv2[i], "_WQStats")) 
  wqDO_plot_list[[i]] <- df_source %>% 
  filter(SectionName == lv3[i]) %>%
  ggplot(aes(x = as.POSIXct(Plot_Date), y = DOMean, color = as.factor(StationNumber), group = as.factor(StationNumber)))+ #Set base data to present
  geom_line(color = "black") + #Add connecting lines
  geom_point(aes(shape = as.factor(StationNumber), fill = as.factor(StationNumber)), color = "black", size = 2.5) +  #Then add points on top. Fill = inside color of shape; Color = outside line of shape    
  scale_x_datetime("", expand = c(0.035, 0), #Set axis title and remove spacing
                   date_breaks = "1 month", date_labels = "%b %Y", #Set axis breaks, label format
                   guide = guide_axis(angle = 45))+
  scale_y_continuous("DO (mg/L)", expand = c(0, 0),
                     limits = c(0, 15), pretty_breaks())+
  ggtitle(lv4[i]) + BaseForm + Station_color + Station_fill + Station_shape
}
# You can access individual plots using recruit_plot_list[[i]]. For example: print(recruit_plot_list[1])
#print(wqDO_plot_list)
```

```{r ABDOFigs, warning = FALSE, message = FALSE, fig.cap = "Figure 14. Monthly mean dissolved oxygen (DO) at recruitment and sedimentation monitoring stations in the West, Central, and East sections of Apalachicola Bay over the past fifteen months (five quarters). "}
wqDO_plot_list[[1]] + rremove('x.text') + theme(plot.margin = unit(c(0,0.2,-0.5,0.1), "lines")) +
wqDO_plot_list[[2]] + rremove('x.text')+ theme(plot.margin = unit(c(-0.5,0.2,-0.5,0.1), "lines")) +
wqDO_plot_list[[3]] + theme(plot.margin = unit(c(-0.5,0.2,-0.5,0.1), "lines")) +
plot_layout(ncol = 1)
```

```{r SSDOFigs, warning = FALSE, message = FALSE, fig.cap = "Figure 20. Monthly mean dissolved oxygen (DO) at recruitment monitoring stations in the North, Central, and South sections of Suwannee Sound over the past fifteen months (five quarters). "}
wqDO_plot_list[[4]] + rremove('x.text') + theme(plot.margin = unit(c(0,0.2,-0.5,0.1), "lines")) +
wqDO_plot_list[[5]] + rremove('x.text')+ theme(plot.margin = unit(c(-0.5,0.2,-0.5,0.1), "lines")) +
wqDO_plot_list[[6]] + theme(plot.margin = unit(c(-0.5,0.2,-0.5,0.1), "lines")) +
plot_layout(ncol = 1)
```

```{r phFigs}
#Creating pH figures per section for better customization
wqpH_plot_list <- list()

for (i in seq_along(lv2)) {
  df_source <- get(paste0(lv2[i], "_WQStats")) 
  wqpH_plot_list[[i]] <- df_source %>% 
  filter(SectionName == lv3[i]) %>%
  ggplot(aes(x = as.POSIXct(Plot_Date), y = pHMean, color = as.factor(StationNumber), group = as.factor(StationNumber)))+ #Set base data to present
  geom_line(color = "black") + #Add connecting lines
  geom_point(aes(shape = as.factor(StationNumber), fill = as.factor(StationNumber)), color = "black", size = 2.5) +  #Then add points on top. Fill = inside color of shape; Color = outside line of shape    
  scale_x_datetime("", expand = c(0.035, 0), #Set axis title and remove spacing
                   date_breaks = "1 month", date_labels = "%b %Y", #Set axis breaks, label format
                   guide = guide_axis(angle = 45))+
  scale_y_continuous("pH", expand = c(0, 0),
                     limits = c(0, 15), pretty_breaks())+
  ggtitle(lv4[i]) + BaseForm + Station_color + Station_fill + Station_shape
}
# You can access individual plots using recruit_plot_list[[i]]. For example: print(recruit_plot_list[1])
#print(wqpH_plot_list)
```

```{r ABphFigs, warning = FALSE, message = FALSE, fig.cap = "Figure 15. Monthly mean pH at recruitment and sedimentation monitoring stations in the West, Central, and East sections of Apalachicola Bay over the past fifteen months (five quarters). "}
wqpH_plot_list[[1]] + rremove('x.text') + theme(plot.margin = unit(c(0,0.2,-0.5,0.1), "lines")) +
wqpH_plot_list[[2]] + rremove('x.text')+ theme(plot.margin = unit(c(-0.5,0.2,-0.5,0.1), "lines")) +
wqpH_plot_list[[3]] + theme(plot.margin = unit(c(-0.5,0.2,-0.5,0.1), "lines")) +
plot_layout(ncol = 1)
```

```{r SSphFigs, warning = FALSE, message = FALSE, fig.cap = "Figure 21. Monthly mean pH at recruitment monitoring stations in the North, Central, and South sections of Suwannee Sound over the past fifteen months (five quarters). "}
wqpH_plot_list[[4]] + rremove('x.text') + theme(plot.margin = unit(c(0,0.2,-0.5,0.1), "lines")) +
wqpH_plot_list[[5]] + rremove('x.text')+ theme(plot.margin = unit(c(-0.5,0.2,-0.5,0.1), "lines")) +
wqpH_plot_list[[6]] + theme(plot.margin = unit(c(-0.5,0.2,-0.5,0.1), "lines")) +
plot_layout(ncol = 1)
```

```{r SecchiFigs}
#Creating secchi figures per section for better customization
wqsecchi_plot_list <- list()

for (i in seq_along(lv2[1:3])) {
  df_source <- get(paste0(lv2[i], "_WQStats")) 
  wqsecchi_plot_list[[i]] <- df_source %>% 
  filter(SectionName == lv3[i]) %>%
  ggplot(aes(x = as.POSIXct(Plot_Date), y = SecchiMean, fill = as.factor(StationNumber)))+ #Set base data to present
  geom_bar(stat = "identity", position = "dodge",  color = "black", width = 1565200) + #Edit first 2 digits of width to change (talk to EL for more in depth)
  scale_x_datetime("", expand = c(0.005, 0), #Set axis title and remove spacing
                   date_breaks = "1 month", date_labels = "%b %Y", #Set axis breaks, label format
                   guide = guide_axis(angle = 45))+
  scale_y_reverse("% Secchi Penetration", expand = c(0, 0),
                     limits = c(100, 0), pretty_breaks())+
  ggtitle(lv4[i]) + BaseForm + Station_fill
}
# You can access individual plots using recruit_plot_list[[i]]. For example: print(recruit_plot_list[1])
#print(wqsecchi_plot_list)
```

```{r ABSecchiFigs, warning = FALSE, message = FALSE, fig.cap = "Figure 16. Monthly mean Secchi penetration (percentage of water depth through which the Secchi disk could be seen) at recruitment and sedimentation monitoring stations in the West, Central, and East sections of Apalachicola Bay over the past fifteen months (five quarters). "}
wqsecchi_plot_list[[1]] + rremove('x.text') + theme(plot.margin = unit(c(0,0.2,-0.5,0.1), "lines")) +
wqsecchi_plot_list[[2]] + rremove('x.text')+ theme(plot.margin = unit(c(-0.5,0.2,-0.5,0.1), "lines")) +
wqsecchi_plot_list[[3]] + theme(plot.margin = unit(c(-0.5,0.2,-0.5,0.1), "lines")) +
plot_layout(ncol = 1)
```


