---
output: 
  word_document:
  toc: true
---

```{r include = FALSE}
# Set your variables
REnd <- as.Date("2023-09-30")  # Report End Date
```

```{r include = FALSE}
# Load necessary R packages
library(tidyverse)
library(odbc)
library(DBI)
library(dbplyr)
library(lubridate)
library(knitr)
library(ggpubr) #Required for arranging multiple plots
library(scales)

RECode = "AB"  # Report Estuary Code. Use 2-letter code in Primary Keys
REName = "Apalachicola Bay"  # Report Estuary Name. Use long name you want to appear in report
RStart <- floor_date(REnd %m-% months(14), unit = "month") 
QStart <- floor_date(REnd %m-% months(2), unit = "month")
SUCode = "SS"
```

```{r setup, include=FALSE}
# Configure chunks
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, fig.width = 8, fig.height = 10)
```

```{r}
# Connect to Local database server and pull all necessary data, then close connection 
con <- dbConnect(odbc(),
                    Driver= "SQL Server", 
                    Server = "localhost\\MATTLOCALSQL",
                    Database= "OysterLocalMD20231019",
                    Authentication = "ActiveDirectoryIntegrated")

FixedLocations <- tbl(con,in_schema("dbo", "FixedLocations")) %>%
  collect() %>% 
  filter(Estuary == RECode)
hsdbWaterQuality <- tbl(con,in_schema("hsdb", "SampleEventWQ")) %>%
  collect() %>%
  filter(substring(SampleEventWQID,1,2) == RECode)
dboWaterQuality <- tbl(con,in_schema("dbo", "SampleEventWQ")) %>%
  collect() %>%
  filter(substring(SampleEventWQID,1,2) == RECode)
hsdbRecruitment <- tbl(con,in_schema("hsdb", "Recruitment")) %>%
  collect() %>%
  filter(substring(SampleEventID,1,2) == RECode)
dboRecruitment <- tbl(con,in_schema("dbo", "Recruitment")) %>%
  collect() %>%
  filter(substring(SampleEventID,1,2) == RECode)
hsdbSedTrap <- tbl(con,in_schema("hsdb", "SedimentTrap")) %>%
  collect() %>%
  filter(substring(SampleEventID,1,2) == RECode)
dboSedTrap <- tbl(con,in_schema("dbo", "SedimentTrap")) %>%
  collect() %>%
  filter(substring(SampleEventID,1,2) == RECode)
DBI::dbDisconnect(con)

```

```{r include = FALSE}
# Arrange data frames using data from the database, doing basic filters, adding necessary columns for statistics and performing statistics.
FL1 <- FixedLocations %>% 
  mutate(StationNumber = as.factor(StationNumber)) %>% #changed to factor based on EL's code
  select(FixedLocationID,
         Estuary,
         SectionName, 
         StationNumber) %>% 
  distinct()
          
WQ1 <- union(hsdbWaterQuality, dboWaterQuality) %>% 
  mutate(RetDate = as.Date(substring(SampleEventID, 8, 15), format = "%Y%m%d"), 
         FixedLocationID = substring(SampleEventID, 19, 22), 
         AnalysisDate = floor_date(RetDate, unit = "month"),
         Plot_Date = AnalysisDate + 14,
         SecchiPercent = (Secchi / Depth) * 100) %>%
  select(SampleEventWQID,
         FixedLocationID,
         SampleEventID,
         RetDate,
         AnalysisDate,
         Plot_Date,
         Temperature,
         Salinity,
         DissolvedOxygen,
         pH,
         SecchiPercent) %>% 
  drop_na(Temperature) %>%
  filter(RetDate >= RStart & RetDate < REnd) %>%
  distinct()

WQ2 <- left_join(WQ1, FL1, by = c("FixedLocationID")) %>%
  unique()
  
R_WQStats <- WQ2 %>% 
  filter(str_detect(SampleEventWQID, 'RCRT|SDTP') & Estuary == RECode) %>%
  group_by(AnalysisDate, Plot_Date, Estuary, StationNumber, SectionName) %>% 
  summarise(TempMean = mean(Temperature, na.rm = TRUE),
            SalMean = mean(Salinity, na.rm = TRUE),
            DOMean = mean(DissolvedOxygen, na.rm = TRUE), 
            pHMean = mean(pH, na.rm = TRUE), 
            SecchiMean = mean(SecchiPercent, na.rm = TRUE))

S_WQStats <- WQ2 %>% 
  filter(str_detect(SampleEventWQID, 'SRVY') & Estuary == SUCode) %>%
  group_by(AnalysisDate, Plot_Date, Estuary, StationNumber, SectionName) %>% 
  summarise(TempMean = mean(Temperature, na.rm = TRUE),
            SalMean = mean(Salinity, na.rm = TRUE),
            DOMean = mean(DissolvedOxygen, na.rm = TRUE), 
            pHMean = mean(pH, na.rm = TRUE), 
            SecchiMean = mean(SecchiPercent, na.rm = TRUE))

WQText <- R_WQStats %>%
  filter(Plot_Date >= QStart & Plot_Date < REnd)

R1 <- union(hsdbRecruitment, dboRecruitment) %>% 
  filter(ShellPosition %in% c(2,3,4,5,8,9,10,11)) %>%
  mutate(DeployedDate = as.Date(DeployedDate), 
         RetDate = as.Date(substring(SampleEventID, 8, 15), format = "%Y%m%d"), 
         FixedLocationID = substring(ShellID, 19, 22), 
         NumDays = as.numeric(RetDate-DeployedDate),
         BottomMonth= NumBottom/(NumDays/28),
         AnalysisDate = floor_date(RetDate, unit = "month"),
         Plot_Date = AnalysisDate + 14) %>%
  select(ShellID,
         FixedLocationID,
         SampleEventID,
         DeployedDate,
         RetDate,
         AnalysisDate,
         Plot_Date,
         NumDays,
         ShellPosition,
         NumBottom,
         BottomMonth) %>% 
  filter(RetDate >= RStart & RetDate < REnd) %>%
  distinct()

R2 <- left_join(R1, FL1, by = c("FixedLocationID")) %>%
  unique()
  
RStats <- R2 %>% 
  group_by(AnalysisDate, Plot_Date, Estuary, StationNumber, SectionName) %>% 
  summarise(RecMean = mean(BottomMonth, na.rm = TRUE), 
            SD= sd(BottomMonth, na.rm = TRUE),
            Upper = RecMean + SD)

RText <- RStats %>%
  filter(Plot_Date >= QStart & Plot_Date < REnd)

RW <- RStats %>%
  filter(SectionName == "W") %>%
  dplyr::select(-Upper, -Plot_Date) %>% #Drop column as needed
  group_by(StationNumber) 

RC <- RStats %>%
  filter(SectionName == "C") %>%
  dplyr::select(-Upper, -Plot_Date) %>% #Drop column as needed
  group_by(StationNumber) 

RE <- RStats %>%
  filter(SectionName == "E") %>%
  dplyr::select(-Upper, -Plot_Date) %>% #Drop column as needed
  group_by(StationNumber) 


###########

ST1 <- union(hsdbSedTrap, dboSedTrap) %>% 
  filter(NumFish == 0 & NumCrabs < 2 & NumDrills < 2 & NumHermitCrabs < 5) %>%
  mutate(DeployedDate = as.Date(DeployedDate), 
         RetDate = as.Date(substring(SampleEventID, 8, 15), format = "%Y%m%d"), 
         FixedLocationID = substring(SampleEventID, 19, 22), 
         NumDays = as.numeric(RetDate-DeployedDate),
         AnalysisDate = floor_date(RetDate, unit = "month"),
         Plot_Date = AnalysisDate + 14,
         SedWeight = (FilterDryWeight + PanDryWeight) - (FilterTareWeight + PanTareWeight),
         SedRate = SedWeight / (NumDays/28)) %>%
  select(CupSampleID,
         FixedLocationID,
         SampleEventID,
         DeployedDate,
         RetDate,
         AnalysisDate,
         Plot_Date,
         NumDays,
         SedWeight,
         SedRate) %>% 
  filter(RetDate >= RStart & RetDate < REnd) %>%
  distinct()

ST2 <- left_join(ST1, FL1, by = c("FixedLocationID")) %>%
  unique()
  
STStats <- ST2 %>% 
  group_by(AnalysisDate, Plot_Date, Estuary, StationNumber, SectionName) %>% 
  summarise(SedMean = mean(SedRate, na.rm = TRUE), 
            SD = sd(SedRate, na.rm = TRUE),
            Upper = SedMean + SD)

STText <- STStats %>%
  filter(Plot_Date >= QStart & Plot_Date < REnd)

```

Data reported in this section is preliminary as it has not been subjected to the full QA/QC process.

Preliminary recruitment data is available through the end of `r format(max(RText$AnalysisDate), "%B %Y")`. Recruitment rates ranged from `r round(min(RText$RecMean, na.rm = TRUE), 1)` to `r round(max(RText$RecMean, na.rm = TRUE), 1)` spat per shell in the last quarter. The maximum rate of `r round(max(RText$RecMean, na.rm = TRUE), 1)` was observed at Station `r RText$StationNumber[which.max(RText$RecMean)]` during sampling in `r format(RText$AnalysisDate[which.max(RText$RecMean)], "%B %Y")`. 

Preliminary sediment trap data is available through the end of `r format(max(STText$AnalysisDate), "%B %Y")`. Sediment rates ranged from `r round(min(STText$SedMean, na.rm = TRUE), 1)` to `r round(max(STText$SedMean, na.rm = TRUE), 1)` grams (dry weight) of sediment in the last quarter. The maximum rate of `r round(max(STText$SedMean, na.rm = TRUE), 1)` was observed at Station `r STText$StationNumber[which.max(STText$SedMean)]` during sampling in `r format(STText$AnalysisDate[which.max(STText$SedMean)], "%B %Y")`. 

Preliminary water quality data is available through the end of `r format(max(WQText$AnalysisDate), "%B %Y")`. Water temperature, salinity, dissolved oxygen concentration, pH, water depth and Secchi depth were recorded during sampling (Figs. 10 – 14). Over the past quarter, water temperatures ranged from `r round(min(WQText$TempMean, na.rm = TRUE), 1)` to `r round(max(WQText$TempMean, na.rm = TRUE), 1)`°C; Salinities ranged from `r round(min(WQText$SalMean, na.rm = TRUE), 1)` to `r round(max(WQText$SalMean, na.rm = TRUE), 1)`; dissolved oxygen  ranged from `r round(min(WQText$DOMean, na.rm = TRUE), 1)` to `r round(max(WQText$DOMean, na.rm = TRUE), 1)` mg/L; pH values ranged from `r round(min(WQText$pHMean, na.rm = TRUE), 1)` to `r round(max(WQText$pHMean, na.rm = TRUE), 1)`; and secchi penetration values (percentage of the water column through which the Secchi disk could be seen) ranged from `r round(min(WQText$SecchiMean, na.rm = TRUE), 1)` to `r round(max(WQText$SecchiMean, na.rm = TRUE), 1)`%.

RText$StationNumber(which.max(RText$RecMean))







```{r include = FALSE}
#Base formatting for figure consistency
BaseForm <- theme_classic() +
  theme(panel.border = element_rect(color = "black", fill = NA), #Add border
        plot.title = element_text(hjust = 0, vjust = -7, family = "serif", color = "black", size = 12), #Add plot title for section
        axis.title = element_text(family = "serif", color = "black", size = 12), #Adjust axis title and text
        axis.text = element_text(family = "serif", color = "black", size = 10),
        axis.line = element_line(color = "black"),
        axis.ticks.length.x = unit(0.20, "cm"),
        axis.ticks.length.y = unit(0.1, "cm"),
        legend.position = "top", legend.justification = "right",  legend.box.spacing = unit(0.05, "line"), #Adjust legend position
        legend.title = element_blank(), legend.key.height = unit(0.5, "line"), legend.key.width = unit(1, "lines"), #Adjust legend title and spacing
        legend.text = element_text(family = "serif", color = "black", size = 9)) #Adjust legend text

#Color and shape to station number
Stations <- c("1" = "Station 1", "2" = "Station 2", "3" = "Station 3", "4" = "Station 4", "5" = "Station 5",
              "6" = "Station 6", "7" = "Station 7", "8" = "Station 8", "9" = "Station 9", "10" = "Station 10",
              "11" = "Station 11", "12" = "Station 12", "13" = "Station 13", "14" = "Station 14", "15" = "Station 15")
Stat_pal <- c(rgb(0, 64, 0, maxColorValue = 255), rgb(0, 255, 0, maxColorValue = 255), rgb(0, 128, 0, maxColorValue = 255), rgb(192, 255, 0, maxColorValue = 255), rgb(64, 192, 0, maxColorValue = 255),
              rgb(128, 0, 0, maxColorValue = 255), rgb(192, 192, 0, maxColorValue = 255), rgb(96, 0, 0, maxColorValue = 255), rgb(255, 128, 0, maxColorValue = 255), rgb(128, 64, 0, maxColorValue = 255),
              rgb(0, 0, 128, maxColorValue = 255), rgb(0, 128, 255, maxColorValue = 255), rgb(0, 0, 96, maxColorValue = 255), rgb(0, 128, 128, maxColorValue = 255), rgb(0, 64, 128, maxColorValue = 255))
Station_fill <- scale_fill_manual("", labels = Stations, values = setNames(Stat_pal, 1:15), na.value = "#999999")
Station_color <- scale_color_manual("", labels = Stations, values = setNames(Stat_pal, 1:15), na.value = "#999999")
Station_shape <- scale_shape_manual("",labels = Stations, values = setNames(c(21, 25, 22, 23, 24, 21, 25, 22, 23, 24, 21, 25, 22, 23, 24), 1:15))
#
```

```{r include = FALSE}
#Creating Recruitment figures per section for better customization
#
##West
RW_fig2 <- RStats %>% filter(SectionName == "W") %>%  #Filter to one section
  ggplot(aes(x = as.POSIXct(Plot_Date), y = RecMean, fill = StationNumber))+ #Set base data to present
  geom_bar(stat = "identity", position = "dodge",  color = "black", width = 1565200) + #Add bars. Deafult = 2365200. Edit first 2 digits of width to change (talk to EL for more in depth)
  geom_errorbar(aes(as.POSIXct(Plot_Date), ymin = RecMean, ymax = Upper), position = position_dodge(), width = 1565200)+ #Add error bars
  scale_x_datetime("", expand = c(0.005, 0), #Set axis title and remove spacing
                   date_breaks = "1 month", date_labels = "%b %Y", #Set axis breaks, label format
                   guide = guide_axis(angle = 45))+
  scale_y_continuous("Spat / Shell", expand = c(0, 0),
                     limits = c(0,
                                2*ceiling(max(ungroup(RStats) %>% filter(SectionName == "W") %>% dplyr::select(Upper), na.rm = T)/2)), #Round to next highest even number for limits and breaks
                     breaks = seq(0, 2*ceiling(max(ungroup(RStats) %>% filter(SectionName == "W") %>% dplyr::select(Upper), na.rm = T)/2), by = 3))+ #Change by = # to adjust number of breaks
  ggtitle("West") + BaseForm + Station_fill
#

##Central
RC_fig2 <- RStats %>% filter(SectionName == "C") %>%  #Filter to one section
  ggplot(aes(x = as.POSIXct(Plot_Date), y = RecMean, fill = StationNumber))+ #Set base data to present
  geom_bar(stat = "identity", position = "dodge",  color = "black", width = 1565200) + #Add bars
  geom_errorbar(aes(as.POSIXct(Plot_Date), ymin = RecMean, ymax = Upper), position = position_dodge(), width = 1565200)+ #Add error bars
  scale_x_datetime("", expand = c(0.005, 0), #Set axis title and remove spacing
                   date_breaks = "1 month", date_labels = "%b %Y", #Set axis breaks, label format
                   guide = guide_axis(angle = 45))+
  scale_y_continuous("Spat / Shell", expand = c(0, 0),
                     limits = c(0,
                                2*ceiling(max(ungroup(RStats) %>% filter(SectionName == "C") %>% dplyr::select(Upper), na.rm = T)/2)), #Round to next highest even number for limits and breaks
                     breaks = seq(0, 2*ceiling(max(ungroup(RStats) %>% filter(SectionName == "C") %>% dplyr::select(Upper), na.rm = T)/2), by = 2))+ #Change by = # to adjust number of breaks
  ggtitle("Central")+ BaseForm + Station_fill
#

##East
RE_fig2 <- RStats %>% filter(SectionName == "E") %>%  #Filter to one section
  ggplot(aes(x = as.POSIXct(Plot_Date), y = RecMean, fill = StationNumber))+ #Set base data to present
  geom_bar(stat = "identity", position = "dodge",  color = "black", width = 1565200) + #Add bars
  geom_errorbar(aes(as.POSIXct(Plot_Date), ymin = RecMean, ymax = Upper), position = position_dodge(), width = 1565200)+ #Add error bars
  scale_x_datetime("", expand = c(0.005, 0), #Set axis title and remove spacing
                   date_breaks = "1 month", date_labels = "%b %Y", #Set axis breaks, label format
                   guide = guide_axis(angle = 45))+
  scale_y_continuous("Spat / Shell", expand = c(0, 0),
                     limits = c(0,
                                2*ceiling(max(ungroup(RStats) %>% filter(SectionName == "E") %>% dplyr::select(Upper), na.rm = T)/2)), #Round to next highest even number for limits and breaks
                     breaks = seq(0, 2*ceiling(max(ungroup(RStats) %>% filter(SectionName == "E") %>% dplyr::select(Upper), na.rm = T)/2), by = 3))+ #Change by = # to adjust number of breaks
  ggtitle("East")+ BaseForm + Station_fill
```

```{r, warning = FALSE, message = FALSE, fig.cap = "Figure 3. Monthly mean number (± S.D.) of spat (oyster recruits) per shell collected at stations in the West, Central, and East sections of Apalachicola Bay over the past fifteen months (five quarters). "}

ggarrange(RW_fig2 + rremove('x.text') + theme(plot.margin = unit(c(0,0.2,-0.5,0.1), "lines")),
          RC_fig2 + rremove('x.text')+ theme(plot.margin = unit(c(-0.5,0.2,-0.5,0.1), "lines")),
          RE_fig2 + theme(plot.margin = unit(c(-0.5,0.2,0,0.1), "lines")),
          nrow = 3, ncol = 1)

```


```{r, echo = FALSE, warning = FALSE, message = FALSE, fig.cap = "Figure X. Monthly mean grams (± S.D.) of sediment per trap per month collected at stations in Apalachicola Bay over the past fifteen months (five quarters). "}
#Creating Sediment Trap figures per section for better customization
#
##ALL
ST_fig2 <- STStats %>% 
  ggplot(aes(x = as.POSIXct(Plot_Date), y = SedMean, fill = StationNumber))+ #Set base data to present
  geom_bar(stat = "identity", position = "dodge",  color = "black", width = 1565200) + #Add bars. Deafult = 2365200. Edit first 2 digits of width to change (talk to EL for more in depth)
  geom_errorbar(aes(as.POSIXct(Plot_Date), ymin = SedMean, ymax = Upper), position = position_dodge(), width = 1565200)+ #Add error bars
  scale_x_datetime("Date", expand = c(0.005, 0), #Set axis title and remove spacing
                   date_breaks = "1 month", date_labels = "%b %Y", #Set axis breaks, label format
                   guide = guide_axis(angle = 45))+
  scale_y_continuous("Sediment rate (g / month)", expand = c(0, 0),
                     limits = c(0,
                                2.1*ceiling(max(ungroup(STStats) %>% dplyr::select(Upper), na.rm = T)/2)), #Round to next highest even number for limits and breaks
                     breaks = seq(0, 2*ceiling(max(ungroup(STStats) %>% dplyr::select(Upper), na.rm = T)/2), by = 50))+ #Change by = # to adjust number of breaks
  ggtitle("All") + BaseForm + Station_fill

# 
# ##East
# RE_fig2 <- RStats %>% filter(SectionName == "E") %>%  #Filter to one section
#   ggplot(aes(x = as.POSIXct(Plot_Date), y = RecMean, fill = StationNumber))+ #Set base data to present
#   geom_bar(stat = "identity", position = "dodge",  color = "black", width = 1565200) + #Add bars
#   geom_errorbar(aes(as.POSIXct(Plot_Date), ymin = RecMean, ymax = Upper), position = position_dodge(), width = 1565200)+ #Add error bars
#   scale_x_datetime("", expand = c(0.005, 0), #Set axis title and remove spacing
#                    date_breaks = "1 month", date_labels = "%b %Y", #Set axis breaks, label format
#                    guide = guide_axis(angle = 45))+
#   scale_y_continuous("Spat / Shell", expand = c(0, 0),
#                      limits = c(0,
#                                 2*ceiling(max(ungroup(RStats) %>% filter(SectionName == "E") %>% dplyr::select(Upper), na.rm = T)/2)), #Round to next highest even number for limits and breaks
#                      breaks = seq(0, 2*ceiling(max(ungroup(RStats) %>% filter(SectionName == "E") %>% dplyr::select(Upper), na.rm = T)/2), by = 3))+ #Change by = # to adjust number of breaks
#   ggtitle("East")+ BaseForm + Station_fill
```

```{r, warning = FALSE, message = FALSE, fig.cap = "Figure X. Monthly mean grams (± S.D.) of sediment per trap per month collected at stations in Apalachicola Bay over the past fifteen months (five quarters). "}

ggarrange(ST_fig2 + theme(plot.margin = unit(c(0,0.2,0,0.1), "lines")),
          nrow = 1, ncol = 1)

```


```{r include = FALSE}
#Creating Temperature figures per section for better customization
#
##West
TW_fig3 <- R_WQStats %>% filter(SectionName == "W") %>%  #Filter to one section
  ggplot(aes(x = as.POSIXct(Plot_Date), y = TempMean, color = StationNumber, group = StationNumber))+ #Set base data to present
  geom_line(aes(group=StationNumber), color = "black") + #Add connecting lines
  geom_point(aes(shape = StationNumber, fill = StationNumber), color = "black", size = 2.5) +  #Then add points on top. Fill = inside color of shape; Color = outside line of shape
  scale_x_datetime("", expand = c(0.035, 0), #Set axis title and remove spacing
                   date_breaks = "1 month", date_labels = "%b %Y", #Set axis breaks, label format
                   guide = guide_axis(angle = 45))+
  scale_y_continuous("Temperature (°C)", expand = c(0, 0),
                     limits = c(0, 40), pretty_breaks())+
  ggtitle("West") + BaseForm + Station_color + Station_fill + Station_shape
#

##Central
TC_fig3 <- R_WQStats %>% filter(SectionName == "C") %>%  #Filter to one section
  ggplot(aes(x = as.POSIXct(Plot_Date), y = TempMean, color = StationNumber, group = StationNumber))+ #Set base data to present
  geom_line(aes(group=StationNumber), color = "black") + #Add connecting lines
  geom_point(aes(shape = StationNumber, fill = StationNumber), color = "black", size = 2.5) +  #Then add points on top. Fill = inside color of shape; Color = outside line of shape
  scale_x_datetime("", expand = c(0.035, 0), #Set axis title and remove spacing
                   date_breaks = "1 month", date_labels = "%b %Y", #Set axis breaks, label format
                   guide = guide_axis(angle = 45))+
  scale_y_continuous("Temperature (°C)", expand = c(0, 0),
                     limits = c(0, 40), pretty_breaks())+
  ggtitle("Central") + BaseForm + Station_color + Station_fill + Station_shape
#

##East
TE_fig3 <- R_WQStats %>% filter(SectionName == "E") %>%  #Filter to one section
  ggplot(aes(x = as.POSIXct(Plot_Date), y = TempMean, color = StationNumber, group = StationNumber))+ #Set base data to present
  geom_line(aes(group=StationNumber), color = "black") + #Add connecting lines
  geom_point(aes(shape = StationNumber, fill = StationNumber), color = "black", size = 2.5) +  #Then add points on top. Fill = inside color of shape; Color = outside line of shape
  scale_x_datetime("", expand = c(0.035, 0), #Set axis title and remove spacing
                   date_breaks = "1 month", date_labels = "%b %Y", #Set axis breaks, label format
                   guide = guide_axis(angle = 45))+
  scale_y_continuous("Temperature (°C)", expand = c(0, 0),
                     limits = c(0, 40), pretty_breaks())+
  ggtitle("East") + BaseForm + Station_color + Station_fill + Station_shape


```

```{r, warning = FALSE, message = FALSE, fig.cap = "Figure 4. Monthly mean temperature at recruitment and sedimentation monitoring stations in the West, Central, and East sections of Apalachicola Bay over the past fifteen months (five quarters). "}

ggarrange(TW_fig3 + rremove('x.text') + theme(plot.margin = unit(c(0,0.2,-0.5,0.1), "lines")),
          TC_fig3 + rremove('x.text')+ theme(plot.margin = unit(c(-0.5,0.2,-0.5,0.1), "lines")),
          TE_fig3 + theme(plot.margin = unit(c(-0.5,0.2,0,0.1), "lines")),
          nrow = 3, ncol = 1)

```


```{r include = FALSE}
#Creating Salinity figures per section for better customization
#
##West
SW_fig4 <-  R_WQStats %>% filter(SectionName == "W") %>%  #Filter to one section
  ggplot(aes(x = as.POSIXct(Plot_Date), y = SalMean, color = StationNumber, group = StationNumber))+ #Set base data to present
  geom_line(aes(group=StationNumber), color = "black") + #Add connecting lines
  geom_point(aes(shape = StationNumber, fill = StationNumber), color = "black", size = 2.5) +  #Then add points on top. Fill = inside color of shape; Color = outside line of shape
  scale_x_datetime("", expand = c(0.035, 0), #Set axis title and remove spacing
                   date_breaks = "1 month", date_labels = "%b %Y", #Set axis breaks, label format
                   guide = guide_axis(angle = 45))+
  scale_y_continuous("Salinity", expand = c(0, 0),
                     limits = c(0, 40), pretty_breaks())+
  ggtitle("West") + BaseForm + Station_color + Station_fill + Station_shape
#

##Central
SC_fig4 <-  R_WQStats %>% filter(SectionName == "C") %>%  #Filter to one section
  ggplot(aes(x = as.POSIXct(Plot_Date), y = SalMean, color = StationNumber, group = StationNumber))+ #Set base data to present
  geom_line(aes(group=StationNumber), color = "black") + #Add connecting lines
  geom_point(aes(shape = StationNumber, fill = StationNumber), color = "black", size = 2.5) +  #Then add points on top. Fill = inside color of shape; Color = outside line of shape
  scale_x_datetime("", expand = c(0.035, 0), #Set axis title and remove spacing
                   date_breaks = "1 month", date_labels = "%b %Y", #Set axis breaks, label format
                   guide = guide_axis(angle = 45))+
  scale_y_continuous("Salinity", expand = c(0, 0),
                     limits = c(0, 40), pretty_breaks())+
  ggtitle("Central") + BaseForm + Station_color + Station_fill + Station_shape
#

##East
SE_fig4 <-  R_WQStats %>% filter(SectionName == "E") %>%  #Filter to one section
  ggplot(aes(x = as.POSIXct(Plot_Date), y = SalMean, color = StationNumber, group = StationNumber))+ #Set base data to present
  geom_line(aes(group=StationNumber), color = "black") + #Add connecting lines
  geom_point(aes(shape = StationNumber, fill = StationNumber), color = "black", size = 2.5) +  #Then add points on top. Fill = inside color of shape; Color = outside line of shape
  scale_x_datetime("", expand = c(0.035, 0), #Set axis title and remove spacing
                   date_breaks = "1 month", date_labels = "%b %Y", #Set axis breaks, label format
                   guide = guide_axis(angle = 45))+
  scale_y_continuous("Salinity", expand = c(0, 0),
                     limits = c(0, 40), pretty_breaks())+
  ggtitle("East") + BaseForm + Station_color + Station_fill + Station_shape


```

```{r, warning = FALSE, message = FALSE, fig.cap = "Figure 5. Monthly mean salinity at recruitment and sedimentation monitoring stations in the West, Central, and East sections of Apalachicola Bay over the past fifteen months (five quarters). "}

ggarrange(SW_fig4 + rremove('x.text') + theme(plot.margin = unit(c(0,0.2,-0.5,0.1), "lines")),
          SC_fig4 + rremove('x.text')+ theme(plot.margin = unit(c(-0.5,0.2,-0.5,0.1), "lines")),
          SE_fig4 + theme(plot.margin = unit(c(-0.5,0.2,0,0.1), "lines")),
          nrow = 3, ncol = 1)

```


```{r include = FALSE}
#Creating DO figures per section for better customization
#
##West
DW_fig5 <- R_WQStats %>% filter(Estuary == RECode) %>%
  filter(SectionName == "W") %>%  #Filter to one section
  ggplot(aes(x = as.POSIXct(Plot_Date), y = DOMean, color = StationNumber, group = StationNumber))+ #Set base data to present
  geom_line(aes(group=StationNumber), color = "black") + #Add connecting lines
  geom_point(aes(shape = StationNumber, fill = StationNumber), color = "black", size = 2.5) +  #Then add points on top. Fill = inside color of shape; Color = outside line of shape
  scale_x_datetime("", expand = c(0.035, 0), #Set axis title and remove spacing
                   date_breaks = "1 month", date_labels = "%b %Y", #Set axis breaks, label format
                   guide = guide_axis(angle = 45))+
  scale_y_continuous("DO (mg/L)", expand = c(0, 0),
                     limits = c(0, 15), pretty_breaks())+
  ggtitle("West") + BaseForm + Station_color + Station_fill + Station_shape
#

##Central
DC_fig5 <- R_WQStats %>% filter(Estuary == RECode) %>%
  filter(SectionName == "C") %>%  #Filter to one section
  ggplot(aes(x = as.POSIXct(Plot_Date), y = DOMean, color = StationNumber, group = StationNumber))+ #Set base data to present
  geom_line(aes(group=StationNumber), color = "black") + #Add connecting lines
  geom_point(aes(shape = StationNumber, fill = StationNumber), color = "black", size = 2.5) +  #Then add points on top. Fill = inside color of shape; Color = outside line of shape
  scale_x_datetime("", expand = c(0.035, 0), #Set axis title and remove spacing
                   date_breaks = "1 month", date_labels = "%b %Y", #Set axis breaks, label format
                   guide = guide_axis(angle = 45))+
  scale_y_continuous("DO (mg/L)", expand = c(0, 0),
                     limits = c(0, 15), pretty_breaks())+
  ggtitle("Central") + BaseForm + Station_color + Station_fill + Station_shape
#

##East
DE_fig5 <- R_WQStats %>% filter(Estuary == RECode) %>%
  filter(SectionName == "E") %>%  #Filter to one section
  ggplot(aes(x = as.POSIXct(Plot_Date), y = DOMean, color = StationNumber, group = StationNumber))+ #Set base data to present
  geom_line(aes(group=StationNumber), color = "black") + #Add connecting lines
  geom_point(aes(shape = StationNumber, fill = StationNumber), color = "black", size = 2.5) +  #Then add points on top. Fill = inside color of shape; Color = outside line of shape
  scale_x_datetime("", expand = c(0.035, 0), #Set axis title and remove spacing
                   date_breaks = "1 month", date_labels = "%b %Y", #Set axis breaks, label format
                   guide = guide_axis(angle = 45))+
  scale_y_continuous("DO (mg/L)", expand = c(0, 0),
                     limits = c(0, 15), pretty_breaks())+
  ggtitle("East") + BaseForm + Station_color + Station_fill + Station_shape


```

```{r, warning = FALSE, message = FALSE, fig.cap = "Figure 6. Monthly mean dissolved oxygen (DO) concentration at recruitment and sedimentation monitoring stations in the West, Central, and East sections of Apalachicola Bay over the past fifteen months (five quarters). "}

ggarrange(DW_fig5 + rremove('x.text') + theme(plot.margin = unit(c(0,0.2,-0.5,0.1), "lines")),
          DC_fig5 + rremove('x.text')+ theme(plot.margin = unit(c(-0.5,0.2,-0.5,0.1), "lines")),
          DE_fig5 + theme(plot.margin = unit(c(-0.5,0.2,0,0.1), "lines")),
          nrow = 3, ncol = 1)

```


```{r include = FALSE}
#Creating pH figures per section for better customization
#
##West
pW_fig6 <- R_WQStats %>% filter(SectionName == "W") %>%  #Filter to one section
  ggplot(aes(x = as.POSIXct(Plot_Date), y = pHMean, color = StationNumber, group = StationNumber))+ #Set base data to present
  geom_line(aes(group=StationNumber), color = "black") + #Add connecting lines
  geom_point(aes(shape = StationNumber, fill = StationNumber), color = "black", size = 2.5) +  #Then add points on top. Fill = inside color of shape; Color = outside line of shape
  scale_x_datetime("", expand = c(0.035, 0), #Set axis title and remove spacing
                   date_breaks = "1 month", date_labels = "%b %Y", #Set axis breaks, label format
                   guide = guide_axis(angle = 45))+
  scale_y_continuous("pH", expand = c(0, 0),
                     limits = c(6, 10), pretty_breaks())+
  ggtitle("West") + BaseForm + Station_color + Station_fill + Station_shape
#

##Central
pC_fig6 <- R_WQStats %>% filter(SectionName == "C") %>%  #Filter to one section
  ggplot(aes(x = as.POSIXct(Plot_Date), y = pHMean, color = StationNumber, group = StationNumber))+ #Set base data to present
  geom_line(aes(group=StationNumber), color = "black") + #Add connecting lines
  geom_point(aes(shape = StationNumber, fill = StationNumber), color = "black", size = 2.5) +  #Then add points on top. Fill = inside color of shape; Color = outside line of shape
  scale_x_datetime("", expand = c(0.035, 0), #Set axis title and remove spacing
                   date_breaks = "1 month", date_labels = "%b %Y", #Set axis breaks, label format
                   guide = guide_axis(angle = 45))+
  scale_y_continuous("pH", expand = c(0, 0),
                     limits = c(6, 10), pretty_breaks())+
  ggtitle("Central") + BaseForm + Station_color + Station_fill + Station_shape
#

##East
pE_fig6 <- R_WQStats %>% filter(SectionName == "E") %>%  #Filter to one section
  ggplot(aes(x = as.POSIXct(Plot_Date), y = pHMean, color = StationNumber, group = StationNumber))+ #Set base data to present
  geom_line(aes(group=StationNumber), color = "black") + #Add connecting lines
  geom_point(aes(shape = StationNumber, fill = StationNumber), color = "black", size = 2.5) +  #Then add points on top. Fill = inside color of shape; Color = outside line of shape
  scale_x_datetime("", expand = c(0.035, 0), #Set axis title and remove spacing
                   date_breaks = "1 month", date_labels = "%b %Y", #Set axis breaks, label format
                   guide = guide_axis(angle = 45))+
  scale_y_continuous("pH", expand = c(0, 0),
                     limits = c(6, 10), pretty_breaks())+
  ggtitle("East") + BaseForm + Station_color + Station_fill + Station_shape


```

```{r, warning = FALSE, message = FALSE, fig.cap = "Figure 7. Monthly mean pH at recruitment and sedimentation monitoring stations in the West, Central, and East sections of Apalachicola Bay over the past fifteen months (five quarters). "}

ggarrange(pW_fig6 + rremove('x.text') + theme(plot.margin = unit(c(0,0.2,-0.5,0.1), "lines")),
          pC_fig6 + rremove('x.text')+ theme(plot.margin = unit(c(-0.5,0.2,-0.5,0.1), "lines")),
          pE_fig6 + theme(plot.margin = unit(c(-0.5,0.2,0,0.1), "lines")),
          nrow = 3, ncol = 1)

```


```{r include = FALSE}
#Creating Secchi pentration figures per section for better customization
#
##West
SeW_fig7 <- R_WQStats %>% filter(SectionName == "W") %>%  #Filter to one section
  ggplot(aes(x = as.POSIXct(Plot_Date), y = SecchiMean, fill = StationNumber))+ #Set base data to present
  geom_bar(stat = "identity", position = "dodge",  color = "black", width = 1565200) + #Edit first 2 digits of width to change (talk to EL for more in depth)
  scale_x_datetime("", expand = c(0.005, 0), #Set axis title and remove spacing
                   date_breaks = "1 month", date_labels = "%b %Y", #Set axis breaks, label format
                   guide = guide_axis(angle = 45))+
  scale_y_reverse("% Secchi Penetration", expand = c(0, 0),
                     limits = c(100, 0), pretty_breaks())+
  ggtitle("West") + BaseForm + Station_fill
#

##Central
SeC_fig7 <- R_WQStats %>% filter(SectionName == "C") %>%  #Filter to one section
  ggplot(aes(x = as.POSIXct(Plot_Date), y = SecchiMean, fill = StationNumber))+ #Set base data to present
  geom_bar(stat = "identity", position = "dodge",  color = "black", width = 1565200) + #Mess with first 2 digits of width to change (talk to EL for more indepth)
  scale_x_datetime("", expand = c(0.005, 0), #Set axis title and remove spacing
                   date_breaks = "1 month", date_labels = "%b %Y", #Set axis breaks, label format
                   guide = guide_axis(angle = 45))+
  scale_y_reverse("% Secchi Penetration", expand = c(0, 0),
                     limits = c(100, 0), pretty_breaks())+
  ggtitle("West") + BaseForm + Station_fill
#

##East
SeE_fig7 <- R_WQStats %>% filter(SectionName == "E") %>%  #Filter to one section
  ggplot(aes(x = as.POSIXct(Plot_Date), y = SecchiMean, fill = StationNumber))+ #Set base data to present
  geom_bar(stat = "identity", position = "dodge",  color = "black", width = 1565200) + #Mess with first 2 digits of width to change (talk to EL for more indepth)
  scale_x_datetime("", expand = c(0.005, 0), #Set axis title and remove spacing
                   date_breaks = "1 month", date_labels = "%b %Y", #Set axis breaks, label format
                   guide = guide_axis(angle = 45))+
  scale_y_reverse("% Secchi Penetration", expand = c(0, 0),
                     limits = c(100, 0), pretty_breaks())+
  ggtitle("West") + BaseForm + Station_fill


```

```{r, warning = FALSE, message = FALSE, fig.cap = "Figure 8. Monthly mean Secchi penetration (percentage of water depth through which the Secchi disk could be seen) at recruitment and sedimentation monitoring stations in the West, Central, and East sections of Apalachicola Bay over the past fifteen months (five quarters). "}

ggarrange(SeW_fig7 + rremove('x.text') + theme(plot.margin = unit(c(0,0.2,-0.5,0.1), "lines")),
          SeC_fig7 + rremove('x.text')+ theme(plot.margin = unit(c(-0.5,0.2,-0.5,0.1), "lines")),
          SeE_fig7 + theme(plot.margin = unit(c(-0.5,0.2,0,0.1), "lines")),
          nrow = 3, ncol = 1)

```

