---
output: 
  word_document:
  toc: true
---

```{r include = FALSE}
# Set your variables
REnd <- as.Date("2023-09-30")  # Report End Date
```

```{r include = FALSE}
# Load necessary R packages
library(tidyverse)
library(odbc)
library(DBI)
library(dbplyr)
library(lubridate)
library(knitr)
library(ggpubr) #Required for arranging multiple plots
library(scales)

EstuaryCode = "AB"  # Report Estuary Code. Use 2-letter code in Primary Keys
REName = "Apalachicola Bay"  # Report Estuary Name. Use long name you want to appear in report
SBMStart <- floor_date(REnd %m-% months(20), unit = "month") 
QStart <- floor_date(REnd %m-% months(2), unit = "month")

```

```{r setup, include=FALSE}
# Configure chunks
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, fig.width = 8, fig.height = 10)
```

```{r DatabaseDownload}
# Connect to Local database server and pull all necessary data, then close connection 
con <- dbConnect(odbc(),
                    Driver= "SQL Server", 
                    Server = "localhost\\MATTLOCALSQL",
                    Database= "OysterLocalMD20231019",
                    Authentication = "ActiveDirectoryIntegrated")

dboFixedLocations <- tbl(con,in_schema("dbo", "FixedLocations")) %>%
  collect() %>% 
  filter(Estuary == EstuaryCode, ShellBudget == "Y")

hsdbSBMQuadrat <- tbl(con,in_schema("hsdb", "ShellBudgetQuadrat")) %>%
  collect() 
  
dboSBMQuadrat <- tbl(con,in_schema("dbo", "ShellBudgetQuadrat")) %>%
  collect() 

hsdbSBMSH <- tbl(con,in_schema("hsdb", "ShellBudgetSH")) %>%
  collect() 

dboSBMSH <- tbl(con,in_schema("dbo", "ShellBudgetSH")) %>%
  collect()

DBI::dbDisconnect(con)

```

```{r DataFilters}
# Filter data frames so that only data collected from Recruitment trips in the specified Estuary, in the correct date range, which have been Proofed, are present.
FixedLocations1 <- dboFixedLocations %>% 
  mutate(StationNumber = as.numeric(StationNumber)) %>%
  select(FixedLocationID,
         Estuary,
         StationName, 
         StationNumber,
         ParcelName) %>% 
  distinct()
          
SBM_Quad1 <- union_all(dboSBMQuadrat, hsdbSBMQuadrat) %>%
  filter(substring(QuadratID,1,2) == EstuaryCode) %>%
  mutate(TripDate = as.Date(substring(QuadratID, 8, 15), format = "%Y%m%d"),
       FixedLocationID = substring(QuadratID, 19, 22),
       Year = year(TripDate),
       OtherWeight = DrillWeight + OtherBiotaWeight + BlackAndOtherSubstrateWeight) %>%
  left_join(FixedLocations1, SampleEvent1, by = c("FixedLocationID")) %>%
  arrange(TripDate, StationNumber) %>%
  mutate(Survey = case_when(
        month(ymd(TripDate)) >= 1 & month(ymd(TripDate)) <= 3 ~ "Winter",
        month(ymd(TripDate)) >= 4 & month(ymd(TripDate)) <= 6 ~ "Spring",
        month(ymd(TripDate)) >= 7 & month(ymd(TripDate)) <= 9 ~ "Summer",
        month(ymd(TripDate)) > 9 ~ "Fall",
        TRUE ~ "Invalid")) %>%
  select(QuadratID, SampleEventID, TripDate, FixedLocationID, StationNumber, StationName, ParcelName, Survey, Year, NumLiveOysters, NumDrills, TotalSampleWeight, LiveOysterWeight, OysterShellWeight, PlantedShellWeight, ShellHashWeight, OtherWeight, Comments)

SBM_SH1 <- union_all(dboSBMSH, hsdbSBMSH) %>%
  mutate(TripDate = as.Date(substring(QuadratID, 8, 15), format = "%Y%m%d"),
       FixedLocationID = substring(QuadratID, 19, 22),
       Year = year(TripDate)) %>%
  left_join(FixedLocations1, SampleEvent1, by = c("FixedLocationID")) %>%
  arrange(TripDate, StationName) %>%
  mutate(Survey = case_when(
        month(ymd(TripDate)) >= 1 & month(ymd(TripDate)) <= 3 ~ "Winter",
        month(ymd(TripDate)) >= 4 & month(ymd(TripDate)) <= 6 ~ "Spring",
        month(ymd(TripDate)) >= 7 & month(ymd(TripDate)) <= 9 ~ "Summer",
        month(ymd(TripDate)) > 9 ~ "Fall",
        TRUE ~ "Invalid")) %>%
  filter(ShellHeightID != "#N/A") %>% ### Remove line once hsdb has been repaired
  select(ShellHeightID, QuadratID, TripDate, FixedLocationID, StationNumber, StationName, ParcelName, Survey, Year, LiveOrDead, ShellHeight)

### Provide stats for mean number of live oys (Fig 4); mean number of drills (Fig 7); mean weight (Fig 8)
SBM_QuadStats1 <- SBM_Quad1 %>%
  filter(TripDate > SBMStart) %>%
  mutate(OyDensity = NumLiveOysters * 4,
         DrillDensity = NumDrills * 4,
         WeightDensity = TotalSampleWeight * 4,
         Survey_Year = paste(Survey, Year, sep = " ")) %>%
  group_by(TripDate, Survey_Year, Survey, Year, FixedLocationID, StationNumber, StationName, ParcelName) %>%
  summarise(OyDensityMean = mean(OyDensity, na.rm = TRUE),
            OyDensitySD = sd(OyDensity, na.rm = TRUE),
            DrillDensityMean = mean(DrillDensity, na.rm = TRUE),
            DrillDensitySD = sd(DrillDensity, na.rm = TRUE),
            WeightDensityMean = mean(WeightDensity, na.rm = TRUE),
            WeightDensitySD = sd(WeightDensity, na.rm = TRUE)) %>%
  arrange(TripDate)

### Provide stats for mean weights of components (Fig 9)
SBM_QuadStats2 <- SBM_Quad1 %>%
  filter(TripDate > "2023-01-01") %>% ### This date needs to be changed to a variable!
  mutate(LiveOysterWeightDensity = LiveOysterWeight * 4,
         OysterShellWeightDensity = OysterShellWeight * 4,
         PlantedShellWeightDensity = PlantedShellWeight * 4,
         ShellHashWeightDensity = ShellHashWeight * 4,
         OtherWeightDensity = OtherWeight * 4) %>%
  group_by(Survey, Year, FixedLocationID, StationNumber, StationName, ParcelName) %>%
  summarise(LiveOysterWeightMean = mean(LiveOysterWeightDensity, na.rm = TRUE),
            LiveOysterWeightSD = sd(LiveOysterWeightDensity, na.rm = TRUE),
            OysterShellWeightMean = mean(OysterShellWeightDensity, na.rm = TRUE),
            OysterShellWeightSD = sd(OysterShellWeightDensity, na.rm = TRUE),
            PlantedShellWeightMean = mean(PlantedShellWeightDensity, na.rm = TRUE),
            PlantedShellWeightSD = sd(PlantedShellWeightDensity, na.rm = TRUE),
            ShellHashWeightMean = mean(ShellHashWeightDensity, na.rm = TRUE),
            ShellHashWeightSD = sd(ShellHashWeightDensity, na.rm = TRUE),
            OtherWeightMean = mean(OtherWeightDensity, na.rm = TRUE),
            OtherWeightSD = sd(OtherWeightDensity, na.rm = TRUE))

### Provides stats for Mean Shell Height LIVE (Fig 5)
SBM_SHStatsLive <- SBM_SH1 %>%
  filter(TripDate > SBMStart & LiveOrDead == "Live") %>%
  group_by(Survey, Year, FixedLocationID, StationNumber, StationName, ParcelName) %>%
  summarise(SHMean = mean(ShellHeight, na.rm = TRUE),
            SHSD = sd(ShellHeight, na.rm = TRUE))

### Provides stats for Mean Shell Height DEAD (Fig 6)
SBM_SHStatsDead <- SBM_SH1 %>%
  filter(TripDate > SBMStart & LiveOrDead == "Dead") %>%
  group_by(Survey, Year, FixedLocationID, StationNumber, StationName, ParcelName) %>%
  summarise(SHMean = mean(ShellHeight, na.rm = TRUE),
            SHSD = sd(ShellHeight, na.rm = TRUE))

### Provides stats for report text
SBM_QuadTextStats <- SBM_QuadStats1 %>%
  filter(Year > 2022) ### This date needs to be changed to a variable!

SBM_QuadWeightStats <- SBM_QuadStats2 %>%
  mutate(TotalWt = LiveOysterWeightMean + OysterShellWeightMean + PlantedShellWeightMean + ShellHashWeightMean + OtherWeightMean)

SBM_SHLiveTextStats <- SBM_SHStatsLive %>%
  filter(Year > 2022) ### This date needs to be changed to a variable!

SBM_SHDeadTextStats <- SBM_SHStatsDead %>%
  filter(Year > 2022) ### This date needs to be changed to a variable!

ReportTotalLive <- SBM_SH1 %>%
  filter(ShellHeight > 0 & Year == 2023 & LiveOrDead == "Live")

# SBM_SH2 <- SBM_SH1 %>%
#   group_by(Survey, Year, StationName, ParcelName, QuadratID) %>%
#   summarise(LegalCount = sum(ShellHeight > 74)) %>%
#   right_join(SBM_Quad1, by = c("QuadratID", "Year", "Survey", "StationName", "ParcelName")) %>%
#   filter(Year > 2020 & StationName != "SBM Normans" & StationName != "SBM Bulkhead" & StationName != "SBM Halfmoon" & ParcelName != "Cat Point Deep South" & ParcelName != "Cat Point Shallow" & ParcelName != "East Lumps South" & ParcelName != "Hotel West" & ParcelName != "Lighthouse South") %>%
#   mutate(OysterDensity = NumLiveOysters * 4, 
#          LegalTotal = ifelse(NumLiveOysters > 50, ((NumLiveOysters * LegalCount) / 50), LegalCount),
#          LegalDensity = LegalTotal *4,
#          BagsPerAcre = (LegalDensity * 4047) / 225)
  
# SBM_QuadStats2 <- SBM_SH2 %>%
#   group_by(Survey, Year, StationName) %>%
#   summarise(OysterDensityMean = mean(OysterDensity, na.rm = TRUE),
#             OysterDensitySD = sd(OysterDensity, na.rm = TRUE),
#             LegalDensityMean = mean(LegalDensity, na.rm = TRUE),
#             LegalDensitySD = sd(LegalDensity, na.rm = TRUE),
#             BagsPerAcreMean = mean(BagsPerAcre, na.rm = TRUE),
#             BagsPerAcreSD = sd(BagsPerAcre, na.rm = TRUE))
# 
# AllStats <- right_join(SBM_SHStats, SBM_QuadStats2, by = c("Year", "Survey", "StationName")) %>%
#   arrange(StationName, Year, desc(Survey)) 

```

Preliminary shell budget data is available through the end of `r format(max(SBM_Quad1$TripDate), "%B %Y")`.

Live oysters were present at all stations in the most recent samples (Fig. XXX). Mean oyster densities ranged from `r round(min(SBM_QuadTextStats$OyDensityMean, na.rm = TRUE), 0)` oysters/m² at `r paste(SBM_QuadTextStats$StationName, SBM_QuadTextStats$StationNumber)[which.min(SBM_QuadTextStats$OyDensityMean)]` to `r round(max(SBM_QuadTextStats$OyDensityMean, na.rm = TRUE), 0)` oysters/m² at `r paste(SBM_QuadTextStats$StationName, SBM_QuadTextStats$StationNumber)[which.max(SBM_QuadTextStats$OyDensityMean)]`. Mean densities were generally highest at stations which were recently cultched (Lighthouse, East Lumps, and Cat Point) though nearly all were recently settled spat. 

Live oyster shell height means ranged from `r round(min(SBM_SHLiveTextStats$SHMean, na.rm = TRUE), 0)` to `r round(max(SBM_SHLiveTextStats$SHMean, na.rm = TRUE), 0)` mm (Fig. 5) and an overall average shell height of `r round(mean(SBM_SHLiveTextStats$SHMean, na.rm = TRUE), 0)` mm. There were `r sum(ReportTotalLive$ShellHeight > 30)` oysters larger than 30 mm measured (`r percent(sum(ReportTotalLive$ShellHeight > 30) / nrow(ReportTotalLive), accuracy = 0.1)` of total measured), and there were `r sum(ReportTotalLive$ShellHeight > 75)` oyster of legal harvest size (SH>=76 mm) measured (`r percent(sum(ReportTotalLive$ShellHeight > 75) / nrow(ReportTotalLive), accuracy = 0.1)` of total measured) during this quarter.

Dead oysters were collected at most stations. Dead oyster shell heights averages ranged from `r round(min(SBM_SHDeadTextStats$SHMean, na.rm = TRUE), 0)` to `r round(max(SBM_SHDeadTextStats$SHMean, na.rm = TRUE), 0)` mm (Fig. 6) and the overall average shell height of dead oysters was `r round(mean(SBM_SHDeadTextStats$SHMean, na.rm = TRUE), 0)` mm.

No oyster drills (Stramonita floridana) were found at any station this quarter. Mean oyster drill densities were very low ranging from 0 to 0 oyster drill/m² (Fig. 7).
<!-- This needs to be updated next time as it won't always be true -->

Substrate weights were measured for all parcels (Figure 8). Substrate weights were highest at stations which were recently cultched (Lighthouse, East Lumps, and Cat Point). The main substrate components accounted for `r percent((sum(SBM_QuadWeightStats$TotalWt) - sum(SBM_QuadWeightStats$OtherWeightMean)) / sum(SBM_QuadWeightStats$TotalWt), accuracy = 0.1)` of total weight which were: cultch (`r percent(sum(SBM_QuadWeightStats$PlantedShellWeightMean) / sum(SBM_QuadWeightStats$TotalWt), accuracy = 0.1)` of total weight), shell hash (`r percent(sum(SBM_QuadWeightStats$ShellHashWeightMean) / sum(SBM_QuadWeightStats$TotalWt), accuracy = 0.1)` of total weight), live oysters (`r percent(sum(SBM_QuadWeightStats$LiveOysterWeightMean) / sum(SBM_QuadWeightStats$TotalWt), accuracy = 0.1)` of total weight) and oyster shell (`r percent(sum(SBM_QuadWeightStats$OysterShellWeightMean) / sum(SBM_QuadWeightStats$TotalWt), accuracy = 0.1)` of total weight). Proportions of substrate components differed between parcels with shell hash and cultch being the predominant substrate types (Figure 9). 


```{r}
#Base formatting for figure consistency
BaseForm <- theme_classic() +
  theme(panel.border = element_rect(color = "black", fill = NA), #Add border
        plot.title = element_text(hjust = 0, vjust = -7, family = "serif", color = "black", size = 12), #Add plot title for section
        axis.title = element_text(family = "serif", color = "black", size = 12), #Adjust axis title and text
        axis.text = element_text(family = "serif", color = "black", size = 10),
        axis.line = element_line(color = "black"),
        axis.ticks.length.x = unit(0.20, "cm"),
        axis.ticks.length.y = unit(0.1, "cm"),
        legend.position = "top", legend.justification = "right",  legend.box.spacing = unit(0.05, "line"), #Adjust legend position
        legend.title = element_blank(), legend.key.height = unit(0.5, "line"), legend.key.width = unit(1, "lines"), #Adjust legend title and spacing
        legend.text = element_text(family = "serif", color = "black", size = 9)) #Adjust legend text

#Color and shape to Fixed Locations
FixedLocations <- c("0009" = "Halfmoon-6", "0017" = "Normans-8", "0022" = "Hotel-East", "0023" = "Hotel-West", "0103" = "Bulkhead-North", "0104" = "Bulkhead-South", "0309" = "Lighthouse-Rest", "0310" = "East Lumps-Rest", "0311" = "Cat Point-Rest", "0530" = "Cat Point-Shallow", "0095" = "Cat Point-Shallow")
Stat_pal <- c(rgb(0, 64, 0, maxColorValue = 255), rgb(0, 255, 0, maxColorValue = 255), rgb(0, 128, 0, maxColorValue = 255), rgb(192, 255, 0, maxColorValue = 255), rgb(64, 192, 0, maxColorValue = 255),
              rgb(128, 0, 0, maxColorValue = 255), rgb(192, 192, 0, maxColorValue = 255), rgb(96, 0, 0, maxColorValue = 255), rgb(255, 128, 0, maxColorValue = 255), rgb(128, 64, 0, maxColorValue = 255),
              rgb(0, 0, 128, maxColorValue = 255), rgb(0, 128, 255, maxColorValue = 255), rgb(0, 0, 96, maxColorValue = 255), rgb(0, 128, 128, maxColorValue = 255), rgb(0, 64, 128, maxColorValue = 255))
Station_fill <- scale_fill_manual("", labels = FixedLocations, values = setNames(Stat_pal, 1:11), na.value = "#999999")
Station_color <- scale_color_manual("", labels = FixedLocations, values = setNames(Stat_pal, 1:11), na.value = "#999999")
Station_shape <- scale_shape_manual("",labels = FixedLocations, values = setNames(c(21, 25, 22, 23, 24, 21, 25, 22, 23, 24, 21, 25, 22, 23, 24), 1:15))
#
```

```{r}
#Creating Shell Budget figures Mean Live Oysters
#

SBM_fig4 <- SBM_QuadStats1 %>% 
  ggplot(aes(x = factor(Survey_Year), y = OyDensityMean, fill = FixedLocationID))+ #Set base data to present
  geom_bar(stat = "identity", position = "dodge",  color = "black", width = 0.5) + #Add bars. Deafult = 2365200. Edit first 2 digits of width to change (talk to EL for more in depth)
  geom_errorbar(aes(factor(Survey_Year), ymin = OyDensityMean, ymax = OyDensityMean + OyDensitySD), position = position_dodge(), width = 0.5)+ #Add error bars
  scale_x_discrete("", expand = c(0.005, 0), #Set axis title and remove spacing
                   guide = guide_axis(angle = 45))+
  scale_y_continuous("Live oysters / m2", expand = c(0, 0))+
  ggtitle("") + BaseForm + Station_fill

SBM_fig4
```


```{r}
library(openxlsx)

mydatasets <- list('Sheet1' = SBM_QuadStats1, 'Sheet2' = SBM_QuadStats2, 'Sheet3' = SBM_SHStatsLive, 'Sheet4' = SBM_SHStatsDead)
write.xlsx(mydatasets, "SBM_ReportStats.xlsx", colNames = TRUE, rowNames = FALSE)

```

