---
title: "Quarterly Report Information"
author: "ELevine"
date: "`r Sys.Date()`"
output: 
  html_document:
  word_document: NULL
params:
  Start_date: "2025-10-01"
  End_date: "2025-12-30"
---
<style>
.main-container {
    max-width: 9000px;
    margin-left: 20px;
    margin-right: auto;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
#
Start_date <- as.Date(params$Start_date)
End_date <- as.Date(params$End_date)

#Packages
if (!require("pacman")) {install.packages("pacman")}
#p_unlock()
pacman::p_load(odbc, DBI, dbplyr,
  tidyverse, dplyr,  stringr, #DF manipulation
  DT, openxlsx,         #Excel
  lubridate, zoo,         #Dates
  knitr, kableExtra, scales, gt, gtExtras,
  install = TRUE)
#
#
# Function to determine increase/decrease
get_change <- function(col) {
  first <- col[1]
  last <- col[length(col)]
  if (last > first) {
    return("increased")
  } else if (last < first) {
    return("decreased")
  } else {
    return("no change")
  }
}
#
#
```

```{css}
p {
font-size: 12pt;
}

caption {
  color: black;
  font-weight: bold;
  font-size: 14;
  text-indent: 5%;
} 

h1 {
font-size: 21pt;
font-weight: bold;
}

h2 {
font-size: 17pt;
font-weight: bold;
}

h3 {
font-size: 13pt;
font-style: italic;
text-decoration: underline;
}

h4 {
  color: black;
  font-weight: bold;
  font-size: 17;
  text-indent: 5%;
}
```

```{r Data gather from summary file}
WQ_Sal_s <-  readWorkbook("../Summary data/CERP_PBC_WQ_Summary_Data.xlsx", sheet = 'Salinity Station', detectDates = TRUE, check.names = TRUE)
WQ_Secchi_s <-  readWorkbook("../Summary data/CERP_PBC_WQ_Summary_Data.xlsx", sheet = 'Secchi Station', detectDates = TRUE, check.names = TRUE)
Dermo_df <- readWorkbook("../Summary data/CERP_PBC_Summary_Data.xlsx", sheet = 'Dermo Station', detectDates = TRUE, check.names = TRUE)
Rcrt_df <- readWorkbook("../Summary data/CERP_PBC_Summary_Data.xlsx", sheet = 'Rcrt Station', detectDates = TRUE, check.names = TRUE)
Repro_df <- readWorkbook("../Summary data/CERP_PBC_Summary_Data.xlsx", sheet = 'Repro', detectDates = TRUE, check.names = TRUE)
Counts_df <- readWorkbook("../Summary data/CERP_PBC_Summary_Data.xlsx", sheet = 'DeadRatio Station', detectDates = TRUE, check.names = TRUE)
SH_df <- readWorkbook("../Summary data/CERP_PBC_Summary_Data.xlsx", sheet = 'SH Station', detectDates = TRUE, check.names = TRUE)
Cage_df <- readWorkbook("../Summary data/CERP_PBC_Summary_Data.xlsx", sheet = 'SH Mort Cage', detectDates = TRUE, check.names = TRUE)
```

```{r Data selection and cleaning}
#
##Salinity
WQ_Sal_CERP <- WQ_Sal_s %>% dplyr::select(starts_with("SL"), starts_with("LX")) %>% subset(SL.C_RetDate_Sal > Start_date & SL.C_RetDate_Sal < End_date) %>% rename(RetDate = SL.C_RetDate_Sal) %>% dplyr::select(-SL.N_RetDate_Sal, -SL.S_RetDate_Sal, -LX.N_RetDate_Sal, -LX.S_RetDate_Sal) %>% mutate(RetDate = as.yearmon(RetDate))
WQ_Sal_CRE <- WQ_Sal_s %>% dplyr::select(starts_with("CR")) %>% subset(CR.E_RetDate_Sal > Start_date & CR.E_RetDate_Sal < End_date)  %>% rename(RetDate = CR.E_RetDate_Sal) %>% dplyr::select(-CR.W_RetDate_Sal)
#
#Secchi
WQ_Sec_CERP <- WQ_Secchi_s %>% dplyr::select(starts_with("SL"), starts_with("LX")) %>% subset(SL.C_RetDate_SP > Start_date & SL.C_RetDate_SP < End_date) %>% rename(RetDate = SL.C_RetDate_SP) %>% dplyr::select(-SL.N_RetDate_SP, -SL.S_RetDate_SP, -LX.N_RetDate_SP, -LX.S_RetDate_SP) %>% mutate(RetDate = as.yearmon(RetDate))
WQ_Sec_CRE <- WQ_Secchi_s %>% dplyr::select(starts_with("CR")) %>% subset(CR.E_RetDate_SP > Start_date & CR.E_RetDate_SP < End_date)  %>% rename(RetDate = CR.E_RetDate_SP) %>% dplyr::select(-CR.W_RetDate_SP)
#
#Dermo
Dermo_CERP <- Dermo_df %>% dplyr::select(starts_with("SL"), starts_with("LX")) %>% dplyr::select(!contains("SD")) %>% subset(SL.C_RetDate > Start_date & SL.C_RetDate < End_date) %>% rename(RetDate = SL.C_RetDate) %>% dplyr::select(-SL.N_RetDate, -SL.S_RetDate, -LX.N_RetDate, -LX.S_RetDate) %>% mutate(RetDate = as.yearmon(RetDate))
Dermo_CRE <- Dermo_df %>% dplyr::select(starts_with("CR")) %>% dplyr::select(!contains("SD")) %>% subset(CR.E_RetDate > Start_date & CR.E_RetDate < End_date) %>% rename(RetDate = CR.E_RetDate) %>% dplyr::select(-CR.W_RetDate) %>% mutate(RetDate = as.yearmon(RetDate))
#
#Rcrt
Rcrt_CERP <- Rcrt_df %>% dplyr::select(starts_with("SL"), starts_with("LX")) %>% dplyr::select(!contains("SD")) %>% subset(SL.C_RetDate > Start_date & SL.C_RetDate < End_date) %>% rename(RetDate = SL.C_RetDate) %>% dplyr::select(-SL.N_RetDate, -SL.S_RetDate, -LX.N_RetDate, -LX.S_RetDate) %>% mutate(RetDate = as.yearmon(RetDate))
Rcrt_CRE <- Rcrt_df %>% dplyr::select(starts_with("CR")) %>% dplyr::select(!contains("SD")) %>% subset(CR.E_RetDate > Start_date & CR.E_RetDate < End_date) %>% rename(RetDate = CR.E_RetDate) %>% dplyr::select(-CR.W_RetDate) %>% mutate(RetDate = as.yearmon(RetDate))
#
#Repro
Repro_CERP <- Repro_df %>% dplyr::select(starts_with("SL"), starts_with("LX")) %>% subset(SL.C_RetDate > Start_date & SL.C_RetDate < End_date) %>% rename(RetDate = SL.C_RetDate) %>% dplyr::select(-SL.N_RetDate, -SL.S_RetDate, -LX.N_RetDate, -LX.S_RetDate) %>% mutate(RetDate = as.yearmon(RetDate))
Repro_CRE <- Repro_df %>% dplyr::select(starts_with("CR")) %>% subset(CR.E_RetDate > Start_date & CR.E_RetDate < End_date) %>% rename(RetDate = CR.E_RetDate) %>% dplyr::select(-CR.W_RetDate) %>% mutate(RetDate = as.yearmon(RetDate))
#
##Survey counts
Counts_CERP <- Counts_df %>% dplyr::select(AnalysisDate, starts_with("SL"), starts_with("LX")) %>%  mutate(AnalysisDate = as.yearmon(AnalysisDate)) %>% subset(AnalysisDate > (as.yearmon(End_date %m-% months(7))) & AnalysisDate < as.yearmon(End_date %m+% months(1))) %>% replace(is.na(.), -999)
Counts_CERP_change <- as.data.frame(t(sapply(Counts_CERP, get_change))) 
#
Counts_CRE <- Counts_df %>% dplyr::select(AnalysisDate, starts_with("CR")) %>%  mutate(AnalysisDate = as.yearmon(AnalysisDate)) %>% subset(AnalysisDate > (as.yearmon(End_date %m-% months(7))) & AnalysisDate < as.yearmon(End_date %m+% months(1))) %>% replace(is.na(.), -999)
Counts_CRE_change <- as.data.frame(t(sapply(Counts_CRE, get_change))) 
#
#
##Survey SHs
SH_CERP <- SH_df %>% dplyr::select(AnalysisDate, starts_with("SL"), starts_with("LX")) %>%  mutate(AnalysisDate = as.yearmon(AnalysisDate)) %>% subset(AnalysisDate > (as.yearmon(End_date %m-% months(7))) & AnalysisDate < as.yearmon(End_date %m+% months(1))) %>% replace(is.na(.), -999)
SH_CRE <- SH_df %>% dplyr::select(AnalysisDate, starts_with("CR")) %>%  mutate(AnalysisDate = as.yearmon(AnalysisDate)) %>% subset(AnalysisDate > (as.yearmon(End_date %m-% months(7))) & AnalysisDate < as.yearmon(End_date %m+% months(1))) %>% replace(is.na(.), -999)
#
##Cages
Cage_CERP <- Cage_df %>% dplyr::select(starts_with("SL"), starts_with("LX")) %>% dplyr::select(!contains("SD")) %>% subset(SL.C_RetDate > Start_date & SL.C_RetDate < End_date) %>% rename(RetDate = SL.C_RetDate) %>% dplyr::select(-LX.N_RetDate) %>% mutate(RetDate = as.yearmon(RetDate))
Cage_CRE <- Cage_df %>% dplyr::select(starts_with("CR")) %>% dplyr::select(!contains("SD")) %>% subset(CR.E_RetDate > Start_date & CR.E_RetDate < End_date) %>% rename(RetDate = CR.E_RetDate) %>% dplyr::select(-CR.W_RetDate) %>% mutate(RetDate = as.yearmon(RetDate))
#
#
```

```{r table formatting, results = "asis"}
#Salinity
CERP_Sal <- WQ_Sal_CERP %>% gt() %>% data_color(columns = contains("Sal"), fn = scales::col_numeric(palette = "plasma", domain = WQ_Sal_CERP %>% dplyr::select(contains("Sal")) %>% unlist() %>% range(na.rm = T))) %>% gt_add_divider(columns = c(1, 4, 7, 10, 13, 16), sides = "right", color = "black") %>% cols_label_with(fn = ~gsub("_Sal","", .)) %>% cols_align(align = c("center"), columns = everything())
#
CRE_Sal <- WQ_Sal_CRE %>% gt() %>% data_color(columns = contains("Sal"), fn = scales::col_numeric(palette = "plasma", domain = WQ_Sal_CRE %>% dplyr::select(contains("Sal")) %>% unlist() %>% range(na.rm = T))) %>% gt_add_divider(columns = c(1, 3), sides = "right", color = "black") %>% cols_label_with(fn = ~gsub("_Sal","", .)) %>% cols_align(align = c("center"), columns = everything())
#
#
#
##Secchi
CERP_Sec <- WQ_Sec_CERP %>% gt() %>% data_color(columns = contains("SP"), fn = scales::col_numeric(palette = "plasma", domain = WQ_Sec_CERP %>% dplyr::select(contains("SP")) %>% unlist() %>% range(na.rm = T))) %>% gt_add_divider(columns = c(1, 4, 7, 10, 13, 16), sides = "right", color = "black") %>% cols_label_with(fn = ~gsub("_SP","", .)) %>% cols_align(align = c("center"), columns = everything())
#
CRE_Sec <- WQ_Sec_CRE %>% gt() %>% data_color(columns = contains("SP"), fn = scales::col_numeric(palette = "plasma", domain = WQ_Sec_CRE %>% dplyr::select(contains("SP")) %>% unlist() %>% range(na.rm = T))) %>% gt_add_divider(columns = c(1, 3), sides = "right", color = "black") %>% cols_label_with(fn = ~gsub("_SP","", .)) %>% cols_align(align = c("center"), columns = everything())
#
#
#
##Dermo
CERP_dermo <- Dermo_CERP %>% gt() %>% data_color(columns = contains("Pct"), fn = scales::col_numeric(palette = "plasma", domain = Dermo_CERP %>% dplyr::select(contains("Pct")) %>% unlist() %>% range(na.rm = T))) %>% cols_label_with(fn = ~gsub("_Mean","", .)) %>% cols_label_with(fn = ~gsub("_Pct","", .)) %>% gt_add_divider(columns = c(1, 3, 5, 7, 9, 11, 13, 15, 17, 19, 21, 23, 25, 27, 29), sides = "right", color = "black") %>% cols_align(align = c("center"), columns = everything()) %>% tab_options(container.width = 2000)
#
CRE_dermo <- Dermo_CRE %>% gt() %>% data_color(columns = contains("Pct"), fn = scales::col_numeric(palette = "plasma", domain = Dermo_CRE %>% dplyr::select(contains("Pct")) %>% unlist() %>% range(na.rm = T))) %>% cols_label_with(fn = ~gsub("_Mean","", .)) %>% cols_label_with(fn = ~gsub("_Pct","", .)) %>% gt_add_divider(columns = c(1, 3, 5, 7), sides = "right", color = "black") %>% cols_align(align = c("center"), columns = everything())
#
#
#
##Rcrt
CERP_rcrt <- Rcrt_CERP %>% gt() %>% 
  data_color(columns = contains("Mean"), fn = scales::col_numeric(palette = "plasma", domain = Rcrt_CERP %>% dplyr::select(contains("Mean")) %>% unlist() %>% range(na.rm = T))) %>% 
  gt_add_divider(columns = c(1, 4, 7, 10, 13), sides = "right", color = "black") %>% 
  cols_align(align = c("center"), columns = everything()) %>% 
  tab_options(container.width = 1800)
#
CRE_rcrt <- Rcrt_CRE %>% gt() %>% data_color(columns = contains("Mean"), fn = scales::col_numeric(palette = "plasma", domain = Rcrt_CRE %>% dplyr::select(contains("Mean")) %>% unlist() %>% range(na.rm = T))) %>% gt_add_divider(columns = c(1, 3), sides = "right", color = "black") %>% cols_align(align = c("center"), columns = everything())
#
#
#
##Repro
if(nrow(Repro_CERP) > 0){
  CERP_repro <- Repro_CERP %>% gather(Site, Pct, -RetDate) %>% mutate(Station = substr(Site, 1, 4), Stage = substr(Site, 6, 8)) %>% dplyr::select(-Site) %>% spread(Stage, Pct) %>% arrange(Station, RetDate) %>% gt(rowname_col = "RetDate", groupname_col = "Station") %>% cols_move(Dev, Ind) %>% data_color(direction = "row", method = "numeric", palette = c("plasma"), alpha = 0.8) %>% cols_align(align = c("center"), columns = everything()) %>% tab_options(row_group.border.top.color = "black", row_group.border.bottom.color = "black", row_group.font.weight = "bold")
} else {
  CERP_repro <- "Data unavailable."
}
#
if(nrow(Repro_CRE) > 0){
  CRE_repro <- Repro_CRE %>% gather(Site, Pct, -RetDate) %>% mutate(Station = substr(Site, 1, 4), Stage = substr(Site, 6, 8)) %>% dplyr::select(-Site) %>% spread(Stage, Pct) %>% arrange(Station, RetDate) %>% gt(rowname_col = "RetDate", groupname_col = "Station") %>% cols_move(Dev, Ind) %>% data_color(direction = "row", method = "numeric", palette = c("plasma"), alpha = 0.8) %>% cols_align(align = c("center"), columns = everything()) %>% tab_options(row_group.border.top.color = "black", row_group.border.bottom.color = "black", row_group.font.weight = "bold")
} else {
  CRE_repro <- "Data unavailable."
}
#
#
#
##Counts - gt_gtoup objetc must be completed in line for RMarkdown to output correctly - CERP tables moved in-line
#CERP_count <- Counts_CERP %>% dplyr::select(AnalysisDate, contains("Live"))%>% gt() %>% data_color(rows = (AnalysisDate > as.yearmon(Start_date) & AnalysisDate < as.yearmon(End_date %m+% months(1))), columns = contains("Mean"), fn = scales::col_numeric(palette = "plasma", domain = Counts_CERP %>% filter(AnalysisDate > as.yearmon(Start_date)) %>% dplyr::select(contains("Mean")) %>% unlist() %>% range(na.rm = T) )) %>% cols_align(align = c("center"), columns = everything()) %>% cols_label_with(fn = ~gsub("LiveMean","Mean", .)) %>% cols_label_with(fn = ~gsub("LiveSD","SD", .)) %>% gt_add_divider(columns = c(1, 3, 5, 7, 9, 11, 13, 15, 17, 19, 21, 23, 25, 27, 29), sides = "right", color = "black") %>% tab_caption(caption = "Monthly CERP live oyster counts") %>% gt_split(col_slice_at = "SL.S3_LiveSD") %>%   grp_options(container.width = 2000)

#CERP_count_change <- as.data.frame(t(sapply(Counts_CERP, get_change))) %>% dplyr::select(AnalysisDate, contains("Live")) %>% gt() %>% sub_values(columns = "AnalysisDate", rows = 1, pattern = "creased", replacement = "--") %>% sub_values(columns = contains("SD"), rows = 1, pattern = "creased", replacement = "--") %>% cols_align(align = c("center"), columns = everything()) %>% cols_label_with(fn = ~gsub("LiveMean","Mean", .)) %>% cols_label_with(fn = ~gsub("LiveSD","SD", .)) %>% gt_add_divider(columns = c(1, 3, 5, 7, 9, 11, 13, 15, 17, 19, 21, 23, 25, 27, 29), sides = "right", color = "black") %>% gt_split(col_slice_at = "SL.S3_LiveSD") %>% grp_options(container.width = 2000)
#
CRE_count <- Counts_CRE %>% dplyr::select(AnalysisDate, contains("Live")) %>% gt() %>% data_color(rows = (AnalysisDate > as.yearmon(Start_date) & AnalysisDate < as.yearmon(End_date %m+% months(1))), columns = contains("Mean"), fn = scales::col_numeric(palette = "plasma", domain = Counts_CRE %>% filter(AnalysisDate > as.yearmon(Start_date)) %>% dplyr::select(contains("Mean")) %>% unlist() %>% range(na.rm = T))) %>% cols_align(align = c("center"), columns = everything()) %>% cols_label_with(fn = ~gsub("LiveMean","Mean", .)) %>% cols_label_with(fn = ~gsub("LiveSD","SD", .)) %>% gt_add_divider(columns = c(1, 3, 5, 7), sides = "right", color = "black")

CRE_count_change <- as.data.frame(t(sapply(Counts_CRE, get_change))) %>% 
  dplyr::select(AnalysisDate, contains("Live")) %>% gt() %>% 
  sub_values(columns = "AnalysisDate", rows = 1, pattern = "creased", replacement = "--") %>% 
  sub_values(columns = contains("SD"), rows = 1, pattern = "creased", replacement = "--") %>% 
  cols_align(align = c("center"), columns = everything()) %>% 
     cols_label_with(fn = ~gsub("LiveMean","Mean", .)) %>% 
     cols_label_with(fn = ~gsub("LiveSD","SD", .)) %>% 
     gt_add_divider(columns = c(1, 3, 5, 7), sides = "right", color = "black") 
#
#
#
##Dead Ratios -   (see Counts comment)
#CERP_dead <- Counts_CERP %>% dplyr::select(AnalysisDate, contains("Dead")) %>% gt() %>% data_color(rows = (AnalysisDate > as.yearmon(Start_date) & AnalysisDate < as.yearmon(End_date %m+% months(1))), columns = contains("Mean"), fn = scales::col_numeric(palette = "plasma", domain = Counts_CERP %>% filter(AnalysisDate > as.yearmon(Start_date)) %>% dplyr::select(contains("Mean")) %>% unlist() %>% range(na.rm = T))) %>% cols_align(align = c("center"), columns = everything()) %>% cols_label_with(fn = ~gsub("DeadRatioMean","Mean", .)) %>% cols_label_with(fn = ~gsub("DeadRatioSD","SD", .)) %>% gt_add_divider(columns = c(1, 3, 5, 7, 9, 11, 13, 15, 17, 19, 21, 23, 25, 27, 29), sides = "right", color = "black") %>% tab_caption(caption = "Monthly CERP dead ratios")%>% gt_split(col_slice_at = "SL.S3_DeadRatioSD") %>% grp_options(container.width = 1500)

#CERP_dead_change <- as.data.frame(t(sapply(Counts_CERP, get_change))) %>% dplyr::select(AnalysisDate, contains("Dead")) %>% gt() %>% sub_values(columns = "AnalysisDate", rows = 1, pattern = "creased", replacement = "--") %>% sub_values(columns = contains("SD"), rows = 1, pattern = "creased", replacement = "--") %>% cols_align(align = c("center"), columns = everything()) %>% cols_label_with(fn = ~gsub("DeadRatioMean","Mean", .)) %>% cols_label_with(fn = ~gsub("DeadSD","SD", .)) %>% gt_add_divider(columns = c(1, 3, 5, 7, 9, 11, 13, 15, 17, 19, 21, 23, 25, 27, 29), sides = "right", color = "black") %>% gt_split(col_slice_at = "SL.S3_DeadRatioSD") %>% grp_options(container.width = 2000)
#
CRE_dead <- Counts_CRE %>% dplyr::select(AnalysisDate, contains("Dead")) %>% gt() %>% data_color(rows = (AnalysisDate > as.yearmon(Start_date) & AnalysisDate < as.yearmon(End_date %m+% months(1))), columns = contains("Mean"), fn = scales::col_numeric(palette = "plasma", domain = Counts_CRE %>% filter(AnalysisDate > as.yearmon(Start_date)) %>% dplyr::select(contains("Mean")) %>% unlist() %>% range(na.rm = T))) %>% cols_align(align = c("center"), columns = everything()) %>% cols_label_with(fn = ~gsub("DeadRatioMean","Mean", .)) %>% cols_label_with(fn = ~gsub("DeadRatioSD","SD", .)) %>% gt_add_divider(columns = c(1, 3, 5, 7), sides = "right", color = "black")

CRE_dead_change <- as.data.frame(t(sapply(Counts_CRE, get_change))) %>% 
  dplyr::select(AnalysisDate, contains("Dead")) %>% gt() %>% 
  sub_values(columns = "AnalysisDate", rows = 1, pattern = "creased", replacement = "--") %>%   
  sub_values(columns = contains("SD"), rows = 1, pattern = "creased", replacement = "--") %>% 
  cols_align(align = c("center"), columns = everything()) %>% 
     cols_label_with(fn = ~gsub("DeadMean","Mean", .)) %>% 
     cols_label_with(fn = ~gsub("DeadSD","SD", .)) %>% 
     gt_add_divider(columns = c(1, 3, 5, 7), sides = "right", color = "black") 
#
#
#
##SHs
#CERP_SH <- SH_CERP %>% dplyr::select(AnalysisDate, contains("Mean")) %>% gt() %>% data_color(rows = (AnalysisDate > as.yearmon(Start_date) & AnalysisDate < as.yearmon(End_date %m+% months(1))), columns = contains("Mean"), fn = scales::col_numeric(palette = "plasma", domain = SH_CERP %>% filter(AnalysisDate > as.yearmon(Start_date)) %>% dplyr::select(contains("Mean")) %>% unlist() %>% range(na.rm = T))) %>% cols_align(align = c("center"), columns = everything()) %>% gt_add_divider(columns = c(1, 4, 7, 10, 13), sides = "right", color = "black") %>% tab_caption(caption = "Monthly CERP shell heights")%>% gt_split(col_slice_at = "SL.S3_SHMean") %>% grp_options(container.width = 1500)
#
CRE_SH <- SH_CRE %>% dplyr::select(AnalysisDate, contains("Mean")) %>% gt() %>% data_color(rows = (AnalysisDate > as.yearmon(Start_date) & AnalysisDate < as.yearmon(End_date %m+% months(1))), columns = contains("Mean"), fn = scales::col_numeric(palette = "plasma", domain = SH_CRE %>% filter(AnalysisDate > as.yearmon(Start_date)) %>% dplyr::select(contains("Mean")) %>% unlist() %>% range(na.rm = T))) %>% cols_align(align = c("center"), columns = everything()) %>% gt_add_divider(columns = c(1, 3), sides = "right", color = "black")
#
#
#
#
##Cages
SL_Cage <- Cage_CERP %>% dplyr::select(RetDate, contains("SL")) %>% gt() %>% data_color(columns = contains("Pct"), fn = scales::col_numeric(palette = "plasma", domain = Cage_CERP %>% dplyr::select(RetDate, contains("SL")) %>% dplyr::select(contains("Pct")) %>% unlist() %>% range(na.rm = T))) %>% cols_label_with(fn = ~gsub("_SHMean","", .)) %>% cols_align(align = c("center"), columns = everything()) %>% tab_options(container.width = 1500)
#
LX_Cage <- Cage_CERP %>% dplyr::select(RetDate, contains("LX")) %>% gt() %>% data_color(columns = contains("Pct"), fn = scales::col_numeric(palette = "plasma", domain = Cage_CERP %>% dplyr::select(RetDate, contains("LX")) %>% dplyr::select(contains("Pct")) %>% unlist() %>% range(na.rm = T))) %>% cols_label_with(fn = ~gsub("_SHMean","", .)) %>% cols_align(align = c("center"), columns = everything()) %>% tab_options(container.width = 1500)
#
CRE_Cage <- Cage_CRE %>% dplyr::select(RetDate, contains("CR.E")) %>% gt() %>% data_color(columns = contains("Pct"), fn = scales::col_numeric(palette = "plasma", domain = Cage_CRE %>% dplyr::select(RetDate, contains("CR.E")) %>% dplyr::select(contains("Pct")) %>% unlist() %>% range(na.rm = T))) %>% cols_label_with(fn = ~gsub("_SHMean","", .)) %>% cols_align(align = c("center"), columns = everything()) %>% tab_options(container.width = 1500)
#
CRW_Cage <- Cage_CRE %>% dplyr::select(RetDate, contains("CR.W")) %>% gt() %>% data_color(columns = contains("Pct"), fn = scales::col_numeric(palette = "plasma", domain = Cage_CRE %>% dplyr::select(RetDate, contains("CR.W")) %>% dplyr::select(contains("Pct")) %>% unlist() %>% range(na.rm = T))) %>% cols_label_with(fn = ~gsub("_SHMean","", .)) %>% cols_align(align = c("center"), columns = everything()) %>% tab_options(container.width = 1500)
#
#
```

```{r Summary data: ranges, include = FALSE}
#
###Summary data:

#CERP summary
CERP_Counts_temp <- Counts_CERP %>% filter(AnalysisDate > as.yearmon(Start_date) & AnalysisDate < as.yearmon(End_date %m+% months(1))) %>% dplyr::select(contains("LiveMean")) %>% mutate(across(where(is.numeric), ~ifelse(. <= 0 | is.na(.), NA, .))) %>% gather(Station, Value) %>% arrange(desc(Value)) %>% drop_na()
CERP_DR_temp <-  Counts_CERP %>% filter(AnalysisDate > as.yearmon(Start_date) & AnalysisDate < as.yearmon(End_date %m+% months(1))) %>% dplyr::select(contains("DeadRatioMean")) %>% mutate(across(where(is.numeric), ~ifelse(. <= 0 | is.na(.), NA, .))) %>% gather(Station, Value) %>% arrange(desc(Value)) %>% drop_na()
CERP_SH_temp <- SH_CERP %>% filter(AnalysisDate > as.yearmon(Start_date) & AnalysisDate < as.yearmon(End_date %m+% months(1))) %>% dplyr::select(contains("Mean")) %>% mutate(across(where(is.numeric), ~ifelse(. < 0 | is.na(.), NA, .))) %>% gather(Station, Value) %>% arrange(desc(Value)) %>% drop_na()
CERP_Rcrt_temp <- Rcrt_CERP %>% dplyr::select(contains("Mean")) %>% gather(Station, Value) %>% arrange(desc(Value)) %>% drop_na() %>% dplyr::select(Value) %>% distinct()
CERP_Sal_temp <- WQ_Sal_CERP %>% dplyr::select(contains("Sal")) %>% gather(Station, Value) %>% arrange(desc(Value)) %>% drop_na() %>% dplyr::select(Value) %>% distinct()
#
#CRE summary
CRE_Counts_temp <- Counts_CRE %>% filter(AnalysisDate > as.yearmon(Start_date) & AnalysisDate < as.yearmon(End_date %m+% months(1))) %>% dplyr::select(contains("LiveMean")) %>% mutate(across(where(is.numeric), ~ifelse(. <= 0 | is.na(.), NA, .))) %>% gather(Station, Value) %>% arrange(desc(Value)) %>% drop_na()
CRE_DR_temp <-  Counts_CRE %>% filter(AnalysisDate > as.yearmon(Start_date) & AnalysisDate < as.yearmon(End_date %m+% months(1))) %>% dplyr::select(contains("DeadRatioMean")) %>% mutate(across(where(is.numeric), ~ifelse(. <= 0 | is.na(.), NA, .))) %>% gather(Station, Value) %>% arrange(desc(Value)) %>% drop_na()
CRE_SH_temp <- SH_CRE %>% filter(AnalysisDate > as.yearmon(Start_date) & AnalysisDate < as.yearmon(End_date %m+% months(1))) %>% dplyr::select(contains("Mean")) %>% mutate(across(where(is.numeric), ~ifelse(. < 0 | is.na(.), NA, .))) %>% gather(Station, Value) %>% arrange(desc(Value)) %>% drop_na()
CRE_Rcrt_temp <- Rcrt_CRE %>% dplyr::select(contains("Mean")) %>% gather(Station, Value) %>% arrange(desc(Value)) %>% drop_na() %>% dplyr::select(Value) %>% distinct()
CRE_Sal_temp <- WQ_Sal_CRE %>% dplyr::select(contains("Sal")) %>% gather(Station, Value) %>% arrange(desc(Value)) %>% drop_na() %>% dplyr::select(Value) %>% distinct()
#
#
```

## Report summary
This data summary was compiled on `r format(Sys.Date(), "%d %B %Y")` and summarizes data for the **CERP** quarterly report from `r format(Start_date, "%B %Y")` through `r format(End_date, "%B %Y")`.\

<h1>`r paste("CERP Quarterly Report")`</h1>
<h2>`r paste("East Coast")`</h2>
Minimum and maximum values observed during the quarter and data ordered by increasing values.
<h3> `r paste("Survey summary")`</h3>
Live Counts range: `r CERP_Counts_temp  %>% slice(n()) %>% pull(Value)` - `r CERP_Counts_temp  %>% slice(1) %>% pull(Value)`\
Live Counts mid-range: `r CERP_Counts_temp  %>% slice(n()-1) %>% pull(Value)` - `r CERP_Counts_temp  %>% slice(2) %>% pull(Value)`
```{r CERP counts table, results= "asis" }
 Counts_CERP %>% dplyr::select(AnalysisDate, contains("Live"))%>% 
  gt() %>% 
  data_color(rows = (AnalysisDate > as.yearmon(Start_date) & AnalysisDate < as.yearmon(End_date %m+% months(1))),
             columns = contains("Mean"), 
             fn = scales::col_numeric(
               palette = "plasma", 
               domain = Counts_CERP %>% filter(AnalysisDate > as.yearmon(Start_date)) %>% dplyr::select(contains("Mean")) %>% unlist() %>% range(na.rm = T) )) %>%
  cols_align(align = c("center"), columns = everything()) %>% 
  cols_label_with(fn = ~gsub("LiveMean","Mean", .)) %>% 
  cols_label_with(fn = ~gsub("LiveSD","SD", .)) %>% 
  gt_add_divider(columns = c(1, 3, 5, 7, 9, 11, 13, 15, 17, 19, 21, 23, 25, 27, 29), sides = "right", color = "black") %>%
  tab_caption(caption = "Monthly CERP live oyster counts") %>%
  gt_split(col_slice_at = "SL.S3_LiveSD") %>% 
  grp_options(container.width = 2000)

as.data.frame(t(sapply(Counts_CERP, get_change))) %>% 
  dplyr::select(AnalysisDate, contains("Live")) %>% gt() %>% 
  sub_values(columns = "AnalysisDate", rows = 1, pattern = "creased", replacement = "--") %>% 
  sub_values(columns = contains("SD"), rows = 1, pattern = "creased", replacement = "--") %>% 
  cols_align(align = c("center"), columns = everything()) %>% 
     cols_label_with(fn = ~gsub("LiveMean","Mean", .)) %>% 
     cols_label_with(fn = ~gsub("LiveSD","SD", .)) %>% 
     gt_add_divider(columns = c(1, 3, 5, 7, 9, 11, 13, 15, 17, 19, 21, 23, 25, 27, 29), sides = "right", color = "black") %>%
  tab_caption(caption = "Survey live counts comparison") %>%
     gt_split(col_slice_at = "SL.S3_LiveSD") %>% 
     grp_options(container.width = 2000)
```
\
\
\
DeadRatio range: `r CERP_DR_temp  %>% slice(n()) %>% pull(Value)` - `r CERP_DR_temp  %>% slice(1) %>% pull(Value)` \
DeadRatio mid-range:`r CERP_DR_temp  %>% slice(n()-1) %>% pull(Value)` - `r CERP_DR_temp  %>% slice(2) %>% pull(Value)`
```{r CERP dead ratios tables}
Counts_CERP %>% dplyr::select(AnalysisDate, contains("Dead")) %>% gt() %>% data_color(rows = (AnalysisDate > as.yearmon(Start_date) & AnalysisDate < as.yearmon(End_date %m+% months(1))), columns = contains("Mean"), fn = scales::col_numeric(palette = "plasma", domain = Counts_CERP %>% filter(AnalysisDate > as.yearmon(Start_date)) %>% dplyr::select(contains("Mean")) %>% unlist() %>% range(na.rm = T))) %>% cols_align(align = c("center"), columns = everything()) %>% cols_label_with(fn = ~gsub("DeadRatioMean","Mean", .)) %>% cols_label_with(fn = ~gsub("DeadRatioSD","SD", .)) %>% gt_add_divider(columns = c(1, 3, 5, 7, 9, 11, 13, 15, 17, 19, 21, 23, 25, 27, 29), sides = "right", color = "black") %>% tab_caption(caption = "Monthly CERP dead ratios")%>% gt_split(col_slice_at = "SL.S3_DeadRatioSD") %>% grp_options(container.width = 1500)

as.data.frame(t(sapply(Counts_CERP, get_change))) %>% 
  dplyr::select(AnalysisDate, contains("Dead")) %>% gt() %>% 
  sub_values(columns = "AnalysisDate", rows = 1, pattern = "creased", replacement = "--") %>% 
  sub_values(columns = contains("SD"), rows = 1, pattern = "creased", replacement = "--") %>% 
  cols_align(align = c("center"), columns = everything()) %>% 
     cols_label_with(fn = ~gsub("DeadRatioMean","Mean", .)) %>% 
     cols_label_with(fn = ~gsub("DeadRatioSD","SD", .)) %>% 
     gt_add_divider(columns = c(1, 3, 5, 7, 9, 11, 13, 15, 17, 19, 21, 23, 25, 27, 29), sides = "right", color = "black") %>%
  tab_caption(caption = "CERP dead ratio comparisons") %>% 
     gt_split(col_slice_at = "SL.S3_DeadRatioSD") %>% 
     grp_options(container.width = 2000)
```
\
\
\
Shell height range: `r CERP_SH_temp  %>% slice(n()) %>% pull(Value)` - `r CERP_SH_temp  %>% slice(1) %>% pull(Value)`\
Shell height mid-range:`r CERP_SH_temp  %>% slice(n()-1) %>% pull(Value)` - `r CERP_SH_temp  %>% slice(2) %>% pull(Value)`
```{r CERP shell heights}
SH_CERP %>% dplyr::select(AnalysisDate, contains("Mean")) %>% gt() %>% data_color(rows = (AnalysisDate > as.yearmon(Start_date) & AnalysisDate < as.yearmon(End_date %m+% months(1))), columns = contains("Mean"), fn = scales::col_numeric(palette = "plasma", domain = SH_CERP %>% filter(AnalysisDate > as.yearmon(Start_date)) %>% dplyr::select(contains("Mean")) %>% unlist() %>% range(na.rm = T))) %>% cols_align(align = c("center"), columns = everything()) %>% gt_add_divider(columns = c(1, 4, 7, 10, 13), sides = "right", color = "black") %>% tab_caption(caption = "Monthly CERP shell heights")%>% gt_split(col_slice_at = "SL.S3_SHMean") %>% grp_options(container.width = 1500)

as.data.frame(t(sapply(SH_CERP, get_change))) %>% 
  dplyr::select(AnalysisDate, contains("Mean")) %>% gt() %>% 
  sub_values(columns = "AnalysisDate", rows = 1, pattern = "creased", replacement = "--") %>% 
  cols_align(align = c("center"), columns = everything()) %>% 
     gt_add_divider(columns = c(1, 4, 7, 10, 13), sides = "right", color = "black") %>%
  tab_caption(caption = "CERP shell height comparisons") %>% 
     gt_split(col_slice_at = "SL.S3_SHMean") %>% 
     grp_options(container.width = 2000)
```
\
\
\
\
<h3> `r paste("Recruitment summary")` </h3>
`r Rcrt_CERP %>% gather(Station, RateMean, -RetDate) %>% mutate(Station = substr(Station, 1, 5)) %>% filter(is.na(RateMean)) %>% dplyr::select(-RateMean) %>% group_by(Station) %>% gt() %>% tab_caption(caption = "Missing samples")`
`r CERP_rcrt %>% tab_caption(caption = "Monthly CERP recruitment rates")`
Recruitment range: `r CERP_Rcrt_temp %>% slice(n()) %>% pull(Value)` - `r CERP_Rcrt_temp %>% slice(1) %>% pull(Value)` 
Recruitment mid-range: `r CERP_Rcrt_temp %>% slice(n()-1) %>% pull(Value)` - `r CERP_Rcrt_temp %>% slice(2) %>% pull(Value)` 
`r Rcrt_CERP %>% pivot_longer(names_to = "Station", cols = -RetDate) %>% mutate(Station = sub("_Mean", "", Station)) %>% filter(value == 0) %>% arrange(RetDate) %>% gt(groupname_col = "RetDate") %>% tab_caption(caption = "No recruitment")`
\
\
\
\
<h3> `r paste("Repro summary")` </h3>
`r if(!is.null(CERP_repro) & !is.character(CRE_repro)){CERP_repro %>% tab_caption(caption = "Monthly CERP reproductive stages")} else {paste0("Repro data is not available for the quarter specified.")}`
\
\
\
\
<h3> `r paste("Dermo summary")` </h3>
`r Dermo_CERP %>% dplyr::select(RetDate, contains("Mean")) %>% gather(Station, Mean, -RetDate) %>% mutate(Station = substr(Station, 1, 5)) %>% filter(is.na(Mean)) %>% dplyr::select(-Mean) %>% group_by(Station) %>% gt() %>% tab_caption(caption = "Missing samples. *Note: Extra samples may have been collected from a different station.")`
`r CERP_dermo %>% tab_caption(caption = "Monthly CERP dermo intensity and prevalence")`
Intensity range: `r Dermo_CERP %>% dplyr::select(contains("Mean")) %>% unlist() %>% min(na.rm = T)` - `r Dermo_CERP %>% dplyr::select(contains("Mean")) %>% unlist() %>% max(na.rm = T)`\
`r paste("Intensity categories: 0-Uninfected; 0.5-Very light;  1-Light;  2-Light to moderate;  3-Moderate;  4-Moderate heavy,  5-Heavy")`\
Prevalence range: `r Dermo_CERP %>% dplyr::select(contains("Pct")) %>% unlist() %>% min(na.rm = T)` - `r Dermo_CERP %>% dplyr::select(contains("Pct")) %>% unlist() %>% max(na.rm = T)` 
\
\
\
\
<h3> `r paste("Cage summary")` </h3>
`r Cage_CERP %>% gather(Station, SHMean, -RetDate) %>% mutate(Station = substr(Station, 1, 6)) %>% filter(is.na(SHMean)) %>% dplyr::select(-SHMean) %>% group_by(Station) %>% gt() %>% tab_caption(caption = "Missing samples")`\
`r SL_Cage %>% tab_caption(caption = "Monthly St. Lucie cage data")`\
*The SL cages were moved to station 2 in January 2024, Oysters are still collected from station 1.\
Percent Mortality Range: `r Cage_CERP %>% dplyr::select(RetDate, contains("SL")) %>% dplyr::select(contains('Pct')) %>% mutate(across(where(is.numeric), ~ifelse(. < 0 | is.na(.), NA, .))) %>% summarise(min_value = min(across(everything()), na.rm = TRUE)) %>% unlist()` - `r Cage_CERP %>% dplyr::select(RetDate, contains("SL")) %>% dplyr::select(contains('Pct')) %>% mutate(across(where(is.numeric), ~ifelse(. < 0 | is.na(.), NA, .))) %>% summarise(max_value = max(across(everything()), na.rm = TRUE)) %>% unlist()`\
Deployed SH Range: `r Cage_CERP %>% dplyr::select(RetDate, contains("SL")) %>% dplyr::select(contains('Dep')) %>% mutate(across(where(is.numeric), ~ifelse(. < 0 | is.na(.), NA, .))) %>% summarise(min_value = min(across(everything()), na.rm = TRUE)) %>% unlist()` - `r Cage_CERP %>% dplyr::select(RetDate, contains("SL")) %>% dplyr::select(contains('Dep')) %>% mutate(across(where(is.numeric), ~ifelse(. < 0 | is.na(.), NA, .))) %>% summarise(max_value = max(across(everything()), na.rm = TRUE)) %>% unlist()`\
Retrieved SH Range: `r Cage_CERP %>% dplyr::select(contains("SL")) %>% dplyr::select(contains('Ret')) %>% mutate(across(where(is.numeric), ~ifelse(. <= 0 | is.na(.), NA, .))) %>% summarise(min_value = min(across(everything()), na.rm = TRUE)) %>% unlist()` - `r Cage_CERP %>% dplyr::select(contains("SL")) %>% dplyr::select(contains('Ret')) %>% mutate(across(where(is.numeric), ~ifelse(. < 0 | is.na(.), NA, .))) %>% summarise(max_value = max(across(everything()), na.rm = TRUE)) %>% unlist()`\
*Any "NA" retrieved shell height values indicate when a cage was not retrieved due to being missing, flipped, or some other issue.

`r LX_Cage %>% tab_caption(caption = "Monthly Loxahatchee cage data")`

Percent Mortality Range: `r Cage_CERP %>% dplyr::select(RetDate, contains("LX")) %>% dplyr::select(contains('Pct')) %>% mutate(across(where(is.numeric), ~ifelse(. < 0 | is.na(.), NA, .))) %>% summarise(min_value = min(across(everything()), na.rm = TRUE)) %>% unlist()` - `r Cage_CERP %>% dplyr::select(RetDate, contains("LX")) %>% dplyr::select(contains('Pct')) %>% mutate(across(where(is.numeric), ~ifelse(. < 0 | is.na(.), NA, .))) %>% summarise(max_value = max(across(everything()), na.rm = TRUE)) %>% unlist()`\
Deployed SH Range: `r Cage_CERP %>% dplyr::select(RetDate, contains("LX")) %>% dplyr::select(contains('Dep')) %>% mutate(across(where(is.numeric), ~ifelse(. < 0 | is.na(.), NA, .))) %>% summarise(min_value = min(across(everything()), na.rm = TRUE)) %>% unlist()` - `r Cage_CERP %>% dplyr::select(RetDate, contains("LX")) %>% dplyr::select(contains('Dep')) %>% mutate(across(where(is.numeric), ~ifelse(. < 0 | is.na(.), NA, .))) %>% summarise(max_value = max(across(everything()), na.rm = TRUE)) %>% unlist()`\
Retrieved SH Range: `r Cage_CERP %>% dplyr::select(contains("LX")) %>% dplyr::select(contains('Ret')) %>% mutate(across(where(is.numeric), ~ifelse(. < 0 | is.na(.), NA, .))) %>% summarise(min_value = min(across(everything()), na.rm = TRUE)) %>% unlist()` - `r Cage_CERP %>% dplyr::select(contains("LX")) %>% dplyr::select(contains('Ret')) %>% mutate(across(where(is.numeric), ~ifelse(. < 0 | is.na(.), NA, .))) %>% summarise(max_value = max(across(everything()), na.rm = TRUE)) %>% unlist()`\
*Any "NA" retrieved shell height values indicate when a cage was not retrieved due to being missing, flipped, or some other issue.
\
\
\
\
<h3> `r paste("Water Quality summary")` </h3>
`r CERP_Sal %>% tab_caption(caption = "Monthly CERP salinity measurements")`
Salinity range: `r CERP_Sal_temp %>% slice(n()) %>% pull(Value)` - `r CERP_Sal_temp %>% slice(1) %>% pull(Value)`\
Salinity Mid-range: `r CERP_Sal_temp %>% slice(n()-1) %>% pull(Value)` - `r CERP_Sal_temp %>% slice(2) %>% pull(Value)`\
`r CERP_Sec %>% tab_caption(caption = "Monthly CERP secchi measurements")`
Secchi range: `r WQ_Sec_CERP %>% dplyr::select(contains("SP")) %>% unlist() %>% min()` - `r WQ_Sec_CERP %>% dplyr::select(contains("SP")) %>% unlist() %>% max()`\
\
\
\
\
\
<h2>`r paste("West Coast")`</h2>
Minimum and maximum values observed during the quarter and data ordered by increasing values.
<h3> `r paste("Survey summary")` </h3>
`r CRE_count %>% tab_caption(caption = "Monthly CRE live oyster counts")`
Live Counts range: `r CRE_Counts_temp  %>% slice(n()) %>% pull(Value)` - `r CRE_Counts_temp  %>% slice(1) %>% pull(Value)`\
Live Counts Mid-range: `r {if (nrow(CRE_Counts_temp) > 2) slice(., n() - 1) %>% pull(Value) else paste("")}` - `r {if (nrow(CRE_Counts_temp) > 2) slice(2)%>% pull(Value) else paste("")} `
`r CRE_count_change`
\
\
\
\
`r CRE_dead %>% tab_caption(caption = "Monthly CRE dead ratios")`
DeadRatio range: `r CRE_DR_temp  %>% slice(n()) %>% pull(Value)` - `r CRE_DR_temp  %>% slice(1) %>% pull(Value)`\
DeadRatio Mid-range: `r {if (nrow(CRE_DR_temp) > 2) slice(n()-1) %>% pull(Value) else paste("")}` - `r {if (nrow(CRE_DR_temp) > 2)  slice(2) %>% pull(Value) else paste("")} ` 
`r CRE_dead_change`
\
\
\
\
`r CRE_SH %>% tab_caption(caption = "Monthly CRE shell heights")`
Shell height range: `r CRE_SH_temp  %>% slice(n()) %>% pull(Value)` - `r CRE_SH_temp  %>% slice(1) %>% pull(Value)` \
Shell height mid-range: `r {if (nrow(CRE_SH_temp) > 2) slice(n()-1)  %>% pull(Value)else paste("")}` - `r {if (nrow(CRE_SH_temp) > 2) slice(2) %>% pull(Value) else paste("")}` 
\
\
\
\
<h3> `r paste("Recruitment summary")` </h3>
`r Rcrt_CRE %>% gather(Station, RateMean, -RetDate) %>% mutate(Station = substr(Station, 1, 5)) %>% filter(is.na(RateMean)) %>% dplyr::select(-RateMean) %>% group_by(Station) %>% gt() %>% tab_caption(caption = "Missing samples")`
`r CRE_rcrt %>% tab_caption(caption = "Monthly CRE recruitment rates")`
Recruitment range: `r CRE_Rcrt_temp  %>% slice(n()) %>% pull(Value)` - `r CRE_Rcrt_temp  %>% slice(1) %>% pull(Value)` \
Recruitment mid-range: `r CRE_Rcrt_temp  %>% slice(n()-1) %>% pull(Value)` - `r CRE_Rcrt_temp  %>% slice(2) %>% pull(Value)`
`r Rcrt_CRE %>% pivot_longer(names_to = "Station", cols = -RetDate) %>% mutate(Station = sub("_Mean", "", Station)) %>% filter(value == 0) %>% arrange(RetDate) %>% gt(groupname_col = "RetDate") %>% tab_caption(caption = "No recruitment")`
\
\
\
\
<h3> `r paste("Repro summary")` </h3>
`r if(!is.null(CRE_repro) & !is.character(CRE_repro)){CRE_repro %>% tab_caption(caption = "Monthly CRE reproductive stages")} else {paste0("Repro data is not available for the quarter specified.")}`
\
\
\
\
<h3> `r paste("Dermo summary")` </h3>
`r Dermo_CRE %>% dplyr::select(RetDate, contains("Mean")) %>% gather(Station, Mean, -RetDate) %>% mutate(Station = substr(Station, 1, 5)) %>% filter(is.na(Mean)) %>% dplyr::select(-Mean) %>% group_by(Station) %>% gt() %>% tab_caption(caption = "Missing samples")`
`r CRE_dermo %>% tab_caption(caption = "Monthly CRE dermo intensity and prevalence")`
Intensity range: `r Dermo_CRE %>% dplyr::select(contains("Mean")) %>% unlist() %>% min(na.rm = T)` - `r Dermo_CRE %>% dplyr::select(contains("Mean")) %>% unlist() %>% max(na.rm = T)`\
`r paste("Intensity categories: 0-Uninfected; 0.5-Very light;  1-Light;  2-Light to moderate;  3-Moderate;  4-Moderate heavy,  5-Heavy")`\
Prevalence range: `r Dermo_CRE %>% dplyr::select(contains("Pct")) %>% unlist() %>% min(na.rm = T)` - `r Dermo_CRE %>% dplyr::select(contains("Pct")) %>% unlist() %>% max(na.rm = T)`
\
\
\
\
<h3> `r paste("Cage summary")` </h3>
`r Cage_CRE %>% gather(Station, SHMean, -RetDate) %>% mutate(Station = substr(Station, 1, 6)) %>% filter(is.na(SHMean)) %>% dplyr::select(-SHMean) %>% group_by(Station) %>% gt() %>% tab_caption(caption = "Missing samples")`
`r CRE_Cage %>% tab_caption(caption = "Monthly CRE-East cage data")`

Deployed SH Range: `r Cage_CRE %>% dplyr::select(RetDate, contains("CR.E")) %>% dplyr::select(contains('Dep')) %>% mutate(across(where(is.numeric), ~ifelse(. <= 0 | is.na(.), NA, .))) %>% summarise(min_value = min(across(everything()), na.rm = TRUE)) %>% unlist()` - `r Cage_CRE %>% dplyr::select(RetDate, contains("CR.E")) %>% dplyr::select(contains('Dep')) %>% mutate(across(where(is.numeric), ~ifelse(. <= 0 | is.na(.), NA, .))) %>% summarise(max_value = max(across(everything()), na.rm = TRUE)) %>% unlist()`\
Retrieved SH Range: `r Cage_CRE %>% dplyr::select(contains("CR.E")) %>% dplyr::select(contains('Ret')) %>% mutate(across(where(is.numeric), ~ifelse(. <= 0 | is.na(.), NA, .))) %>% summarise(min_value = min(across(everything()), na.rm = TRUE)) %>% unlist()` - `r Cage_CRE %>% dplyr::select(contains("CR.E")) %>% dplyr::select(contains('Ret')) %>% mutate(across(where(is.numeric), ~ifelse(. <= 0 | is.na(.), NA, .))) %>% summarise(max_value = max(across(everything()), na.rm = TRUE)) %>% unlist()`\
Percent Mortality Range: `r Cage_CRE %>% dplyr::select(RetDate, contains("CR.E")) %>% dplyr::select(contains('Pct')) %>% mutate(across(where(is.numeric), ~ifelse(. <= 0 | is.na(.), NA, .))) %>% summarise(min_value = min(across(everything()), na.rm = TRUE)) %>% unlist()` - `r Cage_CRE %>% dplyr::select(RetDate, contains("CR.E")) %>% dplyr::select(contains('Pct')) %>% mutate(across(where(is.numeric), ~ifelse(. <= 0 | is.na(.), NA, .))) %>% summarise(max_value = max(across(everything()), na.rm = TRUE)) %>% unlist()`

`r CRW_Cage %>% tab_caption(caption = "Monthly CR-West cage data")`
*The CRW cages were moved to station 4 in January 2026. Oysters are still collected from station 3.\
Percent Mortality Range: `r Cage_CRE %>% dplyr::select(RetDate, contains("CR.W")) %>% dplyr::select(contains('Pct')) %>% mutate(across(where(is.numeric), ~ifelse(. <= 0 | is.na(.), NA, .))) %>% summarise(min_value = min(across(everything()), na.rm = TRUE)) %>% unlist()` - `r Cage_CRE %>% dplyr::select(RetDate, contains("CR.W")) %>% dplyr::select(contains('Pct')) %>% mutate(across(where(is.numeric), ~ifelse(. <= 0 | is.na(.), NA, .))) %>% summarise(max_value = max(across(everything()), na.rm = TRUE)) %>% unlist()`\
Deployed SH Range: `r Cage_CRE %>% dplyr::select(RetDate, contains("CR.W")) %>% dplyr::select(contains('Dep')) %>% mutate(across(where(is.numeric), ~ifelse(. <= 0 | is.na(.), NA, .))) %>% summarise(min_value = min(across(everything()), na.rm = TRUE)) %>% unlist()` - `r Cage_CRE %>% dplyr::select(RetDate, contains("CR.W")) %>% dplyr::select(contains('Dep')) %>% mutate(across(where(is.numeric), ~ifelse(. <= 0 | is.na(.), NA, .))) %>% summarise(max_value = max(across(everything()), na.rm = TRUE)) %>% unlist()`\
Retrieved SH Range: `r Cage_CRE %>% dplyr::select(contains("CR.W")) %>% dplyr::select(contains('Ret')) %>% mutate(across(where(is.numeric), ~ifelse(. <= 0 | is.na(.), NA, .))) %>% summarise(min_value = min(across(everything()), na.rm = TRUE)) %>% unlist()` - `r Cage_CRE %>% dplyr::select(contains("CR.W")) %>% dplyr::select(contains('Ret')) %>% mutate(across(where(is.numeric), ~ifelse(. <= 0 | is.na(.), NA, .))) %>% summarise(max_value = max(across(everything()), na.rm = TRUE)) %>% unlist()`
*Any "NA" retrieved shell height values indicate when a cage was not retrieved due to being missing, flipped, or some other issue.
\
\
\
\
<h3> `r paste("Water Quality summary")` </h3>
`r CRE_Sal %>% tab_caption(caption = "Monthly CRE salinity measurements")`
Salinity range: `r CRE_Sal_temp %>% slice(n()) %>% pull(Value)` - `r CRE_Sal_temp %>% slice(1) %>% pull(Value)`\
Salinity Mid-range: `r CRE_Sal_temp %>% slice(n()-1) %>% pull(Value)` - `r CRE_Sal_temp %>% slice(2) %>% pull(Value)`\
`r CRE_Sec %>% tab_caption(caption = "Monthly CRE secchi measurements")`
Secchi range: `r WQ_Sec_CRE %>% dplyr::select(contains("SP")) %>% unlist() %>% min(na.rm = T)` - `r WQ_Sec_CRE %>% dplyr::select(contains("SP")) %>% unlist() %>% max(na.rm = T)`\
\