---
title: "Quarterly Report Information"
author: "ELevine"
date: "`r Sys.Date()`"
output: 
  html_document:
  word_document: NULL
params:
  Start_date: "2025-10-01"
  End_date: "2025-12-30"
---
<style>
.main-container {
    max-width: 9000px;
    margin-left: 20px;
    margin-right: auto;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
#
Start_date <- as.Date(params$Start_date)
End_date <- as.Date(params$End_date)

#Packages
if (!require("pacman")) {install.packages("pacman")}
#p_unlock()
pacman::p_load(odbc, DBI, dbplyr,
  tidyverse, dplyr,  stringr, #DF manipulation
  DT, openxlsx,         #Excel
  lubridate, zoo,         #Dates
  knitr, kableExtra, scales, gt, gtExtras,
  install = TRUE)
#
#
# Function to determine increase/decrease
get_change <- function(col) {
  first <- col[1]
  last <- col[length(col)]
  if (last > first) {
    return("increased")
  } else if (last < first) {
    return("decreased")
  } else {
    return("no change")
  }
}
#
#
```

```{css}
p {
font-size: 12pt;
}

caption {
  color: black;
  font-weight: bold;
  font-size: 14;
  text-indent: 5%;
} 

h1 {
font-size: 21pt;
font-weight: bold;
}

h2 {
font-size: 17pt;
font-weight: bold;
}

h3 {
font-size: 13pt;
font-style: italic;
text-decoration: underline;
}

h4 {
  color: black;
  font-weight: bold;
  font-size: 17;
  text-indent: 5%;
}
```

```{r Data gather from summary file}
WQ_Sal_s <-  readWorkbook("../Summary data/CERP_PBC_WQ_Summary_Data.xlsx", sheet = 'Salinity Station', detectDates = TRUE, check.names = TRUE)
WQ_Secchi_s <-  readWorkbook("../Summary data/CERP_PBC_WQ_Summary_Data.xlsx", sheet = 'Secchi Station', detectDates = TRUE, check.names = TRUE)
Dermo_df <- readWorkbook("../Summary data/CERP_PBC_Summary_Data.xlsx", sheet = 'Dermo Station', detectDates = TRUE, check.names = TRUE)
Rcrt_df <- readWorkbook("../Summary data/CERP_PBC_Summary_Data.xlsx", sheet = 'Rcrt Station', detectDates = TRUE, check.names = TRUE)
Repro_df <- readWorkbook("../Summary data/CERP_PBC_Summary_Data.xlsx", sheet = 'Repro', detectDates = TRUE, check.names = TRUE)
Counts_df <- readWorkbook("../Summary data/CERP_PBC_Summary_Data.xlsx", sheet = 'DeadRatio Station', detectDates = TRUE, check.names = TRUE)
SH_df <- readWorkbook("../Summary data/CERP_PBC_Summary_Data.xlsx", sheet = 'SH Station', detectDates = TRUE, check.names = TRUE)
Sedi_sta <- readWorkbook("../Summary data/CERP_PBC_Summary_Data.xlsx", sheet = 'Sedi Stations', detectDates = TRUE, check.names = TRUE)
Sedi_pos <- readWorkbook("../Summary data/CERP_PBC_Summary_Data.xlsx", sheet = 'Sedi Position', detectDates = TRUE, check.names = TRUE)
```

```{r Data selection and cleaning}
#
##Salinity
WQ_Sal_PBC <- WQ_Sal_s %>% dplyr::select(starts_with("LW")) %>% subset(LW.L_RetDate_Sal > Start_date & LW.L_RetDate_Sal < End_date) %>% rename(RetDate = LW.L_RetDate_Sal) %>% dplyr::select(-LW.R_RetDate_Sal)
#
#Secchi
WQ_Sec_PBC <- WQ_Secchi_s %>% dplyr::select(starts_with("LW")) %>% subset(LW.L_RetDate_SP > Start_date & LW.L_RetDate_SP < End_date) %>% rename(RetDate = LW.L_RetDate_SP) %>% dplyr::select(-LW.R_RetDate_SP)
#
#Dermo
Dermo_PBC <- Dermo_df %>% dplyr::select(starts_with("LW")) %>% dplyr::select(!contains("SD")) %>% subset(LW.L_RetDate > Start_date & LW.L_RetDate < End_date) %>% rename(RetDate = LW.L_RetDate) %>% dplyr::select(-LW.R_RetDate) %>% mutate(RetDate = as.yearmon(RetDate))
#
#Rcrt
Rcrt_PBC <- Rcrt_df %>% dplyr::select(starts_with("LW")) %>% dplyr::select(!contains("SD")) %>% subset(LW.L_RetDate > Start_date & LW.L_RetDate < End_date) %>% rename(RetDate = LW.L_RetDate) %>% dplyr::select(-LW.R_RetDate) %>% mutate(RetDate = as.yearmon(RetDate))
#
#Repro
Repro_PBC <- Repro_df %>% dplyr::select(starts_with("LW")) %>% subset(LW.L_RetDate > Start_date & LW.L_RetDate < End_date) %>% rename(RetDate = LW.L_RetDate) %>% dplyr::select(-LW.R_RetDate) %>% mutate(RetDate = as.yearmon(RetDate))
#
##Survey counts
Counts_PBC <- Counts_df %>% dplyr::select(AnalysisDate, starts_with("LW")) %>%  mutate(AnalysisDate = as.yearmon(AnalysisDate)) %>% subset(AnalysisDate > (as.yearmon(End_date %m-% months(7))) & AnalysisDate < as.yearmon(End_date %m+% months(1))) %>% replace(is.na(.), -999)
Counts_PBC_change <- as.data.frame(t(sapply(Counts_PBC, get_change))) 
#
##Survey SHs
SH_PBC <- SH_df %>% dplyr::select(AnalysisDate, starts_with("LW")) %>%  mutate(AnalysisDate = as.yearmon(AnalysisDate)) %>% subset(AnalysisDate > (as.yearmon(End_date %m-% months(7))) & AnalysisDate < as.yearmon(End_date %m+% months(1))) %>% replace(is.na(.), -999)
#
##Sediment
Rate_sta <- Sedi_sta %>% dplyr::select(AnalysisDate, contains("RateMean")) %>% subset(AnalysisDate >= Start_date & AnalysisDate < End_date) %>%
  mutate(LW.R2_RateMean = case_when(AnalysisDate == as.Date("2025-09-01") ~ 37.47, TRUE ~ LW.R2_RateMean),
         LW.R3_RateMean = case_when(AnalysisDate == as.Date("2025-09-01") ~ 19.93, TRUE ~ LW.R3_RateMean),
         LW.R4_RateMean = case_when(AnalysisDate == as.Date("2025-09-01") ~ 6.82, TRUE ~ LW.R4_RateMean))
Rate_annual <- Sedi_sta  %>% dplyr::select(AnalysisDate, contains("RateMean")) %>% subset(AnalysisDate > (End_date %m-% months(12)) & AnalysisDate < End_date)
Pct_sta <- Sedi_sta %>% dplyr::select(AnalysisDate, contains("OrganicMean")) %>% subset(AnalysisDate >= Start_date & AnalysisDate < End_date)
Pct_annual <- Sedi_sta %>% dplyr::select(AnalysisDate, contains("OrganicMean")) %>% subset(AnalysisDate >= (End_date %m-% months(12)) & AnalysisDate < End_date)
Wt_sta <- Sedi_sta %>% dplyr::select(AnalysisDate, contains("WtMean")) %>% subset(AnalysisDate >= Start_date & AnalysisDate < End_date)
Wt_annual <- Sedi_sta %>% dplyr::select(AnalysisDate, contains("WtMean")) %>% subset(AnalysisDate >= (End_date %m-% months(12)) & AnalysisDate < End_date)

Reef_type_summ <- Sedi_sta %>% subset(AnalysisDate >= Start_date & AnalysisDate < End_date) %>% dplyr::select(-contains("Ret"), -AnalysisDate) %>% gather("Info", Value) %>% mutate(Station = substr(Info, 1, 5), Measure = str_extract(Info, "(?<=_).*")) %>% dplyr::select(-Info) %>% filter(!grepl("SD", Measure)) %>% mutate(ReefType = case_when(grepl("LW.L", Station) ~ "Natural", grepl("LW.R", Station) ~ "Restoration"), Position = case_when(grepl(c("R4|L1|L2"), Station) ~ "North", grepl(c("R2|R3|L3"), Station) ~ "South"))
Reef_type_annual <- Sedi_sta %>% subset(AnalysisDate >= (End_date %m-% months(12)) & AnalysisDate < End_date) %>% dplyr::select(-contains("Ret"), -AnalysisDate) %>% gather("Info", Value) %>% mutate(Station = substr(Info, 1, 5), Measure = str_extract(Info, "(?<=_).*")) %>% dplyr::select(-Info) %>% filter(!grepl("SD", Measure)) %>% mutate(ReefType = case_when(grepl("LW.L", Station) ~ "Natural", grepl("LW.R", Station) ~ "Restoration"), Position = case_when(grepl(c("R4|L1|L2"), Station) ~ "North", grepl(c("R2|R3|L3"), Station) ~ "South"))

```

```{r table formatting, results = "asis"}
#Salinity
PBC_Sal <- WQ_Sal_PBC %>% gt() %>% data_color(columns = contains("Sal"), fn = scales::col_numeric(palette = "plasma", domain = WQ_Sal_PBC %>% dplyr::select(contains("Sal")) %>% unlist() %>% range(na.rm = T))) %>% gt_add_divider(columns = c(1, 4), sides = "right", color = "black") %>% cols_label_with(fn = ~gsub("_Sal","", .)) %>% cols_align(align = c("center"), columns = everything())
#
#
##Secchi
PBC_Sec <- WQ_Sec_PBC %>% gt() %>% data_color(columns = contains("SP"), fn = scales::col_numeric(palette = "plasma", domain = WQ_Sec_PBC %>% dplyr::select(contains("SP")) %>% unlist() %>% range(na.rm = T))) %>% gt_add_divider(columns = c(1, 4), sides = "right", color = "black") %>% cols_label_with(fn = ~gsub("_SP","", .)) %>% cols_align(align = c("center"), columns = everything())
#
#
##Dermo
PBC_dermo <- Dermo_PBC %>% gt() %>% data_color(columns = contains("Pct"), fn = scales::col_numeric(palette = "plasma", domain = Dermo_PBC %>% dplyr::select(contains("Pct")) %>% unlist() %>% range(na.rm = T))) %>% cols_label_with(fn = ~gsub("_Mean","", .)) %>% cols_label_with(fn = ~gsub("_Pct","", .)) %>% gt_add_divider(columns = c(1, 3, 5, 7), sides = "right", color = "black") %>% cols_align(align = c("center"), columns = everything())
#
#
##Rcrt
PBC_rcrt <- Rcrt_PBC %>% gt() %>% data_color(columns = contains("Mean"), fn = scales::col_numeric(palette = "plasma", domain = Rcrt_PBC %>% dplyr::select(contains("Mean")) %>% unlist() %>% range(na.rm = T))) %>% gt_add_divider(columns = c(1, 4), sides = "right", color = "black") %>% cols_align(align = c("center"), columns = everything())
#
#
##Repro
if(nrow(Repro_PBC) > 0){
  PBC_repro <- Repro_PBC %>% gather(Site, Pct, -RetDate) %>% mutate(Station = substr(Site, 1, 4), Stage = substr(Site, 6, 8)) %>% dplyr::select(-Site) %>% spread(Stage, Pct) %>% arrange(Station, RetDate) %>% gt(rowname_col = "RetDate", groupname_col = "Station") %>% cols_move(Dev, Ind) %>% data_color(direction = "row", method = "numeric", palette = c("plasma"), alpha = 0.8) %>% cols_align(align = c("center"), columns = everything()) %>% tab_options(row_group.border.top.color = "black", row_group.border.bottom.color = "black", row_group.font.weight = "bold")
} else {
  PBC_repro <- "Data unavailable."
}
#
#
##Counts 
PBC_count <- Counts_PBC %>% dplyr::select(AnalysisDate, contains("Live")) %>% gt() %>% data_color(rows = (AnalysisDate > as.yearmon(Start_date) & AnalysisDate < as.yearmon(End_date %m+% months(1))), columns = contains("Mean"), fn = scales::col_numeric(palette = "plasma", domain = Counts_PBC %>% filter(AnalysisDate > as.yearmon(Start_date)) %>% dplyr::select(contains("Mean")) %>% unlist() %>% range(na.rm = T))) %>% cols_align(align = c("center"), columns = everything()) %>% cols_label_with(fn = ~gsub("LiveMean","Mean", .)) %>% cols_label_with(fn = ~gsub("LiveSD","SD", .)) %>% gt_add_divider(columns = c(1, 3, 5, 7, 9, 11, 13), sides = "right", color = "black") %>% tab_options(container.width = 1500)

PBC_count_change <- as.data.frame(t(sapply(Counts_PBC, get_change))) %>% 
  dplyr::select(AnalysisDate, contains("Live")) %>% gt() %>% 
  sub_values(columns = "AnalysisDate", rows = 1, pattern = "creased", replacement = "--") %>% 
  sub_values(columns = contains("SD"), rows = 1, pattern = "creased", replacement = "--") %>% 
  cols_align(align = c("center"), columns = everything()) %>% 
     cols_label_with(fn = ~gsub("LiveMean","Mean", .)) %>% 
     cols_label_with(fn = ~gsub("LiveSD","SD", .)) %>% 
     gt_add_divider(columns = c(1, 3, 5, 7, 9, 11, 13), sides = "right", color = "black") 
#
#
##Dead Ratios -   (see Counts comment)
PBC_dead <- Counts_PBC %>% dplyr::select(AnalysisDate, contains("Dead")) %>% gt() %>% data_color(rows = (AnalysisDate > as.yearmon(Start_date) & AnalysisDate < as.yearmon(End_date %m+% months(1))), columns = contains("Mean"), fn = scales::col_numeric(palette = "plasma", domain = Counts_PBC %>% filter(AnalysisDate > as.yearmon(Start_date)) %>% dplyr::select(contains("Mean")) %>% unlist() %>% range(na.rm = T))) %>% cols_align(align = c("center"), columns = everything()) %>% cols_label_with(fn = ~gsub("DeadRatioMean","Mean", .)) %>% cols_label_with(fn = ~gsub("DeadRatioSD","SD", .)) %>% gt_add_divider(columns = c(1, 3, 5, 7, 9, 11, 13), sides = "right", color = "black") %>% tab_options(container.width = 1500)

PBC_dead_change <- as.data.frame(t(sapply(Counts_PBC, get_change))) %>% 
  dplyr::select(AnalysisDate, contains("Dead")) %>% gt() %>% 
  sub_values(columns = "AnalysisDate", rows = 1, pattern = "creased", replacement = "--") %>% 
  sub_values(columns = contains("SD"), rows = 1, pattern = "creased", replacement = "--") %>% 
  cols_align(align = c("center"), columns = everything()) %>% 
     cols_label_with(fn = ~gsub("DeadMean","Mean", .)) %>% 
     cols_label_with(fn = ~gsub("DeadSD","SD", .)) %>% 
     gt_add_divider(columns = c(1, 3, 5, 7, 9, 11, 13), sides = "right", color = "black") 
#
#
##SHs
PBC_SH <- SH_PBC %>% dplyr::select(AnalysisDate, contains("Mean")) %>% gt() %>% data_color(rows = (AnalysisDate > as.yearmon(Start_date) & AnalysisDate < as.yearmon(End_date %m+% months(1))), columns = contains("Mean"), fn = scales::col_numeric(palette = "plasma", domain = SH_PBC %>% filter(AnalysisDate > as.yearmon(Start_date)) %>% dplyr::select(contains("Mean")) %>% unlist() %>% range(na.rm = T))) %>% cols_align(align = c("center"), columns = everything()) %>% gt_add_divider(columns = c(1, 4), sides = "right", color = "black") %>% tab_options(container.width = 1500)
#
#Survey summary table - PBC
PBC_survey_sum <- left_join(rbind(
  Counts_PBC %>% filter(as.yearmon(AnalysisDate) >= as.yearmon(End_date %m-% months(1))) %>% 
    gather(Info, Value, -AnalysisDate) %>% 
    mutate(Value = na_if(Value, -999), Station = str_remove(str_extract(Info, "^.{5}"), "\\."), Measure = substr(Info, 7, n())) %>% 
    group_by(Station, Measure) %>% 
    summarise(mean = round(mean(Value, na.rm = T), 2)) %>% 
    spread(Measure, mean), 
  Counts_PBC %>% filter(as.yearmon(AnalysisDate) >= as.yearmon(End_date %m-% months(1))) %>% 
    gather(Info, Value, -AnalysisDate) %>% 
    mutate(Value = na_if(Value, -999), Station = paste0(str_remove(str_extract(Info, "^.{4}"), "\\."),"_mean"), Measure = substr(Info, 7, n())) %>% 
    group_by(Station, Measure) %>% 
    summarise(mean = round(mean(Value, na.rm = T), 2)) %>% 
    spread(Measure, mean)) %>% 
    arrange(Station) %>% ungroup() %>% dplyr::select(Station, "Live density (oysters/m2)" = LiveMean, "Dead Ratio" = DeadRatioMean), 
      rbind(SH_PBC %>% filter(as.yearmon(AnalysisDate) >= as.yearmon(End_date %m-% months(1))) %>% 
              gather(Info, Value, -AnalysisDate) %>% 
              mutate(Value = na_if(Value, -999), Station = str_remove(str_extract(Info, "^.{5}"), "\\."), Measure = substr(Info, 7, n())) %>% 
              group_by(Station, Measure) %>% 
              summarise(mean = round(mean(Value, na.rm = T), 2)) %>% spread(Measure, mean), 
            SH_PBC %>% filter(as.yearmon(AnalysisDate) >= as.yearmon(End_date %m-% months(1))) %>% 
              gather(Info, Value, -AnalysisDate) %>% mutate(Value = na_if(Value, -999), Station = paste0(str_remove(str_extract(Info, "^.{4}"), "\\."), "_mean"), Measure = substr(Info, 7, n())) %>%
              group_by(Station, Measure) %>% 
              summarise(mean = round(mean(Value, na.rm = T), 2)) %>% 
              spread(Measure, mean)) %>% 
    arrange(Station) %>% 
    ungroup() %>% 
    dplyr::select(Station, "Shell height (mm)" = SHMean)) %>% gt() %>% tab_style(style = cell_text(weight = "bold"), locations = cells_body(rows = c(4, 8))) %>% cols_align(align = c("center"), columns = everything()) %>%  gt_add_divider(columns = c(1, 2, 3), sides = "right", color = "black") %>% tab_style(style = cell_borders(sides = "top", color = "black"), locations = cells_body(rows = c(1, 5)))
#
#
#
##Sediment
Sta_Rates <- Rate_sta %>% replace(is.na(.), -25) %>% gt() %>% data_color(columns = contains("Rate"), fn = scales::col_numeric(palette = "plasma", domain = Rate_sta %>% replace(is.na(.), -25) %>% dplyr::select(contains("Rate")) %>% unlist() %>% range(na.rm = T))) %>% cols_label_with(fn = ~gsub("_Rate","", .)) %>% cols_align(align = c("center"), columns = everything()) %>%  gt_add_divider(columns = c(1, 4), sides = "right", color = "black")
#
Sta_Pcts <- Pct_sta %>% replace(is.na(.), -12) %>% gt() %>% data_color(columns = contains("Organic"), fn = scales::col_numeric(palette = "plasma", domain = Pct_sta %>% replace(is.na(.), -12) %>% dplyr::select(contains("Organic")) %>% unlist() %>% range(na.rm = T))) %>% cols_label_with(fn = ~gsub("_PctOrganic","", .)) %>% cols_align(align = c("center"), columns = everything()) %>%  gt_add_divider(columns = c(1, 4), sides = "right", color = "black")
#
Sta_Wts <- Wt_sta %>% replace(is.na(.), -1) %>% gt() %>% data_color(columns = contains("OrgWt"), fn = scales::col_numeric(palette = "plasma", domain = Wt_sta %>% replace(is.na(.), -1) %>% dplyr::select(contains("OrgWt")) %>% unlist() %>% range(na.rm = T))) %>% cols_label_with(fn = ~gsub("_OrgWt","", .)) %>% cols_align(align = c("center"), columns = everything()) %>%  gt_add_divider(columns = c(1, 4), sides = "right", color = "black")

Pos_Rates <- Sedi_pos %>% subset(AnalysisDate >= Start_date & AnalysisDate < End_date) %>% replace(is.na(.), -0.5) %>% dplyr::select(AnalysisDate, contains("RateMean")) %>% gt() %>% data_color(columns = contains("RateMean"), fn = scales::col_numeric(palette = "plasma", domain = Sedi_pos %>% subset(AnalysisDate >= Start_date & AnalysisDate < End_date) %>% replace(is.na(.), -0.5) %>% dplyr::select(contains("Rate")) %>% unlist() %>% range(na.rm = T))) %>% cols_align(align = c("center"), columns = everything()) %>%  gt_add_divider(columns = c(1, 3), sides = "right", color = "black")

Pos_Pcts <- Sedi_pos %>% subset(AnalysisDate >= Start_date & AnalysisDate < End_date) %>% replace(is.na(.), -0.5) %>% dplyr::select(AnalysisDate, contains("OrganicMean")) %>% gt() %>% data_color(columns = contains("OrganicMean"), fn = scales::col_numeric(palette = "plasma", domain = Sedi_pos %>% replace(is.na(.), -0.5) %>% dplyr::select(contains("OrganicMean")) %>% unlist() %>% range(na.rm = T))) %>% cols_align(align = c("center"), columns = everything()) %>%  gt_add_divider(columns = c(1, 3), sides = "right", color = "black")

Pos_Wts <- Sedi_pos %>% subset(AnalysisDate >= Start_date & AnalysisDate < End_date) %>% replace(is.na(.), -0.1) %>% dplyr::select(AnalysisDate, contains("OrgWtMean")) %>% gt() %>% data_color(columns = contains("OrgWtMean"), fn = scales::col_numeric(palette = "plasma", domain = Sedi_pos %>% replace(is.na(.), -0.1) %>% dplyr::select(contains("OrgWtMean")) %>% unlist() %>% range(na.rm = T))) %>% cols_align(align = c("center"), columns = everything()) %>%  gt_add_divider(columns = c(1, 3), sides = "right", color = "black")
#
#Summary tables 
LWL_sum_tab <- rbind(
  #Quarterly means by station
  left_join(Reef_type_summ %>% mutate(Station = str_remove(Station, "\\.")) %>% filter(grepl("LWL", Station)) %>% group_by(Station, Measure) %>% mutate(Measure = paste0("Quarterly_", Measure)) %>% summarise(meanValue = round(mean(Value, na.rm = T),2)) %>% spread(Measure, meanValue) %>% dplyr::select(Station, contains("RateMean"), contains("PctOrganicMean"), contains("OrgWtMean")),
            #Annual means by station
            Reef_type_annual %>% mutate(Station = str_remove(Station, "\\.")) %>% filter(grepl("LWL", Station)) %>% group_by(Station, Measure) %>% mutate(Measure = paste0("Annual_", Measure)) %>% summarise(meanValue = round(mean(Value, na.rm = T),2)) %>% spread(Measure, meanValue) %>% dplyr::select(Station, contains("RateMean"), contains("PctOrganicMean"), contains("OrgWtMean"))), 
  #Quarterly means
  left_join(Reef_type_summ %>% mutate(Station = str_remove(Station, "\\.")) %>% filter(grepl("LWL", Station)) %>% group_by(Measure) %>% mutate(Measure = paste0("Quarterly_", Measure)) %>% summarise(meanValue = round(mean(Value, na.rm = T),2)) %>% spread(Measure, meanValue) %>% mutate(Station = "Mean"),
            #Annual means
            Reef_type_annual %>% mutate(Station = str_remove(Station, "\\.")) %>% filter(grepl("LWL", Station)) %>% group_by(Measure) %>% mutate(Measure = paste0("Annual_", Measure)) %>% summarise(meanValue = round(mean(Value, na.rm = T),2)) %>% spread(Measure, meanValue) %>% mutate(Station = "Mean"))) %>% 
  rename("Sedimentation Rate (g/month)" = Quarterly_RateMean, "Sedimentation Rate (g/month) " = Annual_RateMean, "% Organic" = Quarterly_PctOrganicMean, "% Organic " = Annual_PctOrganicMean, "Organic Weight (g)" = Quarterly_OrgWtMean, "Organic Weight (g) " = Annual_OrgWtMean) %>% ungroup() %>% gt() %>% tab_spanner(label = "Quarterly", columns = c(2, 3, 4)) %>% tab_spanner(label = "Annual", columns = c(5, 6, 7)) %>%  tab_style(style = cell_text(weight = "bold"), locations = cells_body(rows = c(4))) %>% tab_style(style = cell_borders(sides = c("bottom"), style = "hidden"), locations = cells_body(rows = c(1, 2, 4))) %>% tab_options(heading.title.font.size = "12px", heading.border.bottom.style = "solid", heading.border.bottom.color = "black", table.border.top.style = "hidden", table.font.names = c("Times New Roman"), table.font.size = "12px") %>% cols_align(align = "center") %>% tab_header(title = "Natural reefs") %>% opt_align_table_header(align = "left") %>% gt_add_divider(columns = c(1, 2, 3, 4, 5, 6), sides = "right", color = "black") %>% tab_style(style = cell_borders(sides = "top", color = "black"), locations = cells_body(rows = c(1, 4))) %>% tab_style(style = cell_borders(sides = "left", color = "black", weight = px(2.5)), locations = cells_body(columns = c(2, 5))) %>% tab_style(style = cell_borders(sides = "left", color = "black", weight = px(2.5)), locations = cells_column_spanners(spanners = c("Quarterly", "Annual"))) %>% tab_style(style = cell_borders(sides = "left", color = "black", weight = px(2.5)), locations = cells_column_labels(columns = c(2, 5)))
#
LWR_sum_tab <- rbind(
  #Quarterly means by station
  left_join(Reef_type_summ %>% mutate(Station = str_remove(Station, "\\.")) %>% filter(grepl("LWR", Station)) %>% group_by(Station, Measure) %>% mutate(Measure = paste0("Quarterly_", Measure)) %>% summarise(meanValue = round(mean(Value, na.rm = T),2)) %>% spread(Measure, meanValue) %>% dplyr::select(Station, contains("RateMean"), contains("PctOrganicMean"), contains("OrgWtMean")), 
            #Annual means by station
            Reef_type_annual %>% mutate(Station = str_remove(Station, "\\.")) %>% filter(grepl("LWR", Station)) %>% group_by(Station, Measure) %>% mutate(Measure = paste0("Annual_", Measure)) %>% summarise(meanValue = round(mean(Value, na.rm = T),2)) %>% spread(Measure, meanValue) %>% dplyr::select(Station, contains("RateMean"), contains("PctOrganicMean"), contains("OrgWtMean"))), 
  #Quarterly means
  left_join(Reef_type_summ %>% mutate(Station = str_remove(Station, "\\.")) %>% filter(grepl("LWR", Station)) %>% group_by(Measure) %>% mutate(Measure = paste0("Quarterly_", Measure))  %>% summarise(meanValue = round(mean(Value, na.rm = T),2)) %>% spread(Measure, meanValue) %>% mutate(Station = "Mean"),
  #Annual means
  Reef_type_annual %>% mutate(Station = str_remove(Station, "\\.")) %>% filter(grepl("LWR", Station)) %>% group_by(Measure) %>% mutate(Measure = paste0("Annual_", Measure)) %>% summarise(meanValue = round(mean(Value, na.rm = T),2)) %>% spread(Measure, meanValue) %>% mutate(Station = "Mean"))) %>% 
  rename("Sedimentation Rate (g/month)" = Quarterly_RateMean, "Sedimentation Rate (g/month) " = Annual_RateMean, "% Organic" = Quarterly_PctOrganicMean, "% Organic " = Annual_PctOrganicMean, "Organic Weight (g)" = Quarterly_OrgWtMean, "Organic Weight (g) " = Annual_OrgWtMean) %>% ungroup() %>% gt() %>% tab_spanner(label = "Quarterly", columns = c(2, 3, 4)) %>% tab_spanner(label = "Annual", columns = c(5, 6, 7)) %>%  tab_style(style = cell_text(weight = "bold"), locations = cells_body(rows = c(4))) %>% tab_style(style = cell_borders(sides = c("bottom"), style = "hidden"), locations = cells_body(rows = c(1, 2, 4))) %>% tab_options(heading.title.font.size = "12px", heading.border.bottom.style = "solid", heading.border.bottom.color = "black", table.border.top.style = "hidden", table.font.names = c("Times New Roman"), table.font.size = "12px") %>% cols_align(align = "center") %>% tab_header(title = "Restoration reefs") %>% opt_align_table_header(align = "left") %>% gt_add_divider(columns = c(1, 2, 3, 4, 5, 6), sides = "right", color = "black") %>% tab_style(style = cell_borders(sides = "top", color = "black"), locations = cells_body(rows = c(1, 4))) %>% tab_style(style = cell_borders(sides = "left", color = "black", weight = px(2.5)), locations = cells_body(columns = c(2, 5))) %>% tab_style(style = cell_borders(sides = "left", color = "black", weight = px(2.5)), locations = cells_column_spanners(spanners = c("Quarterly", "Annual"))) %>% tab_style(style = cell_borders(sides = "left", color = "black", weight = px(2.5)), locations = cells_column_labels(columns = c(2, 5)))
#
North_sum_tab <- rbind(
  #Quarterly
  left_join(Reef_type_summ %>% mutate(Station = str_remove(Station, "\\.")) %>% filter(Position == "North") %>% group_by(Station, Measure) %>% mutate(Measure = paste0("Quarterly_", Measure)) %>% summarise(meanValue = round(mean(Value, na.rm = T),2)) %>% spread(Measure, meanValue) %>% dplyr::select(Station, contains("RateMean"), contains("PctOrganicMean"), contains("OrgWtMean")) %>% arrange(factor(Station, levels = c("LWR4", "LWL1", "LWL2"))),
            #Annual 
            Reef_type_annual %>% mutate(Station = str_remove(Station, "\\.")) %>% filter(Position == "North") %>% group_by(Station, Measure) %>% mutate(Measure = paste0("Annual_", Measure)) %>% summarise(meanValue = round(mean(Value, na.rm = T),2)) %>% spread(Measure, meanValue) %>% dplyr::select(Station, contains("RateMean"), contains("PctOrganicMean"), contains("OrgWtMean"))), 
  #Quarterly 
  left_join(Reef_type_summ %>% mutate(Station = str_remove(Station, "\\.")) %>% filter(Position == "North") %>% group_by(Measure) %>% mutate(Measure = paste0("Quarterly_", Measure)) %>% summarise(meanValue = round(mean(Value, na.rm = T),2)) %>% spread(Measure, meanValue) %>% mutate(Station = "Mean"),
            Reef_type_annual %>% mutate(Station = str_remove(Station, "\\.")) %>% filter(Position == "North") %>% group_by(Measure) %>% mutate(Measure = paste0("Annual_", Measure)) %>% summarise(meanValue = round(mean(Value, na.rm = T),2)) %>% spread(Measure, meanValue) %>% mutate(Station = "Mean"))) %>% 
  rename("Sedimentation Rate (g/month)" = Quarterly_RateMean, "Sedimentation Rate (g/month) " = Annual_RateMean, "% Organic" = Quarterly_PctOrganicMean, "% Organic " = Annual_PctOrganicMean, "Organic Weight (g)" = Quarterly_OrgWtMean, "Organic Weight (g) " = Annual_OrgWtMean) %>% ungroup() %>% gt() %>% tab_spanner(label = "Quarterly", columns = c(2, 3, 4)) %>% tab_spanner(label = "Annual", columns = c(5, 6, 7)) %>%  tab_style(style = cell_text(weight = "bold"), locations = cells_body(rows = c(4))) %>% tab_style(style = cell_borders(sides = c("bottom"), style = "hidden"), locations = cells_body(rows = c(1, 2, 4))) %>% tab_options(heading.title.font.size = "12px", heading.border.bottom.style = "solid", heading.border.bottom.color = "black", table.border.top.style = "hidden", table.font.names = c("Times New Roman"), table.font.size = "12px") %>% cols_align(align = "center") %>% tab_header(title = "North reefs") %>% opt_align_table_header(align = "left") %>% gt_add_divider(columns = c(1, 2, 3, 4, 5, 6), sides = "right", color = "black") %>% tab_style(style = cell_borders(sides = "top", color = "black"), locations = cells_body(rows = c(1, 4))) %>% tab_style(style = cell_borders(sides = "left", color = "black", weight = px(2.5)), locations = cells_body(columns = c(2, 5))) %>% tab_style(style = cell_borders(sides = "left", color = "black", weight = px(2.5)), locations = cells_column_spanners(spanners = c("Quarterly", "Annual"))) %>% tab_style(style = cell_borders(sides = "left", color = "black", weight = px(2.5)), locations = cells_column_labels(columns = c(2, 5)))
#
South_sum_tab <- rbind(
  #Quarterly
  left_join(Reef_type_summ %>% mutate(Station = str_remove(Station, "\\.")) %>% filter(Position == "South") %>% group_by(Station, Measure) %>% mutate(Measure = paste0("Quarterly_", Measure)) %>% summarise(meanValue = round(mean(Value, na.rm = T),2)) %>% spread(Measure, meanValue) %>% dplyr::select(Station, contains("RateMean"), contains("PctOrganicMean"), contains("OrgWtMean")) %>% arrange(factor(Station, levels = c("LWR2", "LWR3", "LWL3"))),
            #Annual 
            Reef_type_annual %>% mutate(Station = str_remove(Station, "\\.")) %>% filter(Position == "South") %>% group_by(Station, Measure) %>% mutate(Measure = paste0("Annual_", Measure)) %>% summarise(meanValue = round(mean(Value, na.rm = T),2)) %>% spread(Measure, meanValue) %>% dplyr::select(Station, contains("RateMean"), contains("PctOrganicMean"), contains("OrgWtMean"))), 
  #Quarterly 
  left_join(Reef_type_summ %>% mutate(Station = str_remove(Station, "\\.")) %>% filter(Position == "South") %>% group_by(Measure) %>% mutate(Measure = paste0("Quarterly_", Measure)) %>% summarise(meanValue = round(mean(Value, na.rm = T),2)) %>% spread(Measure, meanValue) %>% mutate(Station = "Mean"),
            Reef_type_annual %>% mutate(Station = str_remove(Station, "\\.")) %>% filter(Position == "South") %>% group_by(Measure) %>% mutate(Measure = paste0("Annual_", Measure)) %>% summarise(meanValue = round(mean(Value, na.rm = T),2)) %>% spread(Measure, meanValue) %>% mutate(Station = "Mean"))) %>% 
  rename("Sedimentation Rate (g/month)" = Quarterly_RateMean, "Sedimentation Rate (g/month) " = Annual_RateMean, "% Organic" = Quarterly_PctOrganicMean, "% Organic " = Annual_PctOrganicMean, "Organic Weight (g)" = Quarterly_OrgWtMean, "Organic Weight (g) " = Annual_OrgWtMean) %>% ungroup() %>% gt() %>% tab_spanner(label = "Quarterly", columns = c(2, 3, 4)) %>% tab_spanner(label = "Annual", columns = c(5, 6, 7)) %>%  tab_style(style = cell_text(weight = "bold"), locations = cells_body(rows = c(4))) %>% tab_style(style = cell_borders(sides = c("bottom"), style = "hidden"), locations = cells_body(rows = c(1, 2, 4))) %>% tab_options(heading.title.font.size = "12px", heading.border.bottom.style = "solid", heading.border.bottom.color = "black", table.border.top.style = "hidden", table.font.names = c("Times New Roman"), table.font.size = "12px") %>% cols_align(align = "center") %>% tab_header(title = "South reefs") %>% opt_align_table_header(align = "left") %>% gt_add_divider(columns = c(1, 2, 3, 4, 5, 6), sides = "right", color = "black") %>% tab_style(style = cell_borders(sides = "top", color = "black"), locations = cells_body(rows = c(1, 4))) %>% tab_style(style = cell_borders(sides = "left", color = "black", weight = px(2.5)), locations = cells_body(columns = c(2, 5))) %>% tab_style(style = cell_borders(sides = "left", color = "black", weight = px(2.5)), locations = cells_column_spanners(spanners = c("Quarterly", "Annual"))) %>% tab_style(style = cell_borders(sides = "left", color = "black", weight = px(2.5)), locations = cells_column_labels(columns = c(2, 5)))
```

```{r Summary data: ranges, include = FALSE}
#
###Summary data:

#PBC summary
PBC_Counts_temp <- Counts_PBC %>% filter(AnalysisDate > as.yearmon(Start_date) & AnalysisDate < as.yearmon(End_date %m+% months(1))) %>% dplyr::select(contains("LiveMean")) %>% mutate(across(where(is.numeric), ~ifelse(. <= 0 | is.na(.), NA, .))) %>% gather(Station, Value) %>% arrange(desc(Value)) %>% drop_na()
PBC_DR_temp <-  Counts_PBC %>% filter(AnalysisDate > as.yearmon(Start_date) & AnalysisDate < as.yearmon(End_date %m+% months(1))) %>% dplyr::select(contains("DeadRatioMean")) %>% mutate(across(where(is.numeric), ~ifelse(. <= 0 | is.na(.), NA, .))) %>% gather(Station, Value) %>% arrange(desc(Value)) %>% drop_na()
PBC_SH_temp <- SH_PBC %>% filter(AnalysisDate > as.yearmon(Start_date) & AnalysisDate < as.yearmon(End_date %m+% months(1))) %>% dplyr::select(contains("Mean")) %>% mutate(across(where(is.numeric), ~ifelse(. < 0 | is.na(.), NA, .))) %>% gather(Station, Value) %>% arrange(desc(Value)) %>% drop_na()
PBC_Rcrt_temp <- Rcrt_PBC %>% dplyr::select(contains("Mean")) %>% gather(Station, Value) %>% arrange(desc(Value)) %>% drop_na() %>% dplyr::select(Value) %>% distinct()
PBC_Sal_temp <- WQ_Sal_PBC %>% dplyr::select(contains("Sal")) %>% gather(Station, Value) %>% arrange(desc(Value)) %>% drop_na() %>% dplyr::select(Value) %>% distinct()

#
```

## Report summary
This data summary was compiled on `r format(Sys.Date(), "%d %B %Y")` and summarizes data for the **PBC** quarterly report from `r format(Start_date, "%B %Y")` through `r format(End_date, "%B %Y")`.\

<h1>`r paste("PBC Quarterly Report")`</h1>
Minimum and maximum values observed during the quarter and data ordered by increasing values.
<h3> Station common names</h3>
Natural reef station 1 (LWL1)  -- Audubon Island\
Natural reef station 2 (LWL2)  -- John’s Island\
Natural reef station 3 (LWL3)  -- Bird Island\
Restored reef station 2 (LWR2) -- Grassy Flats\
Restored reef station 3 (LWR3) -- Snook Island\
Restored reef station 4 (LWR4) -- Tarpon Cove\
\
\
<h3> `r paste("Survey summary")` </h3>
`r PBC_count %>% tab_caption(caption = "Monthly PBC live oyster counts")`
Live Counts range: `r PBC_Counts_temp %>% slice(n()) %>% pull(Value)` - `r PBC_Counts_temp %>% slice(1) %>% pull(Value)` \
Live counts Mid-range: `r PBC_Counts_temp %>% slice(n()-1) %>% pull(Value)` - `r PBC_Counts_temp %>% slice(2) %>% pull(Value)`
`r PBC_count_change`\
`r PBC_dead %>% tab_caption(caption = "Monthly PBC dead ratios")`
\
DeadRatio range: `r PBC_DR_temp %>% slice(n()) %>% pull(Value)` - `r PBC_DR_temp %>% slice(1) %>% pull(Value)`\
DeadRatio Mid-range: `r PBC_DR_temp %>% slice(n()-1) %>% pull(Value)` - `r PBC_DR_temp %>% slice(2) %>% pull(Value)` 
`r PBC_dead_change`\
`r PBC_SH %>% tab_caption(caption = "Monthly PBC shell heights")`
Shell height range: `r PBC_SH_temp %>% slice(n()) %>% pull(Value)` - `r PBC_SH_temp %>% slice(1) %>% pull(Value)` \
Shell height Mid-range: `r PBC_SH_temp %>% slice(n()-1) %>% pull(Value)` - `r PBC_SH_temp %>% slice(2) %>% pull(Value)` 
\
Summary by reef type: 
`r Counts_PBC %>% gather(Info, Value, -AnalysisDate) %>% mutate(Value = na_if(Value, -999), Site = substr(Info, 1, 4), Measure = substr(Info, 7, n())) %>% group_by(Site, Measure) %>% summarise(Mean = round(mean(Value, na.rm = T),3)) %>% spread(Measure, Mean) %>% dplyr::select(Site, LiveMean, DeadRatioMean) %>% gt()`
`r SH_PBC %>% gather(Info, Value, -AnalysisDate) %>% mutate(Value = na_if(Value, -999), Site = substr(Info, 1, 4), SH = substr(Info, 7, n())) %>% group_by(Site, SH) %>% summarise(Mean = round(mean(Value, na.rm = T),3)) %>% spread(SH, Mean) %>% gt()`
Survey summary table:
`r PBC_survey_sum %>% tab_caption(caption = "Survey summary by station")`
\
\
\
\
<h3> `r paste("Repro summary")` </h3>
`r if(!is.null(PBC_repro)  & !is.character(PBC_repro)){PBC_repro %>% tab_caption(caption = "Monthly PBC reproductive stages")} else {paste0("Repro data is not available for the quarter specified.")}`
\
\
\
\
<h3> `r paste("Dermo summary")` </h3>
`r Dermo_PBC %>% dplyr::select(RetDate, contains("Mean")) %>% gather(Station, Mean, -RetDate) %>% mutate(Station = substr(Station, 1, 5)) %>% filter(is.na(Mean)) %>% dplyr::select(-Mean) %>% group_by(Station) %>% gt() %>% tab_caption(caption = "Missing samples")`
`r PBC_dermo %>% tab_caption(caption = "Monthly PBC dermo intensity and prevalence")`
Intensity range: `r Dermo_PBC %>% dplyr::select(contains("Mean")) %>% unlist() %>% min(na.rm = T)` - `r Dermo_PBC %>% dplyr::select(contains("Mean")) %>% unlist() %>% max(na.rm = T)`\
`r paste("Intensity categories: 0-Uninfected; 0.5-Very light;  1-Light;  2-Light to moderate;  3-Moderate;  4-Moderately heavy,  5-Heavy")`\
Prevalence range: `r Dermo_PBC %>% dplyr::select(contains("Pct")) %>% unlist() %>% min(na.rm = T)` - `r Dermo_PBC %>% dplyr::select(contains("Pct")) %>% unlist() %>% max(na.rm = T)`\
Summary by reef type:
`r Dermo_PBC %>% gather(Info, Value, -RetDate) %>% mutate(Value = na_if(Value, -999), Site = substr(Info, 1, 4), Measure = substr(Info, 7, n())) %>% group_by(Site, Measure) %>% summarise(meanValue = round(mean(Value, na.rm = T),3)) %>% spread(Measure, meanValue) %>% rename("Intensity" = Mean) %>% gt()`
\
\
\
\
<h3> `r paste("Recruitment summary")` </h3>
`r Rcrt_PBC %>% gather(Station, Mean, -RetDate) %>% mutate(Station = substr(Station, 1, 5)) %>% filter(is.na(Mean)) %>% dplyr::select(-Mean) %>% group_by(Station) %>%  gt() %>% tab_caption(caption = "Missing samples")`
`r PBC_rcrt %>% tab_caption(caption = "Monthly PBC recruitment rates")`
Recruitment range: `r PBC_Rcrt_temp %>% slice(n()) %>% pull(Value)` - `r PBC_Rcrt_temp %>% slice(1) %>% pull(Value)`\
Recruitment Mid-range: `r PBC_Rcrt_temp %>% slice(n()-1) %>% pull(Value)` - `r PBC_Rcrt_temp %>% slice(2) %>% pull(Value)`
`r Rcrt_PBC %>% pivot_longer(names_to = "Station", cols = -RetDate) %>% mutate(Station = sub("_Mean", "", Station)) %>% filter(value == 0) %>% arrange(RetDate) %>% gt(groupname_col = "RetDate") %>% tab_caption(caption = "No recruitment")`
Summary by reef type:
`r Rcrt_PBC %>% gather(Info, Value, -RetDate) %>% mutate(Value = na_if(Value, -999), Site = substr(Info, 1, 4), Measure = substr(Info, 7, n())) %>% group_by(Site, Measure) %>% summarise(meanValue = round(mean(Value, na.rm = T),3)) %>% spread(Measure, meanValue) %>% gt()`
\
\
\
\
<h3> `r paste("Sediment summary")` </h3>
`r Rate_sta %>% gather(Station, RateMean, -AnalysisDate) %>% mutate(Station = substr(Station, 1, 5)) %>% filter(is.na(RateMean)) %>% dplyr::select(-RateMean) %>% group_by(Station) %>% gt() %>% tab_caption(caption = "Missing samples")`
`r Sta_Rates %>% tab_caption(caption = "Monthly sedimentation rate by station")`
*Sedimentation rate range: Overall-*`r Rate_sta %>% dplyr::select(contains("Mean")) %>% unlist() %>% setdiff(., NA) %>% min(na.rm = T)` - `r Rate_sta %>% dplyr::select(contains("Mean")) %>% unlist()  %>% setdiff(., NA) %>% max(na.rm = T)`
-- -- --*by Site-* 
LWL- `r Rate_sta %>% dplyr::select(contains("LW.L")) %>% unlist() %>% setdiff(., NA) %>% min(na.rm = T)` - `r Rate_sta %>% dplyr::select(contains("Lw.L")) %>%  unlist() %>% setdiff(., NA) %>% max(na.rm = T)`
-- -- LWR-  `r Rate_sta %>% dplyr::select(contains("LW.R")) %>% unlist() %>% setdiff(., NA) %>% min(na.rm = T)` - `r Rate_sta %>% dplyr::select(contains("Lw.R")) %>% unlist() %>% setdiff(., NA) %>% max(na.rm = T)`\
*Sedimentation rate mean: Overall-*`r Rate_sta %>% dplyr::select(contains("Mean")) %>% unlist() %>% setdiff(., NA)%>% mean(na.rm = T) %>% round(2)`\
*by Site- *`r Rate_sta %>% dplyr::select(contains("Mean")) %>% gather(Info, Value) %>% mutate(Site = substr(Info,  1, 4)) %>% group_by(Site) %>% summarise(mean = round(mean(Value, na.rm = T), 2)) %>% gt()`
\
\
`r Sta_Pcts %>% tab_caption(caption = "Monthly sedimentation percent organic by station")`
*Percent organic range: Overall-*`r Pct_sta %>% dplyr::select(contains("Mean")) %>% unlist() %>% setdiff(., NA) %>% min(na.rm = T)` - `r Pct_sta %>% dplyr::select(contains("Mean")) %>% unlist()  %>% setdiff(., NA) %>% max(na.rm = T)`
-- -- --*by Site-* 
LWL- `r Pct_sta %>% dplyr::select(contains("LW.L")) %>% unlist()  %>% setdiff(., NA) %>% min(na.rm = T)` - `r Pct_sta %>% dplyr::select(contains("Lw.L")) %>% unlist() %>% setdiff(., NA) %>% max(na.rm = T)`
-- -- LWR-  `r Pct_sta %>% dplyr::select(contains("LW.R")) %>% unlist() %>% setdiff(., NA) %>% min(na.rm = T)` - `r Pct_sta %>% dplyr::select(contains("Lw.R")) %>% unlist()  %>% setdiff(., NA) %>% max(na.rm = T)`\
*Percent organic mean: Overall-*`r Pct_sta %>% dplyr::select(contains("Mean")) %>% unlist() %>% setdiff(., NA) %>% mean(na.rm = T) %>% round(2)`\
*by Site- *`r Pct_sta %>% dplyr::select(contains("Mean")) %>% gather(Info, Value)  %>% mutate(Site = substr(Info,  1, 4)) %>% group_by(Site) %>% summarise(mean = round(mean(Value, na.rm = T), 2)) %>% gt()`
\
\
`r Sta_Wts %>% tab_caption(caption = "Monthly sedimentation organic weights by station")`
*Organic weight range: Overall-*`r Wt_sta %>% dplyr::select(contains("Mean")) %>% unlist() %>% setdiff(., NA) %>% min(na.rm = T)` - `r Wt_sta %>% dplyr::select(contains("Mean")) %>% unlist()  %>% setdiff(., NA) %>% max(na.rm = T)`
-- -- --*by Site-* 
LWL- `r Wt_sta %>% dplyr::select(contains("LW.L")) %>% unlist()  %>% setdiff(., NA) %>% min(na.rm = T)` - `r Wt_sta %>% dplyr::select(contains("Lw.L")) %>% unlist() %>% setdiff(., NA) %>% max(na.rm = T)`
-- -- LWR-  `r Wt_sta %>% dplyr::select(contains("LW.R")) %>% unlist() %>% setdiff(., NA) %>% min(na.rm = T)` - `r Wt_sta %>% dplyr::select(contains("Lw.R")) %>% unlist()  %>% setdiff(., NA) %>% max(na.rm = T)`\
*Organic weight mean: Overall-*`r Wt_sta %>% dplyr::select(contains("Mean")) %>% unlist()  %>% setdiff(., NA) %>% mean(na.rm = T) %>% round(2)`\
*by Site- *`r Wt_sta %>% dplyr::select(contains("Mean")) %>% gather(Info, Value)  %>% mutate(Site = substr(Info,  1, 4)) %>% group_by(Site) %>% summarise(mean = round(mean(Value, na.rm = T), 2)) %>% gt()`
\
\
\
`r Pos_Rates %>% tab_caption(caption = "Monthly sedimentation rate by North v South stations")`
*Sedimentation rate mean:* (North, South) `r Sedi_pos %>% subset(AnalysisDate >= Start_date & AnalysisDate < End_date) %>% dplyr::select(contains("RateMean")) %>% drop_na() %>% colMeans() %>% round(2)`
`r Pos_Pcts %>% tab_caption(caption = "Monthly sedimentation percent organic by North v South stations")`
*Percent organic mean:* (North, South) `r Sedi_pos %>% subset(AnalysisDate >= Start_date & AnalysisDate < End_date) %>% dplyr::select(contains("PctOrganicMean")) %>% drop_na() %>% colMeans() %>% round(2)`
`r Pos_Wts %>% tab_caption(caption = "Monthly sedimentation organic weights by North v South stations")`
*Organic weight mean:* (North, South) `r Sedi_pos %>% subset(AnalysisDate >= Start_date & AnalysisDate < End_date) %>% dplyr::select(contains("OrgWtMean")) %>% drop_na() %>% colMeans() %>% round(2)`
Sediment trap summary tables:
`r LWL_sum_tab %>% tab_caption(caption = paste("Mean quarterly sedimentation rate of natural reef stations. Annual data includes samples from", End_date %m-% months(11) %>% format("%B %Y"), "through", End_date %>% format("%B %Y"), ".", sep = ""))`
`r LWR_sum_tab %>% tab_caption(caption = paste("Mean quarterly sedimentation rate of restoration reef stations. Annual data includes samples from", End_date %m-% months(11) %>% format("%B %Y"), "through", End_date %>% format("%B %Y"), ".", sep = ""))`
\
\
`r North_sum_tab %>% tab_caption(caption = paste("Mean quarterly sedimentation rate on reefs at stations North of C-51. Annual data includes samples from", End_date %m-% months(11) %>% format("%B %Y"), "through", End_date %>% format("%B %Y"), ".", sep = ""))`
`r South_sum_tab %>% tab_caption(caption = paste("Mean quarterly sedimentation rate on reefs at stations South of C-51. Annual data includes samples from ", End_date %m-% months(11) %>% format("%B %Y"), " through ", End_date %>% format("%B %Y"), ".", sep = ""))`
\
\
\
\
<h3> `r paste("Water Quality summary")` </h3>
Salintiy and Secchi measurements observed during the quarter.
`r PBC_Sal %>% tab_caption(caption = "Monthly PBC salinity measurements")`
Salinity range: `r PBC_Sal_temp %>% slice(n()) %>% pull(Value)` - `r PBC_Sal_temp %>% slice(1) %>% pull(Value)`\
Salinity Mid-range: `r PBC_Sal_temp %>% slice(n()-1) %>% pull(Value)` - `r PBC_Sal_temp %>% slice(2) %>% pull(Value)`\
`r PBC_Sec %>% tab_caption(caption = "Monthly PBC secchi measurements")`
Secchi range: `r WQ_Sec_PBC %>% dplyr::select(contains("SP")) %>% unlist() %>% min(na.rm = T)` - `r WQ_Sec_PBC %>% dplyr::select(contains("SP")) %>% unlist() %>% max(na.rm = T)`\

\