---
title: "Supplemental Survey Statistics Summary"
output: html_document
date: "2025-07-29"
---

```{r, echo = FALSE, warning = FALSE, message = FALSE}
### VARIABLE SET ###
# Set your variables here


### PACKAGE LOAD ###
# Load necessary R packages
library(tidyverse)
library(lubridate)
library(openxlsx)
library(dplyr)
library(knitr)

knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

### DATA DOWNLOAD ###
setwd("C:/Users/Matthew.Davis/OneDrive - Florida Fish and Wildlife Conservation/Documents/Database/Repos/Oyster-Reports/DMFM/ABFW")

Location_data <- read.xlsx("Intertidal_Supplemental_Survey_2025.xlsx", "Location")

Trip_data <- read.xlsx("Intertidal_Supplemental_Survey_2025.xlsx", "Trip", detectDates = TRUE)

Sample_data <- read.xlsx("Intertidal_Supplemental_Survey_2025.xlsx", "Sample") %>%
  mutate(NumQuads = as.numeric(NumQuads)) %>%
  left_join(Location_data, Sample_data, by = c("Station"))

Quadrat_data <- read.xlsx("Intertidal_Supplemental_Survey_2025.xlsx", "Quadrat", cols = 1:8) %>%
  left_join(Location_data, Quadrat_data, by = c("Station"))

```

```{r Simple stats}
TotStationsVisited <- nrow(Sample_data) # All stations visited
TotStationsSampled <- sum(Sample_data$NumQuads > 0) # Stations where quadrats were collected
PercentSampled <- round((TotStationsSampled/TotStationsVisited) * 100, digits = 1)
StationsWithOys <- Quadrat_data %>% #How many stations had ANY oysters at all
  filter(SpatPA == 'Present' | SublegalPA == 'Present' | NumLegal > 0) %>%
  distinct(Station)
PercentStationsWithOys <- round(nrow(StationsWithOys) / TotStationsSampled * 100, digits = 1)
StationsWithLegals <- Quadrat_data %>% #How many stations had legal oysters present
  filter(NumLegal > 0) %>%
  distinct(Station)
PercentStationsWithLegals <- round(nrow(StationsWithLegals) / TotStationsSampled * 100, digits = 1)

QuadsWithOys <- Quadrat_data %>% # How many quadrats had ANY oysters at all
  filter(SpatPA == 'Present' | SublegalPA == 'Present' | NumLegal > 0)
PercentWithOys <- round(nrow(QuadsWithOys) / nrow(Quadrat_data) * 100, digits = 1)

QuadsWithSpat <- Quadrat_data %>% # How may quadrats had spat present
  filter(SpatPA == 'Present')
PercentWithSpat <- round(nrow(QuadsWithSpat) / nrow(Quadrat_data) * 100, digits = 1)

QuadsWithSublegal <- Quadrat_data %>% # How may quadrats had sublegals present
  filter(SublegalPA == 'Present')
PercentWithSublegal <- round(nrow(QuadsWithSublegal) / nrow(Quadrat_data) * 100, digits = 1)

QuadsWithLegal <- Quadrat_data %>% # How may quadrats had legal oysters present
  filter(NumLegal > 0)
PercentWithLegal <- round(nrow(QuadsWithLegal) / nrow(Quadrat_data) * 100, digits = 1)
# Max number and most frequent number of legals found in a quadrat
LegalMaxMode <- QuadsWithLegal %>%
  summarise(
    MaxValue = max(NumLegal, na.rm = TRUE), # Max number found
    CountMax = sum(NumLegal == max(NumLegal, na.rm = TRUE), na.rm = TRUE), # how many times the max was found
    Mode = {
      t <- table(NumLegal)
      as.numeric(names(t[t == max(t)][1]))  # most frequent value
    },
    CountMode = {
      t <- table(NumLegal)
      max(t)  # how many times mode occurred
    }
  )

QuadsWithDrills <- Quadrat_data %>%
  filter(NumDrills > 0)
PercentWithDrills <- round(nrow(QuadsWithDrills) / nrow(Quadrat_data) * 100, digits = 1)
# Max number and most frequent number of legals found in a quadrat
DrillMaxMode <- QuadsWithDrills %>%
  summarise(
    MaxValue = max(NumDrills, na.rm = TRUE), # Max number found
    CountMax = sum(NumDrills == max(NumDrills, na.rm = TRUE), na.rm = TRUE), # how many times the max was found
    Mode = {
      t <- table(NumDrills)
      as.numeric(names(t[t == max(t)][1]))  # most frequent value
    },
    CountMode = {
      t <- table(NumDrills)
      max(t)  # how many times mode occurred
    }
  )

# Legal Oyster Densities
# RAW
Quadrat_data1 <- Quadrat_data %>%
  mutate(
    LegalDensity = NumLegal * 4,
    BagsPerAcre = (LegalDensity * 4047) / 225
  )

DensitiesALL <- Quadrat_data1 %>%
  summarise(NQuadrats = n(), # number of samples (Quadrats)
            LegalDensityMean = round(mean(LegalDensity, na.rm = TRUE), digits = 1),
            LegalDensitySD = round(sd(LegalDensity, na.rm = TRUE), digits = 1),
            BagsPerAcreDensityMean = round(mean(BagsPerAcre, na.rm = TRUE), digits = 1),
            BagsPerAcreDensitySD = round(sd(BagsPerAcre, na.rm = TRUE), digits = 1)
  )

DensitiesCounty <- Quadrat_data1 %>%
  group_by(County) %>%
  summarise(NQuadrats = n(), # number of samples (Quadrats)
            LegalDensityMean = round(mean(LegalDensity, na.rm = TRUE), digits = 1),
            LegalDensitySD = round(sd(LegalDensity, na.rm = TRUE), digits = 1),
            BagsPerAcreDensityMean = round(mean(BagsPerAcre, na.rm = TRUE), digits = 1),
            BagsPerAcreDensitySD = round(sd(BagsPerAcre, na.rm = TRUE), digits = 1)
  ) 

custom_orderSHA <- c("1552", "1542", "1611")
DensitiesSHA <- Quadrat_data1 %>%
  group_by(SHA) %>%
  summarise(NQuadrats = n(), # number of samples (Quadrats)
            LegalDensityMean = round(mean(LegalDensity, na.rm = TRUE), digits = 1),
            LegalDensitySD = round(sd(LegalDensity, na.rm = TRUE), digits = 1),
            BagsPerAcreDensityMean = round(mean(BagsPerAcre, na.rm = TRUE), digits = 1),
            BagsPerAcreDensitySD = round(sd(BagsPerAcre, na.rm = TRUE), digits = 1)
  ) %>%
  mutate(SHA = factor(SHA, levels = custom_orderSHA)) %>%
  arrange(SHA)

custom_orderSubset <- c("ILW", "ILC", "ILE", "SVS")
DensitiesSubset <- Quadrat_data1 %>%
  group_by(Subset) %>%
  summarise(NQuadrats = n(), # number of samples (Quadrats)
            LegalDensityMean = round(mean(LegalDensity, na.rm = TRUE), digits = 1),
            LegalDensitySD = round(sd(LegalDensity, na.rm = TRUE), digits = 1),
            BagsPerAcreDensityMean = round(mean(BagsPerAcre, na.rm = TRUE), digits = 1),
            BagsPerAcreDensitySD = round(sd(BagsPerAcre, na.rm = TRUE), digits = 1)
  ) %>%
  mutate(Subset = factor(Subset, levels = custom_orderSubset)) %>%
  arrange(Subset)

DensitiesStation <- Quadrat_data1 %>%
  group_by(Station) %>%
  summarise(NQuadrats = n(), # number of samples (Quadrats)
            LegalDensityMean = round(mean(LegalDensity, na.rm = TRUE), digits = 1),
            LegalDensitySD = round(sd(LegalDensity, na.rm = TRUE), digits = 1),
            BagsPerAcreDensityMean = round(mean(BagsPerAcre, na.rm = TRUE), digits = 1),
            BagsPerAcreDensitySD = round(sd(BagsPerAcre, na.rm = TRUE), digits = 1)
  ) %>%
  arrange(desc(BagsPerAcreDensityMean)) %>%
  filter(LegalDensityMean > 0) # only include stations that had legal oysters present

```


Intertidal Supplemental Survey Summary <br>
Trips were carried out on the following dates: <br>
`r unique(Trip_data$Date)`

A total of `r TotStationsVisited` stations were visited <br>
Of the stations visited: <br> 
`r TotStationsSampled` (`r PercentSampled`%) stations were found to have suitable substrate for sampling. <br>

Of the `r TotStationsSampled` Stations that were sampled: <br>
`r nrow(StationsWithOys)` (`r PercentStationsWithOys`%) contained at least a single oyster of any size  <br>
`r nrow(StationsWithLegals)` (`r PercentStationsWithLegals`%) contained legal (over 74 mm Shell Height) oysters  <br>

A total of `r nrow(Quadrat_data)` quadrats were collected and processed. <br>
Of the quadrats collected and processed:  <br>
`r nrow(QuadsWithOys)` (`r PercentWithOys`%) contained at least a single oyster of any size  <br>
`r nrow(QuadsWithSpat)` (`r PercentWithSpat`%) contained spat (1 - 30 mm Shell Height)  <br>
`r nrow(QuadsWithSublegal)` (`r PercentWithSublegal`%) contained sublegal (31 - 74 mm Shell Height) oysters  <br>
`r nrow(QuadsWithLegal)` (`r PercentWithLegal`%) contained legal (over 74 mm Shell Height) oysters  <br>
`r nrow(QuadsWithDrills)` (`r PercentWithDrills`%) contained oyster drill predators  <br>

The maximum number of legal sized oysters encountered in a quadrat was `r LegalMaxMode$MaxValue`, which was found in `r LegalMaxMode$CountMax` quadrat(s)<br>
The most common number of legal sized oysters encountered in a quadrat was `r LegalMaxMode$Mode`, which was found in `r LegalMaxMode$CountMode` quadrat(s)<br>

The maximum number of oyster drills encountered in a quadrat was `r DrillMaxMode$MaxValue`, which was found in `r DrillMaxMode$CountMax` quadrat(s)<br>
The most common number of oyster drills encountered in a quadrat was `r DrillMaxMode$Mode`, which was found in `r DrillMaxMode$CountMode` quadrat(s)<br>

`r kable(DensitiesALL, caption = "Densities of all sampled areas combined.", col.names = c("Quadrats", "Mean Legal Oysters<br>per square meter", "Standard<br>deviation", "Bags per Acre", "Standard<br>deviation"), align = "c")`

`r kable(DensitiesCounty, caption = "Densities of all sampled areas divided by county line at longitude -85.221667.", col.names = c("County", "Quadrats", "Mean Legal Oysters<br>per square meter", "Standard<br>deviation", "Bags per Acre", "Standard<br>deviation"), align = "c")`

`r kable(DensitiesSHA, caption = "Densities of all sampled areas divided by FDACS Shellfish Harvest Areas (SHA). <br>Points west of longitude -85.23500 correspond to 1552, Conditionally Approved, Indian Lagoon Winter B. <br>Points between longitude -85.23500 and -85.221667 correspond to 1542, Conditionally Approved, Indian Lagoon Winter A. <br>Points east of longitude -85.221667 correspond to 1611, Approved, Apalachicola Bay Winter A.", col.names = c("SHA", "Quadrats", "Mean Legal Oysters<br>per square meter", "Standard<br>deviation", "Bags per Acre", "Standard<br>deviation"), align = "c")`

`r kable(DensitiesSubset, caption = "Densities of all sampled areas divided by SHA subsets. <br>Indian Lagoon West (ILW) corresponds to SHA 1552 as defined above. <br>Indian Lagoon Central (ILC) corresponds to SHA 1542 as defined above. <br>Indian Lagoon East (ILE) corresponds to points between longitude -85.221667 and -85.20000. <br>St. Vincent Sound (SVS)  correspond to points east of longitude -85.20000.", col.names = c("Subset", "Quadrats", "Mean Legal Oysters<br>per square meter", "Standard<br>deviation", "Bags per Acre", "Standard<br>deviation"), align = "c")`

`r kable(DensitiesStation, caption = "Densities of all sampled stations listed indivdually and sorted from highest density to lowest density.", col.names = c("Station", "Quadrats", "Mean Legal Oysters<br>per square meter", "Standard<br>deviation", "Bags per Acre", "Standard<br>deviation"), align = "c")`